### 2020-03-29 paper/main.tex
add paper/main.tex and paper/references.bib

% ToDo:
% Abstract
% Tabellen
% Dataset wo auch immer (ohne Stimuli) hochladen

% For more detailed article preparation guidelines, please see:
% http://f1000research.com/author-guidelines
\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
%% Default: numerical citations
\usepackage[numbers]{natbib}

%% Uncomment this lines for superscript citations instead
% \usepackage[super]{natbib}

%% Uncomment these lines for author-year citations instead
% \usepackage[round]{natbib}
% \let\cite\citep

\begin{document}

\title{\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description}
\titlenote{whatever titlenote here}

% provide full affiliation information (including full institutional address, ZIP code and e-mail address) for all authors, and identify who is/are the corresponding author(s).
% EMAIL hier noch "kanonisch" unterbringen
% Madeburg habe ich nicht mit reingenommen, obwohl MD/Sachsen-Anhalt unten wg. Stipendium unter Funding kommt.
\author[1, 2]{Christian~O.~Häusler}
\author[1, 2]{Michael Hanke}

\affil[1]{Institute of Neuroscience and Medicine, Brain \& Behaviour (INM-7), Research Centre Jülich, Jülich, Germany}
\affil[2]{Institute of Systems Neuroscience, Medical Faculty, Heinrich Heine University, Düsseldorf, Germany}

\maketitle
\thispagestyle{fancy}
\begin{abstract}
% up to 300 words
Kommt ganz am Ende;
hier ggf. bereits Praat erwähnen;
im Gegensatz zu Sätzen und Phones haben Einzelworte zusätzliche Annos

\end{abstract}
\section*{Keywords}
% maximal 8
language, speech, annotation, fMRI, natural stimulation, narrative, studyforrest

\clearpage
\section*{Introduction}
% Links sind jetzt im laufenden Text; habs nach wie vor mit \href gemacht
% sieht bei längeren Links natürlich kacke aus

% largely adopted from haeusler2016annotation
% https://f1000research.com/articles/5-2273
% In Einleitung muss wohl noch etwas zu "reproducible research" und "datalad dataset" kommen
Cognitive neuroimaging research is moving towards studying brain behavior
under conditions of real-life(-like complexity). Motion pictures \citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not, lerner2011topographic} are increasingly utilized as so called naturalistic stimuli.

% new; not from haeusler2016annotation
Because naturalistic stimuli are multi-dimensional and their temporal structure
is (usually) unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. Nevertheless, theory-driven analyses like a general
linear model (GLM) are necessary to not just explain how but also when and why a
brain region is responding to a stimulus \citep{hamilton2018revolution}. Studies
using GLMs based on annotations of a stimulus' temporal structure have
elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.

% adapted from haeusler2016annotation
% nun ja, folgend nicht super korrekt: sentences sind nicht vollständige
% Sätze im linguistischen Sinne (Subjekt, Objekt, Prädikat), sondern auch
% Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh").
% Sätze im linguistischen Sinne sind in der Annotation durch "." oder "?" am
% Ende gekennzeichnet. Sollte aber so passen.
For this publication, we annotated the onsets and offsets, and content of
sentences, single words, and phonemes spoken in the movie Forrest Gump (R.
Zemeckis, Paramount Pictures, 1994) \citep{ForrestGumpMovie}. fMRI data of
participants watching the audio-visual movie \citep{hanke2016simultaneous} and
it's audio-description for visually impaired persons \citep{hanke2014audiomovie}
are the core data of the publicly available \textit{studyforrest} dataset
(\href{www.studyforrest.org}{studyforrest.org}). Additional fMRI data
\citep{sengupta2016extension} include retinotopic mappings and localization of
higher visual areas of the same participants.
% paper regarding mention musical not mentioned
% und damit zitiere ich mich als dortiger Coauthor nicht selbst. Skandal!

The current annotation facilitates modelling of hemodynamic brain responses
correlating with speech-related events in the movie and audio-description.
Further, it extends already available annotations of portrayed emotions
\citep{labs2015portrayed} and perceived emtions
\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}. All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional
confound measures describing key properties of major building blocks of the stimulus.

\section*{Materials and methods}
\subsection*{Stimulus}
% References sind vom Anno-Paper in die .bib-Datei übernommen worden; die
% “hardcoded” Zitationen sind aber noch im laufenden Text.
We annotated speech in the slightly shortened "research cut" of the movie
\citep{hanke2016simultaneous} and its temporally aligned audio-description
\citep{hanke2014audiomovie}. For the movie stimulus, we used the audio track of
the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video,
DE103519SV)\citep{ForrestGumpDVD}. For the audio-only stimulus, we used the
movie's audio-description that was broadcast as an additional audio track for
visually impaired listeners on Swiss public television (Koop, Michalski,
Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk,
2009)\citep{ForrestGumpGermanAD}. The plot of the movie is already carried by an
off-screen voice of the main character Forrest Gump. In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content.
\subsection*{Annotation procedure}
% wo kommen die "preliminaries transcriptions" her?
% Die "most basic" Datei, die das Dataset enthält ist der Merge aus Diaolog, Narrator & Non-Speech-Annotation
Preliminary, orthographic transcriptions of dialogues (german\_dialog.csv),
non-speech vocalizations (e.g. laughing or groaning;
non\_speech\_vocalization.json), and the audio-description's narrator
(german\_audio\_description.csv) were merged and converted to Praat's
\citep{boersma2019praat} .TextGrid format (
\href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}). The merged transcription
containing one onset and offset for usually a couple of sentences was opened
along (the audio file of) the audio-description in Praat v6.0.22 for manual
improvements: In several passes, the approximate temporal onsets and offsets
were corrected. Intervals containing several sentences were split into intervals
containing only one sentence. When two or more persons were speaking
simultaneously the less dominant (background) voice was dropped. Low volume
background speech (especially occurring during music or continuous environmental
noise) or low volume non-speech vocalizations that are difficult to recognize by
a regular audience were dropped, too.

% Alignment preparations
We used the Montreal Forced Aligner v1.0.1
\href{montrealcorpustools.github.io/Montreal-Forced-Aligner}{montrealcorpustools.github.io/Montreal-Forced-Aligner}\citep{mcauliffe2017montreal};to
algorithmically identify the onset and offset of each word and phoneme embedded
in the transcribed sentences. To enable the aligner to look up the pronunciation
of every word, we chose a German pronunciation dictionary
\href{https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}{raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}
provided by Prosodylab (\href{http://prosodylab.org}{prosodylab.org}) that uses
the Prosodylab PhoneSet. The dictionary was manually updated with movie-specific
German words. The pronunciation of English words occurring in the otherwise
German audio track was taken from an English pronunciation dictionary
(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.

% Alignment
% Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach
% die Event-Borders zwischen den Phonemen herausgenommen. Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
% Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach).
% kommt selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.
The audio file was converted from .FLAC to .WAV via ffmpeg v4.1.4
(\href{www.ffmpeg.org}{ffmpeg.org}) to meet the aligner's requirements. This
.WAV file, the transcription of sentences, and the updated dictionary were
submitted to the aligner that first trained an acoustic model on the data and
then performed the alignment. In a first step, the resulting .TextGrid file that
contains onsets and offsets of words and phonemes was opened in Praat to check
and correct the automatic alignment. In several passes, words [and their
corresponding phonemes] on which the automatic alignment performed moderately
were corrected. Some (low volume) sentences that are spoken in continuously
noisy settings (pursuit, battle, hurricane, demonstration/rally, disco) were
removed due to poor overall alignment performance. In a second step, the
complete sentences of the orthographic transcription were copied into the
annotation. In a third step, the name of the speaker was added for every sentence.
During every new step results from all previous steps were checked again for errors and corrected.

% descriptive Nouns
% hier ggf. noch angeben, dass die effektiv identisch waren
% Florian hat zwei Regeln falsch verstanden, sonst war übereinstimmung >90%
A further annotation of the audio-description's narrator was done manually: Two
persons performed a categorization of nouns embedded in sentences spoken by the
narrator to describe the movie's missing visual content. Categories focus on the
cinematographic scene's environment, inherent objects, persons, and a person's
appearance. A preliminary annotation according to the rules (s. table XY) was done by one person and corrected in several runs by the author.

% NLP
To automatically analyze linguistic features of words in their corresponding
sentence, we employed the Python package spaCy v2.2.1
(\href{https://spacy.io}{spacy.io}) and a German language model
(de\_core\_news\_md; \href{https://spacy.io/models/de}{spacy.io/models/de})
trained on the TIGER Treebank corpus
(\href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}). We performed
analyses regarding part of speech (i.e. grammatical tagging or word-category
disambiguation), syntactic dependency, lemmatization, word embedding (i.e.
semantic similarity), and if the word is one of the most common words of the
German language. Results of these analyzes were added to the annotation and
saved as .TextGrid file. This .TextGrid file was converted via python script to
a tab separated file in accordance with the brain imaging data structure
(\href{https://bids.neuroimaging.io/}){BIDS}\citep{gorgolewski2016bids}). Non-speech vocalizations were dropped from the sentences before analysis.
% BIDS stuff runter zu "Dataset content"?

\subsection*{Data Legend}
% wo wurde automatisch korrigiert (e.g. NE/NN, NONSPEECH)
% s. dictionaries oben in add_part-of-speech-tagging2textgrid.py
\subsubsection*{Start (\texttt{start})}
the onset of the sentences, word or phoneme provided in seconds of stimulus onset.
\subsubsection*{Duration (\texttt{end})}
the duration of the sentences, word or phoneme provided in seconds.
\subsubsection*{Speaker identity (\texttt{person})}
name of the persons that speaks the sentence, word, phoneme.
% einige Eigennamen (NE/NN) wurden automatisch korrigiert, weil das Sprachmodell
% die naheliegenderweise nicht kannte; eine Liste dieser Eigennamen befindet
% sich oben in dem entsprechendem Skript
% (add_part-of-speech-tagging2textgrid.py)
\subsubsection*{Simple part-of-speech tag (\texttt{pos})}
This column contains tags for whole sentences ("SENTENCE"), phonemes ("PHONEME") and non-speech vocalizations (NONSPEECH). For single words, it contains a simple part-of-speech tagging (grammatical tagging; word-category disambiguation) taking the relationship with adjacent and related words in the same sentence into account. This simple part-of-speech tagging tags follow the \href{https://universaldependencies.org}{Universal Dependencies} v2 POS tag set.

\subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
A detailed part-of-speech tagging following the TIGER Treebank annotation scheme \citep{brants2004tiger} which is based on the \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset} \citep{schiller1999stts}.
\subsubsection*{Syntactic dependency (\texttt{dep})}
A word's column entry provides information about a word's syntactic dependency. Information following the TIGER Treebank annotation scheme \citep{brants2004tiger} is given in the format:
"arc label;word's head;word's child1, word's child2, ..." where the "arc label" describes the type of syntactic relation that connects a "child" (the single word) to its "head".
\subsubsection*{Lemmatization (\texttt{lemma})}
For single words, the base form (root) of the word
\subsubsection*{Common Word (\texttt{stop})}
For single words, this column provides information if the word is part of a stop list, hence one of the most common words in the German language ("True") or not ('"False")?
\subsubsection*{Narrator's descriptive nouns (\texttt{descr})}
A categorizing of nouns that serve as auditory cues about the movie's visual content. Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
\paragraph*{Narrator's descriptive nouns}
\begin{center}
\begin{tabular}{ |c|c|c|c| }
\hline
category & description & examples & count\\
\hline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & 125\\
geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & 105\\
setting\_new & first-time mentioned setting & on a bridge, on an alley, on campus & 86\\
setting\_rec & recurring setting & at the bus stop & 37\\
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt & 66\\
bodypart & limbs and trousers & arm, finger, leg, toe & 69\\
face & face or parts of it & face, ear, nose, mouth & 47\\
head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & 36\\
furniture & movable objects insides/outsides & bench, bed, table, chair & 50\\
object & countable entities with firm boundaries & feather, telephone, car & 232\\
objects & countable entities with firm boundaries & wheels, photos & 52\\
female & female person & nurse, mother, women & 31\\
females & female persons & women & 3\\
fname & female name & Jenny, Carla & 74\\
male & male person & man, father, soldier & 89\\
males & concrete male persons & boys, opponents & 23\\
mname & male name of person present in the scene & Forrest, Bubba, Kennedy & 291\\
persons & concrete persons of unknown sex / gender & hippies, patients & 17\\
++ & nouns, adverbial adjectives, and adverbs & in the evening, it's daytime, later
\\
\hline
\end{tabular}
\end{center}

\subsubsection*{Word embedding (semantic similarity) (\texttt{vector})}
A word's column entry contains a 300-dimensional \href{https://en.wikipedia.org/wiki/Word2vec}{word vector} providing a multi-dimensional meaning representation of the word. Uncommon and out-of-vocabulary words with a vector consisting of 300 dimensions of 0's were set to '\#' [to save space].

\subsubsection*{Phonemes (\texttt{phones})}
Phonemes of German words follow the Prosodylab PhoneSet, English words follow the ARPAbet PhoneSet.

\subsection*{Dataset content}
% habe folgend die Art und Weise aus der Datei p.tex der Schnitt-Annotation übernommen, wobei das im veröffentlichten Paper ganz anders aussieht
% noch mit so Boxen und doi's
% ACHTUNG: github erlaubt laut datalad handbook keine Dateien >100MB
% Anno im Praat Format ist >200MB (und die audiodateien ohnehin)
The released annotation comes in two different versions. First, in a (text-based) .TextGrid file that can be loaded into Praat (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}).
Second, as a text-based tab-separated-value (TSV) formatted table  (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv})  in accordance with the brain imaging data structure BIDS \citep{gorgolewski2016bids} (\href{https://bids.neuroimaging.io/}{bids.neuroimaging.io}). The source code for all descriptive statistics included in this paper is available in \texttt{code/descriptive-statistics.py} (Python script).

\section*{Dataset validation}
% Information about any validation carried out and/or any limitations of the
% datasets, including any allowances made for controlling bias or unwanted
% sources of variability.
% ~170 words => das wird beim folgenden Schreiben definitiv nichts werden
% Intro
In order to assess data quality, we investigated if contrasting speech-related events to non-speech related events lead to increased activation in areas known to be involved in semantic processing \citep{binder2009semantic, dewitt2012phoneme}.
Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (conjunctions) lead to increased activation in congruent brain areas.
% Preprocessing
% die Daten aus Hanke2014 sind eigentlich nicht bewegungskorrigiert und aligned
% Quelle ist in vorliegendem Falle:
% juseless.inm7.de:/data/project/studyforrest/collection/phase1
% bei allem, was folgend mit alignment/co-registration zu tun hat, bin ich mir nicht sicher
We used fMRI BOLD data of the 2h audio-description (7 Tesla, 2s TR, partial
brain coverage with 1.4 mm isotropic voxels) \citep{hanke2014audiomovie} that
were already corrected for motion and aligned [wie?] to study specific group template [co-registered to MNI?].
All further steps analysis steps were carried out using Feat v6.00 (FMRI Expert
Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB’s
Software Library)\citep{smith2004fsl}. Data were temporally high-pass filtered (cut-off 150s), spatially smoothed (Gaussian kernel; 4.0 mm FWHM), and the brain was extracted from surrounding tissue [keine Plan, ob die Reihenfolge so korrek ist]. A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
We implemented a standard three-level, voxel-wise general linear model (GLM) to average parameter estimates across the eight stimulus segments, and later across 19 subjects.
% 1st lvl
At the first level analysing each segment for each subject individually, we defined regressors based on information drawn from the annotation. The top 20 detailed tags by count (“nn” with N=2620 to “prf” with N=157) were modelled as such from the onset to offset of each word. The remaining tags were pooled to a single regressor (“tag\_other” ; N=1123). The top 80 phonemes (“n” with n=6053 to “IY1” with N=32) were pooled to the regressor “phonemes” (N=65251).
The ends of (complete) grammatical sentences were used as the onset of events, abitrarily lasting 0.2s, for the regressors “sentence” (N=1651).
A “no speech” regressor (“no-sp”; N=264) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech. Each event of the no speech condition had a minimum distance of 1.8s to onset/offsets of sentences/words and to each other onset of the no speech condition (s. anno2events-files.py). A length of 0.07s was chosen for these events matching the average length of phonemes.
Two regressors reflecting auditory (low-level) features (left-right loudness/volume/amplitude difference; root mean squared amplitude) aligned to the frame rate of (40 ms) were modelled to reduce nuisance effects.
Those 26 regressors were convolved with FSL's “Double-Gamma HRF” as a model of the hemodynamic response function. Temporal derivatives were also included in the design matrix, and it was subjected to the same temporal filtering as the BOLD time series. Finally, six motion parameters were used as additional nuisance regressors.
The following six t-contrasts were defined: 1) all 21 tag-related regressors > no speech; 2) no speech > all 21 tag-related regressors; 3) proper nouns (“ne”; N=1012) > coordinate conjunctions (“kon”; N=475); 4) coordinate conjunctions > proper nouns; 5) nouns (“nn”) > coordinate conjunctions, and 6) coordinate conjunctions > nouns. The first level analysis that fitted each voxel’s time course separately for each subject was performed in functional space preserving the orientation of the EPI images [richtig?].

% 2nd lvl and 3rd lvl
The second-level analysis which averaged contrast estimates across the eight stimulus segments per subject was carried out using a fixed effects model by forcing the random effects variance to zero in FLAME (FMRIB’s Local Analysis of Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}. The third level analysis which averaged contrast estimates across subjects was carried out using FLAME stage 1 with automatic outlier de-weighting \citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>3.4 and a (corrected) cluster significance threshold of p<.05 \citep{woolrich2008robust}. Brain regions associated with observed clusters were determined with the Juelich Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} the Harvard-Oxford Cortical Atlas \citep{desikan2006automated}[really?] provided by FSL.

% results
% tabelle mit Cluster-Nr., nr. of voxels, max loc (MNI) x, y, z, mean, std; center of mass, structure
% figure

% discussion

\section*{Data availability}
% aus der Schnitt-Annotation übernommen
\texttt{This section will be auto-generated.}

In addition, released data, code, and manuscript sources are also available on
Github (\url{https://github.com/psychoinformatics-de/WHAT-EVER}).

\section*{Conclusions}
% state what you think are the main conclusions that can be realistically drawn from the findings in the paper, taking care not to make claims that cannot be supported.
Conclusion hatten wir bei der Schnitt-Annotation nicht; entspricht im Grunde dem letzten Absatz der Einleitung

\subsection*{Author contributions}
% subsection in Schnitte-Anno
%In order to give appropriate credit to each author of an article, the
%individual contributions of each author to the manuscript should be detailed
%in this section. We recommend using author initials and then stating briefly
%how they contributed.
COH designed, performed, and validated the annotation, and wrote the manuscript.
MH provided critical feedback on the procedure and wrote the manuscript.

\subsection*{Competing interests}
% subsection in Schnitte-Anno
No competing interests were disclosed.

\subsection*{Grant information}
% subsection in Schnitte-Anno
% im Großen und Ganzen: Ich habe keine Ahnung, wer meine Ernährer sind
Christian O. Häusler was supported by a graduate stipend from the German federal state of Saxony-Anhalt and ???
Michale Hanke was supported by ???

\subsection*{Acknowledgements}
We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns, and performed the preliminary annotation of nouns. Christian O. Häusler is also grateful to Valeri Kippes who took care of the author's mental sanity by providing excellent training at his gym in Jülich during the mentally draining period of manual corrections of the annotation.

{\small\bibliographystyle{unsrtnat}
\bibliography{references}}

\end{document}

### 2020-03-29 code/descriptive-statistics-anno.py
add script to create descriptive statistics of speech-annotation

@@ -1,0 +1,447 @@
+#!/usr/bin/python3
+"""
+author: Christian Olaf Haeusler
+created on Friday October 22th 2019
+"""
+import argparse
+import csv
+import spacy
+from collections import defaultdict
+
+
+SEGMENTS_OFFSETS = (
+    (0.00, 0.00),
+    (886.00, 0.00),
+    (1752.08, 0.08),  # third segment's start
+    (2612.16, 0.16),
+    (3572.20, 0.20),
+    (4480.28, 0.28),
+    (5342.36, 0.36),
+    (6410.44, 0.44),  # last segment's start
+    (7086.00, 0.00))  # movie's last time point
+
+
+def parse_arguments():
+    '''
+    '''
+    parser = argparse.ArgumentParser(
+        description='Show decriptive statistics for the annotation of speech'
+    )
+    parser.add_argument('-i',
+                        default='annotation/fg_rscut_ad_ger_speech_tagged.tsv',
+                        help='The input file')
+
+    parser.add_argument('-o',
+                        required=False,
+                        default=None,
+                        help='the tex-file the statistics to write to')
+
+    args = parser.parse_args()
+
+    inFile = args.i
+    outFile = args.o
+
+    return inFile, outFile
+
+
+def read_file(inFile):
+    '''
+    '''
+    with open(inFile) as csvfile:
+        content = csv.reader(csvfile, delimiter='\t')
+        header = next(content, None)
+        content = [x for x in content]
+
+    return header, content
+
+
+def get_run_number(starts, onset):
+    '''
+    '''
+    for start in sorted(starts, reverse=True):
+        if float(onset) >= start:
+            run = starts.index(start)
+            break
+
+    return run
+
+
+def populate_name_count(sent, nonSpeech, phones, data):
+    '''
+    '''
+    segmStarts = [start for start, offset in SEGMENTS_OFFSETS]
+
+    for line in data:
+        # check the run/segment we are in
+        run = get_run_number(segmStarts, line[0])
+        segment = str(run + 1)
+
+        # does the row contain a sentence?
+        if 'SENTENCE' in line[4]:
+            # counter for the whole stimulus (key=0)
+            sent[line[2]]['0'] += 1
+            # counter for the segments
+            sent[line[2]][segment] += 1
+        elif 'NONSPEECH' in line[4]:
+            nonSpeech[line[2]]['0'] += 1
+            nonSpeech[line[2]][segment] += 1
+        elif 'PHONEME' in line[4]:
+            phones[line[3]][segment] += 1
[…]

### 2020-03-29 code/descriptive-statistics-regressors.py
add script to create descriptive statistics of events/regressors

@@ -1,0 +1,72 @@
+#!/usr/bin/env python3
+'''
+created on Fri March 27 2020
+author: Christian Olaf Haeusler
+'''
+from glob import glob
+import argparse
+import os.path
+
+
+def parse_arguments():
+    '''
+    '''
+    parser = argparse.ArgumentParser(
+        description='Counts events in EV3 files for every regressor'
+    )
+    parser.add_argument('-d',
+                        default='./events/onsets/',
+                        help='the directory that contains the segmented annotation')
+
+    parser.add_argument('-o',
+                        default=None,
+                        help='the output file. e.g. ./descr-stats-regressors.tex')
+
+    args = parser.parse_args()
+
+    inDir = args.d
+    outFile = args.o
+
+    return inDir, outFile
+
+
+if __name__ == "__main__":
+    inDir, outFile = parse_arguments()
+
+    # search for event files in the given directory
+    pattern = os.path.join(inDir, '**/*.txt')
+    fPathes = sorted(glob(pattern, recursive=True))
+
+    # get a list of regressors from the event files
+    fileNames = [os.path.basename(path) for path in fPathes]
+    regressors = [os.path.splitext(fileName)[0] for fileName in fileNames]
+    regressors = sorted(list(set(regressors)))
+
+    toWrite = []
+    for regressor in regressors:
+        # filter list of all event files for the current loop's regressor
+        pattern = '/%s.txt' % regressor
+        regFiles = [ev3File for ev3File in fPathes if pattern in ev3File]
+
+        # count the lines (=events) per file/run
+        eventsPerRun = []
+        for regFile in regFiles:
+            noOfEvents = sum(1 for eventsPerRun in open(regFile))
+            eventsPerRun.append(noOfEvents)
+
+        # put the count for all events at the beginning of the list
+        eventsPerRun.insert(0, sum(eventsPerRun))
+
+        # build the lines for the current regressor to write to file
+        for run, count in enumerate(eventsPerRun):
+            regressor = regressor.capitalize()
+            run = 'Run' + str(run)
+            line = '\\newcommand{\\%s%s}{%s}\n' % (regressor, run, count)
+            toWrite.append(line)
+            if run == 'Run8':
+                toWrite.append('\n')
+
+    # write the file if a filename was passed as command line argument
+    if outFile is not None:
+       with open(outFile, 'w') as f:
+           f.writelines(toWrite)

### 2020-03-29 code/plot-corr-of-regressors.py
add script to create figure "correlation of regressors"

@@ -1,0 +1,158 @@
+#!/usr/bin/env python3
+'''
+created on Sun March 29 2020
+author: Christian Olaf Haeusler
+'''
+from glob import glob
+import argparse
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import os
+import pandas as pd
+import re
+import seaborn as sns
+matplotlib.use('Agg')
+
+
+TAG_DESIGN_PATTERN = 'sub-01/run-?_speech-validation.feat/design.mat'
+TAG_USED = list(range(1, 27)) # [1, 2, 3, 5, 6, 7, 8, 9, 10, 11, 17, 18]
+TAG_NAMES = {
+    1: 'adjective, attributive',
+    2: 'adjective, adverbial or predicative',
+    3: 'adverbial determination',
+    4: 'preposition; circumposition left',
+    5: 'preposition with article',
+    6: 'definite or indefinite article',
+    7: 'coordinate conjunction',
+    8: 'proper noun',
+    9: 'noun (singular or mass)',
+    10: 'substituting demonstrative pronoun',
+    11: 'substituting indefinite pronoun',
+    12: 'non-reflexive personal pronoun',
+    13: 'attributive possessive pronoun',
+    14: 'reflexive personal pronoun',
+    15: 'separable verbal particle',
+    16: 'finite verb,auxiliary',
+    17: 'finite verb, modal',
+    18: 'finite verb, full',
+    19: 'infinitive, full',
+    20: 'perfect participle, full',
+    21: 'other tags',
+    22: 'end of sentence',
+    23: 'phonemes',
+    24: 'no speech',
+    25: 'left-right diff',
+    26: 'root mean square'
+}
+
+
+outPath = 'figures'
+
+def parse_arguments():
+    '''
+    '''
+    parser = argparse.ArgumentParser(
+        description="creates the correlation of convoluted regressors from \
+        a subject's 1st lvl results directories (= all single run dirs ")
+
+
+    parser.add_argument('-exmpl',
+                        default='sub-01/run-01_speech-validation.feat/design.mat',
+                    help='pattern of path/file for 1st lvl design files')
+
+    parser.add_argument('-o',
+                        default='figures',
+                        help='the output directory for the PDF and SVG file')
+
+    args = parser.parse_args()
+
+    outDir = args.o
+    example = args.exmpl
+
+    return outDir, example
+
+
+
+def plot_heatmap(matrix, outFpath):
+    '''
+    '''
+    # generate a mask for the upper triangle
[…]

### 2020-03-31 paper/main.tex
minor corrections in main.tex & plot-corr-of-regressors.py

@@
 The ends of (complete) grammatical sentences were used as the onset of events, abitrarily lasting 0.2s, for the regressors “sentence” (N=1651).
-A “no speech” regressor (“no-sp”; N=264) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech.
-Each event of the no speech condition had a minimum distance of 1.8s to onset/offsets of sentences/words and to each other onset of the no speech condition (s.
+A “no-speech” regressor (“no-sp”; N=264) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech.
+Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of sentences/words and to each other onset of the no-speech condition (s.
 anno2events-files.py).

### 2020-03-31 code/plot-corr-of-regressors.py

@@ -47,8 +47,6 @@ TAG_NAMES = {
 }
 
 
-outPath = 'figures'
-
 def parse_arguments():
     '''
     '''
@@ -71,7 +69,6 @@ def parse_arguments():
     example = args.exmpl
 
     return outDir, example
-
 
 
 def plot_heatmap(matrix, outFpath):

### 2020-03-31 code/plot-zmaps.py
add plot-zmaps.py

@@ -1,0 +1,261 @@
+#!/usr/bin/env python3
+'''
+author: Christian Olaf Häusler
+created on Wednesday February 27 2020
+'''
+
+
+from nilearn import plotting
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import argparse
+import os
+
+
+# anatImg = '/usr/share/fsl/5.0/data/standard/MNI152_T1_1mm.nii.gz'
+anatImg = '/usr/share/data/fsl-mni152-templates/MNI152_T1_0.5mm.nii.gz'
+
+# list of primary contrasts
+# words > no-speech (bottom), Ne > kon (middle), Nn > kon (top image)
+primCopes = ['cope1_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz',
+             'cope3_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz',
+             'cope5_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz']
+
+# list of corresponding reverse contrasts
+# No-sp > words, Kon > ne, Kon > nn
+reveCopes = ['cope2_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz',
+             'cope4_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz',
+             'cope6_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz']
+
+
+def parse_arguments():
+    '''
+    '''
+    parser = argparse.ArgumentParser(
+        description='Creates plot of three stacked thresholded zmaps'
+    )
+
+    parser.add_argument('-d',
+                        default='inputs/studyforrest-speechanno-validation/3rd-lvl',
+                        help='directory that contains 3rd lvl COPE directories')
+
+    parser.add_argument('-o',
+                        default='paper/figures/',
+                        help='output dir for zmaps & colorbars')
+
+    args = parser.parse_args()
+
+    inDir = args.d
+    outFile = args.o
+
+    return inDir, outFile
+
+
+def process_group_averages(outfpath, imageList=
+                           ['cope1_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz',
+                            'cope3_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz',
+                            'cope3_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz']
+                           ):
+    '''
+    '''
[…]

### 2020-04-01 code/descriptive-statistics-regressors.py
update descr-stats-reg.py to meet LaTex requirements

@@ -29,6 +29,16 @@ def parse_arguments():
 
     return inDir, outFile
 
+no2alpha = {0: 'All',
+            1: 'I',
+            2: 'II',
+            3: 'III',
+            4: 'IV',
+            5: 'V',
+            6: 'VI',
+            7: 'VII',
+            8: 'VIII'
+            }
 
 if __name__ == "__main__":
     inDir, outFile = parse_arguments()
@@ -60,13 +70,15 @@ if __name__ == "__main__":
         # build the lines for the current regressor to write to file
         for run, count in enumerate(eventsPerRun):
             regressor = regressor.capitalize()
-            run = 'Run' + str(run)
-            line = '\\newcommand{\\%s%s}{%s}\n' % (regressor, run, count)
+            run = no2alpha[run]
+            line = '\\newcommand{\\r%s%s}{%s}\n' % (regressor, run, count)
             toWrite.append(line)
-            if run == 'Run8':
+            if run == 'VIII':
                 toWrite.append('\n')
 
     # write the file if a filename was passed as command line argument
+    toWrite = [line.replace('_', '') for line in toWrite]
+    toWrite = [line.replace('-', '') for line in toWrite]
     if outFile is not None:
        with open(outFile, 'w') as f:
            f.writelines(toWrite)

### 2020-04-01 code/descriptive-statistics-anno.py
update descr-stats-anno.py to meet LaTex requirements

@@ -20,6 +20,17 @@ SEGMENTS_OFFSETS = (
     (6410.44, 0.44),  # last segment's start
     (7086.00, 0.00))  # movie's last time point
 
+no2alpha = {0: 'All',
+            1: 'I',
+            2: 'II',
+            3: 'III',
+            4: 'IV',
+            5: 'V',
+            6: 'VI',
+            7: 'VII',
+            8: 'VIII'
+            }
+
 
 def parse_arguments():
     '''
@@ -172,8 +183,9 @@ def print_word_columns(countsWor, topNr):
             # for the current column/annotation, make a list of all
             # occuring categories by looking up the keys that exist in the dict
             # add the counts per segment later by extending a category's item
-                categories = [[category] for category in countsWor[column].keys()
-                          if category not in ['', '##']]
+                categories = [[category] for category
+                              in countsWor[column].keys()
+                              if category not in ['', '##']]
 
         # create the list with the counts per segment
         # that will be added
@@ -210,18 +222,16 @@ def statsSentPhones(statsFor, countsDict):
         for run in countsDict[speaker].keys():
             countsPerRun[run] += countsDict[speaker][run]
 
-
-
     perRun = [countsPerRun[run] for run in sorted(countsPerRun.keys())]
 
     line = [str(x) for x in perRun]
     line = statsFor + '\t' + '\t'.join(line)
     print(line)
 
-    labels = ['%sRun%s' % (statsFor, x) for x in range(0,9)]
+    labels = ['a%s%s' % (statsFor, no2alpha[x]) for x in range(0, 9)]
     labelsAndCounts = list(zip(labels, perRun))
     linesForLatex = ['\\newcommand{\\%s}{%s}\n' % (label, count)
-                    for label, count in labelsAndCounts]
+                     for label, count in labelsAndCounts]
 
     linesForLatex.append('\n')
 
@@ -245,10 +255,10 @@ def statsWords(countsWor):
     line = 'Words\t' + '\t'.join(line)
     print(line)
 
-    labels = ['%sRun%s' % (statsFor, x) for x in range(0,9)]
+    labels = ['a%s%s' % (statsFor, no2alpha[x]) for x in range(0, 9)]
     labelsAndCounts = list(zip(labels, perRun))
     linesForLatex = ['\\newcommand{\\%s}{%s}\n' % (label, count)
-                    for label, count in labelsAndCounts]
+                     for label, count in labelsAndCounts]
 
[…]

### 2020-04-03 paper/main.tex
add preliminary tables to main.tex

@@
 \usepackage{f1000_styles}
+\usepackage{booktabs}
 \usepackage[
@@
 \begin{document}
+\input{descr-stats-anno.tex}
+\input{descr-stats-regressors.tex}
 
@@
 language, speech, annotation, fMRI, natural stimulation, narrative, studyforrest
+
+\clearpage
+\begin{table*}[t]
+\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments. Words include \aPosNonspeechAll\space non-speech vocalizations.}
+\label{tab:example}
+\begin{tabular}{llllllllll}
+\toprule
+\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
+\midrule
+sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
+words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
+phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+\caption{Sentences spoken by top 10 of 97 (identified) speakers sorted alphabetically. Narrator only in audio-description.}
+\label{tab:example}
+\begin{tabular}{llllllllll}
+\toprule
+\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
+\midrule
+Bubba  & \aBubbaAll & \aBubbaI & \aBubbaII & \aBubbaIII & \aBubbaIV & \aBubbaV & \aBubbaVI & \aBubbaVII & \aBubbaVIII \tabularnewline
+Forrest  & \aForrestAll & \aForrestI & \aForrestII & \aForrestIII & \aForrestIV & \aForrestV & \aForrestVI & \aForrestVII & \aForrestVIII \tabularnewline
+Forrest (child)  & \aForrestchildAll & \aForrestchildI & \aForrestchildII & \aForrestchildIII & \aForrestchildIV & \aForrestchildV & \aForrestchildVI & \aForrestchildVII & \aForrestchildVIII \tabularnewline
+Forrest (v.o.)  & \aForrestvoAll & \aForrestvoI & \aForrestvoII & \aForrestvoIII & \aForrestvoIV & \aForrestvoV & \aForrestvoVI & \aForrestvoVII & \aForrestvoVIII \tabularnewline
+Hancock  & \aHancockAll & \aHancockI & \aHancockII & \aHancockIII & \aHancockIV & \aHancockV & \aHancockVI & \aHancockVII & \aHancockVIII \tabularnewline
+Jenny  & \aJennyAll & \aJennyI & \aJennyII & \aJennyIII & \aJennyIV & \aJennyV & \aJennyVI & \aJennyVII & \aJennyVIII \tabularnewline
+Jenny (child)  & \aJennychildAll & \aJennychildI & \aJennychildII & \aJennychildIII & \aJennychildIV & \aJennychildV & \aJennychildVI & \aJennychildVII & \aJennychildVIII \tabularnewline
+Lt. Dan  & \aLtdanAll & \aLtdanI & \aLtdanII & \aLtdanIII & \aLtdanIV & \aLtdanV & \aLtdanVI & \aLtdanVII & \aLtdanVIII \tabularnewline
+Mrs. Gump  & \aMrsgumpAll & \aMrsgumpI & \aMrsgumpII & \aMrsgumpIII & \aMrsgumpIV & \aMrsgumpV & \aMrsgumpVI & \aMrsgumpVII & \aMrsgumpVIII \tabularnewline
+Narrator  & \aNarratorAll & \aNarratorI & \aNarratorII & \aNarratorIII & \aNarratorIV & \aNarratorV & \aNarratorVI & \aNarratorVII & \aNarratorVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+\caption{Simple part of speech tagging (POS). All 15 categories sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually added.}
+\label{tab:example}
+\begin{tabular}{lllllllllll}
+\toprule
+\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
+\midrule
+ADJ & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII & \aPosAdjVIII & \aPosAdj \tabularnewline
+ADP & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII & \aPosAdp\tabularnewline
+ADV & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII & \aPosAdv\tabularnewline
+AUX & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII & \aPosAux\tabularnewline
+CONJ & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII & \aPosConj \tabularnewline
+DET & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII & \aPosDet\tabularnewline
+NONSPEECH  & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII & non-speech vocalization \tabularnewline
+NOUN & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII & \aPosNoun \tabularnewline
+NUM & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII & \aPosNum\tabularnewline
+PART & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII & \aPosPart \tabularnewline
+PRON & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII & \aPosPron \tabularnewline
+PRON  & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII & \aPosPropn \tabularnewline
+SCONJ & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII & \aPosSconj \tabularnewline
+VERB & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII & \aPosVerb\tabularnewline
+X & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII & \aPosX \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+\caption{Detailed part of speech tagging (TAG). The top 15 of 43 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
+\label{tab:example}
+\begin{tabular}{lllllllllll}
+\toprule
+\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
+\midrule
+ADJA  & \aTagAdjaAll & \aTagAdjaI & \aTagAdjaII & \aTagAdjaIII & \aTagAdjaIV & \aTagAdjaV & \aTagAdjaVI & \aTagAdjaVII & \aTagAdjaVIII & \aTagAdja \tabularnewline
+ADJD  & \aTagAdjdAll & \aTagAdjdI & \aTagAdjdII & \aTagAdjdIII & \aTagAdjdIV & \aTagAdjdV & \aTagAdjdVI & \aTagAdjdVII & \aTagAdjdVIII & \aTagAdjd \tabularnewline
+ADV  & \aTagAdvAll & \aTagAdvI & \aTagAdvII & \aTagAdvIII & \aTagAdvIV & \aTagAdvV & \aTagAdvVI & \aTagAdvVII & \aTagAdvVIII & \aTagAdv \tabularnewline
+APPR  & \aTagApprAll & \aTagApprI & \aTagApprII & \aTagApprIII & \aTagApprIV & \aTagApprV & \aTagApprVI & \aTagApprVII & \aTagApprVIII & \aTagAppr \tabularnewline
+ART  & \aTagArtAll & \aTagArtI & \aTagArtII & \aTagArtIII & \aTagArtIV & \aTagArtV & \aTagArtVI & \aTagArtVII & \aTagArtVIII & \aTagArt \tabularnewline
+KON  & \aTagKonAll & \aTagKonI & \aTagKonII & \aTagKonIII & \aTagKonIV & \aTagKonV & \aTagKonVI & \aTagKonVII & \aTagKonVIII & \aTagKon \tabularnewline
+NE  & \aTagNeAll & \aTagNeI & \aTagNeII & \aTagNeIII & \aTagNeIV & \aTagNeV & \aTagNeVI & \aTagNeVII & \aTagNeVIII & \aTagNe \tabularnewline
+NN  & \aTagNnAll & \aTagNnI & \aTagNnII & \aTagNnIII & \aTagNnIV & \aTagNnV & \aTagNnVI & \aTagNnVII & \aTagNnVIII & \aTagNn \tabularnewline
+PPER  & \aTagPperAll & \aTagPperI & \aTagPperII & \aTagPperIII & \aTagPperIV & \aTagPperV & \aTagPperVI & \aTagPperVII & \aTagPperVIII & \aTagPper \tabularnewline
+PPOSAT  & \aTagPposatAll & \aTagPposatI & \aTagPposatII & \aTagPposatIII & \aTagPposatIV & \aTagPposatV & \aTagPposatVI & \aTagPposatVII & \aTagPposatVIII & \aTagPposat \tabularnewline
+PTKVZ  & \aTagPtkvzAll & \aTagPtkvzI & \aTagPtkvzII & \aTagPtkvzIII & \aTagPtkvzIV & \aTagPtkvzV & \aTagPtkvzVI & \aTagPtkvzVII & \aTagPtkvzVIII & \aTagPtkvz \tabularnewline
+VAFIN  & \aTagVafinAll & \aTagVafinI & \aTagVafinII & \aTagVafinIII & \aTagVafinIV & \aTagVafinV & \aTagVafinVI & \aTagVafinVII & \aTagVafinVIII & \aTagVafin \tabularnewline
+VVFIN  & \aTagVvfinAll & \aTagVvfinI & \aTagVvfinII & \aTagVvfinIII & \aTagVvfinIV & \aTagVvfinV & \aTagVvfinVI & \aTagVvfinVII & \aTagVvfinVIII & \aTagVvfin \tabularnewline
+VVINF  & \aTagVvinfAll & \aTagVvinfI & \aTagVvinfII & \aTagVvinfIII & \aTagVvinfIV & \aTagVvinfV & \aTagVvinfVI & \aTagVvinfVII & \aTagVvinfVIII & \aTagVvinf \tabularnewline
+VVPP  & \aTagVvppAll & \aTagVvppI & \aTagVvppII & \aTagVvppIII & \aTagVvppIV & \aTagVvppV & \aTagVvppVI & \aTagVvppVII & \aTagVvppVIII & \aTagVvpp \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+\caption{Syntactic dependencies (DEP). The top 15 of 37 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
+\label{tab:example}
+\begin{tabular}{lllllllllll}
+\toprule
+\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
+\midrule
+cd  & \aDepCdAll & \aDepCdI & \aDepCdII & \aDepCdIII & \aDepCdIV & \aDepCdV & \aDepCdVI & \aDepCdVII & \aDepCdVIII & \aDepCd \tabularnewline
+cj  & \aDepCjAll & \aDepCjI & \aDepCjII & \aDepCjIII & \aDepCjIV & \aDepCjV & \aDepCjVI & \aDepCjVII & \aDepCjVIII & \aDepCj \tabularnewline
+cp  & \aDepCpAll & \aDepCpI & \aDepCpII & \aDepCpIII & \aDepCpIV & \aDepCpV & \aDepCpVI & \aDepCpVII & \aDepCpVIII & \aDepCp \tabularnewline
+da  & \aDepDaAll & \aDepDaI & \aDepDaII & \aDepDaIII & \aDepDaIV & \aDepDaV & \aDepDaVI & \aDepDaVII & \aDepDaVIII & \aDepDa \tabularnewline
+ju  & \aDepJuAll & \aDepJuI & \aDepJuII & \aDepJuIII & \aDepJuIV & \aDepJuV & \aDepJuVI & \aDepJuVII & \aDepJuVIII & \aDepJu \tabularnewline
+mnr  & \aDepMnrAll & \aDepMnrI & \aDepMnrII & \aDepMnrIII & \aDepMnrIV & \aDepMnrV & \aDepMnrVI & \aDepMnrVII & \aDepMnrVIII & \aDepMnr \tabularnewline
+Mmo  & \aDepMoAll & \aDepMoI & \aDepMoII & \aDepMoIII & \aDepMoIV & \aDepMoV & \aDepMoVI & \aDepMoVII & \aDepMoVIII & \aDepMo \tabularnewline
+nk  & \aDepNkAll & \aDepNkI & \aDepNkII & \aDepNkIII & \aDepNkIV & \aDepNkV & \aDepNkVI & \aDepNkVII & \aDepNkVIII & \aDepNk \tabularnewline
+oa  & \aDepOaAll & \aDepOaI & \aDepOaII & \aDepOaIII & \aDepOaIV & \aDepOaV & \aDepOaVI & \aDepOaVII & \aDepOaVIII & \aDepOa \tabularnewline
+oc  & \aDepOcAll & \aDepOcI & \aDepOcII & \aDepOcIII & \aDepOcIV & \aDepOcV & \aDepOcVI & \aDepOcVII & \aDepOcVIII & \aDepOc \tabularnewline
+pd  & \aDepPdAll & \aDepPdI & \aDepPdII & \aDepPdIII & \aDepPdIV & \aDepPdV & \aDepPdVI & \aDepPdVII & \aDepPdVIII & \aDepPd \tabularnewline
+pnc  & \aDepPncAll & \aDepPncI & \aDepPncII & \aDepPncIII & \aDepPncIV & \aDepPncV & \aDepPncVI & \aDepPncVII & \aDepPncVIII & \aDepPnc \tabularnewline
+ROOT  & \aDepRootAll & \aDepRootI & \aDepRootII & \aDepRootIII & \aDepRootIV & \aDepRootV & \aDepRootVI & \aDepRootVII & \aDepRootVIII & root \tabularnewline
+sb  & \aDepSbAll & \aDepSbI & \aDepSbII & \aDepSbIII & \aDepSbIV & \aDepSbV & \aDepSbVI & \aDepSbVII & \aDepSbVIII & \aDepSb \tabularnewline
+svp  & \aDepSvpAll & \aDepSvpI & \aDepSvpII & \aDepSvpIII & \aDepSvpIV & \aDepSvpV & \aDepSvpVI & \aDepSvpVII & \aDepSvpVIII & separable verb prefix \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+    \caption{Narrator's descriptive nouns.
+All categories sorted alphapetically.
+Examples are given in English.
+Description (of rules) fehlt in dieser Tabelle (vgl.
+alte Tabelle auf der allerletzten Seite).
+Wird nämlich in einer Tabelle mit horizontaler Ausrichtung eng.
+Kategorie ```++''' enthält ausnahmesweise auch adverbiale Best.
+der Zeit'''.}
+\label{tab:example}
+\begin{tabular}{lllllllllll}
+\toprule
+\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} &     \textbf{examples}\\
+\midrule
+body & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII & back, hip, shoulder; jacket, dress, shirt \tabularnewline
+bodypart & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII & arm, finger, leg, toe \tabularnewline
+face  & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII & face, ear, nose, mouth \tabularnewline
+female  & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII & nurse, mother, woman \tabularnewline
+females  & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII & women \tabularnewline
+fname  & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII & Jenny \tabularnewline
+furniture  & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII & bench, bed, table, chair \tabularnewline
+geo  & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII & building, tree, street, alley, meadow, cornfield, river \tabularnewline
+geo-room  & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII & living room; wall, door, window, floor, turf \tabularnewline
+head  & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII & head, hair, ear, neck, helmet \tabularnewline
+male  & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII & man, father, soldier \tabularnewline
+males  & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII & boys, opponents \tabularnewline
+mname  & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII & Bubba, Kennedy \tabularnewline
+object  & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII & telephone, car \tabularnewline
+objects  & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII & wheels, photos \tabularnewline
+persons  & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII & hippies, patients \tabularnewline
+setting\_new  & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII & on a ```bridge''', on an ```alley''', on ```campus''' \tabularnewline
+setting\_rec  & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII & at the ```bus stop''' \tabularnewline
+++  & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII & in the ```evening''', it's ```daytime''', ```later''' \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+\caption{Overview of the 26 REGRESSORS used for the validation analysis.
+The top 20 categories of the detailed part-of speech tagging were used as such.
+Descriptions were taken from spaCy.explain().
+All others tags were pooled to ```tag\_other'''.
+The other categories were build\dots}
+\label{tab:example}
+\begin{tabular}{llllllllllll}
+\toprule
+\textbf{no} & \textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
+\midrule
+1 & adja  & \rAdjaAll & \rAdjaI & \rAdjaII & \rAdjaIII & \rAdjaIV & \rAdjaV & \rAdjaVI & \rAdjaVII & \rAdjaVIII & \aTagAdja \tabularnewline
+2 & adjd  & \rAdjdAll & \rAdjdI & \rAdjdII & \rAdjdIII & \rAdjdIV & \rAdjdV & \rAdjdVI & \rAdjdVII & \rAdjdVIII & \aTagAdjd \tabularnewline
+3 & adv  & \rAdvAll & \rAdvI & \rAdvII & \rAdvIII & \rAdvIV & \rAdvV & \rAdvVI & \rAdvVII & \rAdvVIII & \aTagAdv \tabularnewline
+4 & appr  & \rApprAll & \rApprI & \rApprII & \rApprIII & \rApprIV & \rApprV & \rApprVI & \rApprVII & \rApprVIII & \aTagAppr \tabularnewline
+5 & apprart  & \rApprartAll & \rApprartI & \rApprartII & \rApprartIII & \rApprartIV & \rApprartV & \rApprartVI & \rApprartVII & \rApprartVIII & preposition with article \tabularnewline
+6 & art  & \rArtAll & \rArtI & \rArtII & \rArtIII & \rArtIV & \rArtV & \rArtVI & \rArtVII & \rArtVIII & \aTagArt \tabularnewline
+7 & kon  & \rKonAll & \rKonI & \rKonII & \rKonIII & \rKonIV & \rKonV & \rKonVI & \rKonVII & \rKonVIII & \aTagKon \tabularnewline
+8 & ne  & \rNeAll & \rNeI & \rNeII & \rNeIII & \rNeIV & \rNeV & \rNeVI & \rNeVII & \rNeVIII & \aTagNe \tabularnewline
+9 & nn  & \rNnAll & \rNnI & \rNnII & \rNnIII & \rNnIV & \rNnV & \rNnVI & \rNnVII & \rNnVIII & \aTagNn \tabularnewline
+10 & pds  & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII & substituting demonstrative pronoun \tabularnewline
+11 & pis  & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII & substituting indefinite pronou \tabularnewline
+12 & pper  & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII & \aTagPper \tabularnewline
+13 & pposat & \rPposatAll & \rPposatI & \rPposatII & \rPposatIII & \rPposatIV & \rPposatV & \rPposatVI & \rPposatVII & \rPposatVIII & \aTagPposat \tabularnewline
+14 & prf  & \rPrfAll & \rPrfI & \rPrfII & \rPrfIII & \rPrfIV & \rPrfV & \rPrfVI & \rPrfVII & \rPrfVIII & reflexive personal pronoun \tabularnewline
+15 & ptkvz  & \rPtkvzAll & \rPtkvzI & \rPtkvzII & \rPtkvzIII & \rPtkvzIV & \rPtkvzV & \rPtkvzVI & \rPtkvzVII & \rPtkvzVIII & \aTagPtkvz \tabularnewline
+16 & vafin  & \rVafinAll & \rVafinI & \rVafinII & \rVafinIII & \rVafinIV & \rVafinV & \rVafinVI & \rVafinVII & \rVafinVIII & \aTagVafin \tabularnewline
+17 & vmfin  & \rVmfinAll & \rVmfinI & \rVmfinII & \rVmfinIII & \rVmfinIV & \rVmfinV & \rVmfinVI & \rVmfinVII & \rVmfinVIII & finite verb, modal \tabularnewline
+18 & vvfin  & \rVvfinAll & \rVvfinI & \rVvfinII & \rVvfinIII & \rVvfinIV & \rVvfinV & \rVvfinVI & \rVvfinVII & \rVvfinVIII & \aTagVvfin \tabularnewline
+19 & vvinf  & \rVvinfAll & \rVvinfI & \rVvinfII & \rVvinfIII & \rVvinfIV & \rVvinfV & \rVvinfVI & \rVvinfVII & \rVvinfVIII & \aTagVvinf \tabularnewline
+20 & vvpp  & \rVvppAll & \rVvppI & \rVvppII & \rVvppIII & \rVvppIV & \rVvppV & \rVvppVI & \rVvppVII & \rVvppVIII & \aTagVvpp \tabularnewline
+21 & tag\_other  & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII & all other TAG categories \tabularnewline
+22 & sentence  & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII & complete grammatical sentences \tabularnewline
+23 & phones  & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII & top XY phonemes \tabularnewline
+24 & no-sp  & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII & no speech (```soundscape''') \tabularnewline
+25 & fg\_ad\_lrdiff  & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII & left-right volume difference \tabularnewline
+26 & fg\_ad\_rms  & \rFgadrmsAll & \rFgadrmsI & \rFgadrmsII & \rFgadrmsIII & \rFgadrmsIV & \rFgadrmsV & \rFgadrmsVI & \rFgadrmsVII & \rFgadrmsVIII & root mean square \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
 
@@
 \paragraph*{Narrator's descriptive nouns}
-\begin{center}
-\begin{tabular}{ |c|c|c|c| }
-\hline
-category & description & examples & count\\
-\hline
-geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & 125\\
-geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & 105\\
-setting\_new & first-time mentioned setting & on a bridge, on an alley, on campus & 86\\
-setting\_rec & recurring setting & at the bus stop & 37\\
-body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt & 66\\
-bodypart & limbs and trousers & arm, finger, leg, toe & 69\\
-face & face or parts of it & face, ear, nose, mouth & 47\\
-head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & 36\\
-furniture & movable objects insides/outsides & bench, bed, table, chair & 50\\
-object & countable entities with firm boundaries & feather, telephone, car & 232\\
-objects & countable entities with firm boundaries & wheels, photos & 52\\
-female & female person & nurse, mother, women & 31\\
-females & female persons & women & 3\\
-fname & female name & Jenny, Carla & 74\\
-male & male person & man, father, soldier & 89\\
-males & concrete male persons & boys, opponents & 23\\
-mname & male name of person present in the scene & Forrest, Bubba, Kennedy & 291\\
-persons & concrete persons of unknown sex / gender & hippies, patients & 17\\
-++ & nouns, adverbial adjectives, and adverbs & in the evening, it's daytime, later
-\\
-\hline
-\end{tabular}
-\end{center}
-
 \subsubsection*{Word embedding (semantic similarity) (\texttt{vector})}
@@
 
+\clearpage
+% der alte Entwurf der Tabelle; hier mit rules/description in der Tabelle
+\begin{center}
+\begin{tabular}{ |c|c|c|c| }
+\hline
+category & description & examples & count\\
+\hline
+geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & 125\\
+geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & 105\\
+setting\_new & first-time mentioned setting & on a bridge, on an alley, on campus & 86\\
+setting\_rec & recurring setting & at the bus stop & 37\\
+body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt & 66\\
+bodypart & limbs and trousers & arm, finger, leg, toe & 69\\
+face & face or parts of it & face, ear, nose, mouth & 47\\
+head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & 36\\
+furniture & movable objects insides/outsides & bench, bed, table, chair & 50\\
+object & countable entities with firm boundaries & feather, telephone, car & 232\\
+objects & countable entities with firm boundaries & wheels, photos & 52\\
+female & female person & nurse, mother, women & 31\\
+females & female persons & women & 3\\
+fname & female name & Jenny, Carla & 74\\
+male & male person & man, father, soldier & 89\\
+males & concrete male persons & boys, opponents & 23\\
+mname & male name of person present in the scene & Forrest, Bubba, Kennedy & 291\\
+persons & concrete persons of unknown sex / gender & hippies, patients & 17\\
+++ & nouns, adverbial adjectives, and adverbs & in the evening, it's daytime, later \\
+\hline
+\end{tabular}
+\end{center}
+
 \end{document}

### 2020-04-04 paper/main.tex
add preliminary figure "correlation of regressors" at the top of main.tex

@@
 22 & sentence  & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII & complete grammatical sentences \tabularnewline
-23 & phones  & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII & top XY phonemes \tabularnewline
+23 & phones  & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII & top 80 phonemes \tabularnewline
 24 & no-sp  & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII & no speech (```soundscape''') \tabularnewline
@@
 \end{table*}
+
+% Also weshalb wird das temporal filtering der regressoren wann wie gemacht??? -> nachschlagen
+% “You should normally apply the same temporal filtering to the model as you have applied to the data, as the model is designed to look like the data before temporal filtering was applied.
+In this way, long-time-scale components in the model will be dealt with correctly.
+This is set with the Apply temporal filtering option.”
+\begin{figure*}
+  \centering
+% \includegraphics[width=0.4\textwidth]{frog.jpg}
+  \includegraphics[width=\linewidth]{figures/regressor-corr}
+  \caption{Pearson correlation coefficients of the 26 regressors used in the analysis to validate the annotation.
+Regressors were convolved with FSL's “Double-Gamma HRF” as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation.
+Die unterschiedlichen Farben in den der Schriften kann man noch (wie?) sinnvoll ändern.}
+  \label{fig:correlation}
+\end{figure*}
 

### 2020-04-05 paper/main.tex
add preliminary figure "slicescolorbars" below tables in main.tex
add preliminary tables of significant clusters

@@
 \clearpage
+
 \begin{table*}[t]
@@
 Wird nämlich in einer Tabelle mit horizontaler Ausrichtung eng.
-Kategorie ```++''' enthält ausnahmesweise auch adverbiale Best.
-der Zeit'''.}
+Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best.
+der Zeit.}
 \label{tab:example}
@@
 persons  & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII & hippies, patients \tabularnewline
-setting\_new  & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII & on a ```bridge''', on an ```alley''', on ```campus''' \tabularnewline
-setting\_rec  & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII & at the ```bus stop''' \tabularnewline
-++  & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII & in the ```evening''', it's ```daytime''', ```later''' \tabularnewline
+setting\_new  & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII & on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
+setting\_rec  & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII & at the ``bus stop'' \tabularnewline
+++  & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
 \bottomrule
@@
 Descriptions were taken from spaCy.explain().
-All others tags were pooled to ```tag\_other'''.
+All others tags were pooled to ``tag\_other''.
 The other categories were build\dots}
@@
 23 & phones  & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII & top 80 phonemes \tabularnewline
-24 & no-sp  & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII & no speech (```soundscape''') \tabularnewline
+24 & no-sp  & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII & no speech (``soundscape'') \tabularnewline
 25 & fg\_ad\_lrdiff  & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII & left-right volume difference \tabularnewline
@@
 Regressors were convolved with FSL's “Double-Gamma HRF” as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation.
+NOTE: Bisher werden pdf figures.
 Die unterschiedlichen Farben in den der Schriften kann man noch (wie?) sinnvoll ändern.}
@@
 
+\begin{figure*}
+  \centering
+% \includegraphics[width=0.4\textwidth]{frog.jpg}
+  \includegraphics[width=\linewidth]{figures/slicescolorbars}
+  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05; cluster corr.; MNI template space).}
+  \label{fig:results}
+\end{figure*}
+
+\begin{table*}[t]
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE1: all 21 tag-related regressors > no speech.}
+\begin{tabular}{rrrrrrrrrrp{3cm}}
+\toprule
+& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{5-7} \cmidrule{8-10}
+Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+\midrule
+4 & 14990 & 0 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
+3 & 14469 & 0 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
+2 & 1971 & 2.37E-16 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
+1 & 217 & 0.00214 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
+\bottomrule
+\end{tabular}
+\label{tab:cope1}
+\end{table*}
+
+\begin{table*}[t]
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE3: proper nouns (``ne'') > coordinate conjunctions (``kon'').}
+\begin{tabular}{rrrrrrrrrrp{3cm}}
+\toprule
+& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{5-7} \cmidrule{8-10}
+Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+\midrule
+9 & 7691 & 2.80E-45 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
+8 & 5928 & 5.97E-38 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
+7 & 479 & 1.13E-06 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
+6 & 420 & 4.65E-06 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
+5 & 407 & 6.38E-06 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
+4 & 294 & 0.000115 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
+3 & 121 & 0.0237 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
+2 & 117 & 0.0274 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
+1 & 115 & 0.0295 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
+\bottomrule
+\end{tabular}
+\label{tab:cope3}
+\end{table*}
+
+\begin{table*}[t]
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE5: nouns (``nn'') > coordinate conjunctions (``kon'').}
+\begin{tabular}{rrrrrrrrrrp{3cm}}
+\toprule
+& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{5-7} \cmidrule{8-10}
+Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+\midrule
+4 & 3166 & 2.79E-25 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
+3 & 1753 & 7.18E-17 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
+2 & 166 & 0.00446 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
+1 & 149 & 0.00793 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
+\bottomrule
+\end{tabular}
+\label{tab:cope5}
+\end{table*}
+
 \clearpage
+
 \section*{Introduction}

### 2020-04-05 paper/main.tex
move column "description" to the left in all tableles

@@
 \toprule
-\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
+\textbf{category} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
-ADJ & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII & \aPosAdjVIII & \aPosAdj \tabularnewline
-ADP & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII & \aPosAdp\tabularnewline
-ADV & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII & \aPosAdv\tabularnewline
-AUX & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII & \aPosAux\tabularnewline
-CONJ & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII & \aPosConj \tabularnewline
-DET & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII & \aPosDet\tabularnewline
-NONSPEECH  & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII & non-speech vocalization \tabularnewline
-NOUN & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII & \aPosNoun \tabularnewline
-NUM & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII & \aPosNum\tabularnewline
-PART & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII & \aPosPart \tabularnewline
-PRON & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII & \aPosPron \tabularnewline
-PRON  & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII & \aPosPropn \tabularnewline
-SCONJ & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII & \aPosSconj \tabularnewline
-VERB & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII & \aPosVerb\tabularnewline
-X & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII & \aPosX \tabularnewline
+ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII \tabularnewline
+ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
+ADV & \aPosAdv & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII \tabularnewline
+AUX & \aPosAux & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII \tabularnewline
+CONJ & \aPosConj & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII \tabularnewline
+DET & \aPosDet & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII \tabularnewline
+NONSPEECH & non-speech vocalization & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII \tabularnewline
+NOUN & \aPosNoun & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII \tabularnewline
+NUM & \aPosNum & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII \tabularnewline
+PART & \aPosPart & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII \tabularnewline
+PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
+PRON & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
+SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
+VERB & \aPosVerb & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII \tabularnewline
+X & \aPosX & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII \tabularnewline
 \bottomrule
@@
 \toprule
-\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
+\textbf{category} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
-ADJA  & \aTagAdjaAll & \aTagAdjaI & \aTagAdjaII & \aTagAdjaIII & \aTagAdjaIV & \aTagAdjaV & \aTagAdjaVI & \aTagAdjaVII & \aTagAdjaVIII & \aTagAdja \tabularnewline
-ADJD  & \aTagAdjdAll & \aTagAdjdI & \aTagAdjdII & \aTagAdjdIII & \aTagAdjdIV & \aTagAdjdV & \aTagAdjdVI & \aTagAdjdVII & \aTagAdjdVIII & \aTagAdjd \tabularnewline
-ADV  & \aTagAdvAll & \aTagAdvI & \aTagAdvII & \aTagAdvIII & \aTagAdvIV & \aTagAdvV & \aTagAdvVI & \aTagAdvVII & \aTagAdvVIII & \aTagAdv \tabularnewline
-APPR  & \aTagApprAll & \aTagApprI & \aTagApprII & \aTagApprIII & \aTagApprIV & \aTagApprV & \aTagApprVI & \aTagApprVII & \aTagApprVIII & \aTagAppr \tabularnewline
-ART  & \aTagArtAll & \aTagArtI & \aTagArtII & \aTagArtIII & \aTagArtIV & \aTagArtV & \aTagArtVI & \aTagArtVII & \aTagArtVIII & \aTagArt \tabularnewline
-KON  & \aTagKonAll & \aTagKonI & \aTagKonII & \aTagKonIII & \aTagKonIV & \aTagKonV & \aTagKonVI & \aTagKonVII & \aTagKonVIII & \aTagKon \tabularnewline
-NE  & \aTagNeAll & \aTagNeI & \aTagNeII & \aTagNeIII & \aTagNeIV & \aTagNeV & \aTagNeVI & \aTagNeVII & \aTagNeVIII & \aTagNe \tabularnewline
-NN  & \aTagNnAll & \aTagNnI & \aTagNnII & \aTagNnIII & \aTagNnIV & \aTagNnV & \aTagNnVI & \aTagNnVII & \aTagNnVIII & \aTagNn \tabularnewline
-PPER  & \aTagPperAll & \aTagPperI & \aTagPperII & \aTagPperIII & \aTagPperIV & \aTagPperV & \aTagPperVI & \aTagPperVII & \aTagPperVIII & \aTagPper \tabularnewline
-PPOSAT  & \aTagPposatAll & \aTagPposatI & \aTagPposatII & \aTagPposatIII & \aTagPposatIV & \aTagPposatV & \aTagPposatVI & \aTagPposatVII & \aTagPposatVIII & \aTagPposat \tabularnewline
-PTKVZ  & \aTagPtkvzAll & \aTagPtkvzI & \aTagPtkvzII & \aTagPtkvzIII & \aTagPtkvzIV & \aTagPtkvzV & \aTagPtkvzVI & \aTagPtkvzVII & \aTagPtkvzVIII & \aTagPtkvz \tabularnewline
-VAFIN  & \aTagVafinAll & \aTagVafinI & \aTagVafinII & \aTagVafinIII & \aTagVafinIV & \aTagVafinV & \aTagVafinVI & \aTagVafinVII & \aTagVafinVIII & \aTagVafin \tabularnewline
-VVFIN  & \aTagVvfinAll & \aTagVvfinI & \aTagVvfinII & \aTagVvfinIII & \aTagVvfinIV & \aTagVvfinV & \aTagVvfinVI & \aTagVvfinVII & \aTagVvfinVIII & \aTagVvfin \tabularnewline
-VVINF  & \aTagVvinfAll & \aTagVvinfI & \aTagVvinfII & \aTagVvinfIII & \aTagVvinfIV & \aTagVvinfV & \aTagVvinfVI & \aTagVvinfVII & \aTagVvinfVIII & \aTagVvinf \tabularnewline
-VVPP  & \aTagVvppAll & \aTagVvppI & \aTagVvppII & \aTagVvppIII & \aTagVvppIV & \aTagVvppV & \aTagVvppVI & \aTagVvppVII & \aTagVvppVIII & \aTagVvpp \tabularnewline
+ADJA & \aTagAdja & \aTagAdjaAll & \aTagAdjaI & \aTagAdjaII & \aTagAdjaIII & \aTagAdjaIV & \aTagAdjaV & \aTagAdjaVI & \aTagAdjaVII & \aTagAdjaVIII \tabularnewline
+ADJD & \aTagAdjd & \aTagAdjdAll & \aTagAdjdI & \aTagAdjdII & \aTagAdjdIII & \aTagAdjdIV & \aTagAdjdV & \aTagAdjdVI & \aTagAdjdVII & \aTagAdjdVIII \tabularnewline
+ADV & \aTagAdv & \aTagAdvAll & \aTagAdvI & \aTagAdvII & \aTagAdvIII & \aTagAdvIV & \aTagAdvV & \aTagAdvVI & \aTagAdvVII & \aTagAdvVIII \tabularnewline
+APPR & \aTagAppr & \aTagApprAll & \aTagApprI & \aTagApprII & \aTagApprIII & \aTagApprIV & \aTagApprV & \aTagApprVI & \aTagApprVII & \aTagApprVIII \tabularnewline
+ART & \aTagArt & \aTagArtAll & \aTagArtI & \aTagArtII & \aTagArtIII & \aTagArtIV & \aTagArtV & \aTagArtVI & \aTagArtVII & \aTagArtVIII \tabularnewline
+KON & \aTagKon & \aTagKonAll & \aTagKonI & \aTagKonII & \aTagKonIII & \aTagKonIV & \aTagKonV & \aTagKonVI & \aTagKonVII & \aTagKonVIII \tabularnewline
+NE & \aTagNe & \aTagNeAll & \aTagNeI & \aTagNeII & \aTagNeIII & \aTagNeIV & \aTagNeV & \aTagNeVI & \aTagNeVII & \aTagNeVIII \tabularnewline
+NN & \aTagNn & \aTagNnAll & \aTagNnI & \aTagNnII & \aTagNnIII & \aTagNnIV & \aTagNnV & \aTagNnVI & \aTagNnVII & \aTagNnVIII \tabularnewline
+PPER & \aTagPper & \aTagPperAll & \aTagPperI & \aTagPperII & \aTagPperIII & \aTagPperIV & \aTagPperV & \aTagPperVI & \aTagPperVII & \aTagPperVIII \tabularnewline
+PPOSAT & \aTagPposat & \aTagPposatAll & \aTagPposatI & \aTagPposatII & \aTagPposatIII & \aTagPposatIV & \aTagPposatV & \aTagPposatVI & \aTagPposatVII & \aTagPposatVIII \tabularnewline
+PTKVZ & \aTagPtkvz & \aTagPtkvzAll & \aTagPtkvzI & \aTagPtkvzII & \aTagPtkvzIII & \aTagPtkvzIV & \aTagPtkvzV & \aTagPtkvzVI & \aTagPtkvzVII & \aTagPtkvzVIII \tabularnewline
+VAFIN & \aTagVafin & \aTagVafinAll & \aTagVafinI & \aTagVafinII & \aTagVafinIII & \aTagVafinIV & \aTagVafinV & \aTagVafinVI & \aTagVafinVII & \aTagVafinVIII \tabularnewline
+VVFIN & \aTagVvfin & \aTagVvfinAll & \aTagVvfinI & \aTagVvfinII & \aTagVvfinIII & \aTagVvfinIV & \aTagVvfinV & \aTagVvfinVI & \aTagVvfinVII & \aTagVvfinVIII \tabularnewline
+VVINF & \aTagVvinf & \aTagVvinfAll & \aTagVvinfI & \aTagVvinfII & \aTagVvinfIII & \aTagVvinfIV & \aTagVvinfV & \aTagVvinfVI & \aTagVvinfVII & \aTagVvinfVIII \tabularnewline
+VVPP & \aTagVvpp & \aTagVvppAll & \aTagVvppI & \aTagVvppII & \aTagVvppIII & \aTagVvppIV & \aTagVvppV & \aTagVvppVI & \aTagVvppVII & \aTagVvppVIII \tabularnewline
 \bottomrule
@@
 \toprule
-\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
+\textbf{category} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
-cd  & \aDepCdAll & \aDepCdI & \aDepCdII & \aDepCdIII & \aDepCdIV & \aDepCdV & \aDepCdVI & \aDepCdVII & \aDepCdVIII & \aDepCd \tabularnewline
-cj  & \aDepCjAll & \aDepCjI & \aDepCjII & \aDepCjIII & \aDepCjIV & \aDepCjV & \aDepCjVI & \aDepCjVII & \aDepCjVIII & \aDepCj \tabularnewline
-cp  & \aDepCpAll & \aDepCpI & \aDepCpII & \aDepCpIII & \aDepCpIV & \aDepCpV & \aDepCpVI & \aDepCpVII & \aDepCpVIII & \aDepCp \tabularnewline
-da  & \aDepDaAll & \aDepDaI & \aDepDaII & \aDepDaIII & \aDepDaIV & \aDepDaV & \aDepDaVI & \aDepDaVII & \aDepDaVIII & \aDepDa \tabularnewline
-ju  & \aDepJuAll & \aDepJuI & \aDepJuII & \aDepJuIII & \aDepJuIV & \aDepJuV & \aDepJuVI & \aDepJuVII & \aDepJuVIII & \aDepJu \tabularnewline
-mnr  & \aDepMnrAll & \aDepMnrI & \aDepMnrII & \aDepMnrIII & \aDepMnrIV & \aDepMnrV & \aDepMnrVI & \aDepMnrVII & \aDepMnrVIII & \aDepMnr \tabularnewline
-Mmo  & \aDepMoAll & \aDepMoI & \aDepMoII & \aDepMoIII & \aDepMoIV & \aDepMoV & \aDepMoVI & \aDepMoVII & \aDepMoVIII & \aDepMo \tabularnewline
-nk  & \aDepNkAll & \aDepNkI & \aDepNkII & \aDepNkIII & \aDepNkIV & \aDepNkV & \aDepNkVI & \aDepNkVII & \aDepNkVIII & \aDepNk \tabularnewline
-oa  & \aDepOaAll & \aDepOaI & \aDepOaII & \aDepOaIII & \aDepOaIV & \aDepOaV & \aDepOaVI & \aDepOaVII & \aDepOaVIII & \aDepOa \tabularnewline
-oc  & \aDepOcAll & \aDepOcI & \aDepOcII & \aDepOcIII & \aDepOcIV & \aDepOcV & \aDepOcVI & \aDepOcVII & \aDepOcVIII & \aDepOc \tabularnewline
-pd  & \aDepPdAll & \aDepPdI & \aDepPdII & \aDepPdIII & \aDepPdIV & \aDepPdV & \aDepPdVI & \aDepPdVII & \aDepPdVIII & \aDepPd \tabularnewline
-pnc  & \aDepPncAll & \aDepPncI & \aDepPncII & \aDepPncIII & \aDepPncIV & \aDepPncV & \aDepPncVI & \aDepPncVII & \aDepPncVIII & \aDepPnc \tabularnewline
-ROOT  & \aDepRootAll & \aDepRootI & \aDepRootII & \aDepRootIII & \aDepRootIV & \aDepRootV & \aDepRootVI & \aDepRootVII & \aDepRootVIII & root \tabularnewline
-sb  & \aDepSbAll & \aDepSbI & \aDepSbII & \aDepSbIII & \aDepSbIV & \aDepSbV & \aDepSbVI & \aDepSbVII & \aDepSbVIII & \aDepSb \tabularnewline
-svp  & \aDepSvpAll & \aDepSvpI & \aDepSvpII & \aDepSvpIII & \aDepSvpIV & \aDepSvpV & \aDepSvpVI & \aDepSvpVII & \aDepSvpVIII & separable verb prefix \tabularnewline
+cd & \aDepCd & \aDepCdAll & \aDepCdI & \aDepCdII & \aDepCdIII & \aDepCdIV & \aDepCdV & \aDepCdVI & \aDepCdVII & \aDepCdVIII \tabularnewline
+cj & \aDepCj & \aDepCjAll & \aDepCjI & \aDepCjII & \aDepCjIII & \aDepCjIV & \aDepCjV & \aDepCjVI & \aDepCjVII & \aDepCjVIII \tabularnewline
+cp & \aDepCp & \aDepCpAll & \aDepCpI & \aDepCpII & \aDepCpIII & \aDepCpIV & \aDepCpV & \aDepCpVI & \aDepCpVII & \aDepCpVIII \tabularnewline
+da & \aDepDa & \aDepDaAll & \aDepDaI & \aDepDaII & \aDepDaIII & \aDepDaIV & \aDepDaV & \aDepDaVI & \aDepDaVII & \aDepDaVIII \tabularnewline
+ju & \aDepJu & \aDepJuAll & \aDepJuI & \aDepJuII & \aDepJuIII & \aDepJuIV & \aDepJuV & \aDepJuVI & \aDepJuVII & \aDepJuVIII \tabularnewline
+mnr & \aDepMnr & \aDepMnrAll & \aDepMnrI & \aDepMnrII & \aDepMnrIII & \aDepMnrIV & \aDepMnrV & \aDepMnrVI & \aDepMnrVII & \aDepMnrVIII \tabularnewline
+Mmo & \aDepMo & \aDepMoAll & \aDepMoI & \aDepMoII & \aDepMoIII & \aDepMoIV & \aDepMoV & \aDepMoVI & \aDepMoVII & \aDepMoVIII \tabularnewline
+nk & \aDepNk & \aDepNkAll & \aDepNkI & \aDepNkII & \aDepNkIII & \aDepNkIV & \aDepNkV & \aDepNkVI & \aDepNkVII & \aDepNkVIII \tabularnewline
+oa & \aDepOa & \aDepOaAll & \aDepOaI & \aDepOaII & \aDepOaIII & \aDepOaIV & \aDepOaV & \aDepOaVI & \aDepOaVII & \aDepOaVIII \tabularnewline
+oc & \aDepOc & \aDepOcAll & \aDepOcI & \aDepOcII & \aDepOcIII & \aDepOcIV & \aDepOcV & \aDepOcVI & \aDepOcVII & \aDepOcVIII \tabularnewline
+pd & \aDepPd & \aDepPdAll & \aDepPdI & \aDepPdII & \aDepPdIII & \aDepPdIV & \aDepPdV & \aDepPdVI & \aDepPdVII & \aDepPdVIII \tabularnewline
+pnc & \aDepPnc & \aDepPncAll & \aDepPncI & \aDepPncII & \aDepPncIII & \aDepPncIV & \aDepPncV & \aDepPncVI & \aDepPncVII & \aDepPncVIII \tabularnewline
+ROOT & root of sentence & \aDepRootAll & \aDepRootI & \aDepRootII & \aDepRootIII & \aDepRootIV & \aDepRootV & \aDepRootVI & \aDepRootVII & \aDepRootVIII \tabularnewline
+sb & \aDepSb & \aDepSbAll & \aDepSbI & \aDepSbII & \aDepSbIII & \aDepSbIV & \aDepSbV & \aDepSbVI & \aDepSbVII & \aDepSbVIII \tabularnewline
+svp & separable verb prefix & \aDepSvpAll & \aDepSvpI & \aDepSvpII & \aDepSvpIII & \aDepSvpIV & \aDepSvpV & \aDepSvpVI & \aDepSvpVII & \aDepSvpVIII \tabularnewline
 \bottomrule
@@
 \toprule
-\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} &     \textbf{examples}\\
+\textbf{category} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
-body & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII & back, hip, shoulder; jacket, dress, shirt \tabularnewline
-bodypart & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII & arm, finger, leg, toe \tabularnewline
-face  & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII & face, ear, nose, mouth \tabularnewline
-female  & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII & nurse, mother, woman \tabularnewline
-females  & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII & women \tabularnewline
-fname  & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII & Jenny \tabularnewline
-furniture  & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII & bench, bed, table, chair \tabularnewline
-geo  & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII & building, tree, street, alley, meadow, cornfield, river \tabularnewline
-geo-room  & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII & living room; wall, door, window, floor, turf \tabularnewline
-head  & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII & head, hair, ear, neck, helmet \tabularnewline
-male  & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII & man, father, soldier \tabularnewline
-males  & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII & boys, opponents \tabularnewline
-mname  & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII & Bubba, Kennedy \tabularnewline
-object  & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII & telephone, car \tabularnewline
-objects  & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII & wheels, photos \tabularnewline
-persons  & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII & hippies, patients \tabularnewline
-setting\_new  & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII & on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
-setting\_rec  & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII & at the ``bus stop'' \tabularnewline
-++  & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
+body & back, hip, shoulder; jacket, dress, shirt & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII \tabularnewline
+bodypart  & arm, finger, leg, toe & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII\tabularnewline
+face & face, ear, nose, mouth & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII \tabularnewline
+female & nurse, mother, woman & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII \tabularnewline
+females & women & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII \tabularnewline
+fname & Jenny & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII \tabularnewline
+furniture & bench, bed, table, chair & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII \tabularnewline
+geo & building, tree, street, alley, meadow, cornfield, river & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII \tabularnewline
+geo-room & living room; wall, door, window, floor, turf & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII \tabularnewline
+head & head, hair, ear, neck, helmet & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII \tabularnewline
+male & man, father, soldier & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII \tabularnewline
+males & boys, opponents & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII \tabularnewline
+mname & Bubba, Kennedy & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII \tabularnewline
+object & telephone, car & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII \tabularnewline
+objects & wheels, photos & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII \tabularnewline
+persons & hippies, patients & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII \tabularnewline
+setting\_new & on a ``bridge'', on an ``alley'', on ``campus'' & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII \tabularnewline
+setting\_rec & at the ``bus stop'' & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII \tabularnewline
+++ &  in the ``evening'', it's ``daytime'', ``later'' & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII \tabularnewline
 \bottomrule
@@
 \toprule
-\textbf{no} & \textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} & \textbf{description}\\
+\textbf{no} & \textbf{name} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
-1 & adja  & \rAdjaAll & \rAdjaI & \rAdjaII & \rAdjaIII & \rAdjaIV & \rAdjaV & \rAdjaVI & \rAdjaVII & \rAdjaVIII & \aTagAdja \tabularnewline
-2 & adjd  & \rAdjdAll & \rAdjdI & \rAdjdII & \rAdjdIII & \rAdjdIV & \rAdjdV & \rAdjdVI & \rAdjdVII & \rAdjdVIII & \aTagAdjd \tabularnewline
-3 & adv  & \rAdvAll & \rAdvI & \rAdvII & \rAdvIII & \rAdvIV & \rAdvV & \rAdvVI & \rAdvVII & \rAdvVIII & \aTagAdv \tabularnewline
-4 & appr  & \rApprAll & \rApprI & \rApprII & \rApprIII & \rApprIV & \rApprV & \rApprVI & \rApprVII & \rApprVIII & \aTagAppr \tabularnewline
-5 & apprart  & \rApprartAll & \rApprartI & \rApprartII & \rApprartIII & \rApprartIV & \rApprartV & \rApprartVI & \rApprartVII & \rApprartVIII & preposition with article \tabularnewline
-6 & art  & \rArtAll & \rArtI & \rArtII & \rArtIII & \rArtIV & \rArtV & \rArtVI & \rArtVII & \rArtVIII & \aTagArt \tabularnewline
-7 & kon  & \rKonAll & \rKonI & \rKonII & \rKonIII & \rKonIV & \rKonV & \rKonVI & \rKonVII & \rKonVIII & \aTagKon \tabularnewline
-8 & ne  & \rNeAll & \rNeI & \rNeII & \rNeIII & \rNeIV & \rNeV & \rNeVI & \rNeVII & \rNeVIII & \aTagNe \tabularnewline
-9 & nn  & \rNnAll & \rNnI & \rNnII & \rNnIII & \rNnIV & \rNnV & \rNnVI & \rNnVII & \rNnVIII & \aTagNn \tabularnewline
-10 & pds  & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII & substituting demonstrative pronoun \tabularnewline
-11 & pis  & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII & substituting indefinite pronou \tabularnewline
-12 & pper  & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII & \aTagPper \tabularnewline
-13 & pposat & \rPposatAll & \rPposatI & \rPposatII & \rPposatIII & \rPposatIV & \rPposatV & \rPposatVI & \rPposatVII & \rPposatVIII & \aTagPposat \tabularnewline
-14 & prf  & \rPrfAll & \rPrfI & \rPrfII & \rPrfIII & \rPrfIV & \rPrfV & \rPrfVI & \rPrfVII & \rPrfVIII & reflexive personal pronoun \tabularnewline
-15 & ptkvz  & \rPtkvzAll & \rPtkvzI & \rPtkvzII & \rPtkvzIII & \rPtkvzIV & \rPtkvzV & \rPtkvzVI & \rPtkvzVII & \rPtkvzVIII & \aTagPtkvz \tabularnewline
-16 & vafin  & \rVafinAll & \rVafinI & \rVafinII & \rVafinIII & \rVafinIV & \rVafinV & \rVafinVI & \rVafinVII & \rVafinVIII & \aTagVafin \tabularnewline
-17 & vmfin  & \rVmfinAll & \rVmfinI & \rVmfinII & \rVmfinIII & \rVmfinIV & \rVmfinV & \rVmfinVI & \rVmfinVII & \rVmfinVIII & finite verb, modal \tabularnewline
-18 & vvfin  & \rVvfinAll & \rVvfinI & \rVvfinII & \rVvfinIII & \rVvfinIV & \rVvfinV & \rVvfinVI & \rVvfinVII & \rVvfinVIII & \aTagVvfin \tabularnewline
-19 & vvinf  & \rVvinfAll & \rVvinfI & \rVvinfII & \rVvinfIII & \rVvinfIV & \rVvinfV & \rVvinfVI & \rVvinfVII & \rVvinfVIII & \aTagVvinf \tabularnewline
-20 & vvpp  & \rVvppAll & \rVvppI & \rVvppII & \rVvppIII & \rVvppIV & \rVvppV & \rVvppVI & \rVvppVII & \rVvppVIII & \aTagVvpp \tabularnewline
-21 & tag\_other  & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII & all other TAG categories \tabularnewline
-22 & sentence  & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII & complete grammatical sentences \tabularnewline
-23 & phones  & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII & top 80 phonemes \tabularnewline
-24 & no-sp  & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII & no speech (``soundscape'') \tabularnewline
-25 & fg\_ad\_lrdiff  & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII & left-right volume difference \tabularnewline
-26 & fg\_ad\_rms  & \rFgadrmsAll & \rFgadrmsI & \rFgadrmsII & \rFgadrmsIII & \rFgadrmsIV & \rFgadrmsV & \rFgadrmsVI & \rFgadrmsVII & \rFgadrmsVIII & root mean square \tabularnewline
+1 & adja & \aTagAdja & \rAdjaAll & \rAdjaI & \rAdjaII & \rAdjaIII & \rAdjaIV & \rAdjaV & \rAdjaVI & \rAdjaVII & \rAdjaVIII \tabularnewline
+2 & adjd & \aTagAdjd & \rAdjdAll & \rAdjdI & \rAdjdII & \rAdjdIII & \rAdjdIV & \rAdjdV & \rAdjdVI & \rAdjdVII & \rAdjdVIII \tabularnewline
+3 & adv & \aTagAdv & \rAdvAll & \rAdvI & \rAdvII & \rAdvIII & \rAdvIV & \rAdvV & \rAdvVI & \rAdvVII & \rAdvVIII \tabularnewline
+4 & appr & \aTagAppr & \rApprAll & \rApprI & \rApprII & \rApprIII & \rApprIV & \rApprV & \rApprVI & \rApprVII & \rApprVIII \tabularnewline
+5 & apprart & preposition with article & \rApprartAll & \rApprartI & \rApprartII & \rApprartIII & \rApprartIV & \rApprartV & \rApprartVI & \rApprartVII & \rApprartVIII \tabularnewline
+6 & art & \aTagArt & \rArtAll & \rArtI & \rArtII & \rArtIII & \rArtIV & \rArtV & \rArtVI & \rArtVII & \rArtVIII \tabularnewline
+7 & kon & \aTagKon & \rKonAll & \rKonI & \rKonII & \rKonIII & \rKonIV & \rKonV & \rKonVI & \rKonVII & \rKonVIII \tabularnewline
+8 & ne & \aTagNe & \rNeAll & \rNeI & \rNeII & \rNeIII & \rNeIV & \rNeV & \rNeVI & \rNeVII & \rNeVIII \tabularnewline
+9 & nn & \aTagNn & \rNnAll & \rNnI & \rNnII & \rNnIII & \rNnIV & \rNnV & \rNnVI & \rNnVII & \rNnVIII \tabularnewline
+10 & pds & substituting demonstrative pronoun & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII \tabularnewline
+11 & pis & substituting indefinite pronoun & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII \tabularnewline
+12 & pper & \aTagPper & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII \tabularnewline
+13 & pposat & \aTagPposat & \rPposatAll & \rPposatI & \rPposatII & \rPposatIII & \rPposatIV & \rPposatV & \rPposatVI & \rPposatVII & \rPposatVIII \tabularnewline
+14 & prf & reflexive personal pronoun & \rPrfAll & \rPrfI & \rPrfII & \rPrfIII & \rPrfIV & \rPrfV & \rPrfVI & \rPrfVII & \rPrfVIII \tabularnewline
+15 & ptkvz & \aTagPtkvz & \rPtkvzAll & \rPtkvzI & \rPtkvzII & \rPtkvzIII & \rPtkvzIV & \rPtkvzV & \rPtkvzVI & \rPtkvzVII & \rPtkvzVIII \tabularnewline
+16 & vafin & \aTagVafin & \rVafinAll & \rVafinI & \rVafinII & \rVafinIII & \rVafinIV & \rVafinV & \rVafinVI & \rVafinVII & \rVafinVIII \tabularnewline
+17 & vmfin & finite verb, modal & \rVmfinAll & \rVmfinI & \rVmfinII & \rVmfinIII & \rVmfinIV & \rVmfinV & \rVmfinVI & \rVmfinVII & \rVmfinVIII \tabularnewline
+18 & vvfin & \aTagVvfin & \rVvfinAll & \rVvfinI & \rVvfinII & \rVvfinIII & \rVvfinIV & \rVvfinV & \rVvfinVI & \rVvfinVII & \rVvfinVIII \tabularnewline
+19 & vvinf & \aTagVvinf & \rVvinfAll & \rVvinfI & \rVvinfII & \rVvinfIII & \rVvinfIV & \rVvinfV & \rVvinfVI & \rVvinfVII & \rVvinfVIII \tabularnewline
+20 & vvpp & \aTagVvpp & \rVvppAll & \rVvppI & \rVvppII & \rVvppIII & \rVvppIV & \rVvppV & \rVvppVI & \rVvppVII & \rVvppVIII \tabularnewline
+21 & tag\_other & all other TAG categories & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII \tabularnewline
+22 & sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
+23 & phones & top 80 phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
+24 & no-sp & no speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
+25 & fg\_ad\_lrdiff & left-right volume difference & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII \tabularnewline
+26 & fg\_ad\_rms & root mean square & \rFgadrmsAll & \rFgadrmsI & \rFgadrmsII & \rFgadrmsIII & \rFgadrmsIV & \rFgadrmsV & \rFgadrmsVI & \rFgadrmsVII & \rFgadrmsVIII \tabularnewline
 \bottomrule

### 2020-04-06 paper/main.tex
minor formatting improvements

@@
 Kommt ganz am Ende;
+Intro, Method, Results, Discussion;
 hier ggf. bereits Praat erwähnen;
@@
 \caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments. Words include \aPosNonspeechAll\space non-speech vocalizations.}
-\label{tab:example}
+\label{tab:overview}
 \begin{tabular}{llllllllll}
@@
 \caption{Sentences spoken by top 10 of 97 (identified) speakers sorted alphabetically. Narrator only in audio-description.}
-\label{tab:example}
+\label{tab:speakers}
 \begin{tabular}{llllllllll}
@@
 \caption{Simple part of speech tagging (POS). All 15 categories sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually added.}
-\label{tab:example}
+\label{tab:pos}
 \begin{tabular}{lllllllllll}
@@
 \caption{Detailed part of speech tagging (TAG). The top 15 of 43 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
-\label{tab:example}
+\label{tab:tag}
 \begin{tabular}{lllllllllll}
@@
 \caption{Syntactic dependencies (DEP). The top 15 of 37 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
-\label{tab:example}
+\label{tab:dep}
 \begin{tabular}{lllllllllll}
@@
 der Zeit.}
-\label{tab:example}
+\label{tab:descr-nouns}
 \begin{tabular}{lllllllllll}
@@
 The other categories were build\dots}
-\label{tab:example}
+\label{tab:regressors}
 \begin{tabular}{llllllllllll}
@@
 Die unterschiedlichen Farben in den der Schriften kann man noch (wie?) sinnvoll ändern.}
-  \label{fig:correlation}
+\label{fig:reg-corr}
 \end{figure*}
@@
     \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE1: all 21 tag-related regressors > no speech.}
+\label{tab:cope1}
 \begin{tabular}{rrrrrrrrrrp{3cm}}
@@
 \end{tabular}
-\label{tab:cope1}
 \end{table*}
@@
 \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE3: proper nouns (``ne'') > coordinate conjunctions (``kon'').}
+\label{tab:cope3}
 \begin{tabular}{rrrrrrrrrrp{3cm}}
@@
 \end{tabular}
-\label{tab:cope3}
+
 \end{table*}
@@
     \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE5: nouns (``nn'') > coordinate conjunctions (``kon'').}
+\label{tab:cope5}
 \begin{tabular}{rrrrrrrrrrp{3cm}}
@@
 \end{tabular}
-\label{tab:cope5}
 \end{table*}
@@
 % “hardcoded” Zitationen sind aber noch im laufenden Text.
-We annotated speech in the slightly shortened "research cut" of the movie
+We annotated speech in the slightly shortened ``research cut'' of the movie
 \citep{hanke2016simultaneous} and its temporally aligned audio-description
@@
 off-screen voice of the main character Forrest Gump.
-In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content.
+In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content
 \subsection*{Annotation procedure}
@@
 complete sentences of the orthographic transcription were copied into the
-annotation. In a third step, the name of the speaker was added for every sentence.
+annotation (s.
+table \ref{tab:overview} for an overview of the annotation's contenct).
+In a third step, the name of the speaker was added for every sentence (s.
+table \ref{tab:speakers} for the most often occurring speakers).
 During every new step results from all previous steps were checked again for errors and corrected.
@@
 cinematographic scene's environment, inherent objects, persons, and a person's
-appearance. A preliminary annotation according to the rules (s. table XY) was done by one person and corrected in several runs by the author.
+appearance.
+A preliminary annotation according to the rules (s.
+ist jetzt in der obigen Tabelle aus Platzgründen nicht mehr drin; in dieser,\ref{tab:descr-nouns}, einer neuen Tabelle oder im laufenden Text [wird viel Text] bringen) was done by one person and corrected in several runs by the author.
 
@@
 a tab separated file in accordance with the brain imaging data structure
-(\href{https://bids.neuroimaging.io/}){BIDS}\citep{gorgolewski2016bids}). Non-speech vocalizations were dropped from the sentences before analysis.
+(\href{https://bids.neuroimaging.io/}{BIDS}\citep{gorgolewski2016bids}). Non-speech vocalizations were dropped from the sentences before analysis.
 % BIDS stuff runter zu "Dataset content"?
@@
 % 1st lvl
-At the first level analysing each segment for each subject individually, we defined regressors based on information drawn from the annotation.
-The top 20 detailed tags by count (“nn” with N=2620 to “prf” with N=157) were modelled as such from the onset to offset of each word.
-The remaining tags were pooled to a single regressor (“tag\_other” ; N=1123).
-The top 80 phonemes (“n” with n=6053 to “IY1” with N=32) were pooled to the regressor “phonemes” (N=65251).
-The ends of (complete) grammatical sentences were used as the onset of events, abitrarily lasting 0.2s, for the regressors “sentence” (N=1651).
-A “no-speech” regressor (“no-sp”; N=264) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech.
+At the first level analysing each segment for each subject individually, we defined 26 regressors (s. table \ref{tab:regressors})
+ based on information drawn from the annotation.
+The top 20 detailed tags by count (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word.
+The remaining tags were pooled to a single regressor (``tag\_other``; N=\rTagotherAll).
+The top 80 phonemes (``n'' with n=6053 to ``IY1'' with N=32) were pooled to the regressor ``phonemes'' (N=\rPhonesAll).
+The ends of (complete) grammatical sentences were used as the onset of events, abitrarily lasting 0.2s, for the regressors ``sentence'' (N=\rSentenceAll).
+A ``no-speech'' regressor (``no-sp''; N=\rNospAll) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech.
 Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of sentences/words and to each other onset of the no-speech condition (s.
@@
 Two regressors reflecting auditory (low-level) features (left-right loudness/volume/amplitude difference; root mean squared amplitude) aligned to the frame rate of (40 ms) were modelled to reduce nuisance effects.
-Those 26 regressors were convolved with FSL's “Double-Gamma HRF” as a model of the hemodynamic response function.
+Hier (und das ggf auch mehr auf Korrelation der Regressoren eingehen. \ref{fig:reg-corr}).
+Those 26 regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function.
 Temporal derivatives were also included in the design matrix, and it was subjected to the same temporal filtering as the BOLD time series.
 Finally, six motion parameters were used as additional nuisance regressors.
-The following six t-contrasts were defined: 1) all 21 tag-related regressors > no speech; 2) no speech > all 21 tag-related regressors; 3) proper nouns (“ne”; N=1012) > coordinate conjunctions (“kon”; N=475); 4) coordinate conjunctions > proper nouns; 5) nouns (“nn”) > coordinate conjunctions, and 6) coordinate conjunctions > nouns.
+The following six t-contrasts were defined: 1) all 21 tag-related regressors > no-speech; 2) no-speech > all 21 tag-related regressors; 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll); 4) coordinate conjunctions > proper nouns; 5) nouns (``nn'') > coordinate conjunctions, and 6) coordinate conjunctions > nouns.
 The first level analysis that fitted each voxel’s time course separately for each subject was performed in functional space preserving the orientation of the EPI images [richtig?].
@@
 % results
-% tabelle mit Cluster-Nr., nr. of voxels, max loc (MNI) x, y, z, mean, std; center of mass, structure
-% figure
+% von Interpretation klar(er) getrennt halten
+Results: The first contrast that contrasted words to moments where no speech is audible in the audio-description (all 21 tag-related regressors > no-speech) shows\dots;
+left lateralization (bigger cluster left in BA XY => Broca)
+The contrasts proper nouns > coordinate conjunctions and proper nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.
 
 % discussion
+% careful what you pretend, check & cite (again)
+% \citep{binder2009semantic, dewitt2012phoneme}.
+Discussion: alles total awesome; Correlation der (konvolvierten Regressoren) is gut (s. figure \ref{fig:reg-corr}; Ergebnisse ergeben Sinn -> benutzt die Anno for awesome research
 
@@
 \hline
+\label{tab:descr-nouns-old}
 \end{tabular}

### 2020-04-06 paper/main.tex
revise table captions

@@
-% ToDo:
-% Abstract
-% Tabellen
-% Dataset wo auch immer (ohne Stimuli) hochladen
-
 % For more detailed article preparation guidelines, please see:
@@
 \begin{table*}[t]
-\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments. Words include \aPosNonspeechAll\space non-speech vocalizations.}
+\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments.
+The label ``Sentences''' comprises complete grammatical sentences (i.e.
+having a subject and a predicate, and additionally marked with a full stop in the annotation).
+The  ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g.
+``ha, ha, ha'') or in isolation (e.g.
+``ha'', at time points when speakers rapidly switch).
+The label ``Words'' comprises every single word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
 \label{tab:overview}
@@
 \toprule
-\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
+\textbf{label} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
 \midrule
@@
 
+% bei ein paar Namen bin ich ggf. von Labs abgewichen (genauer identifiziert, ggf. kleine Fehler korrigiert. Ist dann aber nur bei Personen, die 1-2x mit 1-2 Sätzen auftauchen.
 \begin{table*}[t]
-\caption{Sentences spoken by top 10 of 97 (identified) speakers sorted alphabetically. Narrator only in audio-description.}
+\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically.
+The narrator only occurrs in the audio-description of the movie.
+Shown names are identical to the names used in \citep{labs2015portrayed}.
+Overall 97 persons were identified.}
 \label{tab:speakers}
@@
 \begin{table*}[t]
-\caption{Simple part of speech tagging (POS). All 15 categories sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually added.}
+\caption{Simple part of speech tagging (POS). All 15 labels sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually identified.}
 \label{tab:pos}
@@
 \toprule
-\textbf{category} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
@@
 \begin{table*}[t]
-\caption{Detailed part of speech tagging (TAG). The top 15 of 43 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
+\caption{Detailed part of speech tagging (TAG). The 15 most often occurring labels (overall 43 labels) sorted alphabetically. Descriptions were taken from spaCy.explain().}
 \label{tab:tag}
@@
 \begin{table*}[t]
-\caption{Syntactic dependencies (DEP). The top 15 of 37 categories sorted alphabetically. Descriptions were taken from spaCy.explain().}
+\caption{Syntactic dependencies (DEP). The 15 most often occuring labels (overall 37 labels) sorted alphabetically. Descriptions were taken from spaCy.explain().}
 \label{tab:dep}
@@
 mnr & \aDepMnr & \aDepMnrAll & \aDepMnrI & \aDepMnrII & \aDepMnrIII & \aDepMnrIV & \aDepMnrV & \aDepMnrVI & \aDepMnrVII & \aDepMnrVIII \tabularnewline
-Mmo & \aDepMo & \aDepMoAll & \aDepMoI & \aDepMoII & \aDepMoIII & \aDepMoIV & \aDepMoV & \aDepMoVI & \aDepMoVII & \aDepMoVIII \tabularnewline
+mo & \aDepMo & \aDepMoAll & \aDepMoI & \aDepMoII & \aDepMoIII & \aDepMoIV & \aDepMoV & \aDepMoVI & \aDepMoVII & \aDepMoVIII \tabularnewline
 nk & \aDepNk & \aDepNkAll & \aDepNkI & \aDepNkII & \aDepNkIII & \aDepNkIV & \aDepNkV & \aDepNkVI & \aDepNkVII & \aDepNkVIII \tabularnewline
@@
 \toprule
-\textbf{category} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\textbf{label} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
@@
 \begin{table*}[t]
-\caption{Overview of the 26 REGRESSORS used for the validation analysis.
-The top 20 categories of the detailed part-of speech tagging were used as such.
-Descriptions were taken from spaCy.explain().
-All others tags were pooled to ``tag\_other''.
-The other categories were build\dots}
+    \caption{Overview of the 26 regressors for the validation analysis.
+The first column contains the number of the regressor in the design file of FSL \citep{smith2004fsl}.
+The 20 most often occuring labels from the detailed part-of speech tagging were used as such.
+Words belonging to all other labels were pooled to ``tag\_other''.
+The regressor ``sentence'' contains the end of complete grammatical sentences.
+The regressor ``phones'' contains the 80 most often occuring phonemes (``n'' with N=6053 to ``IY1'' with N=32).
+The regressor ``no-sp'' represents moments when no speech was audible.
+''fg\_ad\_lrdiff (left-right volume difference) and ``fg\_ad\_rms'' (root mean square loudness) represent low-level auditory nuissance regressors comprising one event for every movie frame (40ms).}
 \label{tab:regressors}
@@
 \toprule
-\textbf{no} & \textbf{name} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\textbf{no} & \textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
@@
 21 & tag\_other & all other TAG categories & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII \tabularnewline
+\cline{1-12}
 22 & sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
-23 & phones & top 80 phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
-24 & no-sp & no speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
+23 & phones & 80 most often occuring phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
+24 & no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
+\cline{1-12}
 25 & fg\_ad\_lrdiff & left-right volume difference & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII \tabularnewline
@@
   \caption{Pearson correlation coefficients of the 26 regressors used in the analysis to validate the annotation.
-Regressors were convolved with FSL's “Double-Gamma HRF” as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation.
-NOTE: Bisher werden pdf figures.
-Die unterschiedlichen Farben in den der Schriften kann man noch (wie?) sinnvoll ändern.}
+Regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation.}
 \label{fig:reg-corr}
@@
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE1: all 21 tag-related regressors > no speech.}
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast words > no-speech.}
 \label{tab:cope1}
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE3: proper nouns (``ne'') > coordinate conjunctions (``kon'').}
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').}
 \label{tab:cope3}
@@
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE5: nouns (``nn'') > coordinate conjunctions (``kon'').}
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon'').}
 \label{tab:cope5}
@@
 annotation (s.
-table \ref{tab:overview} for an overview of the annotation's contenct).
+table \ref{tab:overview} for an overview of the annotation's content).
 In a third step, the name of the speaker was added for every sentence (s.
@@
 % s. dictionaries oben in add_part-of-speech-tagging2textgrid.py
+
 \subsubsection*{Start (\texttt{start})}
 the onset of the sentences, word or phoneme provided in seconds of stimulus onset.
+
 \subsubsection*{Duration (\texttt{end})}
 the duration of the sentences, word or phoneme provided in seconds.
+
 \subsubsection*{Speaker identity (\texttt{person})}
-name of the persons that speaks the sentence, word, phoneme.
+name of the persons that speaks the sentence, word or phoneme (s. table \ref{tab:speakers}).
+
 % einige Eigennamen (NE/NN) wurden automatisch korrigiert, weil das Sprachmodell
@@
 This column contains tags for whole sentences ("SENTENCE"), phonemes ("PHONEME") and non-speech vocalizations (NONSPEECH).
-For single words, it contains a simple part-of-speech tagging (grammatical tagging; word-category disambiguation) taking the relationship with adjacent and related words in the same sentence into account.
+For single words, it contains a simple part-of-speech tagging (grammatical tagging; word-category disambiguation) taking the relationship with adjacent and related words in the same sentence into account (s.
+table \ref{tab:pos}).
 This simple part-of-speech tagging tags follow the \href{https://universaldependencies.org}{Universal Dependencies} v2 POS tag set.
@@
 \subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
-A detailed part-of-speech tagging following the TIGER Treebank annotation scheme \citep{brants2004tiger} which is based on the \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset} \citep{schiller1999stts}.
+A detailed part-of-speech tagging following the TIGER Treebank annotation scheme \citep{brants2004tiger}(s.
+table \ref{tab:tag}) which is based on the \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset} \citep{schiller1999stts}.
+
 \subsubsection*{Syntactic dependency (\texttt{dep})}
 A word's column entry provides information about a word's syntactic dependency. Information following the TIGER Treebank annotation scheme \citep{brants2004tiger} is given in the format:
-"arc label;word's head;word's child1, word's child2, ..." where the "arc label" describes the type of syntactic relation that connects a "child" (the single word) to its "head".
+"arc label;word's head;word's child1, word's child2, ..." where the "arc label" (s.
+table \ref{tab:dep}) describes the type of syntactic relation that connects a "child" (the single word) to its "head".
+
 \subsubsection*{Lemmatization (\texttt{lemma})}
 For single words, the base form (root) of the word
+
 \subsubsection*{Common Word (\texttt{stop})}
 For single words, this column provides information if the word is part of a stop list, hence one of the most common words in the German language ("True") or not ('"False")?
+
 \subsubsection*{Narrator's descriptive nouns (\texttt{descr})}
@@
 Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
-\paragraph*{Narrator's descriptive nouns}
+
 \subsubsection*{Word embedding (semantic similarity) (\texttt{vector})}
@@
  based on information drawn from the annotation.
-The top 20 detailed tags by count (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word.
+The 20 most often occuring detailed tag labels (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word.
 The remaining tags were pooled to a single regressor (``tag\_other``; N=\rTagotherAll).
@@
 Finally, six motion parameters were used as additional nuisance regressors.
-The following six t-contrasts were defined: 1) all 21 tag-related regressors > no-speech; 2) no-speech > all 21 tag-related regressors; 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll); 4) coordinate conjunctions > proper nouns; 5) nouns (``nn'') > coordinate conjunctions, and 6) coordinate conjunctions > nouns.
+The following six t-contrasts were defined: 1) words (21 tag-related regressors) > no-speech; 2) no-speech > all 21 tag-related regressors; 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll); 4) coordinate conjunctions > proper nouns; 5) nouns (``nn'') > coordinate conjunctions, and 6) coordinate conjunctions > nouns.
 The first level analysis that fitted each voxel’s time course separately for each subject was performed in functional space preserving the orientation of the EPI images [richtig?].

### 2020-04-07 paper/main.tex
revise cluster tables

@@
   \includegraphics[width=\linewidth]{figures/slicescolorbars}
-  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05; cluster corr.; MNI template space).}
+  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected.; MNI template space).}
   \label{fig:results}
@@
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast words > no-speech.}
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words > no-speech. Clusters sorted by voxel size.}
 \label{tab:cope1}
@@
 \toprule
-& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{5-7} \cmidrule{8-10}
-Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{4-6} \cmidrule{7-9}
+voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
 \midrule
-4 & 14990 & 0 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
-3 & 14469 & 0 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
-2 & 1971 & 2.37E-16 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
-1 & 217 & 0.00214 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
+14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
+14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
+1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
+217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
 \bottomrule
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').}
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size.}
 \label{tab:cope3}
@@
 \toprule
-& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{5-7} \cmidrule{8-10}
-Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{4-6} \cmidrule{7-9}
+voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
 \midrule
-9 & 7691 & 2.80E-45 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
-8 & 5928 & 5.97E-38 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
-7 & 479 & 1.13E-06 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
-6 & 420 & 4.65E-06 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
-5 & 407 & 6.38E-06 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
-4 & 294 & 0.000115 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
-3 & 121 & 0.0237 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
-2 & 117 & 0.0274 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
-1 & 115 & 0.0295 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
+7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
+5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
+479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
+420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
+407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
+294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
+121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
+117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
+115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
 \bottomrule
 \end{tabular}
-
 \end{table*}
@@
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon'').}
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size.}
 \label{tab:cope5}
@@
 \toprule
-& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
 \\ \cmidrule{5-7} \cmidrule{8-10}
-Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
 \midrule
-4 & 3166 & 2.79E-25 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
-3 & 1753 & 7.18E-17 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
-2 & 166 & 0.00446 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
-1 & 149 & 0.00793 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
+3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
+1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
+166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
+149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
 \bottomrule

### 2020-04-08 paper/main.tex
remove parts regarding descriptive nouns

@@
 \begin{table*}[t]
-    \caption{Narrator's descriptive nouns.
-All categories sorted alphapetically.
-Examples are given in English.
-Description (of rules) fehlt in dieser Tabelle (vgl.
-alte Tabelle auf der allerletzten Seite).
-Wird nämlich in einer Tabelle mit horizontaler Ausrichtung eng.
-Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best.
-der Zeit.}
-\label{tab:descr-nouns}
-\begin{tabular}{lllllllllll}
-\toprule
-\textbf{label} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-body & back, hip, shoulder; jacket, dress, shirt & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII \tabularnewline
-bodypart  & arm, finger, leg, toe & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII\tabularnewline
-face & face, ear, nose, mouth & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII \tabularnewline
-female & nurse, mother, woman & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII \tabularnewline
-females & women & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII \tabularnewline
-fname & Jenny & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII \tabularnewline
-furniture & bench, bed, table, chair & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII \tabularnewline
-geo & building, tree, street, alley, meadow, cornfield, river & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII \tabularnewline
-geo-room & living room; wall, door, window, floor, turf & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII \tabularnewline
-head & head, hair, ear, neck, helmet & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII \tabularnewline
-male & man, father, soldier & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII \tabularnewline
-males & boys, opponents & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII \tabularnewline
-mname & Bubba, Kennedy & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII \tabularnewline
-object & telephone, car & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII \tabularnewline
-objects & wheels, photos & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII \tabularnewline
-persons & hippies, patients & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII \tabularnewline
-setting\_new & on a ``bridge'', on an ``alley'', on ``campus'' & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII \tabularnewline
-setting\_rec & at the ``bus stop'' & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII \tabularnewline
-++ &  in the ``evening'', it's ``daytime'', ``later'' & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
     \caption{Overview of the 26 regressors for the validation analysis.
@@
 Because naturalistic stimuli are multi-dimensional and their temporal structure
-is (usually) unknown, data-driven methods like intersubject correlation
+is usually unknown, data-driven methods like intersubject correlation
 (ISC)\citep{hasson2004intersubject} or independent component analysis
@@
 sentences, single words, and phonemes spoken in the movie Forrest Gump (R.
-Zemeckis, Paramount Pictures, 1994) \citep{ForrestGumpMovie}. fMRI data of
-participants watching the audio-visual movie \citep{hanke2016simultaneous} and
-it's audio-description for visually impaired persons \citep{hanke2014audiomovie}
-are the core data of the publicly available \textit{studyforrest} dataset
-(\href{www.studyforrest.org}{studyforrest.org}). Additional fMRI data
-\citep{sengupta2016extension} include retinotopic mappings and localization of
-higher visual areas of the same participants.
+Zemeckis, Paramount Pictures, 1994) \citep{ForrestGumpMovie} and its corresponding audio-description for visually impaired persons.
+fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie}
+are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
+Additional fMRI data include retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.
 % paper regarding mention musical not mentioned
@@
 The current annotation facilitates modelling of hemodynamic brain responses
-correlating with speech-related events in the movie and audio-description.
-Further, it extends already available annotations of portrayed emotions
-\citep{labs2015portrayed} and perceived emtions
-\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}.
-All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional
-confound measures describing key properties of major building blocks of the stimulus.
+correlating with speech-related events in the two stimuli.
+Further, it extends already available annotations of portrayed emotions \citep{labs2015portrayed} and perceived emtions \citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}.
+All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional confound measures describing key properties of major building blocks of the stimulus.
 
@@
 % “hardcoded” Zitationen sind aber noch im laufenden Text.
-We annotated speech in the slightly shortened ``research cut'' of the movie
-\citep{hanke2016simultaneous} and its temporally aligned audio-description
-\citep{hanke2014audiomovie}. For the movie stimulus, we used the audio track of
+We annotated speech in the slightly shortened ``research cut'' of the movie \citep{hanke2016simultaneous} and its temporally aligned audio-description \citep{hanke2014audiomovie}.
+For the movie stimulus, we used the audio track of
 the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video,
@@
 movie's audio-description that was broadcast as an additional audio track for
-visually impaired listeners on Swiss public television (Koop, Michalski,
-Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk,
-2009)\citep{ForrestGumpGermanAD}. The plot of the movie is already carried by an
+visually impaired listeners on Swiss public television (Koop, Michalski Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk 2009)\citep{ForrestGumpGermanAD}.
+The plot of the movie is already carried by an
 off-screen voice of the main character Forrest Gump.
@@
 (german\_audio\_description.csv) were merged and converted to Praat's
-\citep{boersma2019praat} .TextGrid format (
-\href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}). The merged transcription
-containing one onset and offset for usually a couple of sentences was opened
-along (the audio file of) the audio-description in Praat v6.0.22 for manual
-improvements: In several passes, the approximate temporal onsets and offsets
-were corrected. Intervals containing several sentences were split into intervals
-containing only one sentence. When two or more persons were speaking
-simultaneously the less dominant (background) voice was dropped. Low volume
-background speech (especially occurring during music or continuous environmental
-noise) or low volume non-speech vocalizations that are difficult to recognize by
-a regular audience were dropped, too.
+\citep{boersma2019praat} .TextGrid format (\href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}).
+The merged transcription containing one onset and offset for usually a couple of sentences was opened along (the audio file of) the audio-description in Praat v6.0.22 for manual improvements: In several passes, the approximate temporal onsets and offsets were corrected.
+Intervals containing several sentences were split into intervals containing only one sentence.
+When two or more persons were speaking simultaneously the less dominant (background) voice was dropped.
+Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations that are difficult to recognize by a regular audience were dropped, too.
 
@@
 We used the Montreal Forced Aligner v1.0.1
-\href{montrealcorpustools.github.io/Montreal-Forced-Aligner}{montrealcorpustools.github.io/Montreal-Forced-Aligner}\citep{mcauliffe2017montreal};to
-algorithmically identify the onset and offset of each word and phoneme embedded
+\href{montrealcorpustools.github.io/Montreal-Forced-Aligner}{montrealcorpustools.github.io/Montreal-Forced-Aligner}\citep{mcauliffe2017montreal} to algorithmically identify the onset and offset of each word and phoneme embedded
 in the transcribed sentences. To enable the aligner to look up the pronunciation
 of every word, we chose a German pronunciation dictionary
-\href{https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}{raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}
-provided by Prosodylab (\href{http://prosodylab.org}{prosodylab.org}) that uses
-the Prosodylab PhoneSet. The dictionary was manually updated with movie-specific
-German words. The pronunciation of English words occurring in the otherwise
-German audio track was taken from an English pronunciation dictionary
-(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.
+\href{https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}{raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict} provided by Prosodylab (\href{http://prosodylab.org}{prosodylab.org}) that uses the Prosodylab PhoneSet.
+The dictionary was manually updated with movie-specific German words.
+The pronunciation of English words occurring in the otherwise German audio track was taken from an English pronunciation dictionary (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.
 
@@
 % kommt selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.
-The audio file was converted from .FLAC to .WAV via ffmpeg v4.1.4
-(\href{www.ffmpeg.org}{ffmpeg.org}) to meet the aligner's requirements. This
-.WAV file, the transcription of sentences, and the updated dictionary were
-submitted to the aligner that first trained an acoustic model on the data and
-then performed the alignment. In a first step, the resulting .TextGrid file that
-contains onsets and offsets of words and phonemes was opened in Praat to check
-and correct the automatic alignment. In several passes, words [and their
-corresponding phonemes] on which the automatic alignment performed moderately
-were corrected. Some (low volume) sentences that are spoken in continuously
-noisy settings (pursuit, battle, hurricane, demonstration/rally, disco) were
-removed due to poor overall alignment performance. In a second step, the
-complete sentences of the orthographic transcription were copied into the
-annotation (s.
+The audio file was converted from .FLAC to .WAV via ffmpeg v4.1.4 (\href{www.ffmpeg.org}{ffmpeg.org}) to meet the aligner's requirements.
+This .WAV file, the transcription of sentences, and the updated dictionary were submitted to the aligner that first trained an acoustic model on the data and then performed the alignment.
+In a first step, the resulting .TextGrid file that contains onsets and offsets of words and phonemes was opened in Praat to check and correct the automatic alignment.
+In several passes, words [and their corresponding phonemes] on which the automatic alignment performed moderately were corrected.
+Some (low volume) sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, demonstration/rally, disco) were removed due to poor overall alignment performance.
+In a second step, the complete sentences of the orthographic transcription were copied into the annotation (s.
 table \ref{tab:overview} for an overview of the annotation's content).
@@
 To automatically analyze linguistic features of words in their corresponding
-sentence, we employed the Python package spaCy v2.2.1
-(\href{https://spacy.io}{spacy.io}) and a German language model
-(de\_core\_news\_md; \href{https://spacy.io/models/de}{spacy.io/models/de})
-trained on the TIGER Treebank corpus
-(\href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}). We performed
-analyses regarding part of speech (i.e. grammatical tagging or word-category
-disambiguation), syntactic dependency, lemmatization, word embedding (i.e.
-semantic similarity), and if the word is one of the most common words of the
-German language. Results of these analyzes were added to the annotation and
-saved as .TextGrid file. This .TextGrid file was converted via python script to
-a tab separated file in accordance with the brain imaging data structure
-(\href{https://bids.neuroimaging.io/}{BIDS}\citep{gorgolewski2016bids}). Non-speech vocalizations were dropped from the sentences before analysis.
+sentence, we employed the Python package spaCy v2.2.1 (\href{https://spacy.io}{spacy.io}) and a German language model (de\_core\_news\_md; \href{https://spacy.io/models/de}{spacy.io/models/de}) trained on the TIGER Treebank corpus (\href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}).
+We performed analyses regarding part of speech (i.e.
+grammatical tagging or word-category
+disambiguation), syntactic dependency, lemmatization, word embedding (i.e.semantic similarity), and if the word is one of the most common words of the German language.
+Results of these analyzes were added to the annotation and saved as .TextGrid file.
+This .TextGrid file was converted via python script to
+a tab separated file in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}\citep{gorgolewski2016bids}).
+Non-speech vocalizations were dropped from the sentences before analysis.
 % BIDS stuff runter zu "Dataset content"?
@@
 \subsection*{Data Legend}
-% wo wurde automatisch korrigiert (e.g. NE/NN, NONSPEECH)
-% s. dictionaries oben in add_part-of-speech-tagging2textgrid.py
 
 \subsubsection*{Start (\texttt{start})}
-the onset of the sentences, word or phoneme provided in seconds of stimulus onset.
+the onset of the sentence, word or phoneme provided in seconds [ss.milliseconds] of stimulus onset.
 
 \subsubsection*{Duration (\texttt{end})}
-the duration of the sentences, word or phoneme provided in seconds.
+the duration of the sentences, word or phoneme provided in seconds [ss.milliseconds].
 
@@
 \subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
-A detailed part-of-speech tagging following the TIGER Treebank annotation scheme \citep{brants2004tiger}(s.
+For single words, a detailed part-of-speech tagging following the TIGER Treebank annotation scheme \citep{brants2004tiger}(s.
 table \ref{tab:tag}) which is based on the \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset} \citep{schiller1999stts}.
@@
 \subsubsection*{Syntactic dependency (\texttt{dep})}
-A word's column entry provides information about a word's syntactic dependency. Information following the TIGER Treebank annotation scheme \citep{brants2004tiger} is given in the format:
+For single words, this column entry provides information about a word's syntactic dependency. Information following the TIGER Treebank annotation scheme \citep{brants2004tiger} is given in the format:
 "arc label;word's head;word's child1, word's child2, ..." where the "arc label" (s.
@@
 \subsubsection*{Common Word (\texttt{stop})}
-For single words, this column provides information if the word is part of a stop list, hence one of the most common words in the German language ("True") or not ('"False")?
-
-\subsubsection*{Narrator's descriptive nouns (\texttt{descr})}
-A categorizing of nouns that serve as auditory cues about the movie's visual content.
-Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
+For single words, this column provides information if the word is part of a stop list, hence one of the most common words in the German language or not (``True'' vs. ``False'')?
 
@@
 In order to assess data quality, we investigated if contrasting speech-related events to non-speech related events lead to increased activation in areas known to be involved in semantic processing \citep{binder2009semantic, dewitt2012phoneme}.
-Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (conjunctions) lead to increased activation in congruent brain areas.
+Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (coordinate conjunctions) lead to increased activation in congruent brain areas.
 % Preprocessing
@@
 Software Library)\citep{smith2004fsl}.
-Data were temporally high-pass filtered (cut-off 150s), spatially smoothed (Gaussian kernel; 4.0 mm FWHM), and the brain was extracted from surrounding tissue [keine Plan, ob die Reihenfolge so korrek ist].
+Data were temporally high-pass filtered (cut-off 150s), spatially smoothed (Gaussian kernel; 4.0 mm FWHM), and the brain was extracted from surrounding tissue [keine Plan, ob die Reihenfolge so korrekt ist].
 A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
@@
 The remaining tags were pooled to a single regressor (``tag\_other``; N=\rTagotherAll).
-The top 80 phonemes (``n'' with n=6053 to ``IY1'' with N=32) were pooled to the regressor ``phonemes'' (N=\rPhonesAll).
+The top 80 phonemes (``n'' with n=6053 to ``IY1'' with N=32) were pooled to the regressor ``phonemes'' (N=\rPhonesAll) to be used as a nuisance regressors.
 The ends of (complete) grammatical sentences were used as the onset of events, abitrarily lasting 0.2s, for the regressors ``sentence'' (N=\rSentenceAll).
-A ``no-speech'' regressor (``no-sp''; N=\rNospAll) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no comprehensible speech.
-Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of sentences/words and to each other onset of the no-speech condition (s.
+A ``no-speech'' regressor (``no-sp''; N=\rNospAll) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no audible/comprehensible speech.
+Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of a sentence or isolated word and to each other onset of the no-speech condition (s.
 anno2events-files.py).
-A length of 0.07s was chosen for these events matching the average length of phonemes.
-Two regressors reflecting auditory (low-level) features (left-right loudness/volume/amplitude difference; root mean squared amplitude) aligned to the frame rate of (40 ms) were modelled to reduce nuisance effects.
-Hier (und das ggf auch mehr auf Korrelation der Regressoren eingehen. \ref{fig:reg-corr}).
+A length of 0.07s was chosen for the events of the no speech regressors  matching the average length of phonemes.
+Two regressors reflecting auditory (low-level) features (left-right difference in loudness and root mean squared loudness) aligned to and averaged across the length of every movie frame (40 ms) were modelled to reduce nuisance effects.
+Hier (?? und das ggf auch mehr auf Korrelation der Regressoren eingehen. \ref{fig:reg-corr}).
 Those 26 regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function.
-Temporal derivatives were also included in the design matrix, and it was subjected to the same temporal filtering as the BOLD time series.
+Temporal derivatives were also included in the design matrix.
+The design was subjected to the same temporal filtering as the BOLD time series.
 Finally, six motion parameters were used as additional nuisance regressors.
-The following six t-contrasts were defined: 1) words (21 tag-related regressors) > no-speech; 2) no-speech > all 21 tag-related regressors; 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll); 4) coordinate conjunctions > proper nouns; 5) nouns (``nn'') > coordinate conjunctions, and 6) coordinate conjunctions > nouns.
+The following six t-contrasts were defined: 1) words (i.e.
+all 21 tag-related regressors; N=15985) > no-speech; 2) no-speech > words 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll); 4) coordinate conjunctions > proper nouns; 5) nouns (``nn'') > coordinate conjunctions, and 6) coordinate conjunctions > nouns.
 The first level analysis that fitted each voxel’s time course separately for each subject was performed in functional space preserving the orientation of the EPI images [richtig?].
@@
 % von Interpretation klar(er) getrennt halten
-Results: The first contrast that contrasted words to moments where no speech is audible in the audio-description (all 21 tag-related regressors > no-speech) shows\dots;
+figure \ref{fig:results}
+words > no-speech \ref{tab:cope1}
+proper nouns > coordinate conjunctions and proper nouns \ref{tab:cope3}
+nouns > coordinate conjunctions \ref{tab:cope5}
+The first contrast that contrasted words to moments where no speech is audible in the audio-description (words > no-speech) shows\dots;
 left lateralization (bigger cluster left in BA XY => Broca)
-The contrasts proper nouns > coordinate conjunctions and proper nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.
+The contrasts proper nouns > coordinate conjunctions and nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.
 

### 2020-04-08 paper/main.tex
add raw version of brain structures to cluster tables

@@
 
+% hier die Lateralisation in den Broca Arealen BA44 und BA45 klarer machen
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words > no-speech. Clusters sorted by voxel size.}
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words > no-speech.
+Clusters sorted by voxel size.
+The first brain structure given contains the voxel with the maximum Z-Value.}
 \label{tab:cope1}
-\begin{tabular}{rrrrrrrrrrp{3cm}}
+\begin{tabular}{rrrrrrrrrp{6cm}}
 \toprule
@@
 \midrule
-14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
-14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
-1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
-217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
+14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & l Heschl's G.; lateral superior Occipital C., Angular G., posterior Supramarginal G., middle Temporal G.
+posterior to anterior; part of Planum Temporale, anterior superior Temporal G.
+\\
+14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & r.
+Superior Temporal G.; Angular G., Supramarginal G., middle Temporal G.
+posterior to anterior, Heschl's G.
+, inferior Frontal Gyrus pars opercularis (BA44); parts of Planum Temporale \& pars triangularis (BA45) \\
+1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & frontal Orbital C.; Precentral G.
+(Broca's area BA44), pars triangularis \& Inferior Frontal G.; part of pars opercularis (Broca's area BA44); NO Precentral Gyrus \\
+217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & l. Thalamus \\
 \bottomrule
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size.}
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').
+Clusters sorted by voxel size.
+The first brain structure given contains the voxel with the maximum Z-Value.}
 \label{tab:cope3}
-\begin{tabular}{rrrrrrrrrrp{3cm}}
+\begin{tabular}{rrrrrrrrrp{6cm}}
 \toprule
@@
 \midrule
-7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
-5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
-479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
-420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
-407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
-294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
-121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
-117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
-115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
+7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & l. Planum Temporale; Angular G., Supramarginal G., Heschl's G., Superior Temporal G., Planum Polare, Temporal Pole \\
+5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & r Parietal Operculum, Planum Temporale; Heschl's G., superior Temporal G., Planum Polare, Temporal Pole; part of Angular G. \\
+479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & l. posterior Cingulate G. \\
+420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & l. Precuneus \\
+407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & r. posterior Cingulate C. \\
+294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & r. Preceus \\
+121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & r. Occipital Pole \\
+117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & r. Heschl's G. \\
+115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & l. superior lateral Occipital C.\\
 \bottomrule
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size.}
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon'').
+Clusters sorted by voxel size.
+The first brain structure given contains the voxel with the maximum Z-Value.}
 \label{tab:cope5}
-\begin{tabular}{rrrrrrrrrrp{3cm}}
+\begin{tabular}{rrrrrrrrrp{6cm}}
 \toprule
@@
 \midrule
-3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
-1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
-166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
-149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
+3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & l.
+anterior superior Temporal G.; posterior Supramarginal G., Parietal Operculum, Planum Temporale, anterior superior Temporal G., Planum Polare; part of Heschl's Gyrus \\
+1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & r. Planum Temporale, Superior Temporal Gyrus; part of Heschl's G. \& Planum Polare \\
+166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & r. posterior Cingulate G. \\
+149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & r. Precuneus \\
 \bottomrule
@@
 nouns > coordinate conjunctions \ref{tab:cope5}
-The first contrast that contrasted words to moments where no speech is audible in the audio-description (words > no-speech) shows\dots;
+Results: The first contrast that contrasted words to moments where no speech is audible in the audio-description (words > no-speech) shows\dots;
 left lateralization (bigger cluster left in BA XY => Broca)
@@
 Discussion: alles total awesome; Correlation der (konvolvierten Regressoren) is gut (s. figure \ref{fig:reg-corr}; Ergebnisse ergeben Sinn -> benutzt die Anno for awesome research
+All contrasts show bilateral clusters in speech-related regions (e.g.
+) but all bigger in voxel count on the left side => Clear involvement of the right hemisphere but bias to the left (see \citep{hamilton2018revolution}
 

### 2020-04-14 paper/main.tex
Change manuscript layout to leave space for margin notes

--- 2020-04-07 paper/main.tex
@@
 % http://f1000research.com/author-guidelines
-\documentclass[10pt,a4paper,twocolumn]{article}
+\documentclass[10pt,a4paper,onecolumn]{article}
 \usepackage{f1000_styles}
+\geometry{right=4cm}
 \usepackage{booktabs}
@@
   \includegraphics[width=\linewidth]{figures/slicescolorbars}
-  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected.; MNI template space).}
+  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05; cluster corr.; MNI template space).}
   \label{fig:results}
@@
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words > no-speech. Clusters sorted by voxel size.}
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast words > no-speech.}
 \label{tab:cope1}
@@
 \toprule
-& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{4-6} \cmidrule{7-9}
-voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
+& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{5-7} \cmidrule{8-10}
+Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
 \midrule
-14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
-14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
-1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
-217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
+4 & 14990 & 0 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
+3 & 14469 & 0 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
+2 & 1971 & 2.37E-16 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
+1 & 217 & 0.00214 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
 \bottomrule
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size.}
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').}
 \label{tab:cope3}
@@
 \toprule
-& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{4-6} \cmidrule{7-9}
-voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
+& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{5-7} \cmidrule{8-10}
+Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
 \midrule
-7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
-5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
-479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
-420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
-407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
-294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
-121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
-117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
-115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
+9 & 7691 & 2.80E-45 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
+8 & 5928 & 5.97E-38 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
+7 & 479 & 1.13E-06 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
+6 & 420 & 4.65E-06 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
+5 & 407 & 6.38E-06 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
+4 & 294 & 0.000115 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
+3 & 121 & 0.0237 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
+2 & 117 & 0.0274 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
+1 & 115 & 0.0295 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
 \bottomrule
 \end{tabular}
+
 \end{table*}
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon''). Clusters sorted by voxel size.}
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon'').}
 \label{tab:cope5}
@@
 \toprule
-& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
 \\ \cmidrule{5-7} \cmidrule{8-10}
-voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
+Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
 \midrule
-3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
-1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
-166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
-149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
+4 & 3166 & 2.79E-25 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
+3 & 1753 & 7.18E-17 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
+2 & 166 & 0.00446 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
+1 & 149 & 0.00793 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
 \bottomrule

### 2020-04-14 paper/main.tex
delete table with rules for descriptive nouns

--- 2020-04-08 paper/main.tex
@@
 
-\clearpage
-% der alte Entwurf der Tabelle; hier mit rules/description in der Tabelle
-\begin{center}
-\begin{tabular}{ |c|c|c|c| }
-\hline
-category & description & examples & count\\
-\hline
-geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & 125\\
-geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & 105\\
-setting\_new & first-time mentioned setting & on a bridge, on an alley, on campus & 86\\
-setting\_rec & recurring setting & at the bus stop & 37\\
-body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt & 66\\
-bodypart & limbs and trousers & arm, finger, leg, toe & 69\\
-face & face or parts of it & face, ear, nose, mouth & 47\\
-head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & 36\\
-furniture & movable objects insides/outsides & bench, bed, table, chair & 50\\
-object & countable entities with firm boundaries & feather, telephone, car & 232\\
-objects & countable entities with firm boundaries & wheels, photos & 52\\
-female & female person & nurse, mother, women & 31\\
-females & female persons & women & 3\\
-fname & female name & Jenny, Carla & 74\\
-male & male person & man, father, soldier & 89\\
-males & concrete male persons & boys, opponents & 23\\
-mname & male name of person present in the scene & Forrest, Bubba, Kennedy & 291\\
-persons & concrete persons of unknown sex / gender & hippies, patients & 17\\
-++ & nouns, adverbial adjectives, and adverbs & in the evening, it's daytime, later \\
-\hline
-\label{tab:descr-nouns-old}
-\end{tabular}
-\end{center}
-
 \end{document}

### 2020-04-15 paper/main.tex
Frontmatter comments

--- 2020-04-14 paper/main.tex
@@
 
-\title{\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description}
-\titlenote{whatever titlenote here}
+\title{A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description}
+%\titlenote{whatever titlenote here}
 
@@
 im Gegensatz zu Sätzen und Phones haben Einzelworte zusätzliche Annos
+
+\todo[inline]{The abstract should come now. It is needed to evaluate the
+concept of the paper in the light of its content and vice versa.}
 
@@
 (ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
-corresponding fMRI data. Nevertheless, theory-driven analyses like a general
+corresponding fMRI data. Nevertheless, theory-driven\todo{model-based?, there is little theroy in GLM} analyses like a general
 linear model (GLM) are necessary to not just explain how but also when and why a

### 2020-04-15 paper/main.tex
Sort tables where they belong in the text

@@
 \clearpage
-
-\begin{table*}[t]
-\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments.
-The label ``Sentences''' comprises complete grammatical sentences (i.e.
-having a subject and a predicate, and additionally marked with a full stop in the annotation).
-The  ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g.
-``ha, ha, ha'') or in isolation (e.g.
-``ha'', at time points when speakers rapidly switch).
-The label ``Words'' comprises every single word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
-\label{tab:overview}
-\begin{tabular}{llllllllll}
-\toprule
-\textbf{label} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
-\midrule
-sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
-words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
-phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-% bei ein paar Namen bin ich ggf. von Labs abgewichen (genauer identifiziert, ggf. kleine Fehler korrigiert. Ist dann aber nur bei Personen, die 1-2x mit 1-2 Sätzen auftauchen.
-\begin{table*}[t]
-\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically.
-The narrator only occurrs in the audio-description of the movie.
-Shown names are identical to the names used in \citep{labs2015portrayed}.
-Overall 97 persons were identified.}
-\label{tab:speakers}
-\begin{tabular}{llllllllll}
-\toprule
-\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
-\midrule
-Bubba  & \aBubbaAll & \aBubbaI & \aBubbaII & \aBubbaIII & \aBubbaIV & \aBubbaV & \aBubbaVI & \aBubbaVII & \aBubbaVIII \tabularnewline
-Forrest  & \aForrestAll & \aForrestI & \aForrestII & \aForrestIII & \aForrestIV & \aForrestV & \aForrestVI & \aForrestVII & \aForrestVIII \tabularnewline
-Forrest (child)  & \aForrestchildAll & \aForrestchildI & \aForrestchildII & \aForrestchildIII & \aForrestchildIV & \aForrestchildV & \aForrestchildVI & \aForrestchildVII & \aForrestchildVIII \tabularnewline
-Forrest (v.o.)  & \aForrestvoAll & \aForrestvoI & \aForrestvoII & \aForrestvoIII & \aForrestvoIV & \aForrestvoV & \aForrestvoVI & \aForrestvoVII & \aForrestvoVIII \tabularnewline
-Hancock  & \aHancockAll & \aHancockI & \aHancockII & \aHancockIII & \aHancockIV & \aHancockV & \aHancockVI & \aHancockVII & \aHancockVIII \tabularnewline
-Jenny  & \aJennyAll & \aJennyI & \aJennyII & \aJennyIII & \aJennyIV & \aJennyV & \aJennyVI & \aJennyVII & \aJennyVIII \tabularnewline
-Jenny (child)  & \aJennychildAll & \aJennychildI & \aJennychildII & \aJennychildIII & \aJennychildIV & \aJennychildV & \aJennychildVI & \aJennychildVII & \aJennychildVIII \tabularnewline
-Lt. Dan  & \aLtdanAll & \aLtdanI & \aLtdanII & \aLtdanIII & \aLtdanIV & \aLtdanV & \aLtdanVI & \aLtdanVII & \aLtdanVIII \tabularnewline
-Mrs. Gump  & \aMrsgumpAll & \aMrsgumpI & \aMrsgumpII & \aMrsgumpIII & \aMrsgumpIV & \aMrsgumpV & \aMrsgumpVI & \aMrsgumpVII & \aMrsgumpVIII \tabularnewline
-Narrator  & \aNarratorAll & \aNarratorI & \aNarratorII & \aNarratorIII & \aNarratorIV & \aNarratorV & \aNarratorVI & \aNarratorVII & \aNarratorVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
-\caption{Simple part of speech tagging (POS). All 15 labels sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually identified.}
-\label{tab:pos}
-\begin{tabular}{lllllllllll}
-\toprule
-\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII \tabularnewline
-ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
-ADV & \aPosAdv & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII \tabularnewline
-AUX & \aPosAux & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII \tabularnewline
-CONJ & \aPosConj & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII \tabularnewline
-DET & \aPosDet & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII \tabularnewline
-NONSPEECH & non-speech vocalization & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII \tabularnewline
-NOUN & \aPosNoun & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII \tabularnewline
-NUM & \aPosNum & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII \tabularnewline
-PART & \aPosPart & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII \tabularnewline
-PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
-PRON & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
-SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
-VERB & \aPosVerb & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII \tabularnewline
-X & \aPosX & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
-\caption{Detailed part of speech tagging (TAG). The 15 most often occurring labels (overall 43 labels) sorted alphabetically. Descriptions were taken from spaCy.explain().}
-\label{tab:tag}
-\begin{tabular}{lllllllllll}
-\toprule
-\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-ADJA & \aTagAdja & \aTagAdjaAll & \aTagAdjaI & \aTagAdjaII & \aTagAdjaIII & \aTagAdjaIV & \aTagAdjaV & \aTagAdjaVI & \aTagAdjaVII & \aTagAdjaVIII \tabularnewline
-ADJD & \aTagAdjd & \aTagAdjdAll & \aTagAdjdI & \aTagAdjdII & \aTagAdjdIII & \aTagAdjdIV & \aTagAdjdV & \aTagAdjdVI & \aTagAdjdVII & \aTagAdjdVIII \tabularnewline
-ADV & \aTagAdv & \aTagAdvAll & \aTagAdvI & \aTagAdvII & \aTagAdvIII & \aTagAdvIV & \aTagAdvV & \aTagAdvVI & \aTagAdvVII & \aTagAdvVIII \tabularnewline
-APPR & \aTagAppr & \aTagApprAll & \aTagApprI & \aTagApprII & \aTagApprIII & \aTagApprIV & \aTagApprV & \aTagApprVI & \aTagApprVII & \aTagApprVIII \tabularnewline
-ART & \aTagArt & \aTagArtAll & \aTagArtI & \aTagArtII & \aTagArtIII & \aTagArtIV & \aTagArtV & \aTagArtVI & \aTagArtVII & \aTagArtVIII \tabularnewline
-KON & \aTagKon & \aTagKonAll & \aTagKonI & \aTagKonII & \aTagKonIII & \aTagKonIV & \aTagKonV & \aTagKonVI & \aTagKonVII & \aTagKonVIII \tabularnewline
-NE & \aTagNe & \aTagNeAll & \aTagNeI & \aTagNeII & \aTagNeIII & \aTagNeIV & \aTagNeV & \aTagNeVI & \aTagNeVII & \aTagNeVIII \tabularnewline
-NN & \aTagNn & \aTagNnAll & \aTagNnI & \aTagNnII & \aTagNnIII & \aTagNnIV & \aTagNnV & \aTagNnVI & \aTagNnVII & \aTagNnVIII \tabularnewline
-PPER & \aTagPper & \aTagPperAll & \aTagPperI & \aTagPperII & \aTagPperIII & \aTagPperIV & \aTagPperV & \aTagPperVI & \aTagPperVII & \aTagPperVIII \tabularnewline
-PPOSAT & \aTagPposat & \aTagPposatAll & \aTagPposatI & \aTagPposatII & \aTagPposatIII & \aTagPposatIV & \aTagPposatV & \aTagPposatVI & \aTagPposatVII & \aTagPposatVIII \tabularnewline
-PTKVZ & \aTagPtkvz & \aTagPtkvzAll & \aTagPtkvzI & \aTagPtkvzII & \aTagPtkvzIII & \aTagPtkvzIV & \aTagPtkvzV & \aTagPtkvzVI & \aTagPtkvzVII & \aTagPtkvzVIII \tabularnewline
-VAFIN & \aTagVafin & \aTagVafinAll & \aTagVafinI & \aTagVafinII & \aTagVafinIII & \aTagVafinIV & \aTagVafinV & \aTagVafinVI & \aTagVafinVII & \aTagVafinVIII \tabularnewline
-VVFIN & \aTagVvfin & \aTagVvfinAll & \aTagVvfinI & \aTagVvfinII & \aTagVvfinIII & \aTagVvfinIV & \aTagVvfinV & \aTagVvfinVI & \aTagVvfinVII & \aTagVvfinVIII \tabularnewline
-VVINF & \aTagVvinf & \aTagVvinfAll & \aTagVvinfI & \aTagVvinfII & \aTagVvinfIII & \aTagVvinfIV & \aTagVvinfV & \aTagVvinfVI & \aTagVvinfVII & \aTagVvinfVIII \tabularnewline
-VVPP & \aTagVvpp & \aTagVvppAll & \aTagVvppI & \aTagVvppII & \aTagVvppIII & \aTagVvppIV & \aTagVvppV & \aTagVvppVI & \aTagVvppVII & \aTagVvppVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
-\caption{Syntactic dependencies (DEP). The 15 most often occuring labels (overall 37 labels) sorted alphabetically. Descriptions were taken from spaCy.explain().}
-\label{tab:dep}
-\begin{tabular}{lllllllllll}
-\toprule
-\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-cd & \aDepCd & \aDepCdAll & \aDepCdI & \aDepCdII & \aDepCdIII & \aDepCdIV & \aDepCdV & \aDepCdVI & \aDepCdVII & \aDepCdVIII \tabularnewline
-cj & \aDepCj & \aDepCjAll & \aDepCjI & \aDepCjII & \aDepCjIII & \aDepCjIV & \aDepCjV & \aDepCjVI & \aDepCjVII & \aDepCjVIII \tabularnewline
-cp & \aDepCp & \aDepCpAll & \aDepCpI & \aDepCpII & \aDepCpIII & \aDepCpIV & \aDepCpV & \aDepCpVI & \aDepCpVII & \aDepCpVIII \tabularnewline
-da & \aDepDa & \aDepDaAll & \aDepDaI & \aDepDaII & \aDepDaIII & \aDepDaIV & \aDepDaV & \aDepDaVI & \aDepDaVII & \aDepDaVIII \tabularnewline
-ju & \aDepJu & \aDepJuAll & \aDepJuI & \aDepJuII & \aDepJuIII & \aDepJuIV & \aDepJuV & \aDepJuVI & \aDepJuVII & \aDepJuVIII \tabularnewline
-mnr & \aDepMnr & \aDepMnrAll & \aDepMnrI & \aDepMnrII & \aDepMnrIII & \aDepMnrIV & \aDepMnrV & \aDepMnrVI & \aDepMnrVII & \aDepMnrVIII \tabularnewline
-mo & \aDepMo & \aDepMoAll & \aDepMoI & \aDepMoII & \aDepMoIII & \aDepMoIV & \aDepMoV & \aDepMoVI & \aDepMoVII & \aDepMoVIII \tabularnewline
-nk & \aDepNk & \aDepNkAll & \aDepNkI & \aDepNkII & \aDepNkIII & \aDepNkIV & \aDepNkV & \aDepNkVI & \aDepNkVII & \aDepNkVIII \tabularnewline
-oa & \aDepOa & \aDepOaAll & \aDepOaI & \aDepOaII & \aDepOaIII & \aDepOaIV & \aDepOaV & \aDepOaVI & \aDepOaVII & \aDepOaVIII \tabularnewline
-oc & \aDepOc & \aDepOcAll & \aDepOcI & \aDepOcII & \aDepOcIII & \aDepOcIV & \aDepOcV & \aDepOcVI & \aDepOcVII & \aDepOcVIII \tabularnewline
-pd & \aDepPd & \aDepPdAll & \aDepPdI & \aDepPdII & \aDepPdIII & \aDepPdIV & \aDepPdV & \aDepPdVI & \aDepPdVII & \aDepPdVIII \tabularnewline
-pnc & \aDepPnc & \aDepPncAll & \aDepPncI & \aDepPncII & \aDepPncIII & \aDepPncIV & \aDepPncV & \aDepPncVI & \aDepPncVII & \aDepPncVIII \tabularnewline
-ROOT & root of sentence & \aDepRootAll & \aDepRootI & \aDepRootII & \aDepRootIII & \aDepRootIV & \aDepRootV & \aDepRootVI & \aDepRootVII & \aDepRootVIII \tabularnewline
-sb & \aDepSb & \aDepSbAll & \aDepSbI & \aDepSbII & \aDepSbIII & \aDepSbIV & \aDepSbV & \aDepSbVI & \aDepSbVII & \aDepSbVIII \tabularnewline
-svp & separable verb prefix & \aDepSvpAll & \aDepSvpI & \aDepSvpII & \aDepSvpIII & \aDepSvpIV & \aDepSvpV & \aDepSvpVI & \aDepSvpVII & \aDepSvpVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
-    \caption{Narrator's descriptive nouns.
-All categories sorted alphapetically.
-Examples are given in English.
-Description (of rules) fehlt in dieser Tabelle (vgl.
-alte Tabelle auf der allerletzten Seite).
-Wird nämlich in einer Tabelle mit horizontaler Ausrichtung eng.
-Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best.
-der Zeit.}
-\label{tab:descr-nouns}
-\begin{tabular}{lllllllllll}
-\toprule
-\textbf{label} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-body & back, hip, shoulder; jacket, dress, shirt & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII \tabularnewline
-bodypart  & arm, finger, leg, toe & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII\tabularnewline
-face & face, ear, nose, mouth & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII \tabularnewline
-female & nurse, mother, woman & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII \tabularnewline
-females & women & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII \tabularnewline
-fname & Jenny & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII \tabularnewline
-furniture & bench, bed, table, chair & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII \tabularnewline
-geo & building, tree, street, alley, meadow, cornfield, river & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII \tabularnewline
-geo-room & living room; wall, door, window, floor, turf & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII \tabularnewline
-head & head, hair, ear, neck, helmet & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII \tabularnewline
-male & man, father, soldier & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII \tabularnewline
-males & boys, opponents & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII \tabularnewline
-mname & Bubba, Kennedy & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII \tabularnewline
-object & telephone, car & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII \tabularnewline
-objects & wheels, photos & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII \tabularnewline
-persons & hippies, patients & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII \tabularnewline
-setting\_new & on a ``bridge'', on an ``alley'', on ``campus'' & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII \tabularnewline
-setting\_rec & at the ``bus stop'' & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII \tabularnewline
-++ &  in the ``evening'', it's ``daytime'', ``later'' & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
-    \caption{Overview of the 26 regressors for the validation analysis.
-The first column contains the number of the regressor in the design file of FSL \citep{smith2004fsl}.
-The 20 most often occuring labels from the detailed part-of speech tagging were used as such.
-Words belonging to all other labels were pooled to ``tag\_other''.
-The regressor ``sentence'' contains the end of complete grammatical sentences.
-The regressor ``phones'' contains the 80 most often occuring phonemes (``n'' with N=6053 to ``IY1'' with N=32).
-The regressor ``no-sp'' represents moments when no speech was audible.
-''fg\_ad\_lrdiff (left-right volume difference) and ``fg\_ad\_rms'' (root mean square loudness) represent low-level auditory nuissance regressors comprising one event for every movie frame (40ms).}
-\label{tab:regressors}
-\begin{tabular}{llllllllllll}
-\toprule
-\textbf{no} & \textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-1 & adja & \aTagAdja & \rAdjaAll & \rAdjaI & \rAdjaII & \rAdjaIII & \rAdjaIV & \rAdjaV & \rAdjaVI & \rAdjaVII & \rAdjaVIII \tabularnewline
-2 & adjd & \aTagAdjd & \rAdjdAll & \rAdjdI & \rAdjdII & \rAdjdIII & \rAdjdIV & \rAdjdV & \rAdjdVI & \rAdjdVII & \rAdjdVIII \tabularnewline
-3 & adv & \aTagAdv & \rAdvAll & \rAdvI & \rAdvII & \rAdvIII & \rAdvIV & \rAdvV & \rAdvVI & \rAdvVII & \rAdvVIII \tabularnewline
-4 & appr & \aTagAppr & \rApprAll & \rApprI & \rApprII & \rApprIII & \rApprIV & \rApprV & \rApprVI & \rApprVII & \rApprVIII \tabularnewline
-5 & apprart & preposition with article & \rApprartAll & \rApprartI & \rApprartII & \rApprartIII & \rApprartIV & \rApprartV & \rApprartVI & \rApprartVII & \rApprartVIII \tabularnewline
-6 & art & \aTagArt & \rArtAll & \rArtI & \rArtII & \rArtIII & \rArtIV & \rArtV & \rArtVI & \rArtVII & \rArtVIII \tabularnewline
-7 & kon & \aTagKon & \rKonAll & \rKonI & \rKonII & \rKonIII & \rKonIV & \rKonV & \rKonVI & \rKonVII & \rKonVIII \tabularnewline
-8 & ne & \aTagNe & \rNeAll & \rNeI & \rNeII & \rNeIII & \rNeIV & \rNeV & \rNeVI & \rNeVII & \rNeVIII \tabularnewline
-9 & nn & \aTagNn & \rNnAll & \rNnI & \rNnII & \rNnIII & \rNnIV & \rNnV & \rNnVI & \rNnVII & \rNnVIII \tabularnewline
-10 & pds & substituting demonstrative pronoun & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII \tabularnewline
-11 & pis & substituting indefinite pronoun & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII \tabularnewline
-12 & pper & \aTagPper & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII \tabularnewline
-13 & pposat & \aTagPposat & \rPposatAll & \rPposatI & \rPposatII & \rPposatIII & \rPposatIV & \rPposatV & \rPposatVI & \rPposatVII & \rPposatVIII \tabularnewline
-14 & prf & reflexive personal pronoun & \rPrfAll & \rPrfI & \rPrfII & \rPrfIII & \rPrfIV & \rPrfV & \rPrfVI & \rPrfVII & \rPrfVIII \tabularnewline
-15 & ptkvz & \aTagPtkvz & \rPtkvzAll & \rPtkvzI & \rPtkvzII & \rPtkvzIII & \rPtkvzIV & \rPtkvzV & \rPtkvzVI & \rPtkvzVII & \rPtkvzVIII \tabularnewline
-16 & vafin & \aTagVafin & \rVafinAll & \rVafinI & \rVafinII & \rVafinIII & \rVafinIV & \rVafinV & \rVafinVI & \rVafinVII & \rVafinVIII \tabularnewline
-17 & vmfin & finite verb, modal & \rVmfinAll & \rVmfinI & \rVmfinII & \rVmfinIII & \rVmfinIV & \rVmfinV & \rVmfinVI & \rVmfinVII & \rVmfinVIII \tabularnewline
-18 & vvfin & \aTagVvfin & \rVvfinAll & \rVvfinI & \rVvfinII & \rVvfinIII & \rVvfinIV & \rVvfinV & \rVvfinVI & \rVvfinVII & \rVvfinVIII \tabularnewline
-19 & vvinf & \aTagVvinf & \rVvinfAll & \rVvinfI & \rVvinfII & \rVvinfIII & \rVvinfIV & \rVvinfV & \rVvinfVI & \rVvinfVII & \rVvinfVIII \tabularnewline
-20 & vvpp & \aTagVvpp & \rVvppAll & \rVvppI & \rVvppII & \rVvppIII & \rVvppIV & \rVvppV & \rVvppVI & \rVvppVII & \rVvppVIII \tabularnewline
-21 & tag\_other & all other TAG categories & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII \tabularnewline
-\cline{1-12}
-22 & sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
-23 & phones & 80 most often occuring phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
-24 & no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
-\cline{1-12}
-25 & fg\_ad\_lrdiff & left-right volume difference & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII \tabularnewline
-26 & fg\_ad\_rms & root mean square & \rFgadrmsAll & \rFgadrmsI & \rFgadrmsII & \rFgadrmsIII & \rFgadrmsIV & \rFgadrmsV & \rFgadrmsVI & \rFgadrmsVII & \rFgadrmsVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
 
@@
 
+\begin{table*}[tbp]
+\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments.
+The label ``Sentences''' comprises complete grammatical sentences (i.e.
+having a subject and a predicate, and additionally marked with a full stop in the annotation).
+The  ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g.
+``ha, ha, ha'') or in isolation (e.g.
+``ha'', at time points when speakers rapidly switch).
+The label ``Words'' comprises every single word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
+\label{tab:overview}
+\begin{tabular}{llllllllll}
+\toprule
+\textbf{label} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
+\midrule
+sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
+words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
+phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
+% bei ein paar Namen bin ich ggf. von Labs abgewichen (genauer identifiziert, ggf. kleine Fehler korrigiert. Ist dann aber nur bei Personen, die 1-2x mit 1-2 Sätzen auftauchen.
+\begin{table*}[btp]
+\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically.
+The narrator only occurrs in the audio-description of the movie.
+Shown names are identical to the names used in \citep{labs2015portrayed}.
+Overall 97 persons were identified.}
+\label{tab:speakers}
+\begin{tabular}{llllllllll}
+\toprule
+\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
+\midrule
+Bubba  & \aBubbaAll & \aBubbaI & \aBubbaII & \aBubbaIII & \aBubbaIV & \aBubbaV & \aBubbaVI & \aBubbaVII & \aBubbaVIII \tabularnewline
+Forrest  & \aForrestAll & \aForrestI & \aForrestII & \aForrestIII & \aForrestIV & \aForrestV & \aForrestVI & \aForrestVII & \aForrestVIII \tabularnewline
+Forrest (child)  & \aForrestchildAll & \aForrestchildI & \aForrestchildII & \aForrestchildIII & \aForrestchildIV & \aForrestchildV & \aForrestchildVI & \aForrestchildVII & \aForrestchildVIII \tabularnewline
+Forrest (v.o.)  & \aForrestvoAll & \aForrestvoI & \aForrestvoII & \aForrestvoIII & \aForrestvoIV & \aForrestvoV & \aForrestvoVI & \aForrestvoVII & \aForrestvoVIII \tabularnewline
+Hancock  & \aHancockAll & \aHancockI & \aHancockII & \aHancockIII & \aHancockIV & \aHancockV & \aHancockVI & \aHancockVII & \aHancockVIII \tabularnewline
+Jenny  & \aJennyAll & \aJennyI & \aJennyII & \aJennyIII & \aJennyIV & \aJennyV & \aJennyVI & \aJennyVII & \aJennyVIII \tabularnewline
+Jenny (child)  & \aJennychildAll & \aJennychildI & \aJennychildII & \aJennychildIII & \aJennychildIV & \aJennychildV & \aJennychildVI & \aJennychildVII & \aJennychildVIII \tabularnewline
+Lt. Dan  & \aLtdanAll & \aLtdanI & \aLtdanII & \aLtdanIII & \aLtdanIV & \aLtdanV & \aLtdanVI & \aLtdanVII & \aLtdanVIII \tabularnewline
+Mrs. Gump  & \aMrsgumpAll & \aMrsgumpI & \aMrsgumpII & \aMrsgumpIII & \aMrsgumpIV & \aMrsgumpV & \aMrsgumpVI & \aMrsgumpVII & \aMrsgumpVIII \tabularnewline
+Narrator  & \aNarratorAll & \aNarratorI & \aNarratorII & \aNarratorIII & \aNarratorIV & \aNarratorV & \aNarratorVI & \aNarratorVII & \aNarratorVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
 % descriptive Nouns
@@
 ist jetzt in der obigen Tabelle aus Platzgründen nicht mehr drin; in dieser,\ref{tab:descr-nouns}, einer neuen Tabelle oder im laufenden Text [wird viel Text] bringen) was done by one person and corrected in several runs by the author.
+
+\begin{table*}[t]
+    \caption{Narrator's descriptive nouns.
+All categories sorted alphapetically.
+Examples are given in English.
+Description (of rules) fehlt in dieser Tabelle (vgl.
+alte Tabelle auf der allerletzten Seite).
+Wird nämlich in einer Tabelle mit horizontaler Ausrichtung eng.
+Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best.
+der Zeit.}
+\label{tab:descr-nouns}
+\begin{tabular}{lllllllllll}
+\toprule
+\textbf{label} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+body & back, hip, shoulder; jacket, dress, shirt & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII \tabularnewline
+bodypart  & arm, finger, leg, toe & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII\tabularnewline
+face & face, ear, nose, mouth & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII \tabularnewline
+female & nurse, mother, woman & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII \tabularnewline
+females & women & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII \tabularnewline
+fname & Jenny & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII \tabularnewline
+furniture & bench, bed, table, chair & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII \tabularnewline
+geo & building, tree, street, alley, meadow, cornfield, river & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII \tabularnewline
+geo-room & living room; wall, door, window, floor, turf & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII \tabularnewline
+head & head, hair, ear, neck, helmet & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII \tabularnewline
+male & man, father, soldier & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII \tabularnewline
+males & boys, opponents & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII \tabularnewline
+mname & Bubba, Kennedy & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII \tabularnewline
+object & telephone, car & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII \tabularnewline
+objects & wheels, photos & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII \tabularnewline
+persons & hippies, patients & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII \tabularnewline
+setting\_new & on a ``bridge'', on an ``alley'', on ``campus'' & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII \tabularnewline
+setting\_rec & at the ``bus stop'' & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII \tabularnewline
+++ &  in the ``evening'', it's ``daytime'', ``later'' & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
 
@@
 
+\begin{table*}[t]
+\caption{Simple part of speech tagging (POS). All 15 labels sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually identified.}
+\label{tab:pos}
+\begin{tabular}{lllllllllll}
+\toprule
+\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII \tabularnewline
+ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
+ADV & \aPosAdv & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII \tabularnewline
+AUX & \aPosAux & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII \tabularnewline
+CONJ & \aPosConj & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII \tabularnewline
+DET & \aPosDet & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII \tabularnewline
+NONSPEECH & non-speech vocalization & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII \tabularnewline
+NOUN & \aPosNoun & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII \tabularnewline
+NUM & \aPosNum & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII \tabularnewline
+PART & \aPosPart & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII \tabularnewline
+PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
+PRON & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
+SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
+VERB & \aPosVerb & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII \tabularnewline
+X & \aPosX & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
 \subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
@@
 table \ref{tab:tag}) which is based on the \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset} \citep{schiller1999stts}.
+
+\begin{table*}[t]
+\caption{Detailed part of speech tagging (TAG). The 15 most often occurring labels (overall 43 labels) sorted alphabetically. Descriptions were taken from spaCy.explain().}
+\label{tab:tag}
+\begin{tabular}{lllllllllll}
+\toprule
+\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+ADJA & \aTagAdja & \aTagAdjaAll & \aTagAdjaI & \aTagAdjaII & \aTagAdjaIII & \aTagAdjaIV & \aTagAdjaV & \aTagAdjaVI & \aTagAdjaVII & \aTagAdjaVIII \tabularnewline
+ADJD & \aTagAdjd & \aTagAdjdAll & \aTagAdjdI & \aTagAdjdII & \aTagAdjdIII & \aTagAdjdIV & \aTagAdjdV & \aTagAdjdVI & \aTagAdjdVII & \aTagAdjdVIII \tabularnewline
+ADV & \aTagAdv & \aTagAdvAll & \aTagAdvI & \aTagAdvII & \aTagAdvIII & \aTagAdvIV & \aTagAdvV & \aTagAdvVI & \aTagAdvVII & \aTagAdvVIII \tabularnewline
+APPR & \aTagAppr & \aTagApprAll & \aTagApprI & \aTagApprII & \aTagApprIII & \aTagApprIV & \aTagApprV & \aTagApprVI & \aTagApprVII & \aTagApprVIII \tabularnewline
+ART & \aTagArt & \aTagArtAll & \aTagArtI & \aTagArtII & \aTagArtIII & \aTagArtIV & \aTagArtV & \aTagArtVI & \aTagArtVII & \aTagArtVIII \tabularnewline
+KON & \aTagKon & \aTagKonAll & \aTagKonI & \aTagKonII & \aTagKonIII & \aTagKonIV & \aTagKonV & \aTagKonVI & \aTagKonVII & \aTagKonVIII \tabularnewline
+NE & \aTagNe & \aTagNeAll & \aTagNeI & \aTagNeII & \aTagNeIII & \aTagNeIV & \aTagNeV & \aTagNeVI & \aTagNeVII & \aTagNeVIII \tabularnewline
+NN & \aTagNn & \aTagNnAll & \aTagNnI & \aTagNnII & \aTagNnIII & \aTagNnIV & \aTagNnV & \aTagNnVI & \aTagNnVII & \aTagNnVIII \tabularnewline
+PPER & \aTagPper & \aTagPperAll & \aTagPperI & \aTagPperII & \aTagPperIII & \aTagPperIV & \aTagPperV & \aTagPperVI & \aTagPperVII & \aTagPperVIII \tabularnewline
+PPOSAT & \aTagPposat & \aTagPposatAll & \aTagPposatI & \aTagPposatII & \aTagPposatIII & \aTagPposatIV & \aTagPposatV & \aTagPposatVI & \aTagPposatVII & \aTagPposatVIII \tabularnewline
+PTKVZ & \aTagPtkvz & \aTagPtkvzAll & \aTagPtkvzI & \aTagPtkvzII & \aTagPtkvzIII & \aTagPtkvzIV & \aTagPtkvzV & \aTagPtkvzVI & \aTagPtkvzVII & \aTagPtkvzVIII \tabularnewline
+VAFIN & \aTagVafin & \aTagVafinAll & \aTagVafinI & \aTagVafinII & \aTagVafinIII & \aTagVafinIV & \aTagVafinV & \aTagVafinVI & \aTagVafinVII & \aTagVafinVIII \tabularnewline
+VVFIN & \aTagVvfin & \aTagVvfinAll & \aTagVvfinI & \aTagVvfinII & \aTagVvfinIII & \aTagVvfinIV & \aTagVvfinV & \aTagVvfinVI & \aTagVvfinVII & \aTagVvfinVIII \tabularnewline
+VVINF & \aTagVvinf & \aTagVvinfAll & \aTagVvinfI & \aTagVvinfII & \aTagVvinfIII & \aTagVvinfIV & \aTagVvinfV & \aTagVvinfVI & \aTagVvinfVII & \aTagVvinfVIII \tabularnewline
+VVPP & \aTagVvpp & \aTagVvppAll & \aTagVvppI & \aTagVvppII & \aTagVvppIII & \aTagVvppIV & \aTagVvppV & \aTagVvppVI & \aTagVvppVII & \aTagVvppVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
 
@@
 table \ref{tab:dep}) describes the type of syntactic relation that connects a "child" (the single word) to its "head".
+
+\begin{table*}[t]
+\caption{Syntactic dependencies (DEP). The 15 most often occuring labels (overall 37 labels) sorted alphabetically. Descriptions were taken from spaCy.explain().}
+\label{tab:dep}
+\begin{tabular}{lllllllllll}
+\toprule
+\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+cd & \aDepCd & \aDepCdAll & \aDepCdI & \aDepCdII & \aDepCdIII & \aDepCdIV & \aDepCdV & \aDepCdVI & \aDepCdVII & \aDepCdVIII \tabularnewline
+cj & \aDepCj & \aDepCjAll & \aDepCjI & \aDepCjII & \aDepCjIII & \aDepCjIV & \aDepCjV & \aDepCjVI & \aDepCjVII & \aDepCjVIII \tabularnewline
+cp & \aDepCp & \aDepCpAll & \aDepCpI & \aDepCpII & \aDepCpIII & \aDepCpIV & \aDepCpV & \aDepCpVI & \aDepCpVII & \aDepCpVIII \tabularnewline
+da & \aDepDa & \aDepDaAll & \aDepDaI & \aDepDaII & \aDepDaIII & \aDepDaIV & \aDepDaV & \aDepDaVI & \aDepDaVII & \aDepDaVIII \tabularnewline
+ju & \aDepJu & \aDepJuAll & \aDepJuI & \aDepJuII & \aDepJuIII & \aDepJuIV & \aDepJuV & \aDepJuVI & \aDepJuVII & \aDepJuVIII \tabularnewline
+mnr & \aDepMnr & \aDepMnrAll & \aDepMnrI & \aDepMnrII & \aDepMnrIII & \aDepMnrIV & \aDepMnrV & \aDepMnrVI & \aDepMnrVII & \aDepMnrVIII \tabularnewline
+mo & \aDepMo & \aDepMoAll & \aDepMoI & \aDepMoII & \aDepMoIII & \aDepMoIV & \aDepMoV & \aDepMoVI & \aDepMoVII & \aDepMoVIII \tabularnewline
+nk & \aDepNk & \aDepNkAll & \aDepNkI & \aDepNkII & \aDepNkIII & \aDepNkIV & \aDepNkV & \aDepNkVI & \aDepNkVII & \aDepNkVIII \tabularnewline
+oa & \aDepOa & \aDepOaAll & \aDepOaI & \aDepOaII & \aDepOaIII & \aDepOaIV & \aDepOaV & \aDepOaVI & \aDepOaVII & \aDepOaVIII \tabularnewline
+oc & \aDepOc & \aDepOcAll & \aDepOcI & \aDepOcII & \aDepOcIII & \aDepOcIV & \aDepOcV & \aDepOcVI & \aDepOcVII & \aDepOcVIII \tabularnewline
+pd & \aDepPd & \aDepPdAll & \aDepPdI & \aDepPdII & \aDepPdIII & \aDepPdIV & \aDepPdV & \aDepPdVI & \aDepPdVII & \aDepPdVIII \tabularnewline
+pnc & \aDepPnc & \aDepPncAll & \aDepPncI & \aDepPncII & \aDepPncIII & \aDepPncIV & \aDepPncV & \aDepPncVI & \aDepPncVII & \aDepPncVIII \tabularnewline
+ROOT & root of sentence & \aDepRootAll & \aDepRootI & \aDepRootII & \aDepRootIII & \aDepRootIV & \aDepRootV & \aDepRootVI & \aDepRootVII & \aDepRootVIII \tabularnewline
+sb & \aDepSb & \aDepSbAll & \aDepSbI & \aDepSbII & \aDepSbIII & \aDepSbIV & \aDepSbV & \aDepSbVI & \aDepSbVII & \aDepSbVIII \tabularnewline
+svp & separable verb prefix & \aDepSvpAll & \aDepSvpI & \aDepSvpII & \aDepSvpIII & \aDepSvpIV & \aDepSvpV & \aDepSvpVI & \aDepSvpVII & \aDepSvpVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
 
@@
 We implemented a standard three-level, voxel-wise general linear model (GLM) to average parameter estimates across the eight stimulus segments, and later across 19 subjects.
+
+\begin{table*}[t]
+    \caption{Overview of the 26 regressors for the validation analysis.
+The first column contains the number of the regressor in the design file of FSL \citep{smith2004fsl}.
+The 20 most often occuring labels from the detailed part-of speech tagging were used as such.
+Words belonging to all other labels were pooled to ``tag\_other''.
+The regressor ``sentence'' contains the end of complete grammatical sentences.
+The regressor ``phones'' contains the 80 most often occuring phonemes (``n'' with N=6053 to ``IY1'' with N=32).
+The regressor ``no-sp'' represents moments when no speech was audible.
+''fg\_ad\_lrdiff (left-right volume difference) and ``fg\_ad\_rms'' (root mean square loudness) represent low-level auditory nuissance regressors comprising one event for every movie frame (40ms).}
+\label{tab:regressors}
+\begin{tabular}{llllllllllll}
+\toprule
+\textbf{no} & \textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\midrule
+1 & adja & \aTagAdja & \rAdjaAll & \rAdjaI & \rAdjaII & \rAdjaIII & \rAdjaIV & \rAdjaV & \rAdjaVI & \rAdjaVII & \rAdjaVIII \tabularnewline
+2 & adjd & \aTagAdjd & \rAdjdAll & \rAdjdI & \rAdjdII & \rAdjdIII & \rAdjdIV & \rAdjdV & \rAdjdVI & \rAdjdVII & \rAdjdVIII \tabularnewline
+3 & adv & \aTagAdv & \rAdvAll & \rAdvI & \rAdvII & \rAdvIII & \rAdvIV & \rAdvV & \rAdvVI & \rAdvVII & \rAdvVIII \tabularnewline
+4 & appr & \aTagAppr & \rApprAll & \rApprI & \rApprII & \rApprIII & \rApprIV & \rApprV & \rApprVI & \rApprVII & \rApprVIII \tabularnewline
+5 & apprart & preposition with article & \rApprartAll & \rApprartI & \rApprartII & \rApprartIII & \rApprartIV & \rApprartV & \rApprartVI & \rApprartVII & \rApprartVIII \tabularnewline
+6 & art & \aTagArt & \rArtAll & \rArtI & \rArtII & \rArtIII & \rArtIV & \rArtV & \rArtVI & \rArtVII & \rArtVIII \tabularnewline
+7 & kon & \aTagKon & \rKonAll & \rKonI & \rKonII & \rKonIII & \rKonIV & \rKonV & \rKonVI & \rKonVII & \rKonVIII \tabularnewline
+8 & ne & \aTagNe & \rNeAll & \rNeI & \rNeII & \rNeIII & \rNeIV & \rNeV & \rNeVI & \rNeVII & \rNeVIII \tabularnewline
+9 & nn & \aTagNn & \rNnAll & \rNnI & \rNnII & \rNnIII & \rNnIV & \rNnV & \rNnVI & \rNnVII & \rNnVIII \tabularnewline
+10 & pds & substituting demonstrative pronoun & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII \tabularnewline
+11 & pis & substituting indefinite pronoun & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII \tabularnewline
+12 & pper & \aTagPper & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII \tabularnewline
+13 & pposat & \aTagPposat & \rPposatAll & \rPposatI & \rPposatII & \rPposatIII & \rPposatIV & \rPposatV & \rPposatVI & \rPposatVII & \rPposatVIII \tabularnewline
+14 & prf & reflexive personal pronoun & \rPrfAll & \rPrfI & \rPrfII & \rPrfIII & \rPrfIV & \rPrfV & \rPrfVI & \rPrfVII & \rPrfVIII \tabularnewline
+15 & ptkvz & \aTagPtkvz & \rPtkvzAll & \rPtkvzI & \rPtkvzII & \rPtkvzIII & \rPtkvzIV & \rPtkvzV & \rPtkvzVI & \rPtkvzVII & \rPtkvzVIII \tabularnewline
+16 & vafin & \aTagVafin & \rVafinAll & \rVafinI & \rVafinII & \rVafinIII & \rVafinIV & \rVafinV & \rVafinVI & \rVafinVII & \rVafinVIII \tabularnewline
+17 & vmfin & finite verb, modal & \rVmfinAll & \rVmfinI & \rVmfinII & \rVmfinIII & \rVmfinIV & \rVmfinV & \rVmfinVI & \rVmfinVII & \rVmfinVIII \tabularnewline
+18 & vvfin & \aTagVvfin & \rVvfinAll & \rVvfinI & \rVvfinII & \rVvfinIII & \rVvfinIV & \rVvfinV & \rVvfinVI & \rVvfinVII & \rVvfinVIII \tabularnewline
+19 & vvinf & \aTagVvinf & \rVvinfAll & \rVvinfI & \rVvinfII & \rVvinfIII & \rVvinfIV & \rVvinfV & \rVvinfVI & \rVvinfVII & \rVvinfVIII \tabularnewline
+20 & vvpp & \aTagVvpp & \rVvppAll & \rVvppI & \rVvppII & \rVvppIII & \rVvppIV & \rVvppV & \rVvppVI & \rVvppVII & \rVvppVIII \tabularnewline
+21 & tag\_other & all other TAG categories & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII \tabularnewline
+\cline{1-12}
+22 & sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
+23 & phones & 80 most often occuring phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
+24 & no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
+\cline{1-12}
+25 & fg\_ad\_lrdiff & left-right volume difference & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII \tabularnewline
+26 & fg\_ad\_rms & root mean square & \rFgadrmsAll & \rFgadrmsI & \rFgadrmsII & \rFgadrmsIII & \rFgadrmsIV & \rFgadrmsV & \rFgadrmsVI & \rFgadrmsVII & \rFgadrmsVIII \tabularnewline
+\bottomrule
+\end{tabular}
+\end{table*}
+
 % 1st lvl

### 2020-04-15 paper/main.tex
Sort result figure and tables into text
Have a TODO list
Add TODOs for pieces that I thought we had agreed to remove

@@
 
-\clearpage
-
-% Also weshalb wird das temporal filtering der regressoren wann wie gemacht??? -> nachschlagen
-% “You should normally apply the same temporal filtering to the model as you have applied to the data, as the model is designed to look like the data before temporal filtering was applied.
-In this way, long-time-scale components in the model will be dealt with correctly.
-This is set with the Apply temporal filtering option.”
-\begin{figure*}
-  \centering
-% \includegraphics[width=0.4\textwidth]{frog.jpg}
-  \includegraphics[width=\linewidth]{figures/regressor-corr}
-  \caption{Pearson correlation coefficients of the 26 regressors used in the analysis to validate the annotation.
-Regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation.}
-\label{fig:reg-corr}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-% \includegraphics[width=0.4\textwidth]{frog.jpg}
-  \includegraphics[width=\linewidth]{figures/slicescolorbars}
-  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05; cluster corr.; MNI template space).}
-  \label{fig:results}
-\end{figure*}
-
-\begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast words > no-speech.}
-\label{tab:cope1}
-\begin{tabular}{rrrrrrrrrrp{3cm}}
-\toprule
-& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{5-7} \cmidrule{8-10}
-Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
-\midrule
-4 & 14990 & 0 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
-3 & 14469 & 0 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
-2 & 1971 & 2.37E-16 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
-1 & 217 & 0.00214 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').}
-\label{tab:cope3}
-\begin{tabular}{rrrrrrrrrrp{3cm}}
-\toprule
-& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{5-7} \cmidrule{8-10}
-Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
-\midrule
-9 & 7691 & 2.80E-45 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
-8 & 5928 & 5.97E-38 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
-7 & 479 & 1.13E-06 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
-6 & 420 & 4.65E-06 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
-5 & 407 & 6.38E-06 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
-4 & 294 & 0.000115 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
-3 & 121 & 0.0237 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
-2 & 117 & 0.0274 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
-1 & 115 & 0.0295 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
-\bottomrule
-\end{tabular}
-
-\end{table*}
-
-\begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon'').}
-\label{tab:cope5}
-\begin{tabular}{rrrrrrrrrrp{3cm}}
-\toprule
-& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{5-7} \cmidrule{8-10}
-Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
-\midrule
-4 & 3166 & 2.79E-25 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
-3 & 1753 & 7.18E-17 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
-2 & 166 & 0.00446 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
-1 & 149 & 0.00793 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
-\bottomrule
-\end{tabular}
-\end{table*}
+\listoftodos
 
@@
 A preliminary annotation according to the rules (s.
-ist jetzt in der obigen Tabelle aus Platzgründen nicht mehr drin; in dieser,\ref{tab:descr-nouns}, einer neuen Tabelle oder im laufenden Text [wird viel Text] bringen) was done by one person and corrected in several runs by the author.
+ist jetzt in der obigen Tabelle aus Platzgründen nicht mehr drin; in dieser,\ref{tab:descr-nouns}, einer neuen Tabelle oder im laufenden Text [wird viel Text] bringen) was done by one person and corrected in several runs by the author.\todo{I thought we said that this aspect should move to the PPA paper?}
 
@@
 \end{tabular}
+\todo[inline]{If the descriptive nounes are moved to the PPA paper, this table should be removed}
 \end{table*}
@@
 
+% Also weshalb wird das temporal filtering der regressoren wann wie gemacht??? -> nachschlagen
+% “You should normally apply the same temporal filtering to the model as you have applied to the data, as the model is designed to look like the data before temporal filtering was applied.
+In this way, long-time-scale components in the model will be dealt with correctly.
+This is set with the Apply temporal filtering option.”
+\begin{figure*}
+  \centering
+% \includegraphics[width=0.4\textwidth]{frog.jpg}
+  \includegraphics[width=\linewidth]{figures/regressor-corr}
+  \caption{Pearson correlation coefficients of the 26 regressors used in the analysis to validate the annotation.
+Regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation.}
+\label{fig:reg-corr}
+\end{figure*}
+
 % 2nd lvl and 3rd lvl
@@
 The contrasts proper nouns > coordinate conjunctions and proper nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.
+
+\begin{figure*}
+  \centering
+% \includegraphics[width=0.4\textwidth]{frog.jpg}
+  \includegraphics[width=\linewidth]{figures/slicescolorbars}
+  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05; cluster corr.; MNI template space).}
+  \label{fig:results}
+  \todo[inline]{Figure not referenced in the text}
+\end{figure*}
+
+\begin{table*}[t]
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast words > no-speech.}
+\label{tab:cope1}
+\begin{tabular}{rrrrrrrrrrp{3cm}}
+\toprule
+& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{5-7} \cmidrule{8-10}
+Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+\midrule
+4 & 14990 & 0 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
+3 & 14469 & 0 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
+2 & 1971 & 2.37E-16 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
+1 & 217 & 0.00214 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
+\bottomrule
+\end{tabular}
+  \todo[inline]{Table not referenced in the text}
+\end{table*}
+
+\begin{table*}[t]
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').}
+\label{tab:cope3}
+\begin{tabular}{rrrrrrrrrrp{3cm}}
+\toprule
+& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{5-7} \cmidrule{8-10}
+Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+\midrule
+9 & 7691 & 2.80E-45 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
+8 & 5928 & 5.97E-38 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
+7 & 479 & 1.13E-06 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
+6 & 420 & 4.65E-06 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
+5 & 407 & 6.38E-06 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
+4 & 294 & 0.000115 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
+3 & 121 & 0.0237 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
+2 & 117 & 0.0274 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
+1 & 115 & 0.0295 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
+\bottomrule
+\end{tabular}
+\todo[inline]{Table not referenced in the text}
+
+\end{table*}
+
+\begin{table*}[t]
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon'').}
+\label{tab:cope5}
+\begin{tabular}{rrrrrrrrrrp{3cm}}
+\toprule
+& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{5-7} \cmidrule{8-10}
+Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+\midrule
+4 & 3166 & 2.79E-25 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
+3 & 1753 & 7.18E-17 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
+2 & 166 & 0.00446 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
+1 & 149 & 0.00793 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
+\bottomrule
+\end{tabular}
+\end{table*}
 
@@
 \end{tabular}
+\todo[inline]{If the descriptive nounes are moved to the PPA paper, this table should be removed}
 \end{center}

### 2020-04-15 paper/main.tex
Remove seemingly unnecessary number column from regressor table
We need to shrink that table further

@@
 \label{tab:regressors}
-\begin{tabular}{llllllllllll}
+\small
+\begin{tabular}{lllllllllll}
 \toprule
-\textbf{no} & \textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
-1 & adja & \aTagAdja & \rAdjaAll & \rAdjaI & \rAdjaII & \rAdjaIII & \rAdjaIV & \rAdjaV & \rAdjaVI & \rAdjaVII & \rAdjaVIII \tabularnewline
-2 & adjd & \aTagAdjd & \rAdjdAll & \rAdjdI & \rAdjdII & \rAdjdIII & \rAdjdIV & \rAdjdV & \rAdjdVI & \rAdjdVII & \rAdjdVIII \tabularnewline
-3 & adv & \aTagAdv & \rAdvAll & \rAdvI & \rAdvII & \rAdvIII & \rAdvIV & \rAdvV & \rAdvVI & \rAdvVII & \rAdvVIII \tabularnewline
-4 & appr & \aTagAppr & \rApprAll & \rApprI & \rApprII & \rApprIII & \rApprIV & \rApprV & \rApprVI & \rApprVII & \rApprVIII \tabularnewline
-5 & apprart & preposition with article & \rApprartAll & \rApprartI & \rApprartII & \rApprartIII & \rApprartIV & \rApprartV & \rApprartVI & \rApprartVII & \rApprartVIII \tabularnewline
-6 & art & \aTagArt & \rArtAll & \rArtI & \rArtII & \rArtIII & \rArtIV & \rArtV & \rArtVI & \rArtVII & \rArtVIII \tabularnewline
-7 & kon & \aTagKon & \rKonAll & \rKonI & \rKonII & \rKonIII & \rKonIV & \rKonV & \rKonVI & \rKonVII & \rKonVIII \tabularnewline
-8 & ne & \aTagNe & \rNeAll & \rNeI & \rNeII & \rNeIII & \rNeIV & \rNeV & \rNeVI & \rNeVII & \rNeVIII \tabularnewline
-9 & nn & \aTagNn & \rNnAll & \rNnI & \rNnII & \rNnIII & \rNnIV & \rNnV & \rNnVI & \rNnVII & \rNnVIII \tabularnewline
-10 & pds & substituting demonstrative pronoun & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII \tabularnewline
-11 & pis & substituting indefinite pronoun & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII \tabularnewline
-12 & pper & \aTagPper & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII \tabularnewline
-13 & pposat & \aTagPposat & \rPposatAll & \rPposatI & \rPposatII & \rPposatIII & \rPposatIV & \rPposatV & \rPposatVI & \rPposatVII & \rPposatVIII \tabularnewline
-14 & prf & reflexive personal pronoun & \rPrfAll & \rPrfI & \rPrfII & \rPrfIII & \rPrfIV & \rPrfV & \rPrfVI & \rPrfVII & \rPrfVIII \tabularnewline
-15 & ptkvz & \aTagPtkvz & \rPtkvzAll & \rPtkvzI & \rPtkvzII & \rPtkvzIII & \rPtkvzIV & \rPtkvzV & \rPtkvzVI & \rPtkvzVII & \rPtkvzVIII \tabularnewline
-16 & vafin & \aTagVafin & \rVafinAll & \rVafinI & \rVafinII & \rVafinIII & \rVafinIV & \rVafinV & \rVafinVI & \rVafinVII & \rVafinVIII \tabularnewline
-17 & vmfin & finite verb, modal & \rVmfinAll & \rVmfinI & \rVmfinII & \rVmfinIII & \rVmfinIV & \rVmfinV & \rVmfinVI & \rVmfinVII & \rVmfinVIII \tabularnewline
-18 & vvfin & \aTagVvfin & \rVvfinAll & \rVvfinI & \rVvfinII & \rVvfinIII & \rVvfinIV & \rVvfinV & \rVvfinVI & \rVvfinVII & \rVvfinVIII \tabularnewline
-19 & vvinf & \aTagVvinf & \rVvinfAll & \rVvinfI & \rVvinfII & \rVvinfIII & \rVvinfIV & \rVvinfV & \rVvinfVI & \rVvinfVII & \rVvinfVIII \tabularnewline
-20 & vvpp & \aTagVvpp & \rVvppAll & \rVvppI & \rVvppII & \rVvppIII & \rVvppIV & \rVvppV & \rVvppVI & \rVvppVII & \rVvppVIII \tabularnewline
-21 & tag\_other & all other TAG categories & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII \tabularnewline
-\cline{1-12}
-22 & sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
-23 & phones & 80 most often occuring phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
-24 & no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
-\cline{1-12}
-25 & fg\_ad\_lrdiff & left-right volume difference & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII \tabularnewline
-26 & fg\_ad\_rms & root mean square & \rFgadrmsAll & \rFgadrmsI & \rFgadrmsII & \rFgadrmsIII & \rFgadrmsIV & \rFgadrmsV & \rFgadrmsVI & \rFgadrmsVII & \rFgadrmsVIII \tabularnewline
+adja & \aTagAdja & \rAdjaAll & \rAdjaI & \rAdjaII & \rAdjaIII & \rAdjaIV & \rAdjaV & \rAdjaVI & \rAdjaVII & \rAdjaVIII \tabularnewline
+adjd & \aTagAdjd & \rAdjdAll & \rAdjdI & \rAdjdII & \rAdjdIII & \rAdjdIV & \rAdjdV & \rAdjdVI & \rAdjdVII & \rAdjdVIII \tabularnewline
+adv & \aTagAdv & \rAdvAll & \rAdvI & \rAdvII & \rAdvIII & \rAdvIV & \rAdvV & \rAdvVI & \rAdvVII & \rAdvVIII \tabularnewline
+appr & \aTagAppr & \rApprAll & \rApprI & \rApprII & \rApprIII & \rApprIV & \rApprV & \rApprVI & \rApprVII & \rApprVIII \tabularnewline
+apprart & preposition with article & \rApprartAll & \rApprartI & \rApprartII & \rApprartIII & \rApprartIV & \rApprartV & \rApprartVI & \rApprartVII & \rApprartVIII \tabularnewline
+art & \aTagArt & \rArtAll & \rArtI & \rArtII & \rArtIII & \rArtIV & \rArtV & \rArtVI & \rArtVII & \rArtVIII \tabularnewline
+kon & \aTagKon & \rKonAll & \rKonI & \rKonII & \rKonIII & \rKonIV & \rKonV & \rKonVI & \rKonVII & \rKonVIII \tabularnewline
+ne & \aTagNe & \rNeAll & \rNeI & \rNeII & \rNeIII & \rNeIV & \rNeV & \rNeVI & \rNeVII & \rNeVIII \tabularnewline
+nn & \aTagNn & \rNnAll & \rNnI & \rNnII & \rNnIII & \rNnIV & \rNnV & \rNnVI & \rNnVII & \rNnVIII \tabularnewline
+pds & substituting demonstrative pronoun & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII \tabularnewline
+pis & substituting indefinite pronoun & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII \tabularnewline
+pper & \aTagPper & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII \tabularnewline
+pposat & \aTagPposat & \rPposatAll & \rPposatI & \rPposatII & \rPposatIII & \rPposatIV & \rPposatV & \rPposatVI & \rPposatVII & \rPposatVIII \tabularnewline
+prf & reflexive personal pronoun & \rPrfAll & \rPrfI & \rPrfII & \rPrfIII & \rPrfIV & \rPrfV & \rPrfVI & \rPrfVII & \rPrfVIII \tabularnewline
+ptkvz & \aTagPtkvz & \rPtkvzAll & \rPtkvzI & \rPtkvzII & \rPtkvzIII & \rPtkvzIV & \rPtkvzV & \rPtkvzVI & \rPtkvzVII & \rPtkvzVIII \tabularnewline
+vafin & \aTagVafin & \rVafinAll & \rVafinI & \rVafinII & \rVafinIII & \rVafinIV & \rVafinV & \rVafinVI & \rVafinVII & \rVafinVIII \tabularnewline
+vmfin & finite verb, modal & \rVmfinAll & \rVmfinI & \rVmfinII & \rVmfinIII & \rVmfinIV & \rVmfinV & \rVmfinVI & \rVmfinVII & \rVmfinVIII \tabularnewline
+vvfin & \aTagVvfin & \rVvfinAll & \rVvfinI & \rVvfinII & \rVvfinIII & \rVvfinIV & \rVvfinV & \rVvfinVI & \rVvfinVII & \rVvfinVIII \tabularnewline
+vvinf & \aTagVvinf & \rVvinfAll & \rVvinfI & \rVvinfII & \rVvinfIII & \rVvinfIV & \rVvinfV & \rVvinfVI & \rVvinfVII & \rVvinfVIII \tabularnewline
+vvpp & \aTagVvpp & \rVvppAll & \rVvppI & \rVvppII & \rVvppIII & \rVvppIV & \rVvppV & \rVvppVI & \rVvppVII & \rVvppVIII \tabularnewline
+tag\_other & all other TAG categories & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII \tabularnewline
+e{1-12}
+sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
+phones & 80 most often occuring phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
+no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
+e{1-12}
+fg\_ad\_lrdiff & left-right volume difference & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII \tabularnewline
+fg\_ad\_rms & root mean square & \rFgadrmsAll & \rFgadrmsI & \rFgadrmsII & \rFgadrmsIII & \rFgadrmsIV & \rFgadrmsV & \rFgadrmsVI & \rFgadrmsVII & \rFgadrmsVIII \tabularnewline
 \bottomrule

### 2020-04-15 paper/main.tex
Compact table to fit page
Comment on terminology
Acknowledgements

@@
 \label{tab:regressors}
-\small
-\begin{tabular}{lllllllllll}
+\footnotesize
+\begin{tabular}{lp{3.5cm}lllllllll}
 \toprule
@@
 tag\_other & all other TAG categories & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII \tabularnewline
-e{1-12}
+%e{1-12}
 sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
@@
 no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
-e{1-12}
+%e{1-12}
 fg\_ad\_lrdiff & left-right volume difference & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII \tabularnewline
@@
 \end{tabular}
+\todo[inline]{I think this table doesn't talk about 'regressors'. It talks about the
+events that were selected/available to build GLM regressors from them. Hence the term
+'event' should be used here, and cross-reference to figure \ref{fig:reg} should be made}
+\todo[inline]{what does e1-12 stand for? It makes the label column too wide}
 \end{table*}
@@
 \subsection*{Grant information}
-% subsection in Schnitte-Anno
-% im Großen und Ganzen: Ich habe keine Ahnung, wer meine Ernährer sind
-Christian O. Häusler was supported by a graduate stipend from the German federal state of Saxony-Anhalt and ???
-Michale Hanke was supported by ???
+
+COH was supported by a graduate stipend from the German federal state of
+Saxony-Anhalt and MH was supported by funds from the German federal state of
+Saxony-Anhalt and the European Regional Development Fund (ERDF), Project:
+Center for Behavioral Brain Sciences (CBBS). Work on the adapting data
+management technology for this study was in part supported by the European
+Union’s Horizon 2020 Research and Innovation Programme under Grant Agreement
+no. 785907 (HBP SGA2).
 

### 2020-04-15 paper/main.tex
Fill in URL

@@
 In addition, released data, code, and manuscript sources are also available on
-Github (\url{https://github.com/psychoinformatics-de/WHAT-EVER}).
+Github (\url{https://github.com/psychoinformatics-de/studyforrest-paper-speechannotation}).
 

### 2020-04-15 paper/main.tex
Thoughts on purpose and conclusion

@@
 
+\todo[inline]{Decide on having a 'conclusion' or not. If the section is not
+  mandatory and there are no further conclusions than at the end of the
+  introduction then I am OK with not having one. However, the paper needs to
+  serve a purpose. One is, of course, to be documentation for the annotation.
+  Another is to attract people to use this work for their own studies. I would
+  even argue that this is the \textit{main} purpose, given that the annotation
+  in itself represents to scientific progress. So the paper need to give an
+  accurate assessment what this can be used for and what is problematic or
+  impossible. ATM this is the only statement in this regard: 'facilitates
+  modelling of hemodynamic brain responses correlating with speech-related
+  events' and the only indication of purpose is 'additional confound measures'. I
+  think this is incongruent with the amount of work and the level of detail of
+  this annotation.}
+
 \subsection*{Author contributions}

### 2020-04-15 paper/main.tex
Add hint on endfloat
Remove the internal label 'research cut'

@@
 \geometry{right=4cm}
+% enable the 'endfloat' package to sort all tables and figures to the
+% end of the document without having to edit the manuscript
+%\usepackage{endfloat}
 \usepackage{booktabs}
@@
 % “hardcoded” Zitationen sind aber noch im laufenden Text.
-We annotated speech in the slightly shortened ``research cut'' of the movie
-\citep{hanke2016simultaneous} and its temporally aligned audio-description
+We annotated speech in stimuli built from the motion picture ``Forrest Gump'' as
+used in two previous studies: an audio-visual movie
+\citep{hanke2016simultaneous}, and its temporally aligned audio-description
 \citep{hanke2014audiomovie}. For the movie stimulus, we used the audio track of

### 2020-04-15 paper/main.tex
More comments on the annotation procedure

@@
 
+\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved}
+
 \section*{Materials and methods}
@@
 In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content
+
 \subsection*{Annotation procedure}
@@
 % Die "most basic" Datei, die das Dataset enthält ist der Merge aus Diaolog, Narrator & Non-Speech-Annotation
-Preliminary, orthographic transcriptions of dialogues (german\_dialog.csv),
+Preliminary, orthographic transcriptions of dialogues (\texttt{german\_dialog.csv})\todo{filenames should have some text markup. I did this example, please apply to other locations as well},
 non-speech vocalizations (e.g. laughing or groaning;
 non\_speech\_vocalization.json), and the audio-description's narrator
-(german\_audio\_description.csv) were merged and converted to Praat's
-\citep{boersma2019praat} .TextGrid format (
+(german\_audio\_description.csv)\todo{where were those from? citation missing} were merged and converted to Praat's
+\citep{boersma2019praat} TextGrid format (
 \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}). The merged transcription
@@
 along (the audio file of) the audio-description in Praat v6.0.22 for manual
-improvements: In several passes, the approximate temporal onsets and offsets
+improvements\todo{in general process information is not relevant: of course you need to open a file to work with it.
+The Q is what you did to it, why, and how exactly.
+So instead of "was opened along (the audio file of) the audio-description in Praat v6.0.22", better "was edited in Praat v6.0.22 for manual validation against the original audio"}: In several passes\todo{why several passes?}, the approximate temporal onsets and offsets
 were corrected. Intervals containing several sentences were split into intervals
@@
 noise) or low volume non-speech vocalizations that are difficult to recognize by
-a regular audience were dropped, too.
+a regular audience\todo{what is a regular audience? without neurological disorders ;-)} were dropped, too.
 
@@
 We used the Montreal Forced Aligner v1.0.1 
-\href{montrealcorpustools.github.io/Montreal-Forced-Aligner}{montrealcorpustools.github.io/Montreal-Forced-Aligner}\citep{mcauliffe2017montreal};to
+\href{montrealcorpustools.github.io/Montreal-Forced-Aligner}{montrealcorpustools.github.io/Montreal-Forced-Aligner}\citep{mcauliffe2017montreal}\todo{we need a consistent way of citing software.
+I think it is overkill to have a reference, plus a URL, plus a version in the main text.
+Either everything in the reference, or (maybe) just name+version in the text};to
 algorithmically identify the onset and offset of each word and phoneme embedded
@@
 provided by Prosodylab (\href{http://prosodylab.org}{prosodylab.org}) that uses
-the Prosodylab PhoneSet. The dictionary was manually updated with movie-specific
-German words. The pronunciation of English words occurring in the otherwise
+the Prosodylab PhoneSet\todo{same here, use a proper bibtex reference}. The dictionary was manually updated with movie-specific
+German words\todo{which words, how determined, why?}. The pronunciation of English words occurring in the otherwise
 German audio track was taken from an English pronunciation dictionary
-(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.
+(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet\todo{It would help a non-expert like me to understand why a PhoneSet is important for this annotation, sounds like a jargon}.
 
@@
 % kommt selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.
-The audio file was converted from .FLAC to .WAV via ffmpeg v4.1.4
+The audio file was converted from .FLAC to .WAV\todo{Better WAV not .WAV, likewise for others} via ffmpeg v4.1.4
 (\href{www.ffmpeg.org}{ffmpeg.org}) to meet the aligner's requirements. This

### 2020-04-17 paper/main.tex
overall revisions

--- 2020-04-15 paper/main.tex
@@
 
-% provide full affiliation information (including full institutional address, ZIP code and e-mail address) for all authors, and identify who is/are the corresponding author(s).
-% EMAIL hier noch "kanonisch" unterbringen
-% Madeburg habe ich nicht mit reingenommen, obwohl MD/Sachsen-Anhalt unten wg. Stipendium unter Funding kommt.
-\author[1, 2]{Christian~O.~Häusler}
-\author[1, 2]{Michael Hanke}
+\author[1, 2]{Christian~O.~Häusler \\ email \href{mailto:c.haeusler@fz-juelich.de}{c.haeusler@fz-juelich.de} }
+\author[1, 2]{Michael~Hanke}
 
-\affil[1]{Institute of Neuroscience and Medicine, Brain \& Behaviour (INM-7), Research Centre Jülich, Jülich, Germany}
-\affil[2]{Institute of Systems Neuroscience, Medical Faculty, Heinrich Heine University, Düsseldorf, Germany}
+\affil[1]{Institute of Neuroscience and Medicine, Brain \& Behaviour (INM-7), Research Centre Jülich, Jülich, 52425, Germany}
+\affil[2]{Institute of Systems Neuroscience, Medical Faculty, Heinrich Heine University, Düsseldorf, 40225, Germany}
 
 \maketitle
+
+\todo[inline]{wie email und ORCID (du: https://orcid.org/0000-0001-6398-6370; ich: https://orcid.org/0000-0002-0936-317X) unterbringen?}
+
 \thispagestyle{fancy}
@@
 % up to 300 words
-Kommt ganz am Ende;
-Intro, Method, Results, Discussion;
-hier ggf. bereits Praat erwähnen;
-im Gegensatz zu Sätzen und Phones haben Einzelworte zusätzliche Annos
+\todo[inline]{The abstract should come now}
+Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and it's audio-only variant (i.e.
+audio-description), as an addition to a large public functional brain imaging dataset (\url{http://studyforrest.org}).
+The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), and \aPhonesAll\ phonemes.
 
-\todo[inline]{The abstract should come now. It is needed to evaluate the
-concept of the paper in the light of its content and vice versa.}
+Zusätzliche Annos der Worte
 
+This annotation enables further studies of language perception and semantic processing under conditions of real-life complexity using the studyforrest dataset.
+
+Wort zur Validierungsstudie?
 \end{abstract}
+
 \section*{Keywords}
 % maximal 8
-language, speech, annotation, fMRI, natural stimulation, narrative, studyforrest
+annnotation, language, speech, lateralization, narrative, natural stimulation, fMRI, studyforrest
 
@@
 \section*{Introduction}
-% Links sind jetzt im laufenden Text; habs nach wie vor mit \href gemacht
-% sieht bei längeren Links natürlich kacke aus
-
-% largely adopted from haeusler2016annotation
-% https://f1000research.com/articles/5-2273
-% In Einleitung muss wohl noch etwas zu "reproducible research" und "datalad dataset" kommen
+\todo[inline]{Bitte am Ende (?) der Einleitung etwas zu "reproducible research" \& "datalad dataset" bringen}
 Cognitive neuroimaging research is moving towards studying brain behavior
-under conditions of real-life(-like complexity).
+under conditions of real-life-like complexity.
 Motion pictures \citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not, lerner2011topographic} are increasingly utilized as so called naturalistic stimuli.
 
-% new; not from haeusler2016annotation
 Because naturalistic stimuli are multi-dimensional and their temporal structure
-is (usually) unknown, data-driven methods like intersubject correlation
-(ISC)\citep{hasson2004intersubject} or independent component analysis
+is usually unknown, data-driven methods like intersubject correlation (ISC)\citep{hasson2004intersubject} or independent component analysis
 (ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
-corresponding fMRI data. Nevertheless, theory-driven\todo{model-based?, there is little theroy in GLM} analyses like a general
-linear model (GLM) are necessary to not just explain how but also when and why a
-brain region is responding to a stimulus \citep{hamilton2018revolution}. Studies
-using GLMs based on annotations of a stimulus' temporal structure have
+corresponding fMRI data.
+Nevertheless, model-driven methods like a general linear model (GLM) are necessary to not just explain how but also when (and why) a brain region is responding to a stimulus \citep{hamilton2018revolution}.
+Studies using GLMs based on annotations of a stimulus' temporal structure have
 elucidated how the brain responds to visual features of a movie
@@
 
-% adapted from haeusler2016annotation
-% nun ja, folgend nicht super korrekt: sentences sind nicht vollständige
-% Sätze im linguistischen Sinne (Subjekt, Objekt, Prädikat), sondern auch
-% Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh").
+% hier sind “sentences” nicht vollständige Sätze im linguistischen Sinne (Subjekt, Objekt, Prädikat), sondern auch Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh").
 % Sätze im linguistischen Sinne sind in der Annotation durch "." oder "?" am
-% Ende gekennzeichnet. Sollte aber so passen.
-For this publication, we annotated the onsets and offsets, and content of
-sentences, single words, and phonemes spoken in the movie Forrest Gump (R.
-Zemeckis, Paramount Pictures, 1994) \citep{ForrestGumpMovie}. fMRI data of
-participants watching the audio-visual movie \citep{hanke2016simultaneous} and
-it's audio-description for visually impaired persons \citep{hanke2014audiomovie}
-are the core data of the publicly available \textit{studyforrest} dataset
-(\href{www.studyforrest.org}{studyforrest.org}). Additional fMRI data
-\citep{sengupta2016extension} include retinotopic mappings and localization of
-higher visual areas of the same participants.
+% Ende gekennzeichnet.
+For this publication, we annotated the onsets and offsets, and content of sentences, single words and phonemes spoken in the audio-visual (AV) movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its corresponding audio-only (AO) variant (i.e.
+audio-description) for visually impaired persons \citep{ForrestGumpDVD}.
 % paper regarding mention musical not mentioned
-% und damit zitiere ich mich als dortiger Coauthor nicht selbst. Skandal!
+fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
+Additional fMRI data include retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.
 
+\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved; welche previous work wird verbessert oder sogar replaced?}
 The current annotation facilitates modelling of hemodynamic brain responses
-correlating with speech-related events in the movie and audio-description.
-Further, it extends already available annotations of portrayed emotions
-\citep{labs2015portrayed} and perceived emtions
-\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}.
-All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional
-confound measures describing key properties of major building blocks of the stimulus.
+correlating with speech-related events in the two stimuli.
+Further, it extends already available annotations of portrayed emotions \citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}.
+All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional confound measures describing key properties of major building blocks of the stimulus.
 
@@
 \subsection*{Stimulus}
-% References sind vom Anno-Paper in die .bib-Datei übernommen worden; die
-% “hardcoded” Zitationen sind aber noch im laufenden Text.
-We annotated speech in stimuli built from the motion picture ``Forrest Gump'' as
-used in two previous studies: an audio-visual movie
-\citep{hanke2016simultaneous}, and its temporally aligned audio-description
-\citep{hanke2014audiomovie}. For the movie stimulus, we used the audio track of
-the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video,
-DE103519SV)\citep{ForrestGumpDVD}. For the audio-only stimulus, we used the
-movie's audio-description that was broadcast as an additional audio track for
-visually impaired listeners on Swiss public television (Koop, Michalski,
-Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk,
-2009)\citep{ForrestGumpGermanAD}. The plot of the movie is already carried by an
-off-screen voice of the main character Forrest Gump.
-In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content
+We annotated speech in the slightly shortened ``research cut'' of the movie \citep{hanke2016simultaneous} and its temporally aligned audio-description \citep{hanke2014audiomovie}.
+For the movie stimulus, we used the audio track of the German DVD release \citep{ForrestGumpDVD}.
+For the audio-only stimulus, we used the movie's audio-description that was broadcast as an additional audio track for visually impaired listeners on Swiss public television \citep{ForrestGumpGermanAD}.
+The plot of the movie is already carried by an off-screen voice of the main character Forrest Gump.
+In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content.
+
 \subsection*{Annotation procedure}
-% wo kommen die "preliminaries transcriptions" her?
-% Die "most basic" Datei, die das Dataset enthält ist der Merge aus Diaolog, Narrator & Non-Speech-Annotation
-Preliminary, orthographic transcriptions of dialogues (german\_dialog.csv),
-non-speech vocalizations (e.g. laughing or groaning;
-non\_speech\_vocalization.json), and the audio-description's narrator
-(german\_audio\_description.csv) were merged and converted to Praat's
-\citep{boersma2019praat} .TextGrid format (
-\href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}). The merged transcription
-containing one onset and offset for usually a couple of sentences was opened
-along (the audio file of) the audio-description in Praat v6.0.22 for manual
-improvements: In several passes, the approximate temporal onsets and offsets
-were corrected. Intervals containing several sentences were split into intervals
-containing only one sentence. When two or more persons were speaking
-simultaneously the less dominant (background) voice was dropped. Low volume
-background speech (especially occurring during music or continuous environmental
-noise) or low volume non-speech vocalizations that are difficult to recognize by
-a regular audience were dropped, too.
+\todo[inline]{wo kommen die "preliminaries transcriptions" etc.?
+Habe die von Medusa; die "most basic" Datei, die das Dataset enthält ist wie abgesprochen der Merge aus Dialog (ungetrennte Sentences), Narrator \& Non-Speech-Annotation = \texttt{speech-vocal.csv}}
+Preliminary, orthographic transcriptions of dialogues (\texttt{german\_dialog.csv}), non-speech vocalizations (e.g.
+laughing or groaning; \texttt{non\_speech\_vocalization.json}), and the audio-description's narrator
+(\texttt{german\_audio\_description.csv}) were merged (\texttt{speech-vocal.csv}) and converted to Praat's \citep{boersma2019praat} TextGrid format  (\texttt{speech-vocal.TextGrid}).
+% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
+The merged transcription containing one onset and offset for usually a couple of sentences was edited in Praat v6.0.22 for manual validation against the original audio.
+The following steps were done in several passes to iteratively improve the quality of the data:
+Approximate temporal onsets and offsets were corrected, and intervals containing several sentences were split into intervals containing only one sentence.
+\todo[inline]{what is a regular audience?
+without neurological disorders ;-); Simpel: eine audience, die den Film nicht 45x auf voller Lautstärke über Kopfhörer mit Transkription danebenliegend gehört hat ;-)}
+When two or more persons were speaking simultaneously the less dominant voice was dropped.
+Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations that are difficult to recognize by the audience were dropped, too.
 
 % Alignment preparations
-We used the Montreal Forced Aligner v1.0.1
-\href{montrealcorpustools.github.io/Montreal-Forced-Aligner}{montrealcorpustools.github.io/Montreal-Forced-Aligner}\citep{mcauliffe2017montreal};to
+We used the Montreal Forced Aligner v1.0.1 \citep{mcauliffe2017montreal} to
 algorithmically identify the onset and offset of each word and phoneme embedded
-in the transcribed sentences. To enable the aligner to look up the pronunciation
-of every word, we chose a German pronunciation dictionary
-\href{https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}{raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict}
-provided by Prosodylab (\href{http://prosodylab.org}{prosodylab.org}) that uses
-the Prosodylab PhoneSet. The dictionary was manually updated with movie-specific
-German words. The pronunciation of English words occurring in the otherwise
-German audio track was taken from an English pronunciation dictionary
-(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.
+in the transcribed sentences.
+% http://prosodylab.org
+% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
+To enable the aligner to look up the phonemes within every word, we chose a German pronunciation dictionary provided by Prosodylab \citep {gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the pronounciation of single phonemes.
+To improve the quality of the automatic alignment, this dictionary was manually updated with German words that were missing in the dictionary but occur in the stimuli.
+The pronunciation of English words occurring in the otherwise German audio track was taken from an English pronunciation dictionary provided by the Montreal Language Modeling lab (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.
 
 % Alignment
-% Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach
-% die Event-Borders zwischen den Phonemen herausgenommen. Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
-% Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach).
-% kommt selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.
-The audio file was converted from .FLAC to .WAV via ffmpeg v4.1.4
-(\href{www.ffmpeg.org}{ffmpeg.org}) to meet the aligner's requirements. This
-.WAV file, the transcription of sentences, and the updated dictionary were
+\todo[inline]{Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach die Event-Borders zwischen den Phonemen herausgenommen.
+Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
+Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach).
+kommt jedoch so selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.}
+The audio file was converted from FLAC to WAV via FFmpeg v4.1.4 \citep{ffmpeg} to meet the aligner's requirements.
+This WAV file, the transcription of sentences, and the updated dictionary were
 submitted to the aligner that first trained an acoustic model on the data and
-then performed the alignment. In a first step, the resulting .TextGrid file that
-contains onsets and offsets of words and phonemes was opened in Praat to check
-and correct the automatic alignment. In several passes, words [and their
-corresponding phonemes] on which the automatic alignment performed moderately
-were corrected. Some (low volume) sentences that are spoken in continuously
-noisy settings (pursuit, battle, hurricane, demonstration/rally, disco) were
-removed due to poor overall alignment performance. In a second step, the
-complete sentences of the orthographic transcription were copied into the
-annotation (s.
-table \ref{tab:overview} for an overview of the annotation's content).
-In a third step, the name of the speaker was added for every sentence (s.
-table \ref{tab:speakers} for the most often occurring speakers).
-During every new step results from all previous steps were checked again for errors and corrected.
+then performed the alignment.
+In a first step, the resulting .TextGrid file that contains onsets and offsets of words and phonemes was corrected in Praat, again interatively in several passes.
+Onsets and offsets of words and their corresponding phonemes on which the automatic alignment performed moderately were corrected.
+Some (low volume) sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, rally, disco) were removed due to poor overall alignment performance.
+In a second step, the complete sentences of the orthographic transcription were copied into the annotation (s. table \ref{tab:overview} for an overview of the annotation's content).
+In a third step, the name of the speaker was added for every sentence (cf. table \ref{tab:speakers} for the most often occurring speakers).
+During every new step results from previous steps were checked again for errors and corrected.
 
 \begin{table*}[tbp]
-\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments.
+\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments used during fMRI scanning.
 The label ``Sentences''' comprises complete grammatical sentences (i.e.
-having a subject and a predicate, and additionally marked with a full stop in the annotation).
-The  ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g.
+having a subject and a predicate) or questions that are additionally marked with a full stop or question mark.
+The  label ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g.
 ``ha, ha, ha'') or in isolation (e.g.
@@
 
-% bei ein paar Namen bin ich ggf. von Labs abgewichen (genauer identifiziert, ggf. kleine Fehler korrigiert. Ist dann aber nur bei Personen, die 1-2x mit 1-2 Sätzen auftauchen.
 \begin{table*}[btp]
@@
 The narrator only occurrs in the audio-description of the movie.
-Shown names are identical to the names used in \citep{labs2015portrayed}.
+Shown names are mostly identical to the names used in \citep{labs2015portrayed}.
 Overall 97 persons were identified.}
@@
 \end{tabular}
-\end{table*}
-
-% descriptive Nouns
-% hier ggf. noch angeben, dass die effektiv identisch waren
-% Florian hat zwei Regeln falsch verstanden, sonst war übereinstimmung >90%
-A further annotation of the audio-description's narrator was done manually: Two
-persons performed a categorization of nouns embedded in sentences spoken by the
-narrator to describe the movie's missing visual content. Categories focus on the
-cinematographic scene's environment, inherent objects, persons, and a person's
-appearance.
-A preliminary annotation according to the rules (s.
-ist jetzt in der obigen Tabelle aus Platzgründen nicht mehr drin; in dieser,\ref{tab:descr-nouns}, einer neuen Tabelle oder im laufenden Text [wird viel Text] bringen) was done by one person and corrected in several runs by the author.\todo{I thought we said that this aspect should move to the PPA paper?}
-
-\begin{table*}[t]
-    \caption{Narrator's descriptive nouns.
-All categories sorted alphapetically.
-Examples are given in English.
-Description (of rules) fehlt in dieser Tabelle (vgl.
-alte Tabelle auf der allerletzten Seite).
-Wird nämlich in einer Tabelle mit horizontaler Ausrichtung eng.
-Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best.
-der Zeit.}
-\label{tab:descr-nouns}
-\begin{tabular}{lllllllllll}
-\toprule
-\textbf{label} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
-\midrule
-body & back, hip, shoulder; jacket, dress, shirt & \aDescrBodyAll & \aDescrBodyI & \aDescrBodyII & \aDescrBodyIII & \aDescrBodyIV & \aDescrBodyV & \aDescrBodyVI & \aDescrBodyVII & \aDescrBodyVIII \tabularnewline
-bodypart  & arm, finger, leg, toe & \aDescrBodypartAll & \aDescrBodypartI & \aDescrBodypartII & \aDescrBodypartIII & \aDescrBodypartIV & \aDescrBodypartV & \aDescrBodypartVI & \aDescrBodypartVII & \aDescrBodypartVIII\tabularnewline
-face & face, ear, nose, mouth & \aDescrFaceAll & \aDescrFaceI & \aDescrFaceII & \aDescrFaceIII & \aDescrFaceIV & \aDescrFaceV & \aDescrFaceVI & \aDescrFaceVII & \aDescrFaceVIII \tabularnewline
-female & nurse, mother, woman & \aDescrFemaleAll & \aDescrFemaleI & \aDescrFemaleII & \aDescrFemaleIII & \aDescrFemaleIV & \aDescrFemaleV & \aDescrFemaleVI & \aDescrFemaleVII & \aDescrFemaleVIII \tabularnewline
-females & women & \aDescrFemalesAll & \aDescrFemalesI & \aDescrFemalesII & \aDescrFemalesIII & \aDescrFemalesIV & \aDescrFemalesV & \aDescrFemalesVI & \aDescrFemalesVII & \aDescrFemalesVIII \tabularnewline
-fname & Jenny & \aDescrFnameAll & \aDescrFnameI & \aDescrFnameII & \aDescrFnameIII & \aDescrFnameIV & \aDescrFnameV & \aDescrFnameVI & \aDescrFnameVII & \aDescrFnameVIII \tabularnewline
-furniture & bench, bed, table, chair & \aDescrFurnitureAll & \aDescrFurnitureI & \aDescrFurnitureII & \aDescrFurnitureIII & \aDescrFurnitureIV & \aDescrFurnitureV & \aDescrFurnitureVI & \aDescrFurnitureVII & \aDescrFurnitureVIII \tabularnewline
-geo & building, tree, street, alley, meadow, cornfield, river & \aDescrGeoAll & \aDescrGeoI & \aDescrGeoII & \aDescrGeoIII & \aDescrGeoIV & \aDescrGeoV & \aDescrGeoVI & \aDescrGeoVII & \aDescrGeoVIII \tabularnewline
-geo-room & living room; wall, door, window, floor, turf & \aDescrGeoroomAll & \aDescrGeoroomI & \aDescrGeoroomII & \aDescrGeoroomIII & \aDescrGeoroomIV & \aDescrGeoroomV & \aDescrGeoroomVI & \aDescrGeoroomVII & \aDescrGeoroomVIII \tabularnewline
-head & head, hair, ear, neck, helmet & \aDescrHeadAll & \aDescrHeadI & \aDescrHeadII & \aDescrHeadIII & \aDescrHeadIV & \aDescrHeadV & \aDescrHeadVI & \aDescrHeadVII & \aDescrHeadVIII \tabularnewline
-male & man, father, soldier & \aDescrMaleAll & \aDescrMaleI & \aDescrMaleII & \aDescrMaleIII & \aDescrMaleIV & \aDescrMaleV & \aDescrMaleVI & \aDescrMaleVII & \aDescrMaleVIII \tabularnewline
-males & boys, opponents & \aDescrMalesAll & \aDescrMalesI & \aDescrMalesII & \aDescrMalesIII & \aDescrMalesIV & \aDescrMalesV & \aDescrMalesVI & \aDescrMalesVII & \aDescrMalesVIII \tabularnewline
-mname & Bubba, Kennedy & \aDescrMnameAll & \aDescrMnameI & \aDescrMnameII & \aDescrMnameIII & \aDescrMnameIV & \aDescrMnameV & \aDescrMnameVI & \aDescrMnameVII & \aDescrMnameVIII \tabularnewline
-object & telephone, car & \aDescrObjectAll & \aDescrObjectI & \aDescrObjectII & \aDescrObjectIII & \aDescrObjectIV & \aDescrObjectV & \aDescrObjectVI & \aDescrObjectVII & \aDescrObjectVIII \tabularnewline
-objects & wheels, photos & \aDescrObjectsAll & \aDescrObjectsI & \aDescrObjectsII & \aDescrObjectsIII & \aDescrObjectsIV & \aDescrObjectsV & \aDescrObjectsVI & \aDescrObjectsVII & \aDescrObjectsVIII \tabularnewline
-persons & hippies, patients & \aDescrPersonsAll & \aDescrPersonsI & \aDescrPersonsII & \aDescrPersonsIII & \aDescrPersonsIV & \aDescrPersonsV & \aDescrPersonsVI & \aDescrPersonsVII & \aDescrPersonsVIII \tabularnewline
-setting\_new & on a ``bridge'', on an ``alley'', on ``campus'' & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII \tabularnewline
-setting\_rec & at the ``bus stop'' & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII \tabularnewline
-++ &  in the ``evening'', it's ``daytime'', ``later'' & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\todo[inline]{If the descriptive nounes are moved to the PPA paper, this table should be removed}
 \end{table*}
@@
 
+\todo[inline]{I think this table doesn't talk about 'regressors'. It talks about the
+events that were selected/available to build GLM regressors from them. Hence the term
+'event' should be used here, and cross-reference to figure \ref{fig:reg} should be made}
+\todo[inline]{what does e1-12 stand for? It makes the label column too wide}
+
 \begin{table*}[t]
@@
 pds & substituting demonstrative pronoun & \rPdsAll & \rPdsI & \rPdsII & \rPdsIII & \rPdsIV & \rPdsV & \rPdsVI & \rPdsVII & \rPdsVIII \tabularnewline
-pis & substituting indefinite pronoun & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & pper \rPisVII & \rPisVIII \tabularnewline
+pis & substituting indefinite pronoun & \rPisAll & \rPisI & \rPisII & \rPisIII & \rPisIV & \rPisV & \rPisVI & \rPisVII & \rPisVIII \tabularnewline
 pper & \aTagPper & \rPperAll & \rPperI & \rPperII & \rPperIII & \rPperIV & \rPperV & \rPperVI & \rPperVII & \rPperVIII \tabularnewline
@@
 \end{tabular}
-\todo[inline]{I think this table doesn't talk about 'regressors'. It talks about the
-events that were selected/available to build GLM regressors from them. Hence the term
-'event' should be used here, and cross-reference to figure \ref{fig:reg} should be made}
-\todo[inline]{what does e1-12 stand for? It makes the label column too wide}
 \end{table*}
@@
 % von Interpretation klar(er) getrennt halten
-Results: The first contrast that contrasted words to moments where no speech is audible in the audio-description (all 21 tag-related regressors > no-speech) shows\dots;
+figure \ref{fig:results}
+words > no-speech \ref{tab:cope1}
+proper nouns > coordinate conjunctions and proper nouns \ref{tab:cope3}
+nouns > coordinate conjunctions \ref{tab:cope5}
+Results: The first contrast that contrasted words to moments where no speech is audible in the audio-description (words > no-speech) shows\dots;
 left lateralization (bigger cluster left in BA XY => Broca)
-The contrasts proper nouns > coordinate conjunctions and proper nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.
+The contrasts proper nouns > coordinate conjunctions and nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.
 
@@
   \centering
+  \label{fig:results}
 % \includegraphics[width=0.4\textwidth]{frog.jpg}
   \includegraphics[width=\linewidth]{figures/slicescolorbars}
-  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05; cluster corr.; MNI template space).}
-  \label{fig:results}
-  \todo[inline]{Figure not referenced in the text}
+  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected.; MNI template space)}.
 \end{figure*}
 
+% hier die Lateralisation in den Broca Arealen BA44 und BA45 klarer machen
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast words > no-speech.}
+    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words > no-speech.
+Clusters sorted by voxel size.
+The first brain structure given contains the voxel with the maximum Z-Value.}
 \label{tab:cope1}
-\begin{tabular}{rrrrrrrrrrp{3cm}}
+\begin{tabular}{rrrrrrrrrp{6cm}}
 \toprule
-& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{5-7} \cmidrule{8-10}
-Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{4-6} \cmidrule{7-9}
+voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
 \midrule
-4 & 14990 & 0 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
-3 & 14469 & 0 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
-2 & 1971 & 2.37E-16 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
-1 & 217 & 0.00214 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
+14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & l Heschl's G.; lateral superior Occipital C., Angular G., posterior Supramarginal G., middle Temporal G.
+posterior to anterior; part of Planum Temporale, anterior superior Temporal G.
+\\
+14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & r.
+Superior Temporal G.; Angular G., Supramarginal G., middle Temporal G.
+posterior to anterior, Heschl's G.
+, inferior Frontal Gyrus pars opercularis (BA44); parts of Planum Temporale \& pars triangularis (BA45) \\
+1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & frontal Orbital C.; Precentral G.
+(Broca's area BA44), pars triangularis \& Inferior Frontal G.; part of pars opercularis (Broca's area BA44); NO Precentral Gyrus \\
+217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & l. Thalamus \\
 \bottomrule
 \end{tabular}
-  \todo[inline]{Table not referenced in the text}
 \end{table*}
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').}
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').
+Clusters sorted by voxel size.
+The first brain structure given contains the voxel with the maximum Z-Value.}
 \label{tab:cope3}
-\begin{tabular}{rrrrrrrrrrp{3cm}}
+\begin{tabular}{rrrrrrrrrp{6cm}}
 \toprule
-& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{5-7} \cmidrule{8-10}
-Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{4-6} \cmidrule{7-9}
+voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
 \midrule
-9 & 7691 & 2.80E-45 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
-8 & 5928 & 5.97E-38 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
-7 & 479 & 1.13E-06 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
-6 & 420 & 4.65E-06 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
-5 & 407 & 6.38E-06 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
-4 & 294 & 0.000115 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
-3 & 121 & 0.0237 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
-2 & 117 & 0.0274 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
-1 & 115 & 0.0295 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
+7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & l. Planum Temporale; Angular G., Supramarginal G., Heschl's G., Superior Temporal G., Planum Polare, Temporal Pole \\
+5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & r Parietal Operculum, Planum Temporale; Heschl's G., superior Temporal G., Planum Polare, Temporal Pole; part of Angular G. \\
+479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & l. posterior Cingulate G. \\
+420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & l. Precuneus \\
+407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & r. posterior Cingulate C. \\
+294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & r. Preceus \\
+121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & r. Occipital Pole \\
+117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & r. Heschl's G. \\
+115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & l. superior lateral Occipital C.\\
 \bottomrule
 \end{tabular}
-\todo[inline]{Table not referenced in the text}
-
 \end{table*}
@@
 \begin{table*}[t]
-    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon'').}
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon'').
+Clusters sorted by voxel size.
+The first brain structure given contains the voxel with the maximum Z-Value.}
 \label{tab:cope5}
-\begin{tabular}{rrrrrrrrrrp{3cm}}
+\begin{tabular}{rrrrrrrrrp{6cm}}
 \toprule
-& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
-\\ \cmidrule{5-7} \cmidrule{8-10}
-Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
+& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+\\ \cmidrule{4-6} \cmidrule{7-9}
+voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
 \midrule
-4 & 3166 & 2.79E-25 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
-3 & 1753 & 7.18E-17 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
-2 & 166 & 0.00446 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
-1 & 149 & 0.00793 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
+3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & l.
+anterior superior Temporal G.; posterior Supramarginal G., Parietal Operculum, Planum Temporale, anterior superior Temporal G., Planum Polare; part of Heschl's Gyrus \\
+1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & r. Planum Temporale, Superior Temporal Gyrus; part of Heschl's G. \& Planum Polare \\
+166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & r. posterior Cingulate G. \\
+149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & r. Precuneus \\
 \bottomrule
@@
 
-\clearpage
-% der alte Entwurf der Tabelle; hier mit rules/description in der Tabelle
-\begin{center}
-\begin{tabular}{ |c|c|c|c| }
-\hline
-category & description & examples & count\\
-\hline
-geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & 125\\
-geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & 105\\
-setting\_new & first-time mentioned setting & on a bridge, on an alley, on campus & 86\\
-setting\_rec & recurring setting & at the bus stop & 37\\
-body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt & 66\\
-bodypart & limbs and trousers & arm, finger, leg, toe & 69\\
-face & face or parts of it & face, ear, nose, mouth & 47\\
-head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & 36\\
-furniture & movable objects insides/outsides & bench, bed, table, chair & 50\\
-object & countable entities with firm boundaries & feather, telephone, car & 232\\
-objects & countable entities with firm boundaries & wheels, photos & 52\\
-female & female person & nurse, mother, women & 31\\
-females & female persons & women & 3\\
-fname & female name & Jenny, Carla & 74\\
-male & male person & man, father, soldier & 89\\
-males & concrete male persons & boys, opponents & 23\\
-mname & male name of person present in the scene & Forrest, Bubba, Kennedy & 291\\
-persons & concrete persons of unknown sex / gender & hippies, patients & 17\\
-++ & nouns, adverbial adjectives, and adverbs & in the evening, it's daytime, later \\
-\hline
-\label{tab:descr-nouns-old}
-\end{tabular}
-\todo[inline]{If the descriptive nounes are moved to the PPA paper, this table should be removed}
-\end{center}
-
 \end{document}

### 2020-04-18 paper/main.tex

@@
 
-\title{A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description}
+\title{A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description}
 %\titlenote{whatever titlenote here}
@@
 % up to 300 words
-\todo[inline]{The abstract should come now}
 Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and it's audio-only variant (i.e.
 audio-description), as an addition to a large public functional brain imaging dataset (\url{http://studyforrest.org}).
-The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), and \aPhonesAll\ phonemes.
-
-Zusätzliche Annos der Worte
-
+The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
+For every word, we provide lemmatization, two different part-of-speech taggings (simple and detailed), syntactic dependencis within each sentence, and a semantic analysis in terms of word embedding (word2vector).
 This annotation enables further studies of language perception and semantic processing under conditions of real-life complexity using the studyforrest dataset.
@@
 
-% hier sind “sentences” nicht vollständige Sätze im linguistischen Sinne (Subjekt, Objekt, Prädikat), sondern auch Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh").
-% Sätze im linguistischen Sinne sind in der Annotation durch "." oder "?" am
-% Ende gekennzeichnet.
-For this publication, we annotated the onsets and offsets, and content of sentences, single words and phonemes spoken in the audio-visual (AV) movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its corresponding audio-only (AO) variant (i.e.
+\todo[inline]{``sentences'' sind hier nicht vollständige Sätze im linguistischen Sinne (Subjekt, Prädikat), sondern auch Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh"); Sätze im linguistischen Sinne sind in der Annotation durch "." oder "?" am Ende gekennzeichnet.
+In der Tabelle ist es aber ausführlich beschrieben}
+For this publication, we annotated the onsets and offsets, and content of sentences, single words, and phonemes spoken in the audio-visual (AV) movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its corresponding audio-only (AO) variant (i.e.
 audio-description) for visually impaired persons \citep{ForrestGumpDVD}.
-% paper regarding mention musical not mentioned
 fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
-Additional fMRI data include retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.
+Additional fMRI data include the perception of musical genres \citep{hanke2015musical}, and retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.
 
@@
 Approximate temporal onsets and offsets were corrected, and intervals containing several sentences were split into intervals containing only one sentence.
-\todo[inline]{what is a regular audience?
-without neurological disorders ;-); Simpel: eine audience, die den Film nicht 45x auf voller Lautstärke über Kopfhörer mit Transkription danebenliegend gehört hat ;-)}
 When two or more persons were speaking simultaneously the less dominant voice was dropped.
 Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations that are difficult to recognize by the audience were dropped, too.
+\todo[inline]{what is a regular audience?
+without neurological disorders ;-); Simpel: eine audience, die den Film nicht 45x auf voller Lautstärke über Kopfhörer mit Transkription danebenliegend gehört hat}
 
 % Alignment preparations
+% http://prosodylab.org
+% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
 We used the Montreal Forced Aligner v1.0.1 \citep{mcauliffe2017montreal} to
@@
 in the transcribed sentences.
-% http://prosodylab.org
-% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
-To enable the aligner to look up the phonemes within every word, we chose a German pronunciation dictionary provided by Prosodylab \citep {gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the pronounciation of single phonemes.
-To improve the quality of the automatic alignment, this dictionary was manually updated with German words that were missing in the dictionary but occur in the stimuli.
-The pronunciation of English words occurring in the otherwise German audio track was taken from an English pronunciation dictionary provided by the Montreal Language Modeling lab (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict} that uses the ARPAbet PhoneSet.
+To enable the aligner to look up the phonemes embedded within each word, we chose a German pronunciation dictionary provided by Prosodylab \citep {gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the pronounciation of phonemes.
+To improve the detection rate of the automatic alignment, this dictionary was manually updated with German words that occur in the stimuli but were missing in the dictionary.
+% \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
+The pronunciation of English words and phonemes occurring in the otherwise German audio track was taken from an English pronunciation dictionary (following the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).
 
@@
 then performed the alignment.
-In a first step, the resulting .TextGrid file that contains onsets and offsets of words and phonemes was corrected in Praat, again interatively in several passes.
-Onsets and offsets of words and their corresponding phonemes on which the automatic alignment performed moderately were corrected.
-Some (low volume) sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, rally, disco) were removed due to poor overall alignment performance.
-In a second step, the complete sentences of the orthographic transcription were copied into the annotation (s. table \ref{tab:overview} for an overview of the annotation's content).
+In a first step, the resulting .TextGrid file that contains onsets and offsets of words and phonemes on which the automatic alignment performed moderately were corrected in Praat interatively in several passes.
+Some low volume sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, rally, disco) were removed due to poor overall alignment performance.
+In a second step, the complete sentences of the orthographic transcription were copied into the annotation (s.
+table \ref{tab:overview} for an overview of the annotation's content regarding sentences, words, and phonemes).
 In a third step, the name of the speaker was added for every sentence (cf. table \ref{tab:speakers} for the most often occurring speakers).
-During every new step results from previous steps were checked again for errors and corrected.
+During every new step results from previous steps were checked again for errors.
 
 \begin{table*}[tbp]
-\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments used during fMRI scanning.
-The label ``Sentences''' comprises complete grammatical sentences (i.e.
-having a subject and a predicate) or questions that are additionally marked with a full stop or question mark.
+\caption{Overview of the speech annotation's content for the whole stimulus and its individual segments used during fMRI scanning.
+The label ``Sentences'' comprises complete grammatical sentences (i.e.
+comprising subject predicate) which are additionally marked with a full stop at the end.
 The label ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g.
 ``ha, ha, ha'') or in isolation (e.g.
-``ha'', at time points when speakers rapidly switch).
+``ha'' at time points when speakers switch rapidly).
 The label ``Words'' comprises every single word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
@@
 The narrator only occurrs in the audio-description of the movie.
-Shown names are mostly identical to the names used in \citep{labs2015portrayed}.
+Names are mostly identical to the names used in \citep{labs2015portrayed}.
 Overall 97 persons were identified.}
@@
 % NLP
+% Tiger Treebank Corpus:
+% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
 To automatically analyze linguistic features of words in their corresponding
 sentence, we employed the Python package spaCy v2.2.1
-(\href{https://spacy.io}{spacy.io}) and a German language model
-(de\_core\_news\_md; \href{https://spacy.io/models/de}{spacy.io/models/de})
-trained on the TIGER Treebank corpus
-(\href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}). We performed
-analyses regarding part of speech (i.e. grammatical tagging or word-category
-disambiguation), syntactic dependency, lemmatization, word embedding (i.e.
-semantic similarity), and if the word is one of the most common words of the
-German language. Results of these analyzes were added to the annotation and
-saved as .TextGrid file. This .TextGrid file was converted via python script to
-a tab separated file in accordance with the brain imaging data structure
-(\href{https://bids.neuroimaging.io/}{BIDS}\citep{gorgolewski2016bids}). Non-speech vocalizations were dropped from the sentences before analysis.
-% BIDS stuff runter zu "Dataset content"?
+(\href{https://spacy.io}{spacy.io}) and its accompanying German language model
+(\texttt{de\_core\_news\_md} trained on the TIGER Treebank corpus \citep{brants2004tiger}.
+Non-speech vocalizations were dropped from the sentences before analysis.
+We then performed analyses regarding part-of-speech (i.e.
+grammatical tagging or word-category disambiguation), syntactic dependencies, lemmatization, word embedding (i.e.
+semantic similarity), and if the word is one of the most common words of the German language.
+Results of these analyzes were added to the annotation which is available as a Praat TextGrid file (\texttt{fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid} and as a tab separated file (\texttt{fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}) \citep{gorgolewski2016bids}).
 
 \subsection*{Data Legend}
-% wo wurde automatisch korrigiert (e.g. NE/NN, NONSPEECH)
-% s. dictionaries oben in add_part-of-speech-tagging2textgrid.py
 
@@
 % sich oben in dem entsprechendem Skript
-% (add_part-of-speech-tagging2textgrid.py)
+% add_part-of-speech-tagging2textgrid.py
 \subsubsection*{Simple part-of-speech tag (\texttt{pos})}
@@
 \begin{table*}[t]
-\caption{Simple part of speech tagging (POS). All 15 labels sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually identified.}
+\caption{Simple part-of-speech tagging (POS). All 15 labels sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually identified.}
 \label{tab:pos}
@@
 \begin{table*}[t]
-\caption{Detailed part of speech tagging (TAG). The 15 most often occurring labels (overall 43 labels) sorted alphabetically. Descriptions were taken from spaCy.explain().}
+\caption{Detailed part-of-speech tagging (TAG). The 15 most often occurring labels (overall 43 labels) sorted alphabetically. Descriptions were taken from spaCy.explain().}
 \label{tab:tag}
@@
 ) but all bigger in voxel count on the left side => Clear involvement of the right hemisphere but bias to the left (see \citep{hamilton2018revolution}
-
 \section*{Data availability}

### 2020-04-18 paper/main.tex
overall revisions results & discussion

@@
 semantic similarity), and if the word is one of the most common words of the German language.
-Results of these analyzes were added to the annotation which is available as a Praat TextGrid file (\texttt{fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid} and as a tab separated file (\texttt{fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}) \citep{gorgolewski2016bids}).
+Results of these analyzes were added to the annotation which is available as a Praat TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid} and as a tab separated file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}) \citep{gorgolewski2016bids}).
 
 \subsection*{Data Legend}
+The annotation in TextGrid format comprises 10 tiers: person, sentence (the text of a sentence), words (thex text of single words), pos, tag, dep, lemma, stop, vector and phones (pronounciation of a phoneme).
+The annotation in TSV format comprises 11 columns: onset, duration, person, text, pos, tag, dep, lemma, stop, vector.
+In the following description column header labels are given in parenthesis.
 
 \subsubsection*{Start (\texttt{start})}
-the onset of the sentences, word or phoneme provided in seconds of stimulus onset.
+The onset of the sentences, word or phoneme. Time stamps are provided in the format seconds.milliseconds of stimulus onset.
 
 \subsubsection*{Duration (\texttt{end})}
-the duration of the sentences, word or phoneme provided in seconds.
+The duration of the sentences, word or phoneme provided provided in the format seconds.milliseconds.
 
 \subsubsection*{Speaker identity (\texttt{person})}
-name of the persons that speaks the sentence, word or phoneme (s. table \ref{tab:speakers}).
+Name of the person that speaks the sentence, word or phoneme (cf. table \ref{tab:speakers} for the ten most often ocurring speakers).
 
-% einige Eigennamen (NE/NN) wurden automatisch korrigiert, weil das Sprachmodell
-% die naheliegenderweise nicht kannte; eine Liste dieser Eigennamen befindet
-% sich oben in dem entsprechendem Skript
+\subsubsection*{Text (\texttt{text})}
+The text of a spoken sentence or word, or the pronounciation of a phoneme.
+Phonemes of German words follow the Prosodylab PhoneSet, English words follow the ARPAbet PhoneSet.
+
+% einige Eigennamen (NE/NN) wurden automatisch durch das Skript korrigiert, weil das Sprachmodell die naheliegenderweise nicht kannte
+% eine Liste dieser Eigennamen befindet sich oben in dem entsprechendem Skript
 % add_part-of-speech-tagging2textgrid.py
 \subsubsection*{Simple part-of-speech tag (\texttt{pos})}
-This column contains tags for whole sentences ("SENTENCE"), phonemes ("PHONEME") and non-speech vocalizations (NONSPEECH).
-For single words, it contains a simple part-of-speech tagging (grammatical tagging; word-category disambiguation) taking the relationship with adjacent and related words in the same sentence into account (s.
-table \ref{tab:pos}).
-This simple part-of-speech tagging tags follow the \href{https://universaldependencies.org}{Universal Dependencies} v2 POS tag set.
+A simple part-of-speech tagging (grammatical tagging; word-category disambiguation) of a word
+The simple part-of-speech tagging tags follow the \href{https://universaldependencies.org}{Universal Dependencies} v2 POS tag set.
+See \ref{tab:pos} for a description of tag labels and respective counts of all 15 labels.
+Additionally in cells of this column, sentences are tagged as "SENTENCE", and phonemes are tagged as "PHONEME" to facilitate sorting and filtering in potential further processing steps of the annotation.
 
 \begin{table*}[t]
-\caption{Simple part-of-speech tagging (POS). All 15 labels sorted alpapetically. Descriptions were taken from spaCy.explain(). Non-speech vocalizations (NONSPEECH) were manually identified.}
+\caption{Simple part-of-speech tagging (POS).
+All 15 labels sorted alpapetically.
+Descriptions were taken from spaCy.explain().
+Non-speech vocalizations (NONSPEECH) were manually identified.
+Counts for the whole stimulus (all) and for each of the eight stimulus segments refer to the audio-description.}
 \label{tab:pos}
@@
 \subsubsection*{Detailed part-of-speech tag (\texttt{tag})}
-A detailed part-of-speech tagging following the TIGER Treebank annotation scheme \citep{brants2004tiger}(s.
-table \ref{tab:tag}) which is based on the \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset} \citep{schiller1999stts}.
+% \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset}
+A detailed part-of-speech tagging of a word following the TIGER Treebank annotation scheme \citep{brants2004tiger} which is based on the Stuttgart-Tübingen-Tagset \citep{schiller1999stts}.
+See table \ref{tab:tag} for a descripion  of tag labels and the respective counts of the 15 most often occuring labels.
 
 \begin{table*}[t]
-\caption{Detailed part-of-speech tagging (TAG). The 15 most often occurring labels (overall 43 labels) sorted alphabetically. Descriptions were taken from spaCy.explain().}
+\caption{Detailed part-of-speech tagging (TAG).
+The 15 most often occurring labels (overall 43 labels) sorted alphabetically.
+Descriptions were taken from spaCy.explain().
+Counts for the whole stimulus (all) and for each of the eight stimulus segments refer to the audio-description.}
 \label{tab:tag}
@@
 \subsubsection*{Syntactic dependency (\texttt{dep})}
-A word's column entry provides information about a word's syntactic dependency. Information following the TIGER Treebank annotation scheme \citep{brants2004tiger} is given in the format:
-"arc label;word's head;word's child1, word's child2, ..." where the "arc label" (s.
+Information about a word's syntactic dependency taking the relationship with adjacent and related words in the same sentence into account.
+Information followsing the TIGER Treebank annotation scheme \citep{brants2004tiger} and is given in the format:
+``arc label;word's head;word's child1, word's child2, ...'', where the ``arc label'' (cf.
 table \ref{tab:dep}) describes the type of syntactic relation that connects a "child" (the single word) to its "head".
@@
 \begin{table*}[t]
-\caption{Syntactic dependencies (DEP). The 15 most often occuring labels (overall 37 labels) sorted alphabetically. Descriptions were taken from spaCy.explain().}
+\caption{Syntactic dependencies (DEP).
+The 15 most often occuring labels (overall 37 labels) sorted alphabetically.
+Descriptions were taken from spaCy.explain().
+Counts for the whole stimulus (all) and for each of the eight stimulus segments refer to the audio-description.}
 \label{tab:dep}
@@
 \subsubsection*{Lemmatization (\texttt{lemma})}
-For single words, the base form (root) of the word
+The base form (root) of a word.
 
 \subsubsection*{Common Word (\texttt{stop})}
-For single words, this column provides information if the word is part of a stop list, hence one of the most common words in the German language or not (``True'' vs. ``False'')?
+This column's cell provides information if the word is part of a stop list, hence one of the most common words in the German language or not (``True'' vs. ``False'')?
 
 \subsubsection*{Word embedding (semantic similarity) (\texttt{vector})}
-A word's column entry contains a 300-dimensional \href{https://en.wikipedia.org/wiki/Word2vec}{word vector} providing a multi-dimensional meaning representation of the word.
-Uncommon and out-of-vocabulary words with a vector consisting of 300 dimensions of 0's were set to '\#' [to save space].
-
-\subsubsection*{Phonemes (\texttt{phones})}
-Phonemes of German words follow the Prosodylab PhoneSet, English words follow the ARPAbet PhoneSet.
+% \href{https://en.wikipedia.org/wiki/Word2vec}{word vector}
+A 300-dimensional word2vec providing a multi-dimensional meaning representation of a word.
+Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes were set to '\#' to save space.
 
 \subsection*{Dataset content}
-% habe folgend die Art und Weise aus der Datei p.tex der Schnitt-Annotation übernommen, wobei das im veröffentlichten Paper ganz anders aussieht
-% noch mit so Boxen und doi's
-% ACHTUNG: github erlaubt laut datalad handbook keine Dateien >100MB
-% Anno im Praat Format ist >200MB (und die audiodateien ohnehin)
-The released annotation comes in two different versions. First, in a (text-based) .TextGrid file that can be loaded into Praat (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}).
-Second, as a text-based tab-separated-value (TSV) formatted table  (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv})  in accordance with the brain imaging data structure BIDS \citep{gorgolewski2016bids} (\href{https://bids.neuroimaging.io/}{bids.neuroimaging.io}).
+% \href{https://bids.neuroimaging.io/}{bids.neuroimaging.io}
+\todo[inline]{darauf gehe ich schon am Ende von “annotation procedure” vor Datalegend ein, weil ich bereits dort erwähne, dass es zwei Versionen gibt und sich die Datalegend auf die TSV file bezieht.}
+The released annotation comes in two different versions. First, in a (text-based) TextGrid file that can be loaded into Praat (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}).
+Second, as a text-based tab-separated-value (TSV) formatted table  (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure BIDS \citep{gorgolewski2016bids}
 The source code for all descriptive statistics included in this paper is available in \texttt{code/descriptive-statistics.py} (Python script).
@@
 % Preprocessing
-% die Daten aus Hanke2014 sind eigentlich nicht bewegungskorrigiert und aligned
-% Quelle ist in vorliegendem Falle:
-% juseless.inm7.de:/data/project/studyforrest/collection/phase1
-% bei allem, was folgend mit alignment/co-registration zu tun hat, bin ich mir nicht sicher
-We used fMRI BOLD data of the 2h audio-description (7 Tesla, 2s TR, partial
-brain coverage with 1.4 mm isotropic voxels) \citep{hanke2014audiomovie} that
-were already corrected for motion and aligned [wie?] to study specific group template [co-registered to MNI?].
-All further steps analysis steps were carried out using Feat v6.00 (FMRI Expert
-Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB’s
-Software Library)\citep{smith2004fsl}.
-Data were temporally high-pass filtered (cut-off 150s), spatially smoothed (Gaussian kernel; 4.0 mm FWHM), and the brain was extracted from surrounding tissue [keine Plan, ob die Reihenfolge so korrekt ist].
+\todo[inline]{die Daten aus Hanke2014 sind nicht bewegungskorrigiert und nicht  aligned. Quelle ist in vorliegendem Falle:
+juseless.inm7.de:/data/project/studyforrest/collection/phase1;
+bei allem, was folgend mit alignment/co-registration zu tun hat, bin ich mir nicht sicher}
+We used fMRI BOLD data of the 2h audio-description (7 Tesla, 2s TR, partial brain coverage with 1.4 mm isotropic voxels) \citep{hanke2014audiomovie} that were already corrected for motion and aligned [+++wie?+++] to study specific group template [+++co-registered to MNI?+++].
+All further steps analysis steps were carried out using Feat v6.00 (FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB’s Software Library)\citep{smith2004fsl}.
+Data were temporally high-pass filtered (cut-off 150s), spatially smoothed (Gaussian kernel; 4.0 mm FWHM), and the brain was extracted from surrounding tissue [+++kein Plan, ob die Reihenfolge so korrekt ist].
 A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
@@
 
-\todo[inline]{I think this table doesn't talk about 'regressors'. It talks about the
-events that were selected/available to build GLM regressors from them. Hence the term
-'event' should be used here, and cross-reference to figure \ref{fig:reg} should be made}
-\todo[inline]{what does e1-12 stand for? It makes the label column too wide}
+\todo[inline]{I think this table doesn't talk about 'regressors'. It talks about the events that were selected/available to build GLM regressors from them.
+    Hence the term 'event' should be used here, and cross-reference to figure \ref{fig:reg-corr} should be made}
+\todo[inline]{what does e1-12 stand for? It makes the label column too wide; das waren hline Befehle}
 
@@
     \caption{Overview of the 26 regressors for the validation analysis.
-The first column contains the number of the regressor in the design file of FSL \citep{smith2004fsl}.
+The first column contains the number of the regressor [+++jetzt offenbar nicht mehr+++] in the design file of FSL \citep{smith2004fsl}.
 The 20 most often occuring labels from the detailed part-of speech tagging were used as such.
 Words belonging to all other labels were pooled to ``tag\_other''.
-The regressor ``sentence'' contains the end of complete grammatical sentences.
-The regressor ``phones'' contains the 80 most often occuring phonemes (``n'' with N=6053 to ``IY1'' with N=32).
+The regressor ``sentence'' contains the end of complete grammatical sentences. The regressor ``phones'' contains the 80 most often occuring phonemes (``n'' with N=6053 to ``IY1'' with N=32).
 The regressor ``no-sp'' represents moments when no speech was audible.
@@
 % 1st lvl
-At the first level analysing each segment for each subject individually, we defined 26 regressors (s. table \ref{tab:regressors})
- based on information drawn from the annotation.
+\todo[inline]{Hier (?) und das ggf auch mehr auf Korrelation der Regressoren eingehen. \ref{fig:reg-corr}.}
+At the first level analysing each segment for each subject individually, we defined 26 regressors (s. table \ref{tab:regressors}) based on information drawn from the annotation.
 The 20 most often occuring detailed tag labels (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word.
@@
 A ``no-speech'' regressor (``no-sp''; N=\rNospAll) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no audible/comprehensible speech.
-Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of a sentence or isolated word and to each other onset of the no-speech condition (s.
-anno2events-files.py).
+Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of a sentence or isolated word and to each other onset of the no-speech condition (s. anno2events-files.py).
 A length of 0.07s was chosen for the events of the no speech regressors  matching the average length of phonemes.
+
 Two regressors reflecting auditory (low-level) features (left-right difference in loudness and root mean squared loudness) aligned to and averaged across the length of every movie frame (40 ms) were modelled to reduce nuisance effects.
-Hier (?? und das ggf auch mehr auf Korrelation der Regressoren eingehen. \ref{fig:reg-corr}).
 Those 26 regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function.
 Temporal derivatives were also included in the design matrix.
-The design was subjected to the same temporal filtering as the BOLD time series.
-Finally, six motion parameters were used as additional nuisance regressors.
-The following six t-contrasts were defined: 1) words (i.e.
-all 21 tag-related regressors; N=15985) > no-speech; 2) no-speech > words 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll); 4) coordinate conjunctions > proper nouns; 5) nouns (``nn'') > coordinate conjunctions, and 6) coordinate conjunctions > nouns.
-The first level analysis that fitted each voxel’s time course separately for each subject was performed in functional space preserving the orientation of the EPI images [richtig?].
+The design was subjected to the same temporal filtering as the BOLD time series. Finally, six motion parameters were used as additional nuisance regressors.
+The following six t-contrasts were defined:
+1) words (i.e. all 21 tag-related regressors; N=15985) > no-speech;
+2) no-speech > words 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll);
+4) coordinate conjunctions > proper nouns;
+5) nouns (``nn'') > coordinate conjunctions, and
+6) coordinate conjunctions > nouns.
+The first level analysis that fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images [+++richtig?+++].
 
@@
 The third level analysis which averaged contrast estimates across subjects was carried out using FLAME stage 1 with automatic outlier de-weighting \citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
+\todo[inline]{wurde Harvar-Oxford Cortical Atlas verwendet?}
 Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>3.4 and a (corrected) cluster significance threshold of p<.05 \citep{woolrich2008robust}.
-Brain regions associated with observed clusters were determined with the Juelich Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} the Harvard-Oxford Cortical Atlas \citep{desikan2006automated}[really?] provided by FSL.
+Brain regions associated with observed clusters were determined with the Juelich Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} the Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
 
@@
 % von Interpretation klar(er) getrennt halten
-figure \ref{fig:results}
+RESULTS:
+
+Figure: \ref{fig:results}
+
 words > no-speech \ref{tab:cope1}
+
 proper nouns > coordinate conjunctions and proper nouns \ref{tab:cope3}
+
 nouns > coordinate conjunctions \ref{tab:cope5}
-Results: The first contrast that contrasted words to moments where no speech is audible in the audio-description (words > no-speech) shows\dots;
+
+The first contrast that contrasted words to moments where no speech is audible in the audio-description (words > no-speech) shows\dots;
 left lateralization (bigger cluster left in BA XY => Broca)
@@
   \centering
-  \label{fig:results}
 % \includegraphics[width=0.4\textwidth]{frog.jpg}
@@
   \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected.; MNI template space)}.
+\label{fig:results}
 \end{figure*}
@@
 % \citep{binder2009semantic, dewitt2012phoneme}.
-Discussion: alles total awesome; Correlation der (konvolvierten Regressoren) is gut (s. figure \ref{fig:reg-corr}; Ergebnisse ergeben Sinn -> benutzt die Anno for awesome research
+Discussion:
+
+alles total awesome; Correlation der (konvolvierten Regressoren) is gut (s. figure \ref{fig:reg-corr}; Ergebnisse ergeben Sinn -> benutzt die Anno for awesome research
 All contrasts show bilateral clusters in speech-related regions (e.g.
 ) but all bigger in voxel count on the left side => Clear involvement of the right hemisphere but bias to the left (see \citep{hamilton2018revolution}
+
 \section*{Data availability}

### 2020-04-19 paper/main.tex
cleaning until results & discussion

@@
 % up to 300 words
-Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and it's audio-only variant (i.e.
-audio-description), as an addition to a large public functional brain imaging dataset (\url{http://studyforrest.org}).
+Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and its audio-description (i.e.
+the audio-only variant), as an addition to a large public functional brain imaging dataset (\url{http://studyforrest.org}).
 The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
-For every word, we provide lemmatization, two different part-of-speech taggings (simple and detailed), syntactic dependencis within each sentence, and a semantic analysis in terms of word embedding (word2vector).
+Additionally for every word, we provide lemmatization, two different part-of-speech taggings (simple and detailed), syntactic dependencis within each sentence, and a semantic analysis in terms of word embedding (word2vector).
 This annotation enables further studies of language perception and semantic processing under conditions of real-life complexity using the studyforrest dataset.
@@
 
-\todo[inline]{``sentences'' sind hier nicht vollständige Sätze im linguistischen Sinne (Subjekt, Prädikat), sondern auch Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh"); Sätze im linguistischen Sinne sind in der Annotation durch "." oder "?" am Ende gekennzeichnet.
-In der Tabelle ist es aber ausführlich beschrieben}
-For this publication, we annotated the onsets and offsets, and content of sentences, single words, and phonemes spoken in the audio-visual (AV) movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its corresponding audio-only (AO) variant (i.e.
-audio-description) for visually impaired persons \citep{ForrestGumpDVD}.
+\todo[inline]{In der Tabelle ausführlicher beschrieben als hier (ist okay so, denke ich): ``sentences'' sind hier nicht vollständige Sätze im linguistischen Sinne (Subjekt, Prädikat), sondern auch Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh")}
+For this publication, we annotated the onsets and offsets, and content of sentences, single words, and phonemes (cf.
+table \ref{tab:overview} for an overview of the annotation's content) spoken in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e.
+the audio-only variant of the movie) for visually impaired persons \citep{ForrestGumpDVD}.
 fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
-Additional fMRI data include the perception of musical genres \citep{hanke2015musical}, and retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.
+Additional fMRI data of this dataset include the perception of musical genres \citep{hanke2015musical}, and retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.
 
-\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved; welche previous work wird verbessert oder sogar replaced?}
+\todo[inline]{was meinst du mit: this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved}
 The current annotation facilitates modelling of hemodynamic brain responses
 correlating with speech-related events in the two stimuli.
-Further, it extends already available annotations of portrayed emotions \citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}.
+It extends already available annotations of portrayed emotions \citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}.
 All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional confound measures describing key properties of major building blocks of the stimulus.
@@
 \todo[inline]{wo kommen die "preliminaries transcriptions" etc.?
-Habe die von Medusa; die "most basic" Datei, die das Dataset enthält ist wie abgesprochen der Merge aus Dialog (ungetrennte Sentences), Narrator \& Non-Speech-Annotation = \texttt{speech-vocal.csv}}
+Habe die von Medusa; die "most basic" Datei, die das Dataset enthält ist wie abgesprochen der Merge aus Dialog (ungetrennte Sentences), Narrator \& Non-Speech-Annotation = \texttt{annotation/speech-vocal.csv}}
 Preliminary, orthographic transcriptions of dialogues (\texttt{german\_dialog.csv}), non-speech vocalizations (e.g.
@@
 (\texttt{german\_audio\_description.csv}) were merged (\texttt{speech-vocal.csv}) and converted to Praat's \citep{boersma2019praat} TextGrid format  (\texttt{speech-vocal.TextGrid}).
+
 % \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
@@
 We used the Montreal Forced Aligner v1.0.1 \citep{mcauliffe2017montreal} to
-algorithmically identify the onset and offset of each word and phoneme embedded
-in the transcribed sentences.
+algorithmically identify the exact onset of offset of the sentences, and the onset and offset of each word and phoneme embedded in the transcribed sentences.
 To enable the aligner to look up the phonemes embedded within each word, we chose a German pronunciation dictionary provided by Prosodylab \citep {gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the pronounciation of phonemes.
-To improve the detection rate of the automatic alignment, this dictionary was manually updated with German words that occur in the stimuli but were missing in the dictionary.
+The dictionary was manually updated with German words that occur in the stimuli but were missing in the dictionary to improve the detection rate of the automatic alignment.
 % \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
@@
 kommt jedoch so selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.}
-The audio file was converted from FLAC to WAV via FFmpeg v4.1.4 \citep{ffmpeg} to meet the aligner's requirements.
+The audio track was converted from FLAC to WAV via FFmpeg v4.1.4 \citep{ffmpeg} to meet the aligner's requirements.
 This WAV file, the transcription of sentences, and the updated dictionary were
@@
 then performed the alignment.
-In a first step, the resulting .TextGrid file that contains onsets and offsets of words and phonemes on which the automatic alignment performed moderately were corrected in Praat interatively in several passes.
+The resulting .TextGrid file that contains onsets and offsets of words and phonemes was corrected manually and iteratively in several passes:
+In a first step, onsets and offsets words and phonemes on which the automatic alignment performed moderately were corrected in Praat.
 Some low volume sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, rally, disco) were removed due to poor overall alignment performance.
-In a second step, the complete sentences of the orthographic transcription were copied into the annotation (s.
-table \ref{tab:overview} for an overview of the annotation's content regarding sentences, words, and phonemes).
+In a second step, the complete sentences of the orthographic transcription were copied into the annotation.
 In a third step, the name of the speaker was added for every sentence (cf. table \ref{tab:speakers} for the most often occurring speakers).
-During every new step results from previous steps were checked again for errors.
+During every step results from previous steps were checked again for errors.
 
 \begin{table*}[tbp]
-\caption{Overview of the speech annotation's content for the whole stimulus and its individual segments used during fMRI scanning.
+\caption{Overview of the annotation's content for the whole stimulus and its individual segments used during fMRI scanning.
 The label ``Sentences'' comprises complete grammatical sentences (i.e.
 comprising subject predicate) which are additionally marked with a full stop at the end.
-The label ``Sentences'' also comprises exlamations or non-speech vocalizations in quick succession (e.g.
-``ha, ha, ha'') or in isolation (e.g.
-``ha'' at time points when speakers switch rapidly).
-The label ``Words'' comprises every single word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
+The label ``Sentences'' also comprises questions (``Do you want a chocolate?'', exlamations (``Run away!), or non-speech vocalizations in quick succession (``ha, ha, ha''), or in isolation (e.g.
+``Forrest?'', ``Forrest!'', ``ha'') at time points when speakers switch rapidly.
+The label ``Words'' comprises each word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
 \label{tab:overview}
@@
 sentence, we employed the Python package spaCy v2.2.1
-(\href{https://spacy.io}{spacy.io}) and its accompanying German language model
-(\texttt{de\_core\_news\_md} trained on the TIGER Treebank corpus \citep{brants2004tiger}.
+(\href{https://spacy.io}{spacy.io}) employing its accompanying German language model (\texttt{de\_core\_news\_md} trained on the TIGER Treebank corpus \citep{brants2004tiger}.
 Non-speech vocalizations were dropped from the sentences before analysis.
-We then performed analyses regarding part-of-speech (i.e.
+We performed analyses regarding part-of-speech (i.e.
 grammatical tagging or word-category disambiguation), syntactic dependencies, lemmatization, word embedding (i.e.
-semantic similarity), and if the word is one of the most common words of the German language.
+semantic similarity), and if the word is one of the most common words of the German language, i.e.
+if the word is part of a stop list.
 Results of these analyzes were added to the annotation which is available as a Praat TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid} and as a tab separated file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}) \citep{gorgolewski2016bids}).
+\todo[inline]{hier bringe ich bereits vor der ``Data availability'' die Pfade/Dateinamen, weil im folgenden die TSV-Datei in der ``Data legend'' beschrieben wird}
 
 \subsection*{Data Legend}
-The annotation in TextGrid format comprises 10 tiers: person, sentence (the text of a sentence), words (thex text of single words), pos, tag, dep, lemma, stop, vector and phones (pronounciation of a phoneme).
+The annotation in TextGrid format comprises 10 tiers: person, sentence (the text of a sentence), words (the text of a word), pos, tag, dep, lemma, stop, vector and phones (pronounciation of a phoneme).
 The annotation in TSV format comprises 11 columns: onset, duration, person, text, pos, tag, dep, lemma, stop, vector.
@@
 \subsubsection*{Start (\texttt{start})}
-The onset of the sentences, word or phoneme. Time stamps are provided in the format seconds.milliseconds of stimulus onset.
+The onset of the sentence, word or phoneme. Time stamps are provided in the format seconds.milliseconds of stimulus onset.
 
 \subsubsection*{Duration (\texttt{end})}
-The duration of the sentences, word or phoneme provided provided in the format seconds.milliseconds.
+The duration of the sentences, word or phoneme provided the format seconds.milliseconds.
 
@@
 \subsubsection*{Simple part-of-speech tag (\texttt{pos})}
-A simple part-of-speech tagging (grammatical tagging; word-category disambiguation) of a word
-The simple part-of-speech tagging tags follow the \href{https://universaldependencies.org}{Universal Dependencies} v2 POS tag set.
-See \ref{tab:pos} for a description of tag labels and respective counts of all 15 labels.
+A simple part-of-speech tagging (grammatical tagging; word-category disambiguation) of a word.
+The simple part-of-speech tagging tags follow the Universal Dependencies v2 POS tag set (\href{https://universaldependencies.org}{universaldependencies.org}).
+See Table \ref{tab:pos} for a description of the labels and the respective counts of all 15 labels.
 Additionally in cells of this column, sentences are tagged as "SENTENCE", and phonemes are tagged as "PHONEME" to facilitate sorting and filtering in potential further processing steps of the annotation.
@@
 \begin{table*}[t]
-\caption{Simple part-of-speech tagging (POS).
+\caption{Simple part-of-speech tagging (pos).
 All 15 labels sorted alpapetically.
@@
 A detailed part-of-speech tagging of a word following the TIGER Treebank annotation scheme \citep{brants2004tiger} which is based on the Stuttgart-Tübingen-Tagset \citep{schiller1999stts}.
-See table \ref{tab:tag} for a descripion  of tag labels and the respective counts of the 15 most often occuring labels.
+See Table \ref{tab:tag} for a descripion  of the labels and the respective counts of the 15 most often occuring labels.
 
 \begin{table*}[t]
-\caption{Detailed part-of-speech tagging (TAG).
+\caption{Detailed part-of-speech tagging (tag).
 The 15 most often occurring labels (overall 43 labels) sorted alphabetically.
@@
 \subsubsection*{Syntactic dependency (\texttt{dep})}
-Information about a word's syntactic dependency taking the relationship with adjacent and related words in the same sentence into account.
-Information followsing the TIGER Treebank annotation scheme \citep{brants2004tiger} and is given in the format:
+Information about a word's syntactic dependencies taking the relationship with other words in the same sentence into account.
+Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger} and is given in the format:
 ``arc label;word's head;word's child1, word's child2, ...'', where the ``arc label'' (cf.
@@
 \begin{table*}[t]
-\caption{Syntactic dependencies (DEP).
+\caption{Syntactic dependencies (dep).
 The 15 most often occuring labels (overall 37 labels) sorted alphabetically.
@@
 bei allem, was folgend mit alignment/co-registration zu tun hat, bin ich mir nicht sicher}
-We used fMRI BOLD data of the 2h audio-description (7 Tesla, 2s TR, partial brain coverage with 1.4 mm isotropic voxels) \citep{hanke2014audiomovie} that were already corrected for motion and aligned [+++wie?+++] to study specific group template [+++co-registered to MNI?+++].
+We used fMRI BOLD data of the 2h audio-description (7 Tesla, 2s TR, 3599 volumes, partial brain coverage with 1.4 mm isotropic voxels) \citep{hanke2014audiomovie} that were already corrected for motion and aligned [+++wie?+++] to study specific group template [+++co-registered to MNI?+++].
 All further steps analysis steps were carried out using Feat v6.00 (FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB’s Software Library)\citep{smith2004fsl}.
@@
 
-\todo[inline]{I think this table doesn't talk about 'regressors'. It talks about the events that were selected/available to build GLM regressors from them.
-    Hence the term 'event' should be used here, and cross-reference to figure \ref{fig:reg-corr} should be made}
 \todo[inline]{what does e1-12 stand for? It makes the label column too wide; das waren hline Befehle}
@@
 \begin{table*}[t]
-    \caption{Overview of the 26 regressors for the validation analysis.
-The first column contains the number of the regressor [+++jetzt offenbar nicht mehr+++] in the design file of FSL \citep{smith2004fsl}.
+    \caption{Overview of the events that were used to create the 26 regressors of the GLM analysis.
+The respective counts are given for the whole stimulus and the eight segments that were used during fMRI scanning.
 The 20 most often occuring labels from the detailed part-of speech tagging were used as such.
 Words belonging to all other labels were pooled to ``tag\_other''.
-The regressor ``sentence'' contains the end of complete grammatical sentences. The regressor ``phones'' contains the 80 most often occuring phonemes (``n'' with N=6053 to ``IY1'' with N=32).
-The regressor ``no-sp'' represents moments when no speech was audible.
-''fg\_ad\_lrdiff (left-right volume difference) and ``fg\_ad\_rms'' (root mean square loudness) represent low-level auditory nuissance regressors comprising one event for every movie frame (40ms).}
+The label ``sentence'' contains the end of complete grammatical sentences. label ``phones'' contains events of the 80 most often occuring phonemes (``n'' with N=6053 to ``IY1'' with N=32).
+The label ``no-sp'' represents moments when no speech was audible.
+''fg\_ad\_lrdiff (left-right volume difference) and ``fg\_ad\_rms'' (root mean square loudness) represent one event for every movie frame (40ms).
+Events were convolved with FSL's ``Double-Gamma HRF'' to create the regressors.
+The correlation of these regressors over the time course of the whole stimulus can be seen in Figure \ref{fig:reg-corr}.}
 \label{tab:regressors}
@@
 % 1st lvl
-\todo[inline]{Hier (?) und das ggf auch mehr auf Korrelation der Regressoren eingehen. \ref{fig:reg-corr}.}
-At the first level analysing each segment for each subject individually, we defined 26 regressors (s. table \ref{tab:regressors}) based on information drawn from the annotation.
+At the first level analyzing each segment for each subject individually, we created 26 regressors (s. table \ref{tab:regressors}) based on events drawn from the annotation.
 The 20 most often occuring detailed tag labels (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word.
-The remaining tags were pooled to a single regressor (``tag\_other``; N=\rTagotherAll).
-The top 80 phonemes (``n'' with n=6053 to ``IY1'' with N=32) were pooled to the regressor ``phonemes'' (N=\rPhonesAll) to be used as a nuisance regressors.
-The ends of (complete) grammatical sentences were used as the onset of events, abitrarily lasting 0.2s, for the regressors ``sentence'' (N=\rSentenceAll).
-A ``no-speech'' regressor (``no-sp''; N=\rNospAll) serving as a control condition was created by the following rationale: events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no audible/comprehensible speech.
-Each event of the no-speech condition had a minimum distance of 1.8s to onset/offsets of a sentence or isolated word and to each other onset of the no-speech condition (s. anno2events-files.py).
-A length of 0.07s was chosen for the events of the no speech regressors  matching the average length of phonemes.
+The remaining tags were pooled to (``tag\_other``; N=\rTagotherAll).
+The top 80 phonemes (``n'' with n=6053 to ``IY1'' with N=32) were pooled to  ``phonemes'' (N=\rPhonesAll) to be used as a nuisance regressors.
+The ends of a complete grammatical sentences were used as onsets of a event abitrarily lasting 0.2s, for the regressors ``sentence'' (N=\rSentenceAll).
+``No-speech'' events (``no-sp''; N=\rNospAll) serving as a control condition were created by the following rationale:
+events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no audible/comprehensible speech.
+Each event of the no-speech condition had a minimum distance of 1.8s to onsets/offsets of a sentence or an isolated word, and to each onset to another event of the no-speech condition.
+A length of 0.07s was chosen for no-speech events matching the average length of phonemes.
+Lastly, we used events reflecting low-level auditory features (left-right difference in loudness and root mean squared loudness) aligned to and averaged across the length of every movie frame (40 ms) to model nuisance effects.
+All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function to create the actual regressors.
+The Pearson correlation coefficients of the 26 regressors across the time course of the stimulus can be seen in Figure \ref{fig:reg-corr}.
+Temporal derivatives were also included in the design matrix and the design was subjected to the same temporal filtering as the BOLD time series.
+Finally, six motion parameters were used as additional nuisance regressors.
 
-Two regressors reflecting auditory (low-level) features (left-right difference in loudness and root mean squared loudness) aligned to and averaged across the length of every movie frame (40 ms) were modelled to reduce nuisance effects.
-Those 26 regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function.
-Temporal derivatives were also included in the design matrix.
-The design was subjected to the same temporal filtering as the BOLD time series. Finally, six motion parameters were used as additional nuisance regressors.
+\todo[inline]{die motion parameters werden nicht konvolviert, oder?}
 The following six t-contrasts were defined:
@@
   \centering
-% \includegraphics[width=0.4\textwidth]{frog.jpg}
   \includegraphics[width=\linewidth]{figures/regressor-corr}
@@
 The third level analysis which averaged contrast estimates across subjects was carried out using FLAME stage 1 with automatic outlier de-weighting \citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
-\todo[inline]{wurde Harvar-Oxford Cortical Atlas verwendet?}
 Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>3.4 and a (corrected) cluster significance threshold of p<.05 \citep{woolrich2008robust}.

### 2020-04-23 paper/main.tex
overall revision (results & tables), add discussion

@@
 \usepackage{f1000_styles}
+\usepackage{units}
 \geometry{right=4cm}
@@
 \author[1, 2]{Christian~O.~Häusler \\ email \href{mailto:c.haeusler@fz-juelich.de}{c.haeusler@fz-juelich.de} }
-\author[1, 2]{Michael~Hanke}
+\author[1, 2]{Michael~Hanke \\ email \href{mailto:m.hanke@fz-juelich.de}{m.hanke@fz-juelich.de} }
 
@@
 
+\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht; Werte würde ich eher runden }
 \thispagestyle{fancy}
@@
 Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and its audio-description (i.e.
-the audio-only variant), as an addition to a large public functional brain imaging dataset (\url{http://studyforrest.org}).
+the audio-only variant) as an addition to a large public functional brain imaging dataset (\href{www.studyforrest.org}{studyforrest.org}).
 The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
-Additionally for every word, we provide lemmatization, two different part-of-speech taggings (simple and detailed), syntactic dependencis within each sentence, and a semantic analysis in terms of word embedding (word2vector).
-This annotation enables further studies of language perception and semantic processing under conditions of real-life complexity using the studyforrest dataset.
-
-Wort zur Validierungsstudie?
+Additionally for every word, we provide lemmatization, two different part-of-speech taggings (simple and detailed), syntactic dependencis within each sentence, and a 300-dimensional semantic representation (word vector).
+This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
 \end{abstract}
@@
 under conditions of real-life-like complexity.
-Motion pictures \citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not, lerner2011topographic} are increasingly utilized as so called naturalistic stimuli.
+Motion pictures \citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not, lerner2011topographic} are increasingly utilized as so called ``naturalistic stimuli''.
 
@@
 corresponding fMRI data.
-Nevertheless, model-driven methods like a general linear model (GLM) are necessary to not just explain how but also when (and why) a brain region is responding to a stimulus \citep{hamilton2018revolution}.
+Nevertheless, model-driven methods like a general linear model (GLM) are necessary to not just explain how but also when and why a brain region is responding to a stimulus \citep{hamilton2018revolution}.
 Studies using GLMs based on annotations of a stimulus' temporal structure have
@@
 \todo[inline]{In der Tabelle ausführlicher beschrieben als hier (ist okay so, denke ich): ``sentences'' sind hier nicht vollständige Sätze im linguistischen Sinne (Subjekt, Prädikat), sondern auch Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh")}
-For this publication, we annotated the onsets and offsets, and content of sentences, single words, and phonemes (cf.
-table \ref{tab:overview} for an overview of the annotation's content) spoken in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e.
-the audio-only variant of the movie) for visually impaired persons \citep{ForrestGumpDVD}.
+For this publication, we annotated the onsets and offsets, and content of sentences, single words, and phonemes spoken in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e.
+the audio-only variant of the movie)\citep{ForrestGumpDVD}(cf.
+table \ref{tab:overview} for an overview of the annotation's content).
 fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
@@
 laughing or groaning; \texttt{non\_speech\_vocalization.json}), and the audio-description's narrator
-(\texttt{german\_audio\_description.csv}) were merged (\texttt{speech-vocal.csv}) and converted to Praat's \citep{boersma2019praat} TextGrid format  (\texttt{speech-vocal.TextGrid}).
+(\texttt{german\_audio\_description.csv}) were merged (\texttt{annotation/speech-vocal.csv}) and converted to Praat's \citep{boersma2019praat} TextGrid format  (\texttt{annotation/speech-vocal.TextGrid}).
 
 % \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
-The merged transcription containing one onset and offset for usually a couple of sentences was edited in Praat v6.0.22 for manual validation against the original audio.
+The merged transcription containing a rough onset and offset for usually a couple of sentences was edited in Praat v6.0.22 for manual validation against the original audio.
 The following steps were done in several passes to iteratively improve the quality of the data:
-Approximate temporal onsets and offsets were corrected, and intervals containing several sentences were split into intervals containing only one sentence.
+approximate temporal onsets and offsets were corrected, and intervals containing several sentences were split into intervals containing only one sentence.
 When two or more persons were speaking simultaneously the less dominant voice was dropped.
@@
 To enable the aligner to look up the phonemes embedded within each word, we chose a German pronunciation dictionary provided by Prosodylab \citep {gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the pronounciation of phonemes.
-The dictionary was manually updated with German words that occur in the stimuli but were missing in the dictionary to improve the detection rate of the automatic alignment.
+To improve the detection rate of the automatic alignment, the dictionary was manually updated with German words that occur in the stimuli but were originally missing in the dictionary.
 % \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
@@
 The resulting .TextGrid file that contains onsets and offsets of words and phonemes was corrected manually and iteratively in several passes:
-In a first step, onsets and offsets words and phonemes on which the automatic alignment performed moderately were corrected in Praat.
+In a first step, onsets and offsets on which the automatic alignment performed moderately were corrected in Praat.
 Some low volume sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, rally, disco) were removed due to poor overall alignment performance.
-In a second step, the complete sentences of the orthographic transcription were copied into the annotation.
-In a third step, the name of the speaker was added for every sentence (cf. table \ref{tab:speakers} for the most often occurring speakers).
+In a second step, the complete sentences of the orthographic transcription were copied into the annotation created by the aligner.
+In a third step, the a speaker's identity was added for each sentence (cf. Table \ref{tab:speakers} for the most often occurring speakers).
 During every step results from previous steps were checked again for errors.
@@
 \caption{Overview of the annotation's content for the whole stimulus and its individual segments used during fMRI scanning.
-The label ``Sentences'' comprises complete grammatical sentences (i.e.
-comprising subject predicate) which are additionally marked with a full stop at the end.
-The label ``Sentences'' also comprises questions (``Do you want a chocolate?'', exlamations (``Run away!), or non-speech vocalizations in quick succession (``ha, ha, ha''), or in isolation (e.g.
+The label ``sentences'' comprises complete grammatical sentences which are additionally marked in the annotation with a full stop at the end (``my feet hurt.'').
+It also comprises questions (``do you want a chocolate?''), exlamations (``run away!), or non-speech vocalizations in quick succession (``ha, ha, ha''), or in isolation (e.g.
 ``Forrest?'', ``Forrest!'', ``ha'') at time points when speakers switch rapidly.
-The label ``Words'' comprises each word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
+The label ``words'' comprises each word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
 \label{tab:overview}
@@
 \begin{table*}[btp]
-\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically.
-The narrator only occurrs in the audio-description of the movie.
-Names are mostly identical to the names used in \citep{labs2015portrayed}.
-Overall 97 persons were identified.}
+\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurrs in the audio-description of the movie.
+Overall 97 persons were identified.
+Names are mostly identical to the names used in \citep{labs2015portrayed}.}
 \label{tab:speakers}
@@
 % \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
-To automatically analyze linguistic features of words in their corresponding
+To automatically analyze linguistic features of each words in their corresponding
 sentence, we employed the Python package spaCy v2.2.1
-(\href{https://spacy.io}{spacy.io}) employing its accompanying German language model (\texttt{de\_core\_news\_md} trained on the TIGER Treebank corpus \citep{brants2004tiger}.
+(\href{https://spacy.io}{spacy.io}) and its accompanying German language model (\texttt{de\_core\_news\_md} that was trained on the TIGER Treebank corpus \citep{brants2004tiger}.
 Non-speech vocalizations were dropped from the sentences before analysis.
@@
 grammatical tagging or word-category disambiguation), syntactic dependencies, lemmatization, word embedding (i.e.
-semantic similarity), and if the word is one of the most common words of the German language, i.e.
-if the word is part of a stop list.
-Results of these analyzes were added to the annotation which is available as a Praat TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid} and as a tab separated file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}) \citep{gorgolewski2016bids}).
-\todo[inline]{hier bringe ich bereits vor der ``Data availability'' die Pfade/Dateinamen, weil im folgenden die TSV-Datei in der ``Data legend'' beschrieben wird}
+multi-dimensional meaning representation of a word), and if the word is one of the most common words of the German language (i.e.
+if the word is part of a stop list).
+Results of these analyzes were added to the annotation which is available as a (text-based) Praat TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid} and as a text-based, tab-separated value (TSV) formatted table (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}) \citep{gorgolewski2016bids}).
+\todo[inline]{hier bringe ich bereits vor der ``Data availability'' die Pfade/Dateinamen, weil im Folgenden die TSV-Datei in der ``Data legend'' beschrieben wird}
 
@@
 The annotation in TextGrid format comprises 10 tiers: person, sentence (the text of a sentence), words (the text of a word), pos, tag, dep, lemma, stop, vector and phones (pronounciation of a phoneme).
-The annotation in TSV format comprises 11 columns: onset, duration, person, text, pos, tag, dep, lemma, stop, vector.
+The annotation in TSV format comprises 11 columns: onset, duration, person, text (of sentence, word or phoneme), pos, tag, dep, lemma, stop, vector.
 In the following description column header labels are given in parenthesis.
@@
 
-\subsubsection*{Duration (\texttt{end})}
+\subsubsection*{Duration (\texttt{duration})}
 The duration of the sentences, word or phoneme provided the format seconds.milliseconds.
@@
 \subsubsection*{Speaker identity (\texttt{person})}
-Name of the person that speaks the sentence, word or phoneme (cf. table \ref{tab:speakers} for the ten most often ocurring speakers).
+Name of the person that speaks the sentence, word or phoneme. See Table \ref{tab:speakers} for the ten most often ocurring speakers.
 
@@
 
-% einige Eigennamen (NE/NN) wurden automatisch durch das Skript korrigiert, weil das Sprachmodell die naheliegenderweise nicht kannte
-% eine Liste dieser Eigennamen befindet sich oben in dem entsprechendem Skript
-% add_part-of-speech-tagging2textgrid.py
 \subsubsection*{Simple part-of-speech tag (\texttt{pos})}
@@
 See Table \ref{tab:pos} for a description of the labels and the respective counts of all 15 labels.
-Additionally in cells of this column, sentences are tagged as "SENTENCE", and phonemes are tagged as "PHONEME" to facilitate sorting and filtering in potential further processing steps of the annotation.
+Nouns that spaCy mistook for proper nouns or vice versa were corrected via script.
+% s. list at the beginning of script
+% code/add_part-of-speech-tagging2textgrid.py
+Additionally in cells of this column, sentences are tagged as "SENTENCE", and phonemes are tagged as "PHONEME" to facilitate sorting, and filtering in potential further processing steps.
 
 \begin{table*}[t]
-\caption{Simple part-of-speech tagging (pos).
+\caption{Simple part-of-speech tagging (pos) performed by the Python package spaCy (\href{https://spacy.io}{spacy.io}).
 All 15 labels sorted alpapetically.
@@
 \toprule
-\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
@@
 PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
-PRON & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
+PROPN & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
 SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
@@
 See Table \ref{tab:tag} for a descripion  of the labels and the respective counts of the 15 most often occuring labels.
+Nouns that spaCy mistook for proper nouns or vice versa were corrected via script.
+% s. list at the beginning of script
+% code/add_part-of-speech-tagging2textgrid.py
 
 \begin{table*}[t]
-\caption{Detailed part-of-speech tagging (tag).
+\caption{Detailed part-of-speech tagging (tag) performed by the Python package spaCy (\href{https://spacy.io}{spacy.io}).
 The 15 most often occurring labels (overall 43 labels) sorted alphabetically.
@@
 \subsubsection*{Syntactic dependency (\texttt{dep})}
-Information about a word's syntactic dependencies taking the relationship with other words in the same sentence into account.
+Information about a word's syntactic dependencies with other words within the same sentence.
 Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger} and is given in the format:
@@
 \begin{table*}[t]
-\caption{Syntactic dependencies (dep).
+\caption{Syntactic dependencies (dep) performed by the Python package spaCy (\href{https://spacy.io}{spacy.io}).
 The 15 most often occuring labels (overall 37 labels) sorted alphabetically.
-Descriptions were taken from spaCy.explain().
+Descriptions were taken from spaCy.explain()(\href{https://spacy.io}{spacy.io}).
 Counts for the whole stimulus (all) and for each of the eight stimulus segments refer to the audio-description.}
@@
 \subsubsection*{Common Word (\texttt{stop})}
-This column's cell provides information if the word is part of a stop list, hence one of the most common words in the German language or not (``True'' vs. ``False'')?
+This column's cell provides information if the word is part of a stop list, hence one of the most common words in the German language or not (``True'' vs. ``False'').
 
-\subsubsection*{Word embedding (semantic similarity) (\texttt{vector})}
+\subsubsection*{Word embedding (\texttt{vector})}
 % \href{https://en.wikipedia.org/wiki/Word2vec}{word vector}
-A 300-dimensional word2vec providing a multi-dimensional meaning representation of a word.
-Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes were set to '\#' to save space.
+A 300-dimensional word vector providing a multi-dimensional meaning representation of a word.
+Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes were set to ``\#'' to save space.
 
@@
 \todo[inline]{darauf gehe ich schon am Ende von “annotation procedure” vor Datalegend ein, weil ich bereits dort erwähne, dass es zwei Versionen gibt und sich die Datalegend auf die TSV file bezieht.}
-The released annotation comes in two different versions. First, in a (text-based) TextGrid file that can be loaded into Praat (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}).
+The released annotation comes in two different versions.
+First, as a text-based TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be conveniently edited with the software Praat \citep{boersma2019praat}.
 Second, as a text-based tab-separated-value (TSV) formatted table  (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure BIDS \citep{gorgolewski2016bids}
@@
 % Intro
-In order to assess data quality, we investigated if contrasting speech-related events to non-speech related events lead to increased activation in areas known to be involved in semantic processing \citep{binder2009semantic, dewitt2012phoneme}.
+In order to assess data quality, we investigated if contrasting speech-related events to events without speech lead to increased activation in areas known to be involved in semantic processing \citep{hickok2007cortical}.
 Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (coordinate conjunctions) lead to increased activation in congruent brain areas.
@@
 \todo[inline]{die Daten aus Hanke2014 sind nicht bewegungskorrigiert und nicht  aligned. Quelle ist in vorliegendem Falle:
-juseless.inm7.de:/data/project/studyforrest/collection/phase1;
-bei allem, was folgend mit alignment/co-registration zu tun hat, bin ich mir nicht sicher}
-We used fMRI BOLD data of the 2h audio-description (7 Tesla, 2s TR, 3599 volumes, partial brain coverage with 1.4 mm isotropic voxels) \citep{hanke2014audiomovie} that were already corrected for motion and aligned [+++wie?+++] to study specific group template [+++co-registered to MNI?+++].
-All further steps analysis steps were carried out using Feat v6.00 (FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB’s Software Library)\citep{smith2004fsl}.
-Data were temporally high-pass filtered (cut-off 150s), spatially smoothed (Gaussian kernel; 4.0 mm FWHM), and the brain was extracted from surrounding tissue [+++kein Plan, ob die Reihenfolge so korrekt ist].
+juseless.inm7.de:/data/project/studyforrest/collection/phase1}
+\todo[inline]{bei allem, was folgend mit alignment/co-registration zu tun hat, bin ich mir nicht sicher \& gehe ggf.
+zu wenig auf den Prozess der Template Erstellung und des alignments ein; vgl.
+Review zum Muscial Genre Paper}
+\todo[inline]{hanke2014 spricht von 20 subjects (age 21–38 years, mean age 26.6 years, 12 male), es fehlt hier aber sub-10}
+We used fMRI BOLD data of the 2h audio-description (\unit[7]{Tesla}, TR=\unit[2]{s}, 3599 volumes, 36 axial slices, thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm} field-of-view) of 19 healthy subjects \citep{hanke2014audiomovie} that were already corrected for motion and aligned [+++wie?+++] to study specific group template [+++co-registered to MNI?+++].
+
+All further analysis steps were carried out using Feat v6.00 (FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB's Software Library)\citep{smith2004fsl}.
+Data were temporally high-pass filtered (cut-off \unit[150]{s}), spatially smoothed (Gaussian kernel; \unit[4.0]{mm} FWHM), and the brain was extracted from surrounding tissue [+++kein Plan, ob die Reihenfolge so korrekt ist].
 A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
-We implemented a standard three-level, voxel-wise general linear model (GLM) to average parameter estimates across the eight stimulus segments, and later across 19 subjects.
 
@@
 % 1st lvl
-At the first level analyzing each segment for each subject individually, we created 26 regressors (s. table \ref{tab:regressors}) based on events drawn from the annotation.
-The 20 most often occuring detailed tag labels (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word.
-The remaining tags were pooled to (``tag\_other``; N=\rTagotherAll).
-The top 80 phonemes (``n'' with n=6053 to ``IY1'' with N=32) were pooled to  ``phonemes'' (N=\rPhonesAll) to be used as a nuisance regressors.
-The ends of a complete grammatical sentences were used as onsets of a event abitrarily lasting 0.2s, for the regressors ``sentence'' (N=\rSentenceAll).
+We implemented a standard three-level, voxel-wise general linear model (GLM) to average parameter estimates across the eight stimulus segments, and later across 19 subjects.
+At the first level analyzing each segment for each subject individually, we created 26 regressors based on events drawn from the annotation (cf. Table \ref{tab:regressors}).
+The 20 most often occuring detailed part-of-speech labels (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word.
+The remaining labels were pooled to (``tag\_other``; N=\rTagotherAll).
+The top 80 phonemes (``n'' with N=6053 to ``IY1'' with N=32) were pooled to  ``phonemes'' (N=\rPhonesAll) to be used as a nuisance regressors.
+The end of each complete grammatical sentenc was used as an onsets of a event abitrarily lasting \unit[0.2]{s} (N=\rSentenceAll).
 ``No-speech'' events (``no-sp''; N=\rNospAll) serving as a control condition were created by the following rationale:
-events were fitted into intervals between onsets and offsets of sentences/words assumed to contain no audible/comprehensible speech.
-Each event of the no-speech condition had a minimum distance of 1.8s to onsets/offsets of a sentence or an isolated word, and to each onset to another event of the no-speech condition.
-A length of 0.07s was chosen for no-speech events matching the average length of phonemes.
-Lastly, we used events reflecting low-level auditory features (left-right difference in loudness and root mean squared loudness) aligned to and averaged across the length of every movie frame (40 ms) to model nuisance effects.
+events were fitted into longer lasting intervals between onsets and offsets of words assumed to contain no audible/comprehensible speech.
+Each event of the no-speech condition had to have a minimum distance of 1.8s to an onsets/offsets of word, and to each onset to another event of the no-speech condition.
+A length of \unit[70]{ms} was chosen for no-speech events matching the average length of phonemes.
+Lastly, we used events reflecting low-level auditory features (left-right difference in loudness and root mean squared loudness) averaged across the length of every movie frame (\unit[40]{ms}).
 All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function to create the actual regressors.
-The Pearson correlation coefficients of the 26 regressors across the time course of the stimulus can be seen in Figure \ref{fig:reg-corr}.
+The Pearson correlation coefficients of the 26 regressors across the time course of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
 Temporal derivatives were also included in the design matrix and the design was subjected to the same temporal filtering as the BOLD time series.
@@
 \todo[inline]{die motion parameters werden nicht konvolviert, oder?}
+\todo[inline]{in den Results/Discussion wird nur auf die COPEs 1, 3, 5 eingegangen; sollte man hier 2, 4, 6 rausnehmen? oder von “and their reverse contrasts” sprechen?}
 The following six t-contrasts were defined:
-1) words (i.e. all 21 tag-related regressors; N=15985) > no-speech;
-2) no-speech > words 3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll);
+
+% events:n all tag-related regressors: N=15985)
+1) words (all 21 tag-related regressors) > no-speech;
+2) no-speech > words;
+3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll);
 4) coordinate conjunctions > proper nouns;
-5) nouns (``nn'') > coordinate conjunctions, and
+5) nouns (``nn''; N=\rNeAll) > coordinate conjunctions, and
 6) coordinate conjunctions > nouns.
-The first level analysis that fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images [+++richtig?+++].
+The first level analysis which fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images [+++richtig?+++].
 
@@
 % 2nd lvl and 3rd lvl
-The second-level analysis which averaged contrast estimates across the eight stimulus segments per subject was carried out using a fixed effects model by forcing the random effects variance to zero in FLAME (FMRIB’s Local Analysis of Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
-The third level analysis which averaged contrast estimates across subjects was carried out using FLAME stage 1 with automatic outlier de-weighting \citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
-Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>3.4 and a (corrected) cluster significance threshold of p<.05 \citep{woolrich2008robust}.
-Brain regions associated with observed clusters were determined with the Juelich Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} the Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
+The second-level analysis which averaged contrast estimates across the eight stimulus segments per subject was carried out using a fixed effects model by forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
+The third level analysis which averaged contrast estimates across subjects was carried out using FLAME stage 1 with automatic outlier de-weighting \citep{woolrich2004multilevel, woolrich2008robust}.
+Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>3.4 and a corrected cluster significance threshold of p<.05 \citep{woolrich2008robust}.
+Brain regions associated with observed clusters were determined with the Juelich Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
 
-% results
-% von Interpretation klar(er) getrennt halten
-RESULTS:
+% Results
+% COPE 1:
+Figure \ref{fig:results} depicts the results of the three \todo{drei = “primary three”} contrasts (all Z-Threshold Z>3.4; p<.05 cluster-corrected).
+The contrast words > no-speech yielded four significant clusters (cf. Table \ref{tab:cope1}):
+one left laterlized cluster spanning from the angular gyrus and inferior posterior supramarginal gyrus across the superior and middle temporal gyrus, including parts of Heschl's gyrus and planum temporale.
+A second left cluster in (inferior) frontal regions, including precentral gyrus, pars opercularis (Brodman Areal 44; BA44) and pars triangularis (BA45).
+Similarly in the right hemisphere, one cluster spanning from the angular gyrus across the superior and middle temporal gyrus but including frontal inferior regions (pars opercularis and pars triangularis).
+A fourth significant cluster is located in the left thalamus.
 
-Figure: \ref{fig:results}
+% COPE 3
+The contrast proper nouns > coordinate conjunctions yielded 9 significant clusters (cf. Table \ref{tab:cope3}):
+one left laterlized cluster spanning from the angular gyrus across planum temporale and superior temporal gyrus, partially covering the Heschl's gyrus, into the anterior middle temporal gyrus.
+A largely congruent but smaller cluster in the right hemisphere.
+Two clusters in posterior cingulate cortex and precuneus of both hemispheres.
+Three small clusters in the right occipital pole, right Heschl's gyrus and left superior lateral occipital pole.
 
-words > no-speech \ref{tab:cope1}
+% COPE 5
+The contrast nouns > coordinate conjunctions yielded 3 significant clusters (cf. Table \ref{tab:cope5}):
+two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction.
+In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hermisphere into the anterior part of superior temporal cortex.
+Finally, two small right lateralized clusters in posterior cingulate gyrus and precuneus.
 
-proper nouns > coordinate conjunctions and proper nouns \ref{tab:cope3}
-
-nouns > coordinate conjunctions \ref{tab:cope5}
-
-The first contrast that contrasted words to moments where no speech is audible in the audio-description (words > no-speech) shows\dots;
-left lateralization (bigger cluster left in BA XY => Broca)
-The contrasts proper nouns > coordinate conjunctions and nouns > coordinate conjunctions identify bilateral, largely congruent (?) areas in areas known to be involved in processing auditory stimuli, word, nouns, semantics.
-
+\todo{Figure zeigt whole brain statt “partial brain coverage”; vgl. Text; Problem?}
 \begin{figure*}
@@
   \includegraphics[width=\linewidth]{figures/slicescolorbars}
-  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected.; MNI template space)}.
+  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected; MNI template space)}.
 \label{fig:results}
@@
 
-% hier die Lateralisation in den Broca Arealen BA44 und BA45 klarer machen
 \begin{table*}[t]
@@
 Clusters sorted by voxel size.
-The first brain structure given contains the voxel with the maximum Z-Value.}
+The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
 \label{tab:cope1}
@@
 \midrule
-14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & l Heschl's G.; lateral superior Occipital C., Angular G., posterior Supramarginal G., middle Temporal G.
-posterior to anterior; part of Planum Temporale, anterior superior Temporal G.
-\\
-14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & r.
-Superior Temporal G.; Angular G., Supramarginal G., middle Temporal G.
-posterior to anterior, Heschl's G.
-, inferior Frontal Gyrus pars opercularis (BA44); parts of Planum Temporale \& pars triangularis (BA45) \\
-1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & frontal Orbital C.; Precentral G.
-(Broca's area BA44), pars triangularis \& Inferior Frontal G.; part of pars opercularis (Broca's area BA44); NO Precentral Gyrus \\
-217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & l. Thalamus \\
+14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 &
+left Heschl's g.;
+lateral superior occipital c., angular g., superior and middle temporal g. (posterior to anterior);
+parts of supramarginal g. \&, planum temporale \\
+14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 &
+right superior temporal g.;
+angular g., superior (and middle) temporal g. (posterior to anterior), Heschl's g.;
+parts of supramarginal g., planum temporale, pars opercularis (BA44) \& pars triangularis (BA45) \\
+1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & left frontal orbital c.;
+pars opercularis (BA44), pars triangularis (BA45);
+parts of precentral g. \\
+217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & left Thalamus \\
 \bottomrule
@@
 Clusters sorted by voxel size.
-The first brain structure given contains the voxel with the maximum Z-Value.}
+The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
 \label{tab:cope3}
@@
 \midrule
-7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & l. Planum Temporale; Angular G., Supramarginal G., Heschl's G., Superior Temporal G., Planum Polare, Temporal Pole \\
-5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & r Parietal Operculum, Planum Temporale; Heschl's G., superior Temporal G., Planum Polare, Temporal Pole; part of Angular G. \\
-479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & l. posterior Cingulate G. \\
-420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & l. Precuneus \\
-407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & r. posterior Cingulate C. \\
-294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & r. Preceus \\
-121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & r. Occipital Pole \\
-117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & r. Heschl's G. \\
-115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & l. superior lateral Occipital C.\\
+7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 &
+left lPanum temporale; posterior inferior supramarginal g., superior temporal g., planum polare,
+parts of posterior angular g.,  Heschl's g., middle temporal gyrus \\
+5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 &
+right planum temporale;
+Heschl's g., superior temporal g., planum polare, temporal pole;
+parts of angular g. \& posterior inferior supramarginal gyrus \\
+479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & left posterior cingulate g. \\
+420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & left precuneus \\
+407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & right posterior cingulate c. \\
+294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & right precuneus \\
+121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & right occipital pole \\
+117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & right Heschl's g. \\
+115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & left superior lateral occipital c.\\
 \bottomrule
@@
 Clusters sorted by voxel size.
-The first brain structure given contains the voxel with the maximum Z-Value.}
+The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
 \label{tab:cope5}
@@
 \midrule
-3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & l.
-anterior superior Temporal G.; posterior Supramarginal G., Parietal Operculum, Planum Temporale, anterior superior Temporal G., Planum Polare; part of Heschl's Gyrus \\
-1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & r. Planum Temporale, Superior Temporal Gyrus; part of Heschl's G. \& Planum Polare \\
-166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & r. posterior Cingulate G. \\
-149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & r. Precuneus \\
+3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 &
+left anterior superior (and middle) temporal g.;
+planum temporale, planum polare, anterior superior temporal g.;
+part of posterior supramarginal g., Heschl's g. \\
+1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & right planum temporale, anterior superior temporal g., planum polare;
+part of\& part of Heschl's G. \\
+166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 &
+right posterior cingulate g. \\
+149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 &
+right precuneus \\
 \bottomrule
@@
 % discussion
-% careful what you pretend, check & cite (again)
-% \citep{binder2009semantic, dewitt2012phoneme}.
-Discussion:
-
-alles total awesome; Correlation der (konvolvierten Regressoren) is gut (s. figure \ref{fig:reg-corr}; Ergebnisse ergeben Sinn -> benutzt die Anno for awesome research
-All contrasts show bilateral clusters in speech-related regions (e.g.
-) but all bigger in voxel count on the left side => Clear involvement of the right hemisphere but bias to the left (see \citep{hamilton2018revolution}
+% wilson2007beyond
+% planum temporale = Wernicke; ist witzigerweise nicht in contrast 1 (words > no speech), aber “stark” in nouns bzw. proper nouns > kon
+In the contrast words > no speech, we expectedly find increased hemodynamic activity in a bilateral cortical network including temporal, parietal and frontal regions realted to processing spoken language \citep{hickok2007cortical}.
+Our results are similar to results of studies that implemented an ISC approach to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not, lerner2011topographic, silbert2014coupled}.
+Contrary to previous studies, we do not find increased medial activation in the precuneus or medial frontal cortex.
+This could be attributed to the fact that our contrast does not [+++sufficiently+++] capture social aspects of the narrative \citep{ferstl2008extended, mar2011neural}\todo{abchecken}.
+The two contrasts contrasting nouns and proper nouns respectively to coordinate junctions lead to unexpected results.
+Increased activation is partially located in early sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most prominently adjacant regions bilaterally (planum temporale; superior temporal gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
+This could be attributed to the fact that a high count of heterogenous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) were averaged across all 300 semantic dimensions (cf.
+\citep{mitchell2008predicting, huth2016natural}), and contrasted to coordinate conjunctions that offered a comparably small amount of events (N=\rKonAll).
+Moreover, the label ``coordinate junctions'' mostly comprises event of the words ``and'' (N=392) and ``but'' (N=49) and thus offered only a small amount of variance.
+A second explanation might be that our phoneme regressors that assumed linear summation of approximatly 70 ms lasting events in quick succession did not capture a sufficiently amount of nuissance variance.
+Nevertheless and more importantly to access the validity of the dataset is the fact that two similar lingustic concepts (nouns and proper nouns) embedded in a naturalistic stimulus that was not designed for linguistic research lead to similar activation patterns.
+% Within the language processing systems, early sensory regions are specialized for representing the immediate physical properties of the environment (form), while higher order regions extract increasingly abstract content (Davis and Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).
 
@@
 \section*{Conclusions}
+\todo[inline]{the paper needs to serve a purpose.
+One is, of course, to be documentation for the annotation.
+Another is to attract people to use this work for their own studies.
+I would even argue that this is the \textit{main} purpose, given that the annotation in itself represents to scientific progress.
+So the paper need to give an  accurate assessment what this can be used for and what is problematic or
+impossible.
+ATM this is the only statement in this regard:
+'facilitates modelling of hemodynamic brain responses correlating with speech-related events' and the only indication of purpose is 'additional confound measures'.
+I think this is incongruent with the amount of work and the level of detail of
+this annotation.}
 % state what you think are the main conclusions that can be realistically drawn from the findings in the paper, taking care not to make claims that cannot be supported.
-Conclusion hatten wir bei der Schnitt-Annotation nicht; entspricht im Grunde dem letzten Absatz der Einleitung
-
-\todo[inline]{Decide on having a 'conclusion' or not. If the section is not
-  mandatory and there are no further conclusions than at the end of the
-  introduction then I am OK with not having one. However, the paper needs to
-  serve a purpose. One is, of course, to be documentation for the annotation.
-  Another is to attract people to use this work for their own studies. I would
-  even argue that this is the \textit{main} purpose, given that the annotation
-  in itself represents to scientific progress. So the paper need to give an
-  accurate assessment what this can be used for and what is problematic or
-  impossible. ATM this is the only statement in this regard: 'facilitates
-  modelling of hemodynamic brain responses correlating with speech-related
-  events' and the only indication of purpose is 'additional confound measures'. I
-  think this is incongruent with the amount of work and the level of detail of
-  this annotation.}
+As an extension of the studoforrest dataset, we present an annotation of spoken language in the two hours lasting ``research cut'' of the audio-visual movie ``Forrest Gump'' and its temporally aligned audio-description.
+We annotated the onset and offset of sentences, words and phonemes, and the corresponding speaker's identity.
+An additional tagging of each word's linguistic features and the public nature of the dataset enable independent working groups to create sophisticated models of hemodynamic activity correlating with speech-related events in a naturalistic stimulus.
+Results of our dataset validating analysis that we run as a proof of concept show that the annotation's content can indeed / in principle be used to isolate/track speech-related networks in the human brain under life-like conditions.
 
@@
 management technology for this study was in part supported by the European
-Union’s Horizon 2020 Research and Innovation Programme under Grant Agreement
+Union's Horizon 2020 Research and Innovation Programme under Grant Agreement
 no. 785907 (HBP SGA2).

### 2020-04-24 paper/main.tex
revision after discussion of previous state of the paper

@@
 \section*{Introduction}
-\todo[inline]{Bitte am Ende (?) der Einleitung etwas zu "reproducible research" \& "datalad dataset" bringen}
 Cognitive neuroimaging research is moving towards studying brain behavior
@@
 
-\todo[inline]{In der Tabelle ausführlicher beschrieben als hier (ist okay so, denke ich): ``sentences'' sind hier nicht vollständige Sätze im linguistischen Sinne (Subjekt, Prädikat), sondern auch Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh")}
-For this publication, we annotated the onsets and offsets, and content of sentences, single words, and phonemes spoken in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e.
-the audio-only variant of the movie)\citep{ForrestGumpDVD}(cf.
-table \ref{tab:overview} for an overview of the annotation's content).
+\todo[inline]{Ausführliche Beschreibung bzgl. Sentences in Tabelle; ich finde es in der Form hier so ok/besser.}
+For this publication, we annotated the exact onsets and offsets, and content of sentences, single words, and phonemes spoken in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e.
+the audio-only variant of the movie)\citep{ForrestGumpDVD}(see Table \ref{tab:overview} for an overview of the annotation's content).
 fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
@@
 
-\todo[inline]{was meinst du mit: this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved}
+\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.}
 The current annotation facilitates modelling of hemodynamic brain responses
@@
 \subsection*{Annotation procedure}
-\todo[inline]{wo kommen die "preliminaries transcriptions" etc.?
-Habe die von Medusa; die "most basic" Datei, die das Dataset enthält ist wie abgesprochen der Merge aus Dialog (ungetrennte Sentences), Narrator \& Non-Speech-Annotation = \texttt{annotation/speech-vocal.csv}}
-Preliminary, orthographic transcriptions of dialogues (\texttt{german\_dialog.csv}), non-speech vocalizations (e.g.
-laughing or groaning; \texttt{non\_speech\_vocalization.json}), and the audio-description's narrator
-(\texttt{german\_audio\_description.csv}) were merged (\texttt{annotation/speech-vocal.csv}) and converted to Praat's \citep{boersma2019praat} TextGrid format  (\texttt{annotation/speech-vocal.TextGrid}).
+Preliminary, manual orthographic transcriptions of dialogues, non-speech vocalizations (e.g.
+laughing or groaning) and script for the audio-description's narrator were merged, and converted to Praat's \citep{boersma2019praat} TextGrid format.
 
 % \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
-The merged transcription containing a rough onset and offset for usually a couple of sentences was edited in Praat v6.0.22 for manual validation against the original audio.
+The merged transcription containing a rough onset and offset for usually a couple of sentences was edited in Praat for manual validation against the original audio.
 The following steps were done in several passes to iteratively improve the quality of the data:
@@
 When two or more persons were speaking simultaneously the less dominant voice was dropped.
-Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations that are difficult to recognize by the audience were dropped, too.
-\todo[inline]{what is a regular audience?
-without neurological disorders ;-); Simpel: eine audience, die den Film nicht 45x auf voller Lautstärke über Kopfhörer mit Transkription danebenliegend gehört hat}
+Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations which were subjectively assessed to be incomprehensible for the audience were dropped, too.
 
@@
 % https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
-We used the Montreal Forced Aligner v1.0.1 \citep{mcauliffe2017montreal} to
+We used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
 algorithmically identify the exact onset of offset of the sentences, and the onset and offset of each word and phoneme embedded in the transcribed sentences.
@@
 % Alignment
-\todo[inline]{Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach die Event-Borders zwischen den Phonemen herausgenommen.
-Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
-Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach).
-kommt jedoch so selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.}
-The audio track was converted from FLAC to WAV via FFmpeg v4.1.4 \citep{ffmpeg} to meet the aligner's requirements.
+The audio track was converted from FLAC to WAV via FFmpeg \citep{ffmpeg} to meet the aligner's requirements.
 This WAV file, the transcription of sentences, and the updated dictionary were
@@
 In a second step, the complete sentences of the orthographic transcription were copied into the annotation created by the aligner.
-In a third step, the a speaker's identity was added for each sentence (cf. Table \ref{tab:speakers} for the most often occurring speakers).
+In a third step, the a speaker's identity was added for each sentence (see Table \ref{tab:speakers} for the most often occurring speakers).
 During every step results from previous steps were checked again for errors.
@@
     \caption{Overview of the annotation's content for the whole stimulus and its individual segments used during fMRI scanning.
-The label ``sentences'' comprises complete grammatical sentences which are additionally marked in the annotation with a full stop at the end (``my feet hurt.'').
+The category \texttt{sentences} comprises complete grammatical sentences which are additionally marked in the annotation with a full stop at the end (``my feet hurt.'').
     It also comprises questions (``do you want a chocolate?''), exlamations (``run away!), or non-speech vocalizations in quick succession (``ha, ha, ha''), or in isolation (e.g.
 ``Forrest?'', ``Forrest!'', ``ha'') at time points when speakers switch rapidly.
-The label ``words'' comprises each word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
+The category \texttt{words} comprises each word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
 \label{tab:overview}
@@
 \toprule
-\textbf{label} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
+\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
 \midrule
@@
 To automatically analyze linguistic features of each words in their corresponding
-sentence, we employed the Python package spaCy v2.2.1
-(\href{https://spacy.io}{spacy.io}) and its accompanying German language model (\texttt{de\_core\_news\_md} that was trained on the TIGER Treebank corpus \citep{brants2004tiger}.
+sentence, we employed the Python package spaCy \citep{spacy2} and its accompanying German language model (\texttt{de\_core\_news\_md} that was trained on the TIGER Treebank corpus \citep{brants2004tiger}.
 Non-speech vocalizations were dropped from the sentences before analysis.
@@
 if the word is part of a stop list).
-Results of these analyzes were added to the annotation which is available as a (text-based) Praat TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid} and as a text-based, tab-separated value (TSV) formatted table (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}) \citep{gorgolewski2016bids}).
-\todo[inline]{hier bringe ich bereits vor der ``Data availability'' die Pfade/Dateinamen, weil im Folgenden die TSV-Datei in der ``Data legend'' beschrieben wird}
 
 \subsection*{Data Legend}
-The annotation in TextGrid format comprises 10 tiers: person, sentence (the text of a sentence), words (the text of a word), pos, tag, dep, lemma, stop, vector and phones (pronounciation of a phoneme).
-The annotation in TSV format comprises 11 columns: onset, duration, person, text (of sentence, word or phoneme), pos, tag, dep, lemma, stop, vector.
-In the following description column header labels are given in parenthesis.
+\todo[inline]{Minimale Info hier, dass es zwei Versionen gibt und sich der folgende Abschnitt auf TSV file bezieht}
+The annotation is available in two different versions, both providing the same information: a) as a (text-based) Praat TextGrid file and b) as a text-based, tab-separated value (TSV) formatted table.
+The following descriptions refer to the ten columns of the TSV file, namely
+\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text} (of sentence, word or phoneme), \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma}, \texttt{stop}, \texttt{vector}.
 
@@
 \subsubsection*{Text (\texttt{text})}
+\todo[inline]{Großphoneme erwähnen;Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach die Event-Borders zwischen den Phonemen herausgenommen.
+Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
+Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach).
+kommt jedoch so selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.}
 The text of a spoken sentence or word, or the pronounciation of a phoneme.
@@
 % code/add_part-of-speech-tagging2textgrid.py
-Additionally in cells of this column, sentences are tagged as "SENTENCE", and phonemes are tagged as "PHONEME" to facilitate sorting, and filtering in potential further processing steps.
+Additionally in cells of this column, sentences are tagged as \texttt{SENTENCE}, and phonemes are tagged as \texttt{PHONEME} to facilitate sorting, and filtering in potential further processing steps.
 
 \begin{table*}[t]
-\caption{Simple part-of-speech tagging (pos) performed by the Python package spaCy (\href{https://spacy.io}{spacy.io}).
+\caption{Simple part-of-speech tagging (\texttt{pos}) performed by the Python package spaCy \citep{spacy2}.
 All 15 labels sorted alpapetically.
 Descriptions were taken from spaCy.explain().
-Non-speech vocalizations (NONSPEECH) were manually identified.
-Counts for the whole stimulus (all) and for each of the eight stimulus segments refer to the audio-description.}
+Non-speech vocalizations (\texttt{NONSPEECH}) were manually identified.
+Counts for the whole stimulus (\texttt{all}) and for each of the eight stimulus segments refer to the audio-description.}
 \label{tab:pos}
@@
 \toprule
-textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
@@
 \begin{table*}[t]
-\caption{Detailed part-of-speech tagging (tag) performed by the Python package spaCy (\href{https://spacy.io}{spacy.io}).
+\caption{Detailed part-of-speech tagging (\texttt{tag}) performed by the Python package spaCy \citep{spacy2}.
 The 15 most often occurring labels (overall 43 labels) sorted alphabetically.
 Descriptions were taken from spaCy.explain().
-Counts for the whole stimulus (all) and for each of the eight stimulus segments refer to the audio-description.}
+Counts for the whole stimulus (\texttt{all}) and for each of the eight stimulus segments refer to the audio-description.}
 \label{tab:tag}
@@
 Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger} and is given in the format:
-``arc label;word's head;word's child1, word's child2, ...'', where the ``arc label'' (cf.
-table \ref{tab:dep}) describes the type of syntactic relation that connects a "child" (the single word) to its "head".
+``arc label;word's head;word's child1, word's child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the type of syntactic relation that connects a "child" (the single word) to its "head".
 
 \begin{table*}[t]
-\caption{Syntactic dependencies (dep) performed by the Python package spaCy (\href{https://spacy.io}{spacy.io}).
+\caption{Syntactic dependencies (\texttt{dep}) performed by the Python package spaCy \citep{spacy2}.
 The 15 most often occuring labels (overall 37 labels) sorted alphabetically.
-Descriptions were taken from spaCy.explain()(\href{https://spacy.io}{spacy.io}).
-Counts for the whole stimulus (all) and for each of the eight stimulus segments refer to the audio-description.}
+Descriptions were taken from spaCy.explain().
+Counts for the whole stimulus (\texttt{all}) and for each of the eight stimulus segments refer to the audio-description.}
 \label{tab:dep}
@@
 \subsubsection*{Common Word (\texttt{stop})}
-This column's cell provides information if the word is part of a stop list, hence one of the most common words in the German language or not (``True'' vs. ``False'').
+This column's cell provides information if the word is part of a stop list, hence one of the most common words in the German language or not (\texttt{True} vs. \texttt{False}).
 
@@
 A 300-dimensional word vector providing a multi-dimensional meaning representation of a word.
-Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes were set to ``\#'' to save space.
+Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes were set to \texttt{\#} to save space.
 
@@
 % \href{https://bids.neuroimaging.io/}{bids.neuroimaging.io}
-\todo[inline]{darauf gehe ich schon am Ende von “annotation procedure” vor Datalegend ein, weil ich bereits dort erwähne, dass es zwei Versionen gibt und sich die Datalegend auf die TSV file bezieht.}
 The released annotation comes in two different versions.
 First, as a text-based TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be conveniently edited with the software Praat \citep{boersma2019praat}.
-Second, as a text-based tab-separated-value (TSV) formatted table  (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure BIDS \citep{gorgolewski2016bids}
+Second, as a text-based, tab-separated-value (TSV) formatted table  (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS} \citep{gorgolewski2016bids}).
 The source code for all descriptive statistics included in this paper is available in \texttt{code/descriptive-statistics.py} (Python script).
@@
 % Preprocessing
-\todo[inline]{die Daten aus Hanke2014 sind nicht bewegungskorrigiert und nicht  aligned. Quelle ist in vorliegendem Falle:
-juseless.inm7.de:/data/project/studyforrest/collection/phase1}
-\todo[inline]{bei allem, was folgend mit alignment/co-registration zu tun hat, bin ich mir nicht sicher \& gehe ggf.
-zu wenig auf den Prozess der Template Erstellung und des alignments ein; vgl.
-Review zum Muscial Genre Paper}
 \todo[inline]{hanke2014 spricht von 20 subjects (age 21–38 years, mean age 26.6 years, 12 male), es fehlt hier aber sub-10}
-We used fMRI BOLD data of the 2h audio-description (\unit[7]{Tesla}, TR=\unit[2]{s}, 3599 volumes, 36 axial slices, thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm} field-of-view) of 19 healthy subjects \citep{hanke2014audiomovie} that were already corrected for motion and aligned [+++wie?+++] to study specific group template [+++co-registered to MNI?+++].
-
+% Details of the alignment procedure are given in the section on “Technical Validation”.
+%Data aligned by applying an affine transformation only are available in bold_dico_dico7Tad2grpbold7Tad.nii.gz.
+% Data aligned by non-linear warping are available in bold_dico_dico7Tad2grpbold7Tad_nl.nii.gz.
+We used blood oxygenation level-dependent (BOLD) functional magnetic resonance imaging (fMRI) data of the 2h audio-description (\unit[7]{Tesla}, \unit[2]{s} repetition time, 3599 volumes, 36 axial slices, thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm} field-of-view) of 19 healthy subjects \citep{hanke2014audiomovie}.
+Data were already corrected for motion at the scanner computer.
+Further, individual BOLD time-series were already aligned by non-linear warping to a study-specific T2*-weighted echo planar imaging (EPI) group template (cf.
+\citep{hanke2014audiomovie} for details on how the group template was created).
+\todo[inline]{So korrekt und “vollständig?
+MNI152 co-registration?
+Im Übrigen finde ich 3-4 Paper, die als Zitation für den MNI152-space in Frage kommen, wobei keines richtig passen will; hanke2014 zitiert keines}
 All further analysis steps were carried out using Feat v6.00 (FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB's Software Library)\citep{smith2004fsl}.
@@
 
-\todo[inline]{what does e1-12 stand for? It makes the label column too wide; das waren hline Befehle}
-
 \begin{table*}[t]
@@
 The respective counts are given for the whole stimulus and the eight segments that were used during fMRI scanning.
-The 20 most often occuring labels from the detailed part-of speech tagging were used as such.
-Words belonging to all other labels were pooled to ``tag\_other''.
-The label ``sentence'' contains the end of complete grammatical sentences. label ``phones'' contains events of the 80 most often occuring phonemes (``n'' with N=6053 to ``IY1'' with N=32).
-The label ``no-sp'' represents moments when no speech was audible.
-''fg\_ad\_lrdiff (left-right volume difference) and ``fg\_ad\_rms'' (root mean square loudness) represent one event for every movie frame (40ms).
+The 20 most often occuring labels from the detailed part-of speech tagging (\texttt{tag}) were used as such.
+Words belonging to all other labels were pooled to \texttt{tag\_other}.
+The label \texttt{sentence} contains the end of complete grammatical sentences.
+The label \texttt{phones} contains events of the 80 most often occuring phonemes (phoneme \texttt{n} with N=6053 to phoneme \texttt{IY1} with N=32).
+The label \texttt{no-sp} represents moments when no speech was audible.
+\texttt{fg\_ad\_lrdiff} (left-right volume difference) and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
 Events were convolved with FSL's ``Double-Gamma HRF'' to create the regressors.
@@
 tag\_other & all other TAG categories & \rTagotherAll & \rTagotherI & \rTagotherII & \rTagotherIII & \rTagotherIV & \rTagotherV & \rTagotherVI & \rTagotherVII & \rTagotherVIII \tabularnewline
-%e{1-12}
+%\hline
 sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
@@
 no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
-%e{1-12}
+%\hline
 fg\_ad\_lrdiff & left-right volume difference & \rFgadlrdiffAll & \rFgadlrdiffI & \rFgadlrdiffII & \rFgadlrdiffIII & \rFgadlrdiffIV & \rFgadlrdiffV & \rFgadlrdiffVI & \rFgadlrdiffVII & \rFgadlrdiffVIII \tabularnewline
@@
 We implemented a standard three-level, voxel-wise general linear model (GLM) to average parameter estimates across the eight stimulus segments, and later across 19 subjects.
-At the first level analyzing each segment for each subject individually, we created 26 regressors based on events drawn from the annotation (cf. Table \ref{tab:regressors}).
-The 20 most often occuring detailed part-of-speech labels (``nn'' with N=\rNnAll\space to ``prf'' with N=\rPrfAll) were modelled as such from the onset to offset of each word.
-The remaining labels were pooled to (``tag\_other``; N=\rTagotherAll).
-The top 80 phonemes (``n'' with N=6053 to ``IY1'' with N=32) were pooled to  ``phonemes'' (N=\rPhonesAll) to be used as a nuisance regressors.
+At the first level analyzing each segment for each subject individually, we created 26 regressors based on events drawn from the annotation (see Table \ref{tab:regressors}).
+The 20 most often occuring detailed part-of-speech labels (\texttt{nn} with N=\rNnAll\space to text{prf} with N=\rPrfAll) were modelled as such from the onset to offset of each word.
+The remaining labels were pooled to (\texttt{tag\_other}; N=\rTagotherAll).
+The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) to be used as a nuisance regressors.
 The end of each complete grammatical sentenc was used as an onsets of a event abitrarily lasting \unit[0.2]{s} (N=\rSentenceAll).
-``No-speech'' events (``no-sp''; N=\rNospAll) serving as a control condition were created by the following rationale:
-events were fitted into longer lasting intervals between onsets and offsets of words assumed to contain no audible/comprehensible speech.
-Each event of the no-speech condition had to have a minimum distance of 1.8s to an onsets/offsets of word, and to each onset to another event of the no-speech condition.
+``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control condition were created by the following rationale:
+events were fitted into longer lasting intervals between onsets and offsets of words assumed to contain no audible speech.
+Each event of the no-speech condition had to have a minimum distance of \unit[1.8]{s} to an onsets/offsets of word, and to each onset to another event of the no-speech condition.
 A length of \unit[70]{ms} was chosen for no-speech events matching the average length of phonemes.
-Lastly, we used events reflecting low-level auditory features (left-right difference in loudness and root mean squared loudness) averaged across the length of every movie frame (\unit[40]{ms}).
+Lastly, we used events reflecting low-level auditory features (left-right difference in volume and root mean squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
 All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function to create the actual regressors.
@@
 \todo[inline]{die motion parameters werden nicht konvolviert, oder?}
-\todo[inline]{in den Results/Discussion wird nur auf die COPEs 1, 3, 5 eingegangen; sollte man hier 2, 4, 6 rausnehmen? oder von “and their reverse contrasts” sprechen?}
-The following six t-contrasts were defined:
-
-% events:n all tag-related regressors: N=15985)
-1) words (all 21 tag-related regressors) > no-speech;
-2) no-speech > words;
-3) proper nouns (``ne''; N=\rNeAll) > coordinate conjunctions (``kon''; N=\rKonAll);
-4) coordinate conjunctions > proper nouns;
-5) nouns (``nn''; N=\rNeAll) > coordinate conjunctions, and
-6) coordinate conjunctions > nouns.
+The following three t-contrasts were defined:
+% 1b) no-speech > words;
+% 2b) coordinate conjunctions > proper nouns;
+% 3b) coordinate conjunctions > nouns.
+1) words (all 21 \texttt{tag}-related regressors; N=15985) > no-speech (\texttt{no-sp}; N=\rNospAll),
+2) proper nouns (\texttt{ne}; N=\rNeAll) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
+3) nouns (\texttt{nn}; N=\rNeAll) > coordinate conjunctions.
 The first level analysis which fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images [+++richtig?+++].
@@
 % COPE 1:
-Figure \ref{fig:results} depicts the results of the three \todo{drei = “primary three”} contrasts (all Z-Threshold Z>3.4; p<.05 cluster-corrected).
-The contrast words > no-speech yielded four significant clusters (cf. Table \ref{tab:cope1}):
+Figure \ref{fig:results} depicts the results of the three contrasts (all Z-Threshold Z>3.4; p<.05 cluster-corrected).
+The contrast words (all 21 \texttt{tag-related} regressors) > no-speech yielded four significant clusters (see Table \ref{tab:cope1}):
 one left laterlized cluster spanning from the angular gyrus and inferior posterior supramarginal gyrus across the superior and middle temporal gyrus, including parts of Heschl's gyrus and planum temporale.
@@
 % COPE 3
-The contrast proper nouns > coordinate conjunctions yielded 9 significant clusters (cf. Table \ref{tab:cope3}):
+The contrast proper nouns > coordinate conjunctions yielded 9 significant clusters (see Table \ref{tab:cope3}):
 one left laterlized cluster spanning from the angular gyrus across planum temporale and superior temporal gyrus, partially covering the Heschl's gyrus, into the anterior middle temporal gyrus.
@@
 % COPE 5
-The contrast nouns > coordinate conjunctions yielded 3 significant clusters (cf. Table \ref{tab:cope5}):
+The contrast nouns > coordinate conjunctions yielded 3 significant clusters (see Table \ref{tab:cope5}):
 two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction.
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words > no-speech.
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words (all 21 \texttt{tag}-related regressors) > no-speech.
 Clusters sorted by voxel size.
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (``ne'') > coordinate conjunctions (``kon'').
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}).
 Clusters sorted by voxel size.
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (``nn'') > coordinate conjunctions (``kon'').
+\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (\texttt{nn}) > coordinate conjunctions (\texttt{kon}).
 Clusters sorted by voxel size.
@@
 
+\todo[inline]{Lass uns bzgl.
+der Discussion am besten unterhalten; im Grunde geht es darum, wie weit ich ins Detail gehen soll (kann nämlich viel zu sehr ins Detail gehen); im Grunde geht es imo nicht darum, alle Cluster inkl.
+Areale durchzudiskutieren, sondern zu kommunizieren, dass die Anno brauchbar ist; wie dem auch sei: Hier wird noch Inhalt nach dem Lesen der Reviews hinzukommen}
 % discussion
@@
 % planum temporale = Wernicke; ist witzigerweise nicht in contrast 1 (words > no speech), aber “stark” in nouns bzw. proper nouns > kon
-In the contrast words > no speech, we expectedly find increased hemodynamic activity in a bilateral cortical network including temporal, parietal and frontal regions realted to processing spoken language \citep{hickok2007cortical}.
+In the contrast words > no speech, we expectedly find increased hemodynamic activity in a bilateral cortical network including temporal, parietal and frontal regions realted to processing spoken language \citep{friederici2011brain, hickok2007cortical,price2012twentyyears}.\todo{abchecken}
 Our results are similar to results of studies that implemented an ISC approach to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not, lerner2011topographic, silbert2014coupled}.
@@
 \citep{mitchell2008predicting, huth2016natural}), and contrasted to coordinate conjunctions that offered a comparably small amount of events (N=\rKonAll).
-Moreover, the label ``coordinate junctions'' mostly comprises event of the words ``and'' (N=392) and ``but'' (N=49) and thus offered only a small amount of variance.
+Moreover, the coordinate junctions (\texttt{kon}) mostly comprises event of the words ``and'' (N=392) and ``but'' (N=49) and thus offered only a small amount of variance.
 A second explanation might be that our phoneme regressors that assumed linear summation of approximatly 70 ms lasting events in quick succession did not capture a sufficiently amount of nuissance variance.
@@
 I would even argue that this is the \textit{main} purpose, given that the annotation in itself represents to scientific progress.
-So the paper need to give an  accurate assessment what this can be used for and what is problematic or
-impossible.
+The need to give an accurate assessment what this can be used for and what is problematic or impossible.
 ATM this is the only statement in this regard:
@@
 I think this is incongruent with the amount of work and the level of detail of
-this annotation.}
+this annotation; öööööhh, okay. Mir sind da jetzt über 2 Tage wenig Superlative eingefallen, die über den bisherigen Text hinausgehen; fehlt mir wohl die geeignete Perspektive}
 % state what you think are the main conclusions that can be realistically drawn from the findings in the paper, taking care not to make claims that cannot be supported.

### 2020-05-07 paper/main.tex
Acknowledgment still suitable?

@@
 \subsection*{Acknowledgements}
-We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns, and performed the preliminary annotation of nouns.
+We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns\todo{should it still be here?
+or move in PPA paper?}, and performed the preliminary annotation of nouns.
 Christian O.

### 2020-05-07 paper/main.tex
Note on abstract
GLMs are not _necessary_, but very useful

@@
 This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
+\todo[inline]{I don't understand what "two different part-of-speech taggings (simple and detailed)" means}
+\todo[inline]{"300-dimensional semantic representation (word vector)" I think we need to find a better description, but I could not come up with one so far}
 \end{abstract}
@@
 Because naturalistic stimuli are multi-dimensional and their temporal structure
-is usually unknown, data-driven methods like intersubject correlation (ISC)\citep{hasson2004intersubject} or independent component analysis
+is usually unknown, data-driven methods like intersubject correlation
+(ISC)\citep{hasson2004intersubject} or independent component analysis
 (ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
-corresponding fMRI data.
-Nevertheless, model-driven methods like a general linear model (GLM) are necessary to not just explain how but also when and why a brain region is responding to a stimulus \citep{hamilton2018revolution}.
-Studies using GLMs based on annotations of a stimulus' temporal structure have
-elucidated how the brain responds to visual features of a movie
+corresponding fMRI data.  Nevertheless, model-driven methods, like a general
+linear model (GLM), can be useful to investigate which specific stimulus
+properties a brain region is responding to \citep{hamilton2018revolution}. For
+example, studies using GLMs based on annotations of a stimulus' temporal
+structure have elucidated how the brain responds to visual features of a movie
 \citep{bartels2004mapping} or speech-related features of a narrative

### 2020-05-07 paper/main.tex
Disable pieces that are out-of-scope for the paper IMHO

@@
 
-\todo[inline]{Ausführliche Beschreibung bzgl. Sentences in Tabelle; ich finde es in der Form hier so ok/besser.}
-For this publication, we annotated the exact onsets and offsets, and content of sentences, single words, and phonemes spoken in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e.
-the audio-only variant of the movie)\citep{ForrestGumpDVD}(see Table \ref{tab:overview} for an overview of the annotation's content).
+For this publication, we annotated the exact onsets and offsets, and content of
+sentences, single words, and phonemes spoken in the audio-visual movie
+``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e. an
+audio-only variant of the movie)\citep{ForrestGumpDVD}.
+% immediate reference not needed in the intro
+%(see Table \ref{tab:overview} for an overview of the annotation's content).
+
 fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
-Additional fMRI data of this dataset include the perception of musical genres \citep{hanke2015musical}, and retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.
+% the following seems unrelated to the scope of the paper
+%Additional fMRI data of this dataset include the perception of musical genres
+%\citep{hanke2015musical}, and retinotopic mappings and localization of higher
+%visual areas of the same participants \citep{sengupta2016extension}.
+The annotation presented here facilitates modelling of hemodynamic brain responses
+correlated with speech-related events in the two stimuli.
+It extends already available annotations of portrayed emotions
+\citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy},
+as well as cuts and locations depicted in the movie
+\citep{haeusler2016annotation}.  All annotations can be used in any study
+focusing on other aspects of real-life cognition by serving as additional
+confound measures describing key properties of major building blocks of the
+stimulus.
 
 \todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.}
-The current annotation facilitates modelling of hemodynamic brain responses
-correlating with speech-related events in the two stimuli.
-It extends already available annotations of portrayed emotions \citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}.
-All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional confound measures describing key properties of major building blocks of the stimulus.
 

### 2020-05-07 paper/main.tex
Comment on introduction

@@
 
-\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.}
+\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.\\
+If you want to take this question in a revision, I am OK with that. However,
+the intro still doesn't say anything about WHY one would want to do "modelling of
+hemodynamic brain responses correlated with speech-related events" other than
+to discard speech as a confound. This seems like a massive underselling.}
 

### 2020-05-17 paper/main.tex
More feedback on the analysis

@@
 % Preprocessing
-\todo[inline]{hanke2014 spricht von 20 subjects (age 21–38 years, mean age 26.6 years, 12 male), es fehlt hier aber sub-10}
+\todo[inline]{hanke2014 spricht von 20 subjects (age 21–38 years, mean age 26.6 years, 12 male), es fehlt hier aber sub-10. MIH: age doesn't matter here. Just say that you left out sub-10, and why}
 % Details of the alignment procedure are given in the section on “Technical Validation”.
@@
 MNI152 co-registration?
-Im Übrigen finde ich 3-4 Paper, die als Zitation für den MNI152-space in Frage kommen, wobei keines richtig passen will; hanke2014 zitiert keines}
+Im Übrigen finde ich 3-4 Paper, die als Zitation für den MNI152-space in Frage kommen, wobei keines richtig passen will; hanke2014 zitiert keines.
+MIH: That is sufficient.
+No need to cite anything for MNI152}
 All further analysis steps were carried out using Feat v6.00 (FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB's Software Library)\citep{smith2004fsl}.
-Data were temporally high-pass filtered (cut-off \unit[150]{s}), spatially smoothed (Gaussian kernel; \unit[4.0]{mm} FWHM), and the brain was extracted from surrounding tissue [+++kein Plan, ob die Reihenfolge so korrekt ist].
+Data were temporally high-pass filtered (cut-off \unit[150]{s}), spatially smoothed (Gaussian kernel; \unit[4.0]{mm} FWHM), and the brain was extracted from surrounding tissue.
 A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
@@
 
-% 1st lvl
+% 1st lv}
+\todo[inline]{What follows has typos}
 We implemented a standard three-level, voxel-wise general linear model (GLM) to average parameter estimates across the eight stimulus segments, and later across 19 subjects.
 At the first level analyzing each segment for each subject individually, we created 26 regressors based on events drawn from the annotation (see Table \ref{tab:regressors}).
-The 20 most often occuring detailed part-of-speech labels (\texttt{nn} with N=\rNnAll\space to text{prf} with N=\rPrfAll) were modelled as such from the onset to offset of each word.
-The remaining labels were pooled to (\texttt{tag\_other}; N=\rTagotherAll).
-The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) to be used as a nuisance regressors.
-The end of each complete grammatical sentenc was used as an onsets of a event abitrarily lasting \unit[0.2]{s} (N=\rSentenceAll).
+The 20 most often occuring detailed part-of-speech labels (\texttt{nn} with N=\rNnAll\space to text{prf} with N=\rPrfAll) were modelled as such from the onset to offset of each word\todo{This has errors that I do not know how to fix}.
+The remaining labels were pooled to (\texttt{tag\_other}; N=\rTagotherAll)\todo{I do not know what this means}.
+The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) to be used as a nuisance regressors\todo{Does that mean they share events with "other"}.
+The end of each complete grammatical sentence was modeled as an impulse event (N=\rSentenceAll)\todo{Why?
+Above it says 'we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns)'.
+What does this need sentences for?}.
 ``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control condition were created by the following rationale:
-events were fitted into longer lasting intervals between onsets and offsets of words assumed to contain no audible speech.
+events were fitted into longer lasting intervals between onsets and offsets of words assumed\todo{Why assumed? Isn't the point of the annotion to "know"?} to contain no audible speech.
 Each event of the no-speech condition had to have a minimum distance of \unit[1.8]{s} to an onsets/offsets of word, and to each onset to another event of the no-speech condition.
 A length of \unit[70]{ms} was chosen for no-speech events matching the average length of phonemes.
-Lastly, we used events reflecting low-level auditory features (left-right difference in volume and root mean squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
+Lastly, we used events\todo{They are not really events, but a continous nuisance regressor} reflecting low-level auditory features (left-right difference in volume and root mean squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
 All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function to create the actual regressors.
@@
 
-\todo[inline]{die motion parameters werden nicht konvolviert, oder?}
+\todo[inline]{die motion parameters werden nicht konvolviert, oder? MIH: Dunno.}
 The following three t-contrasts were defined:
@@
 3) nouns (\texttt{nn}; N=\rNeAll) > coordinate conjunctions.
-The first level analysis which fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images [+++richtig?+++].
+\todo[inline]{I think having the N here is confusion.
+It is a contrast between regressors models.
+The number of events only indirectly accounts for the variance (which is interesting here).
+I would strip this info to reduce confusion}
+% implementation detail. Any analysis should preserve the orientiation.
+%The first level analysis which fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images [+++richtig?+++].
 
@@
 
-\todo{Figure zeigt whole brain statt “partial brain coverage”; vgl. Text; Problem?}
+\todo{Figure zeigt whole brain statt “partial brain coverage”; vgl. Text; Problem? MIH: Could become an issue. In the data paper we showed the coverage. Maybe just ref the figure.}
 \begin{figure*}
@@
 Contrary to previous studies, we do not find increased medial activation in the precuneus or medial frontal cortex.
-This could be attributed to the fact that our contrast does not [+++sufficiently+++] capture social aspects of the narrative \citep{ferstl2008extended, mar2011neural}\todo{abchecken}.
-The two contrasts contrasting nouns and proper nouns respectively to coordinate junctions lead to unexpected results.
+This could be attributed to the fact that our contrast does not [+++sufficiently+++]\todo{Which contrast captures ANY social aspects?} capture social aspects of the narrative \citep{ferstl2008extended, mar2011neural}\todo{abchecken}.
+The two contrasts contrasting nouns and proper nouns respectively to coordinate junctions lead to unexpected results\todo{That seems like an unfortunate statement.
+We make this analysis to show expected results to conclude that the annotation is good.
+But we get unexpected results and conclude...}.
 Increased activation is partially located in early sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most prominently adjacant regions bilaterally (planum temporale; superior temporal gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
@@
 Moreover, the coordinate junctions (\texttt{kon}) mostly comprises event of the words ``and'' (N=392) and ``but'' (N=49) and thus offered only a small amount of variance.
-A second explanation might be that our phoneme regressors that assumed linear summation of approximatly 70 ms lasting events in quick succession did not capture a sufficiently amount of nuissance variance.
-Nevertheless and more importantly to access the validity of the dataset is the fact that two similar lingustic concepts (nouns and proper nouns) embedded in a naturalistic stimulus that was not designed for linguistic research lead to similar activation patterns.
+A second explanation might be that our phoneme regressors that assumed linear summation of approximatly 70 ms lasting events in quick succession did not capture a sufficiently amount of nuissance variance\todo{Reviewer 2 will ask: If you knew all these issues, why did you do it then?}.
+Nevertheless and more importantly to access the validity of the dataset is the fact that two similar lingustic concepts (nouns and proper nouns) embedded in a naturalistic stimulus that was not designed for linguistic research lead to similar activation patterns\todo{That statement is only true, if both contrasts are not (solely) driven by the conjuctions.
+There is no evidence in the paper that this is not the case.}
 % Within the language processing systems, early sensory regions are specialized for representing the immediate physical properties of the environment (form), while higher order regions extract increasingly abstract content (Davis and Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).

### 2020-05-20 paper/main.tex
revise abstract

@@
 The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
-Additionally for every word, we provide lemmatization, two different part-of-speech taggings (simple and detailed), syntactic dependencis within each sentence, and a 300-dimensional semantic representation (word vector).
+Additionally for every word, we provide lemmatization, a simple
+part-of-speech-tagging putting words into 15 grammatical categories, a detailed
+part-of-speech tagging putting words into 43 grammatical categories, syntactic
+dependencies within each sentence, and a semantic analysis based on word
+embedding providing a 300-dimensional word vector.
 This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
-\todo[inline]{I don't understand what "two different part-of-speech taggings (simple and detailed)" means}
-\todo[inline]{"300-dimensional semantic representation (word vector)" I think we need to find a better description, but I could not come up with one so far}
 \end{abstract}

### 2020-05-20 paper/main.tex
revise introduction (and abstract)

@@
 dependencies within each sentence, and a semantic analysis based on word
-embedding providing a 300-dimensional word vector.
+embeddings representing each word in a 300-dimensional semantic space.
 This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
@@
 
+% data-driven methods
 Because naturalistic stimuli are multi-dimensional and their temporal structure
@@
 (ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
-corresponding fMRI data.  Nevertheless, model-driven methods, like a general
-linear model (GLM), can be useful to investigate which specific stimulus
-properties a brain region is responding to \citep{hamilton2018revolution}. For
-example, studies using GLMs based on annotations of a stimulus' temporal
+corresponding fMRI data. However, data-driven methods alone fall short of
+pinpointing their results to specific, time-locked features of a stimulus
+\citep{kauttonen2015optimizing}.
+% model-driven methods
+Model-driven methods, like a general linear model (GLM), can be useful to
+investigate how hemodynamic brain responses in isolated regions correlate with
+stimulus features. They can explain not just ``how'' the brain is responding to
+a stimulus but also ``why'' \citep{hamilton2018revolution}.
+% GLM: example studies
+For example, studies using GLMs based on annotations of a stimulus' temporal
 structure have elucidated how the brain responds to visual features of a movie
@@
 
-For this publication, we annotated the exact onsets and offsets, and content of
-sentences, single words, and phonemes spoken in the audio-visual movie
-``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e. an
-audio-only variant of the movie)\citep{ForrestGumpDVD}.
-% immediate reference not needed in the intro
-%(see Table \ref{tab:overview} for an overview of the annotation's content).
+% We:
+For this publication, we revised previous, preliminary annotations done by our
+lab and now provide one single annotation with exact onsets/offsets and content
+of each sentences, word and phonemes (see Table \ref{tab:overview} for an
+overview) spoken in the audio-visual movie ``Forrest Gump''
+\citep{ForrestGumpMovie} and its audio-description (i.e. an audio-only variant
+of the movie)\citep{ForrestGumpDVD}.
+% the studyforrest dataset
+fMRI data of participants watching the audio-visual movie
+\citep{hanke2016simultaneous} and listening to the audio-description
+\citep{hanke2014audiomovie} are the core data of the publicly available
+\textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
+% why
+This publication enables researchers to model time-locked hemodynamic brain
+responses that correlate with different aspects of spoken occurring in a 2-hour
+lasting naturalistic stimulus.
+% extending previous non-speech annotations
+The current annotation of speech extends already available annotations of
+portrayed emotions \citep{labs2015portrayed}, perceived emotions
+\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the
+movie \citep{haeusler2016annotation}. All annotations can be used in any study
+focusing on aspects of real-life cognition by serving as additional confound
+measures describing key properties of major building blocks of the stimulus.
 
-fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
-% the following seems unrelated to the scope of the paper
-%Additional fMRI data of this dataset include the perception of musical genres
-%\citep{hanke2015musical}, and retinotopic mappings and localization of higher
-%visual areas of the same participants \citep{sengupta2016extension}.
-The annotation presented here facilitates modelling of hemodynamic brain responses
-correlated with speech-related events in the two stimuli.
-It extends already available annotations of portrayed emotions
-\citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy},
-as well as cuts and locations depicted in the movie
-\citep{haeusler2016annotation}.  All annotations can be used in any study
-focusing on other aspects of real-life cognition by serving as additional
-confound measures describing key properties of major building blocks of the
-stimulus.
-
-\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.\\
-If you want to take this question in a revision, I am OK with that. However,
-the intro still doesn't say anything about WHY one would want to do "modelling of
-hemodynamic brain responses correlated with speech-related events" other than
-to discard speech as a confound. This seems like a massive underselling.}
+\todo[inline]{Das “why one should model” ist jetzt drin; Frage an dich als
+Datenanalyse-Pro: Man kann doch bestimmt auch data-driven methods irgendwie
+“constrainen”, und die durch eine Annotation verbessern? Hast du da eine
+Formulierung und/oder auch ein (high-level) Paper für mich zu dem Thema?}
 
@@
 ATM this is the only statement in this regard:
-'facilitates modelling of hemodynamic brain responses correlating with speech-related events' and the only indication of purpose is 'additional confound measures'.
+'facilitates modeling of hemodynamic brain responses correlating with speech-related events' and the only indication of purpose is 'additional confound measures'.
 I think this is incongruent with the amount of work and the level of detail of

### 2020-05-20 paper/main.tex
revise methods until table "overview"

@@
 
-\section*{Materials and methods}
-\subsection*{Stimulus}
-We annotated speech in the slightly shortened ``research cut'' of the movie \citep{hanke2016simultaneous} and its temporally aligned audio-description \citep{hanke2014audiomovie}.
-For the movie stimulus, we used the audio track of the German DVD release \citep{ForrestGumpDVD}.
-For the audio-only stimulus, we used the movie's audio-description that was broadcast as an additional audio track for visually impaired listeners on Swiss public television \citep{ForrestGumpGermanAD}.
-The plot of the movie is already carried by an off-screen voice of the main character Forrest Gump.
-In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content.
+\section*{Materials and methods} \subsection*{Stimulus}
+% stimulus != DVD but ``research cut''
+We annotated speech in the slightly shortened ``research cut'' of the movie
+\citep{hanke2016simultaneous} and its temporally aligned audio-description
+\citep{hanke2014audiomovie}.
+% movie source
+For the movie stimulus, we used the audio track of the German DVD release
+\citep{ForrestGumpDVD}.
+% audio source
+For the audio-only stimulus, we used the movie's audio-description that was
+broadcast as an additional audio track for visually impaired listeners on Swiss
+public television \citep{ForrestGumpGermanAD}.
+% diff in audio AV vs. AO
+The plot of the movie is already carried by an off-screen voice of the main
+character Forrest Gump. In the largely identical audio-description, a male
+narrator additionally describes essential aspects of the visual scenery when
+there is no off-screen voice, dialog, or other relevant auditory content.
 
 \subsection*{Annotation procedure}
-Preliminary, manual orthographic transcriptions of dialogues, non-speech vocalizations (e.g.
-laughing or groaning) and script for the audio-description's narrator were merged, and converted to Praat's \citep{boersma2019praat} TextGrid format.
-
+% preliminary annotations
+Preliminary, manual orthographic transcriptions of dialogues, non-speech
+vocalizations (e.g. laughing or groaning) and script for the audio-description's
+narrator were merged, and converted to Praat's \citep{boersma2019praat} TextGrid
+format.
+% preparing annotation in Praat before forced alignment
 % \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
-The merged transcription containing a rough onset and offset for usually a couple of sentences was edited in Praat for manual validation against the original audio.
-The following steps were done in several passes to iteratively improve the quality of the data:
-approximate temporal onsets and offsets were corrected, and intervals containing several sentences were split into intervals containing only one sentence.
-When two or more persons were speaking simultaneously the less dominant voice was dropped.
-Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations which were subjectively assessed to be incomprehensible for the audience were dropped, too.
-
-% Alignment preparations
+The merged transcription containing a rough onset and offset for usually a
+couple of sentences was edited in Praat for manual validation against the
+original audio.
+% steps conducted
+The following steps were done in several passes to iteratively improve the
+quality of the data: approximate temporal onsets and offsets were corrected, and
+intervals containing several sentences were split into intervals containing only
+one sentence.
+% dropping of sentences hard to understand
+When two or more persons were speaking simultaneously the less dominant voice
+was dropped. Low volume background speech (especially occurring during music or
+continuous environmental noise) or low volume non-speech vocalizations which
+were subjectively assessed to be incomprehensible for the audience were dropped,
+too.
+% intro for forced aligner
+We used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
+algorithmically identify the exact onset of offset of the sentences, and the
+onset and offset of each word and phoneme embedded in the transcribed sentences.
+% preparing other inputs before forced alignment pronounciation dictionary
 % http://prosodylab.org
 % https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
-We used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
-algorithmically identify the exact onset of offset of the sentences, and the onset and offset of each word and phoneme embedded in the transcribed sentences.
-To enable the aligner to look up the phonemes embedded within each word, we chose a German pronunciation dictionary provided by Prosodylab \citep {gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the pronounciation of phonemes.
-To improve the detection rate of the automatic alignment, the dictionary was manually updated with German words that occur in the stimuli but were originally missing in the dictionary.
+To enable the aligner to look up the phonemes embedded within each word, we
+chose a German pronunciation dictionary provided by Prosodylab \citep
+{gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the
+pronunciation of phonemes.
+% extending the dictionary with formerly unknown German words
+To improve the detection rate of the automatic alignment, the dictionary was
+manually updated with German words that occur in the stimuli but were originally
+missing in the dictionary.
 % \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
-The pronunciation of English words and phonemes occurring in the otherwise German audio track was taken from an English pronunciation dictionary (following the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).
+% English words in the otherwise German stimulus
+The pronunciation of English words and phonemes occurring in the otherwise
+German audio track was taken from an English pronunciation dictionary (following
+the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab
+(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).
 
-% Alignment
-The audio track was converted from FLAC to WAV via FFmpeg \citep{ffmpeg} to meet the aligner's requirements.
+% performing the forced alignment audio input to the aligner
+The audio track was converted from FLAC to WAV via FFmpeg \citep{ffmpeg} to meet
+the aligner's requirements.
+% inputs
 This WAV file, the transcription of sentences, and the updated dictionary were
@@
 then performed the alignment.
-The resulting .TextGrid file that contains onsets and offsets of words and phonemes was corrected manually and iteratively in several passes:
-In a first step, onsets and offsets on which the automatic alignment performed moderately were corrected in Praat.
-Some low volume sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, rally, disco) were removed due to poor overall alignment performance.
-In a second step, the complete sentences of the orthographic transcription were copied into the annotation created by the aligner.
-In a third step, the a speaker's identity was added for each sentence (see Table \ref{tab:speakers} for the most often occurring speakers).
-During every step results from previous steps were checked again for errors.
+% output
+The resulting .TextGrid file that contains onsets and offsets of words and
+phonemes was corrected manually and iteratively in several passes:
+% onset/offset checking & correction
+In a first step, onsets and offsets on which the automatic alignment performed
+moderately were corrected in Praat.
+% handling poor performance
+Some low volume sentences that are spoken in continuously noisy settings
+(pursuit, battle, hurricane, rally, disco) were removed due to poor overall
+alignment performance.
+% adding whole sentences
+In a second step, the complete sentences of the orthographic transcription were
+copied into the annotation created by the aligner.
+% speaker identity
+In a third step, a speaker's identity was added for each sentence (see Table
+\ref{tab:speakers} for the most often occurring speakers).
+% constant on-the-fly checking of previous
+During every step results from previous steps were constantly checked again for
+errors and further improvements.
 

### 2020-05-20 paper/main.tex
revise table caption

@@
 Preliminary, manual orthographic transcriptions of dialogues, non-speech
-vocalizations (e.g. laughing or groaning) and script for the audio-description's
+vocalizations (e.g. laughter or groaning) and script for the audio-description's
 narrator were merged, and converted to Praat's \citep{boersma2019praat} TextGrid
@@
 onset and offset of each word and phoneme embedded in the transcribed sentences.
-% preparing other inputs before forced alignment pronounciation dictionary
+% preparing other inputs before forced alignment pronunciation dictionary
 % http://prosodylab.org
@@
 \begin{table*}[tbp]
-    \caption{Overview of the annotation's content for the whole stimulus and its individual segments used during fMRI scanning.
-The category \texttt{sentences} comprises complete grammatical sentences which are additionally marked in the annotation with a full stop at the end (``my feet hurt.'').
-    It also comprises questions (``do you want a chocolate?''), exlamations (``run away!), or non-speech vocalizations in quick succession (``ha, ha, ha''), or in isolation (e.g.
-``Forrest?'', ``Forrest!'', ``ha'') at time points when speakers switch rapidly.
-The category \texttt{words} comprises each word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
+    \caption{Overview of the annotation's content for the audio-only stimulus
+that comprises the additional narrator. Counts are given for the whole stimulus
+(\texttt{all}) and its individual segments used during fMRI scanning.
+The category \texttt{sentences} comprises complete grammatical sentences which
+are additionally marked in the annotation with a full stop at the end (``my feet hurt.'').
+It also comprises questions (``do you want a chocolate?''), exclamations (``run
+away!''), or non-speech vocalizations in quick succession (``ha, ha, ha''), or
+in isolation (e.g. ``Forrest?'', ``Forrest!'', ``ha'') at time points when
+speakers switch rapidly. The category \texttt{words} comprises each word or
+non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
 \label{tab:overview}
@@
 \begin{table*}[btp]
-\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurrs in the audio-description of the movie.
+\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurs in the audio-description of the movie.
 Overall 97 persons were identified.
@@
 
-% NLP
+% natural luanguage processing (NLP)
 % Tiger Treebank Corpus:

### 2020-05-20 paper/main.tex
revise rest of annotation procedure
revise of methods until 1st lvl analysis

@@
 
-% natural luanguage processing (NLP)
+% natural language processing (NLP)
+% spaCy
+To automatically analyze linguistic features of each words in their
+corresponding sentence, we employed the Python package spaCy \citep{spacy2} and
+its accompanying German language model (\texttt{de\_core\_news\_md} that was
+trained on the TIGER Treebank corpus \citep{brants2004tiger}.
 % Tiger Treebank Corpus:
 % \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
-To automatically analyze linguistic features of each words in their corresponding
-sentence, we employed the Python package spaCy \citep{spacy2} and its accompanying German language model (\texttt{de\_core\_news\_md} that was trained on the TIGER Treebank corpus \citep{brants2004tiger}.
-Non-speech vocalizations were dropped from the sentences before analysis.
-We performed analyses regarding part-of-speech (i.e.
-grammatical tagging or word-category disambiguation), syntactic dependencies, lemmatization, word embedding (i.e.
-multi-dimensional meaning representation of a word), and if the word is one of the most common words of the German language (i.e.
-if the word is part of a stop list).
+% dropping of non-speech vocalizations because they often delude the algo
+Non-speech vocalizations were dropped from the sentences before analysis to
+improve results.
+% performed analyses
+We performed analyses regarding part-of-speech (i.e. grammatical tagging or
+word-category disambiguation), syntactic dependencies, lemmatization, word
+embedding (i.e. multi-dimensional meaning representation of a word), and if the
+word is one of the most common words of the German language (i.e. if the word is
+part of a stop list).
 
-\subsection*{Data Legend}
-\todo[inline]{Minimale Info hier, dass es zwei Versionen gibt und sich der folgende Abschnitt auf TSV file bezieht}
-The annotation is available in two different versions, both providing the same information: a) as a (text-based) Praat TextGrid file and b) as a text-based, tab-separated value (TSV) formatted table.
+\subsection*{Data Legend} \todo[inline]{Minimale Info hier, dass es zwei
+Versionen gibt und sich der folgende Abschnitt auf TSV file bezieht}
+% TextGrid vs. TSV
+The annotation is available in two different versions, both providing the same
+information: a) as a (text-based) Praat TextGrid file and b) as a text-based,
+tab-separated value (TSV) formatted table.
+% preview of following subsubsections
 The following descriptions refer to the ten columns of the TSV file, namely
-\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text} (of sentence, word or phoneme), \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma}, \texttt{stop}, \texttt{vector}.
+\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text} (of sentence,
+word or phoneme), \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma},
+\texttt{stop}, \texttt{vector}.
 
-\subsubsection*{Start (\texttt{start})}
-The onset of the sentence, word or phoneme. Time stamps are provided in the format seconds.milliseconds of stimulus onset.
+\subsubsection*{Start (\texttt{start})} The onset of the sentence, word or
+phoneme. Time stamps are provided in the format seconds.milliseconds of stimulus
+onset.
 
-\subsubsection*{Duration (\texttt{duration})}
-The duration of the sentences, word or phoneme provided the format seconds.milliseconds.
+\subsubsection*{Duration (\texttt{duration})} The duration of the sentences,
+word or phoneme provided the format seconds.milliseconds.
 
-\subsubsection*{Speaker identity (\texttt{person})}
-Name of the person that speaks the sentence, word or phoneme. See Table \ref{tab:speakers} for the ten most often ocurring speakers.
+\subsubsection*{Speaker identity (\texttt{person})} Name of the person that
+speaks the sentence, word or phoneme. See Table \ref{tab:speakers} for the ten
+most often occurring speakers.
 
 \subsubsection*{Text (\texttt{text})}
-\todo[inline]{Großphoneme erwähnen;Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach die Event-Borders zwischen den Phonemen herausgenommen.
-Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
-Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach).
-kommt jedoch so selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.}
-The text of a spoken sentence or word, or the pronounciation of a phoneme.
-Phonemes of German words follow the Prosodylab PhoneSet, English words follow the ARPAbet PhoneSet.
+% ``Großphoneme'': n<200
+The text of a spoken sentence or word, or the pronunciation of a phoneme.
+Phonemes of German words follow the Prosodylab PhoneSet, English words follow
+the ARPAbet PhoneSet.
 
-\subsubsection*{Simple part-of-speech tag (\texttt{pos})}
-A simple part-of-speech tagging (grammatical tagging; word-category disambiguation) of a word.
-The simple part-of-speech tagging tags follow the Universal Dependencies v2 POS tag set (\href{https://universaldependencies.org}{universaldependencies.org}).
-See Table \ref{tab:pos} for a description of the labels and the respective counts of all 15 labels.
-Nouns that spaCy mistook for proper nouns or vice versa were corrected via script.
-% s. list at the beginning of script
-% code/add_part-of-speech-tagging2textgrid.py
-Additionally in cells of this column, sentences are tagged as \texttt{SENTENCE}, and phonemes are tagged as \texttt{PHONEME} to facilitate sorting, and filtering in potential further processing steps.
+\subsubsection*{Simple part-of-speech tag (\texttt{pos})} A simple
+part-of-speech tagging (grammatical tagging; word-category disambiguation) of a
+word.
+% annotation scheme
+The simple part-of-speech tagging tags follow the Universal Dependencies v2 POS
+tag set (\href{https://universaldependencies.org}{universaldependencies.org}).
+% reference to table
+See Table \ref{tab:pos} for a description of the labels and the respective
+counts of all 15 labels. Nouns that spaCy mistook for proper nouns or vice
+versa were corrected via script.
+% s. list at the beginning of script code/add_part-of-speech-tagging2textgrid.py
+% flags for sentences and phonemes in POS column
+Additionally in cells of this column, sentences are tagged as \texttt{SENTENCE},
+and phonemes are tagged as \texttt{PHONEME} to facilitate sorting, and filtering
+in potential further processing steps.
 
@@
 % \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset}
-A detailed part-of-speech tagging of a word following the TIGER Treebank annotation scheme \citep{brants2004tiger} which is based on the Stuttgart-Tübingen-Tagset \citep{schiller1999stts}.
-See Table \ref{tab:tag} for a descripion  of the labels and the respective counts of the 15 most often occuring labels.
-Nouns that spaCy mistook for proper nouns or vice versa were corrected via script.
-% s. list at the beginning of script
-% code/add_part-of-speech-tagging2textgrid.py
+A detailed part-of-speech tagging of a word following the TIGER Treebank
+annotation scheme \citep{brants2004tiger} which is based on the
+Stuttgart-Tübingen-Tagset \citep{schiller1999stts}.
+% reference to table
+See Table \ref{tab:tag} for a descripion  of the labels and the respective
+counts of the 15 most often occuring labels. Nouns that spaCy mistook for proper
+nouns or vice versa were corrected via script.
+% s. list at the beginning of script code/add_part-of-speech-tagging2textgrid.py
 
@@
 
-\subsubsection*{Syntactic dependency (\texttt{dep})}
-Information about a word's syntactic dependencies with other words within the same sentence.
-Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger} and is given in the format:
-``arc label;word's head;word's child1, word's child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the type of syntactic relation that connects a "child" (the single word) to its "head".
+\subsubsection*{Syntactic dependency (\texttt{dep})} Information about a word's
+syntactic dependencies with other words within the same sentence.
+% annotation scheme
+Information follows the TIGER Treebank annotation scheme \citep{brants2004tiger}
+and is given in the format: ``arc label;word's head;word's child1, word's
+child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the
+type of syntactic relation that connects a "child" (the single word) to its
+"head".
 
@@
 
-\subsubsection*{Lemmatization (\texttt{lemma})}
-The base form (root) of a word.
+\subsubsection*{Lemmatization (\texttt{lemma})} The base form (root) of a word.
 
@@
 % datasets, including any allowances made for controlling bias or unwanted
-% sources of variability.
-% ~170 words => das wird beim folgenden Schreiben definitiv nichts werden
-% Intro
-In order to assess data quality, we investigated if contrasting speech-related events to events without speech lead to increased activation in areas known to be involved in semantic processing \citep{hickok2007cortical}.
-Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (coordinate conjunctions) lead to increased activation in congruent brain areas.
-% Preprocessing
-\todo[inline]{hanke2014 spricht von 20 subjects (age 21–38 years, mean age 26.6 years, 12 male), es fehlt hier aber sub-10. MIH: age doesn't matter here. Just say that you left out sub-10, and why}
-% Details of the alignment procedure are given in the section on “Technical Validation”.
-%Data aligned by applying an affine transformation only are available in bold_dico_dico7Tad2grpbold7Tad.nii.gz.
-% Data aligned by non-linear warping are available in bold_dico_dico7Tad2grpbold7Tad_nl.nii.gz.
-We used blood oxygenation level-dependent (BOLD) functional magnetic resonance imaging (fMRI) data of the 2h audio-description (\unit[7]{Tesla}, \unit[2]{s} repetition time, 3599 volumes, 36 axial slices, thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm} field-of-view) of 19 healthy subjects \citep{hanke2014audiomovie}.
+% sources of variability. ~170 words => das wird beim folgenden Schreiben
+% definitiv nichts werden intro
+In order to assess data quality, we investigated if contrasting speech-related
+events to events without speech lead to increased activation in areas known to
+be involved in semantic processing \citep{hickok2007cortical}.
+% nouns and proper nouns resp. > coordinate junctions
+Moreover, we tested if similar linguistic concepts providing high semantic
+information (proper nouns and nouns) contrasted to a concept providing low
+semantic information (coordinate conjunctions) lead to increased activation in
+congruent brain areas.
+% data source
+% data aligned by applying an affine transformation only are available in
+% bold_dico_dico7Tad2grpbold7Tad.nii.gz.
+% data aligned by non-linear warping are available in
+% bold_dico_dico7Tad2grpbold7Tad_nl.nii.gz.
+We used a dataset providing blood oxygenation level-dependent (BOLD) functional
+magnetic resonance imaging (fMRI) data of 20 subjects (age 21–38 years, mean age
+26.6 years, 12 male) listening to the 2h audio-description (\unit[7]{Tesla},
+\unit[2]{s} repetition time, 3599 volumes, 36 axial slices, thickness
+\unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm}
+field-of-view) \citep{hanke2014audiomovie}.
+% motion correction
 Data were already corrected for motion at the scanner computer.
-Further, individual BOLD time-series were already aligned by non-linear warping to a study-specific T2*-weighted echo planar imaging (EPI) group template (cf.
+% alignment
+Further, individual BOLD time-series were already aligned by non-linear warping
+to a study-specific T2*-weighted echo planar imaging (EPI) group template (cf.
 \citep{hanke2014audiomovie} for details on how the group template was created).
-\todo[inline]{So korrekt und “vollständig?
-MNI152 co-registration?
-Im Übrigen finde ich 3-4 Paper, die als Zitation für den MNI152-space in Frage kommen, wobei keines richtig passen will; hanke2014 zitiert keines.
-MIH: That is sufficient.
-No need to cite anything for MNI152}
-All further analysis steps were carried out using Feat v6.00 (FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB's Software Library)\citep{smith2004fsl}.
-Data were temporally high-pass filtered (cut-off \unit[150]{s}), spatially smoothed (Gaussian kernel; \unit[4.0]{mm} FWHM), and the brain was extracted from surrounding tissue.
-A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
+% steps done by C.H.
+All further analysis steps were carried out using Feat v6.00 (FMRI Expert
+Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB's
+Software Library)\citep{smith2004fsl}.
+% dropping of subject 10
+Data of one participant was dropped to due to invalid distortion correction
+during scanning.
+% temporal and spatial filter, brain extraction
+Data were temporally high-pass filtered (cut-off \unit[150]{s}), spatially
+smoothed (Gaussian kernel; \unit[4.0]{mm} FWHM), and the brain was extracted
+from surrounding tissue.
+% normalization
+A grand-mean intensity normalization of the entire 4D dataset was performed by a
+single multiplicative factor.
 
@@
     \caption{Overview of the events that were used to create the 26 regressors of the GLM analysis.
-The respective counts are given for the whole stimulus and the eight segments that were used during fMRI scanning.
-The 20 most often occuring labels from the detailed part-of speech tagging (\texttt{tag}) were used as such.
+The respective counts are given for the whole stimulus and the eight segments
+that were used during fMRI scanning.
+The 20 most often occurring labels from the detailed part-of speech tagging     (\texttt{tag}) were used as such.
 Words belonging to all other labels were pooled to \texttt{tag\_other}.
 The label \texttt{sentence} contains the end of complete grammatical sentences.
-The label \texttt{phones} contains events of the 80 most often occuring phonemes (phoneme \texttt{n} with N=6053 to phoneme \texttt{IY1} with N=32).
+The label \texttt{phones} contains events of the 80 most often occurring
+phonemes (phoneme \texttt{n} with N=6053 to phoneme \texttt{IY1} with N=32).
 The label \texttt{no-sp} represents moments when no speech was audible.
@@
 Events were convolved with FSL's ``Double-Gamma HRF'' to create the regressors.
-The correlation of these regressors over the time course of the whole stimulus can be seen in Figure \ref{fig:reg-corr}.}
+The correlation of these regressors over the time course of the whole stimulus
+can be seen in Figure \ref{fig:reg-corr}.}
 \label{tab:regressors}
@@
 sentence & complete grammatical sentences & \rSentenceAll & \rSentenceI & \rSentenceII & \rSentenceIII & \rSentenceIV & \rSentenceV & \rSentenceVI & \rSentenceVII & \rSentenceVIII \tabularnewline
-phones & 80 most often occuring phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
+phones & 80 most often occurring phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
 no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline

### 2020-05-25 paper/main.tex
revision and formatting of 1st lvl analysis

@@
 
-% 1st lv}
-\todo[inline]{What follows has typos}
-We implemented a standard three-level, voxel-wise general linear model (GLM) to average parameter estimates across the eight stimulus segments, and later across 19 subjects.
-At the first level analyzing each segment for each subject individually, we created 26 regressors based on events drawn from the annotation (see Table \ref{tab:regressors}).
-The 20 most often occuring detailed part-of-speech labels (\texttt{nn} with N=\rNnAll\space to text{prf} with N=\rPrfAll) were modelled as such from the onset to offset of each word\todo{This has errors that I do not know how to fix}.
-The remaining labels were pooled to (\texttt{tag\_other}; N=\rTagotherAll)\todo{I do not know what this means}.
-The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) to be used as a nuisance regressors\todo{Does that mean they share events with "other"}.
-The end of each complete grammatical sentence was modeled as an impulse event (N=\rSentenceAll)\todo{Why?
-Above it says 'we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns)'.
-What does this need sentences for?}.
-``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control condition were created by the following rationale:
-events were fitted into longer lasting intervals between onsets and offsets of words assumed\todo{Why assumed? Isn't the point of the annotion to "know"?} to contain no audible speech.
-Each event of the no-speech condition had to have a minimum distance of \unit[1.8]{s} to an onsets/offsets of word, and to each onset to another event of the no-speech condition.
-A length of \unit[70]{ms} was chosen for no-speech events matching the average length of phonemes.
-Lastly, we used events\todo{They are not really events, but a continous nuisance regressor} reflecting low-level auditory features (left-right difference in volume and root mean squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
-All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function to create the actual regressors.
-The Pearson correlation coefficients of the 26 regressors across the time course of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
-Temporal derivatives were also included in the design matrix and the design was subjected to the same temporal filtering as the BOLD time series.
+% intro to analysis
+We implemented a standard three-level, voxel-wise general linear model (GLM) to
+average parameter estimates across the eight stimulus segments, and later across
+19 subjects.
+% 1st lvl
+At the first level analyzing each segment for each subject individually, we
+created 26 regressors based on events drawn from the annotation (see Table
+\ref{tab:regressors}).
+% part-of-speech labels: labels to events, top 20
+The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
+N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
+from onset to offset of each word \todo{This has errors that I do not know how
+to fix; sorry, unclear what you mean by that}.
+% path-of-speech labels: remaining labels
+The remaining other part-of-speech labels were pooled to a single new label
+(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
+function from onset to offset of the corresponding word\todo{I do not know what
+this means; hope it got clearer now}.
+% phonemes
+The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were
+pooled to \texttt{phonemes} (N=\rPhonesAll) and each event modeled as boxcar
+function from onset to offset of the corresponding phoneme.\todo{Does that mean
+they share events with "other"}.
+% sentence (endings)
+The end of each complete grammatical sentence was modeled as an impulse event
+(N=\rSentenceAll) to capture variance of sentence comprehension\todo{Why? Above
+it says 'we tested if similar linguistic concepts providing high semantic
+information (proper nouns and nouns)'. What does this need sentences for?}.
+% no-speech intro
+``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
+condition were created by the following rationale: events were fitted into
+longer lasting intervals between onsets and offsets of words and thus within
+intervals without audible speech \todo{Why assumed? Isn't the point of the
+annotation to "know"? => Words where chosen to carefully; intervals don't
+contain any audible speech with 98 perc. certainty}
+% minimum distance to words
+Each event of the no-speech condition had to have a minimum distance of
+\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
+event of the no-speech condition.
+% length of no-speech events
+A length of \unit[70]{ms} was chosen for no-speech events matching the average
+length of phonemes.
+% low-level nuisance regressors
+Lastly, we used events\todo{They are not really events, but a continuous
+nuisance regressor; okay, how do you phrase that correctly?} reflecting
+low-level auditory features (left-right difference in volume and root mean
+squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
+All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the
+hemodynamic response function to create the actual regressors.
+% reference to figure ``correlation of regressors''
+The Pearson correlation coefficients of the 26 regressors across the time course
+of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
+% temporal derivatives
+Temporal derivatives were also included in the design matrix and the design was
+subjected to the same temporal filtering as the BOLD time series.
+% motion parameters
 Finally, six motion parameters were used as additional nuisance regressors.
@@
 \todo[inline]{die motion parameters werden nicht konvolviert, oder? MIH: Dunno.}
+
+% t-contrasts
 The following three t-contrasts were defined:

### 2020-05-25 paper/main.tex
revision of t-contrasts

@@
 
-\todo[inline]{die motion parameters werden nicht konvolviert, oder? MIH: Dunno.}
-
 % t-contrasts
 The following three t-contrasts were defined:
-% 1b) no-speech > words;
-% 2b) coordinate conjunctions > proper nouns;
-% 3b) coordinate conjunctions > nouns.
-1) words (all 21 \texttt{tag}-related regressors; N=15985) > no-speech (\texttt{no-sp}; N=\rNospAll),
-2) proper nouns (\texttt{ne}; N=\rNeAll) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
-3) nouns (\texttt{nn}; N=\rNeAll) > coordinate conjunctions.
-\todo[inline]{I think having the N here is confusion.
-It is a contrast between regressors models.
-The number of events only indirectly accounts for the variance (which is interesting here).
-I would strip this info to reduce confusion}
-% implementation detail. Any analysis should preserve the orientiation.
-%The first level analysis which fitted each voxel's time course separately for each subject was performed in functional space preserving the orientation of the EPI images [+++richtig?+++].
+1) words (all 21 \texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
+% 1b) no-speech > words
+2) proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
+% 2b) coordinate conjunctions > proper nouns
+3) nouns (\texttt{nn}) > coordinate conjunctions.
+% 3b) coordinate conjunctions > nouns
 
-% Also weshalb wird das temporal filtering der regressoren wann wie gemacht??? -> nachschlagen
-% “You should normally apply the same temporal filtering to the model as you have applied to the data, as the model is designed to look like the data before temporal filtering was applied.
-In this way, long-time-scale components in the model will be dealt with correctly.
-This is set with the Apply temporal filtering option.”
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figures/regressor-corr}
-  \caption{Pearson correlation coefficients of the 26 regressors used in the analysis to validate the annotation.
-Regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation.}
-\label{fig:reg-corr}
-\end{figure*}
+\begin{figure*} \centering
+    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
+    correlation coefficients of the 26 regressors used in the analysis to
+    validate the annotation.
+    Regressors were convolved with FSL's
+    ``Double-Gamma HRF'' as a model of the hemodynamic response function and
+    concatenated across runs before performing the correlation.}
+\label{fig:reg-corr} \end{figure*}
 

### 2020-05-25 paper/main.tex
revision of (cluster) results

@@
 \begin{figure*} \centering
-    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
-    correlation coefficients of the 26 regressors used in the analysis to
-    validate the annotation.
-    Regressors were convolved with FSL's
-    ``Double-Gamma HRF'' as a model of the hemodynamic response function and
-    concatenated across runs before performing the correlation.}
+\includegraphics[width=\linewidth]{figures/regressor-corr}
+\caption{Pearson correlation coefficients of the 26 regressors used in the
+    analysis to validate the annotation.
+    Regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the
+    hemodynamic response function and concatenated across runs before
+    performing the correlation.}
 \label{fig:reg-corr} \end{figure*}
 
-% 2nd lvl and 3rd lvl
-The second-level analysis which averaged contrast estimates across the eight stimulus segments per subject was carried out using a fixed effects model by forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
-The third level analysis which averaged contrast estimates across subjects was carried out using FLAME stage 1 with automatic outlier de-weighting \citep{woolrich2004multilevel, woolrich2008robust}.
-Z (Gaussianised T/F) statistic images were thresholded using clusters determined by Z>3.4 and a corrected cluster significance threshold of p<.05 \citep{woolrich2008robust}.
-Brain regions associated with observed clusters were determined with the Juelich Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
+% 2nd lvl
+The second-level analysis which averaged contrast estimates across the eight
+stimulus segments per subject was carried out using a fixed effects model by
+forcing the random effects variance to zero in FLAME (FMRIB's Local Analysis of
+Mixed Effects) \citep{beckmann2003general, woolrich2004multilevel}.
+% 3rd lvl
+The third level analysis which averaged contrast estimates across subjects was
+carried out using FLAME stage 1 with automatic outlier de-weighting
+\citep{woolrich2004multilevel, woolrich2008robust}.
+% thresholding
+Z (Gaussianised T/F) statistic images were thresholded using clusters determined
+by Z>3.4 and a corrected cluster significance threshold of p<.05
+\citep{woolrich2008robust}.
+% identification of brain regions
+Brain regions associated with observed clusters were determined with the Jülich
+Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the
+Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
 
 % Results
+Figure \ref{fig:results} depicts the results of the three contrasts (Z threshold
+Z>3.4; p<.05 cluster-corrected).
 % COPE 1:
-Figure \ref{fig:results} depicts the results of the three contrasts (all Z-Threshold Z>3.4; p<.05 cluster-corrected).
-The contrast words (all 21 \texttt{tag-related} regressors) > no-speech yielded four significant clusters (see Table \ref{tab:cope1}):
-one left laterlized cluster spanning from the angular gyrus and inferior posterior supramarginal gyrus across the superior and middle temporal gyrus, including parts of Heschl's gyrus and planum temporale.
-A second left cluster in (inferior) frontal regions, including precentral gyrus, pars opercularis (Brodman Areal 44; BA44) and pars triangularis (BA45).
-Similarly in the right hemisphere, one cluster spanning from the angular gyrus across the superior and middle temporal gyrus but including frontal inferior regions (pars opercularis and pars triangularis).
+The contrast words (all 21 \texttt{tag-related} regressors) > no-speech yielded
+four significant clusters (see Table \ref{tab:cope1}):
+% cluster 1
+one left lateralized cluster spanning from the angular gyrus and inferior
+posterior supramarginal gyrus across the superior and middle temporal gyrus,
+including parts of Heschl's gyrus and planum temporale.
+% cluster 2
+A second left cluster in (inferior) frontal regions, including precentral gyrus,
+pars opercularis (Brodmann Areal 44; BA44) and pars triangularis (BA45).
+% cluster 3
+Similarly in the right hemisphere, one cluster spanning from the angular gyrus
+across the superior and middle temporal gyrus but including frontal inferior
+regions (pars opercularis and pars triangularis).
+% cluster 4
 A fourth significant cluster is located in the left thalamus.
@@
 % COPE 3
-The contrast proper nouns > coordinate conjunctions yielded 9 significant clusters (see Table \ref{tab:cope3}):
-one left laterlized cluster spanning from the angular gyrus across planum temporale and superior temporal gyrus, partially covering the Heschl's gyrus, into the anterior middle temporal gyrus.
+The contrast proper nouns > coordinate conjunctions yielded 9 significant
+clusters (see Table \ref{tab:cope3}):
+% cluster 1
+one left lateralized cluster spanning from the angular gyrus across planum
+temporale and superior temporal gyrus, partially covering the Heschl's gyrus,
+into the anterior middle temporal gyrus.
+% cluster 2
 A largely congruent but smaller cluster in the right hemisphere.
+% cluster 3 & 5, and 4 & 6
 Two clusters in posterior cingulate cortex and precuneus of both hemispheres.
-Three small clusters in the right occipital pole, right Heschl's gyrus and left superior lateral occipital pole.
+% remaining 3 clusters of COPE 3
+Three small clusters in the right occipital pole, right Heschl's gyrus and left
+superior lateral occipital pole.
 
 % COPE 5
-The contrast nouns > coordinate conjunctions yielded 3 significant clusters (see Table \ref{tab:cope5}):
+The contrast nouns > coordinate conjunctions yielded 4 significant clusters (see Table \ref{tab:cope5}):
+% cluster 1 & 2
 two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction.
 In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hermisphere into the anterior part of superior temporal cortex.
-Finally, two small right lateralized clusters in posterior cingulate gyrus and precuneus.
+% cluster 3 & 4
+Finally, two small right lateralized clusters in the right posterior cingulate
+gyrus and right precuneus.
 
-\todo{Figure zeigt whole brain statt “partial brain coverage”; vgl. Text; Problem? MIH: Could become an issue. In the data paper we showed the coverage. Maybe just ref the figure.}
+\todo{Figure zeigt whole brain statt “partial brain coverage”; vgl. Text; Problem? MIH: Could become an issue. In the data paper we showed the coverage. Maybe just ref the figure}
 \begin{figure*}

### 2020-05-25 paper/main.tex
to do: FOV in figure
reformatting & correcting typos of discussionto do

@@
 two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction.
-In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hermisphere into the anterior part of superior temporal cortex.
+In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hemisphere into the anterior part of superior temporal cortex.
 % cluster 3 & 4
@@
 
-\todo{Figure zeigt whole brain statt “partial brain coverage”; vgl. Text; Problem? MIH: Could become an issue. In the data paper we showed the coverage. Maybe just ref the figure}
+\todo{“partial brain coverage” / FoV.
+MIH: Could become an issue.
+In the data paper we showed the coverage.
+Maybe just ref the figure => gonna take a look how I can adjust the script to get a FoV mask from the data and use it during plotting; otherwise: ref to paper}
 \begin{figure*}
   \centering
-% \includegraphics[width=0.4\textwidth]{frog.jpg}
   \includegraphics[width=\linewidth]{figures/slicescolorbars}
@@
 
-\todo[inline]{Lass uns bzgl.
-der Discussion am besten unterhalten; im Grunde geht es darum, wie weit ich ins Detail gehen soll (kann nämlich viel zu sehr ins Detail gehen); im Grunde geht es imo nicht darum, alle Cluster inkl.
-Areale durchzudiskutieren, sondern zu kommunizieren, dass die Anno brauchbar ist; wie dem auch sei: Hier wird noch Inhalt nach dem Lesen der Reviews hinzukommen}
-% discussion
-% wilson2007beyond
-% planum temporale = Wernicke; ist witzigerweise nicht in contrast 1 (words > no speech), aber “stark” in nouns bzw. proper nouns > kon
-In the contrast words > no speech, we expectedly find increased hemodynamic activity in a bilateral cortical network including temporal, parietal and frontal regions realted to processing spoken language \citep{friederici2011brain, hickok2007cortical,price2012twentyyears}.\todo{abchecken}
-Our results are similar to results of studies that implemented an ISC approach to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not, lerner2011topographic, silbert2014coupled}.
-Contrary to previous studies, we do not find increased medial activation in the precuneus or medial frontal cortex.
-This could be attributed to the fact that our contrast does not [+++sufficiently+++]\todo{Which contrast captures ANY social aspects?} capture social aspects of the narrative \citep{ferstl2008extended, mar2011neural}\todo{abchecken}.
-The two contrasts contrasting nouns and proper nouns respectively to coordinate junctions lead to unexpected results\todo{That seems like an unfortunate statement.
-We make this analysis to show expected results to conclude that the annotation is good.
-But we get unexpected results and conclude...}.
-Increased activation is partially located in early sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most prominently adjacant regions bilaterally (planum temporale; superior temporal gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
-This could be attributed to the fact that a high count of heterogenous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) were averaged across all 300 semantic dimensions (cf.
-\citep{mitchell2008predicting, huth2016natural}), and contrasted to coordinate conjunctions that offered a comparably small amount of events (N=\rKonAll).
-Moreover, the coordinate junctions (\texttt{kon}) mostly comprises event of the words ``and'' (N=392) and ``but'' (N=49) and thus offered only a small amount of variance.
-A second explanation might be that our phoneme regressors that assumed linear summation of approximatly 70 ms lasting events in quick succession did not capture a sufficiently amount of nuissance variance\todo{Reviewer 2 will ask: If you knew all these issues, why did you do it then?}.
-Nevertheless and more importantly to access the validity of the dataset is the fact that two similar lingustic concepts (nouns and proper nouns) embedded in a naturalistic stimulus that was not designed for linguistic research lead to similar activation patterns\todo{That statement is only true, if both contrasts are not (solely) driven by the conjuctions.
-There is no evidence in the paper that this is not the case.}
-% Within the language processing systems, early sensory regions are specialized for representing the immediate physical properties of the environment (form), while higher order regions extract increasingly abstract content (Davis and Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).
+\todo[inline]{Lass uns bzgl. der Discussion am besten unterhalten; im Grunde
+geht es darum, wie weit ich ins Detail gehen soll (kann nämlich viel zu sehr ins
+Detail gehen); im Grunde geht es imo nicht darum, alle Cluster inkl. Areale
+durchzudiskutieren, sondern zu kommunizieren, dass die Anno brauchbar ist; wie
+dem auch sei: Hier wird noch Inhalt nach dem Lesen der Reviews hinzukommen}
+% words > no-speech
+In the contrast words > no-speech, we find increased hemodynamic activity in a
+bilateral cortical network including temporal, parietal and frontal regions
+related to processing spoken language \citep{friederici2011brain,
+hickok2007cortical,price2012twentyyears}.
+% similarities to previous naturalistic speech paradigms
+Our results are similar to results of studies that implemented an ISC approach
+to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
+lerner2011topographic, silbert2014coupled}.
+% dissimilarities
+Contrary to previous studies, we do not find increased medial activation in the
+precuneus or medial frontal cortex. This could be attributed to the fact that
+our contrast does not \todo{Which contrast captures ANY social aspects? => the
+COPEs in the references} capture social aspects of the narrative
+\citep{ferstl2008extended, mar2011neural}\todo{check it}.
+% (proper) nouns > con
+The two contrasts contrasting nouns and proper nouns respectively to coordinate
+junctions lead to unexpected results\todo{That seems like an unfortunate
+statement. We make this analysis to show expected results to conclude that the
+annotation is good. But we get unexpected results and conclude; the contrast is
+shit; cf. following explanation}.
+% cluster location
+Increased activation is partially located in early sensory regions (Heschl's
+Gyrus; \citep{saenz2014tonotopic}) and most prominently adjacent regions
+bilaterally (planum temporale; superior temporal gyrus;
+\citep{arsenault2015distributed, mesgarani2014phonetic}).
+% interpretation 1a: large amount of semantically different nouns > narrow
+% concept (conjunctions)
+This could be attributed to the fact that a high count of heterogeneous nouns
+(N=\rNnAll) and proper nouns (N=\rNeAll) were averaged across all 300 semantic
+dimensions (cf. \citep{mitchell2008predicting, huth2016natural}), and contrasted
+to coordinate conjunctions that offered a comparably small amount of events
+(N=\rKonAll).
+% interpretation 1b: not just narrow concept but also dominated by just two
+% different words
+Moreover, the coordinate junctions (\texttt{kon}) mostly comprises event of the
+words ``and'' (N=392) and ``but'' (N=49) and thus offered only a small amount of
+variance.
+% interpretation 2
+A second explanation might be that our phoneme regressors that assumed linear
+summation of approximately 70 ms lasting events in quick succession did not
+capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask: If
+you knew all these issues, why did you do it then? hindsight bias after
+exploratory analyses?!}.
+% but...
+Nevertheless and more importantly to access the validity of the dataset is the
+fact that two similar linguistic concepts (nouns and proper nouns) embedded in a
+naturalistic stimulus that was not designed for linguistic research lead to
+similar activation patterns\todo{That statement is only true, if both contrasts
+are not (solely) driven by the conjunctions. There is no evidence in the paper
+that this is not the case.}
+% Within the language processing systems, early sensory regions are specialized
+% for representing the immediate physical properties of the environment (form),
+% while higher order regions extract increasingly abstract content (Davis and
+% Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).
 

### 2020-05-25 paper/main.tex
updated text of to dos (instead of just deleting them)

@@
 function from onset to offset of the corresponding word\todo{I do not know what
-this means; hope it got clearer now}.
+this mean; CH: hope it got clearer now}.
 % phonemes
@@
 function from onset to offset of the corresponding phoneme.\todo{Does that mean
-they share events with "other"}.
+they share events with "other"; CH: dunno what you mean, but text should be
+clearer now}.
 % sentence (endings)
@@
 it says 'we tested if similar linguistic concepts providing high semantic
-information (proper nouns and nouns)'. What does this need sentences for?}.
+information (proper nouns and nouns)'. What does this need sentences for? CH:
+it is kinda nuisance regressor}.
 % no-speech intro
@@
 intervals without audible speech \todo{Why assumed? Isn't the point of the
-annotation to "know"? => Words where chosen to carefully; intervals don't
-contain any audible speech with 98 perc. certainty}
+annotation to "know"? CH: words where chosen to carefully; intervals don't
+contain any audible speech with >98 perc. certainty}
 % minimum distance to words
@@
 Lastly, we used events\todo{They are not really events, but a continuous
-nuisance regressor; okay, how do you phrase that correctly?} reflecting
+nuisance regressor; CH: okay, how do you phrase that correctly?} reflecting
 low-level auditory features (left-right difference in volume and root mean
@@
 
-\todo{“partial brain coverage” / FoV.
-MIH: Could become an issue.
-In the data paper we showed the coverage.
-Maybe just ref the figure => gonna take a look how I can adjust the script to get a FoV mask from the data and use it during plotting; otherwise: ref to paper}
+\todo{“partial brain coverage” / FoV. MIH: Could become an issue. In the data
+paper we showed the coverage. Maybe just ref the figure. CH: gonna take a look how I can adjust the script to get a FoV mask from the data and use it during plotting; otherwise: ref to paper}
 \begin{figure*}
@@
 precuneus or medial frontal cortex. This could be attributed to the fact that
-our contrast does not \todo{Which contrast captures ANY social aspects? => the
+our contrast does not \todo{Which contrast captures ANY social aspects? CH: the
 COPEs in the references} capture social aspects of the narrative
@@
 statement. We make this analysis to show expected results to conclude that the
-annotation is good. But we get unexpected results and conclude; the contrast is
-shit; cf. following explanation}.
+annotation is good. But we get unexpected results and conclude; CH: the contrast
+turned out to yield the result; cf. following explanation; I don't feel
+comfortable of HARKing}.
 % cluster location
@@
 capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask: If
-you knew all these issues, why did you do it then? hindsight bias after
+you knew all these issues, why did you do it then? hindsight bias/HARKing after
 exploratory analyses?!}.
@@
 
-\section*{Conclusions}
-\todo[inline]{the paper needs to serve a purpose.
-One is, of course, to be documentation for the annotation.
-Another is to attract people to use this work for their own studies.
-I would even argue that this is the \textit{main} purpose, given that the annotation in itself represents to scientific progress.
-The need to give an accurate assessment what this can be used for and what is problematic or impossible.
-ATM this is the only statement in this regard:
-'facilitates modeling of hemodynamic brain responses correlating with speech-related events' and the only indication of purpose is 'additional confound measures'.
-I think this is incongruent with the amount of work and the level of detail of
-this annotation; öööööhh, okay. Mir sind da jetzt über 2 Tage wenig Superlative eingefallen, die über den bisherigen Text hinausgehen; fehlt mir wohl die geeignete Perspektive}
-% state what you think are the main conclusions that can be realistically drawn from the findings in the paper, taking care not to make claims that cannot be supported.
-As an extension of the studoforrest dataset, we present an annotation of spoken language in the two hours lasting ``research cut'' of the audio-visual movie ``Forrest Gump'' and its temporally aligned audio-description.
-We annotated the onset and offset of sentences, words and phonemes, and the corresponding speaker's identity.
-An additional tagging of each word's linguistic features and the public nature of the dataset enable independent working groups to create sophisticated models of hemodynamic activity correlating with speech-related events in a naturalistic stimulus.
-Results of our dataset validating analysis that we run as a proof of concept show that the annotation's content can indeed / in principle be used to isolate/track speech-related networks in the human brain under life-like conditions.
+\section*{Conclusions} \todo[inline]{the paper needs to serve a purpose.  One
+is, of course, to be documentation for the annotation.  Another is to attract
+people to use this work for their own studies.  I would even argue that this is
+the \textit{main} purpose, given that the annotation in itself represents to
+scientific progress.  The need to give an accurate assessment what this can be
+used for and what is problematic or impossible.  ATM this is the only statement
+in this regard: 'facilitates modeling of hemodynamic brain responses correlating
+with speech-related events' and the only indication of purpose is 'additional
+confound measures'.  I think this is incongruent with the amount of work and the
+level of detail of this annotation; CH: let's discuss that personally}
+% state what you think are the main conclusions that can be realistically drawn
+% from the findings in the paper, taking care not to make claims that cannot be
+% supported.  intro
+As an extension of the studyforrest dataset, we present an annotation of spoken
+language in the two hours lasting ``research cut'' of the audio-visual movie
+``Forrest Gump'' and its temporally aligned audio-description.
+% what we did
+We annotated the onset and offset of sentences, words and phonemes, and the
+corresponding speaker's identity.
+% what for
+An additional tagging of each word's linguistic features and the public nature
+of the dataset enable independent working groups to create sophisticated models
+of hemodynamic activity correlating with speech-related events in a naturalistic
+stimulus.
+% results
+Results of our dataset validating analysis that we run as a proof of concept
+show that the annotation's content can indeed / in principle be used to
+isolate/track speech-related networks in the human brain under life-like
+conditions.
 
@@
 \subsection*{Grant information}
-
 COH was supported by a graduate stipend from the German federal state of
@@
 \subsection*{Acknowledgements}
-We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated doing the annotation of the descriptive nouns\todo{should it still be here?
-or move in PPA paper?}, and performed the preliminary annotation of nouns.
-Christian O.
-Häusler is also grateful to Valeri Kippes who took care of the author's mental sanity by providing excellent training at his gym in Jülich during the mentally draining period of manual corrections of the annotation.
+COH is grateful to Valeri Kippes who took care of the author's mental sanity by providing excellent training at his gym in Jülich during the mentally draining period of manual corrections of the annotation.
 

### 2020-06-02 paper/main.tex
correct typo
introduction: data- vs. model driven, why worth being published, why bother

@@
 
+\todo[inline]{revised: data-driven vs./in combination (with) model-driven}
 % data-driven methods
@@
 (ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
-corresponding fMRI data. However, data-driven methods alone fall short of
-pinpointing their results to specific, time-locked features of a stimulus
+corresponding fMRI data. However, data-driven methods alone fall usually short
+of pinpointing their results to specific, time-locked features of a stimulus
 \citep{kauttonen2015optimizing}.
@@
 \citep{rocca2019language}.
+% combination of data-driven and model-driven approaches
+Additionally, stimulus annotations can inform data-driven methods about a
+stimulus' temporal dynamics, or model-driven and data-driven methods can be
+combined to improve interpretability of results \citep{lahnakoski2012stimulus}.
 
-% We:
+\todo[inline]{revised: why this anno is better than any previous anno and worth
+being published as a paper}
+% we:
 For this publication, we revised previous, preliminary annotations done by our
@@
 \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
-% why
-This publication enables researchers to model time-locked hemodynamic brain
-responses that correlate with different aspects of spoken occurring in a 2-hour
-lasting naturalistic stimulus.
+% why even bother?
+This publication enables researchers to model hemodynamic brain responses that
+correlate with a variety of time-locked aspects of spoken language ranging from
+a speaker's identity, to phonology, grammar, and semantics.
 % extending previous non-speech annotations
@@
 measures describing key properties of major building blocks of the stimulus.
-
-\todo[inline]{Das “why one should model” ist jetzt drin; Frage an dich als
-Datenanalyse-Pro: Man kann doch bestimmt auch data-driven methods irgendwie
-“constrainen”, und die durch eine Annotation verbessern? Hast du da eine
-Formulierung und/oder auch ein (high-level) Paper für mich zu dem Thema?}
 
@@
 % dropping of subject 10
-Data of one participant was dropped to due to invalid distortion correction
+Data of one participant were dropped to due to invalid distortion correction
 during scanning.

### 2020-06-02 paper/main.tex
revision of a couplele of to dos

@@
 The end of each complete grammatical sentence was modeled as an impulse event
-(N=\rSentenceAll) to capture variance of sentence comprehension\todo{Why? Above
-it says 'we tested if similar linguistic concepts providing high semantic
-information (proper nouns and nouns)'. What does this need sentences for? CH:
-it is kinda nuisance regressor}.
+(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
+\todo{Why? Above it says 'we tested if similar linguistic concepts providing
+    high semantic information (proper nouns and nouns)'. What does this need
+sentences for? CH: it is kinda nuisance regressor}
 % no-speech intro
@@
 
-\section*{Conclusions} \todo[inline]{the paper needs to serve a purpose.  One
-is, of course, to be documentation for the annotation.  Another is to attract
-people to use this work for their own studies.  I would even argue that this is
-the \textit{main} purpose, given that the annotation in itself represents to
-scientific progress.  The need to give an accurate assessment what this can be
-used for and what is problematic or impossible.  ATM this is the only statement
-in this regard: 'facilitates modeling of hemodynamic brain responses correlating
-with speech-related events' and the only indication of purpose is 'additional
-confound measures'.  I think this is incongruent with the amount of work and the
-level of detail of this annotation; CH: let's discuss that personally}
-% state what you think are the main conclusions that can be realistically drawn
-% from the findings in the paper, taking care not to make claims that cannot be
-% supported.  intro
+\todo[inline]{the paper needs to serve a purpose:
+    a) documentation for the annotation.
+    b) attract people to use this work for their own studies.
+    I would even argue that this is the \textit{main} purpose, given that the
+    annotation in itself represents to scientific progress. The need to give an
+    accurate assessment what this can be used for and what is problematic or
+    impossible.  ATM this is the only statement in this regard: 'facilitates
+    modeling of hemodynamic brain responses correlating with speech-related
+events' and the only indication of purpose is 'additional confound measures'. I
+thin this is incongruent with the amount of work and the level of detail of
+this annotation; CH: let's discuss that personally}
+
+\section*{Conclusions} % what the paper is about
 As an extension of the studyforrest dataset, we present an annotation of spoken

### 2020-06-03 code/plot-zmaps.py
plot-zmaps.py uses FoV brain mask

@@ -15,6 +15,9 @@ import os
 # anatImg = '/usr/share/fsl/5.0/data/standard/MNI152_T1_1mm.nii.gz'
 anatImg = '/usr/share/data/fsl-mni152-templates/MNI152_T1_0.5mm.nii.gz'
 
+# T2* EPI group template
+audioMask = 'code/grbold7Tad_brain_inMNI_12dof.nii.gz'
+
 # list of primary contrasts
 # words > no-speech (bottom), Ne > kon (middle), Nn > kon (top image)
 primCopes = ['cope1_z3.4.gfeat/cope1.feat/thresh_zstat1.nii.gz',
@@ -63,7 +66,9 @@ def process_group_averages(outfpath, imageList=
     topImg = imageList[2]
     print('creating plot for 3rd lvl group analysis')
 
-    fig, ((ax1, ax2), (ax3, ax4)) = plt.subplots(nrows=2, ncols=2, figsize=(15,15))
+    fig, ((ax1, ax2), (ax3, ax4)) = plt.subplots(nrows=2,
+                                                 ncols=2,
+                                                 figsize=(15, 15))
     plt.subplots_adjust(wspace=0, hspace=0)
 
     # plot axial / horizontal plane
@@ -102,7 +107,7 @@ def process_group_averages(outfpath, imageList=
 
     # manually, add a legend in bottom, right plot (right sagittal plane
     blue = mpl.patches.Patch(color='blue',
-                             label='tags > no-speech')
+                             label='words > no-speech')
     red = mpl.patches.Patch(color='red',
                             label='proper nouns > coord. conjunctions',)
     green = mpl.patches.Patch(color='green',
@@ -128,7 +133,6 @@ def process_group_averages(outfpath, imageList=
                 pad_inches=0,
                 facecolor=fig.get_facecolor())
 
-
     plt.close()
 
 
@@ -137,13 +141,25 @@ def plot_grp_slice(mode, coord,
                    title=None, anno=True):
     '''
     '''
+    # underlying MNI152 T1 0.5mm image
+    colorMap = plt.cm.get_cmap('copper')
     display = plotting.plot_anat(anat_img=anatImg,
                                  title=title,
                                  axes=axis,
                                  annotate=anno,
                                  display_mode=mode,
+                                 cmap=colorMap,
                                  draw_cross=False,
                                  cut_coords=coord)
+
+    # brain mask 'grbold7Tad' in MNI space aligned with 12dof
[…]

### 2020-06-03 paper/main.tex
adjust caption of group results figure

@@
 
-\todo{“partial brain coverage” / FoV. MIH: Could become an issue. In the data
-paper we showed the coverage. Maybe just ref the figure. CH: gonna take a look how I can adjust the script to get a FoV mask from the data and use it during plotting; otherwise: ref to paper}
-\begin{figure*}
-  \centering
+\todo{manually edit/merge slices.svg and colorbars.svg for final slicescolorbars}
+
+\begin{figure*} \centering
     \includegraphics[width=\linewidth]{figures/slicescolorbars}
-  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05 cluster-corrected; MNI template space)}.
-\label{fig:results}
-\end{figure*}
+    \caption{Mixed-effects group-level (N=14) GLM contrasts for the
+        audio-description of the movie Forrest Gump. Significant clusters
+        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the custom T2* EPI
+        group template (gray; taken from \citep{hanke2014audiomovie}) which is
+    aligned to and overlaid on the MNI152 T1-weighted head template (copper).}
+    \label{fig:results} \end{figure*}
 

### 2020-06-04 paper/main.tex
overall revision to improve flow of reading

@@
 corresponding fMRI data. However, data-driven methods alone fall usually short
-of pinpointing their results to specific, time-locked features of a stimulus
-\citep{kauttonen2015optimizing}.
+of pinpointing their results to specific, time-locked stimulus features \citep{kauttonen2015optimizing}.
 % model-driven methods
@@
 For this publication, we revised previous, preliminary annotations done by our
-lab and now provide one single annotation with exact onsets/offsets and content
-of each sentences, word and phonemes (see Table \ref{tab:overview} for an
-overview) spoken in the audio-visual movie ``Forrest Gump''
-\citep{ForrestGumpMovie} and its audio-description (i.e. an audio-only variant
-of the movie)\citep{ForrestGumpDVD}.
+lab and now provide one single annotation with exact onset and offset of each
+sentence, word and phoneme (see Table \ref{tab:overview} for an overview) spoken
+in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
+audio-description (i.e. the audio-only variant of the
+movie)\citep{ForrestGumpGermanAD}.
 % the studyforrest dataset
@@
 This publication enables researchers to model hemodynamic brain responses that
-correlate with a variety of time-locked aspects of spoken language ranging from
-a speaker's identity, to phonology, grammar, and semantics.
+correlate with a variety of aspects of spoken language ranging from a speaker's
+identity, to phonology, grammar, and semantics.
 % extending previous non-speech annotations
@@
 % preliminary annotations
-Preliminary, manual orthographic transcriptions of dialogues, non-speech
+Preliminary, manual orthographic transcriptions of dialogs, non-speech
 vocalizations (e.g. laughter or groaning) and script for the audio-description's
-narrator were merged, and converted to Praat's \citep{boersma2019praat} TextGrid
+narrator were merged and converted to Praat's \citep{boersma2019praat} TextGrid
 format.
@@
 % intro for forced aligner
-We used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
-algorithmically identify the exact onset of offset of the sentences, and the
-onset and offset of each word and phoneme embedded in the transcribed sentences.
+We then used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
+algorithmically identify the exact onset of offset of each sentence, and the
+onset and offset of each word and phoneme.
 % preparing other inputs before forced alignment pronunciation dictionary
@@
 
-% natural language processing (NLP)
-% spaCy
-To automatically analyze linguistic features of each words in their
-corresponding sentence, we employed the Python package spaCy \citep{spacy2} and
-its accompanying German language model (\texttt{de\_core\_news\_md} that was
-trained on the TIGER Treebank corpus \citep{brants2004tiger}.
+% natural language processing (NLP) spaCy
+To automatically analyze linguistic features of each word in their corresponding
+sentence, we employed the Python package spaCy \citep{spacy2} and its
+accompanying German language model (\texttt{de\_core\_news\_md} that was trained
+on the TIGER Treebank corpus \citep{brants2004tiger}.
 % Tiger Treebank Corpus:
-% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
-% dropping of non-speech vocalizations because they often delude the algo
+% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.  dropping of
+% non-speech vocalizations because they often delude the algo
 Non-speech vocalizations were dropped from the sentences before analysis to
@@
 % performed analyses
-We performed analyses regarding part-of-speech (i.e. grammatical tagging or
+We then performed analyses regarding part-of-speech (i.e. grammatical tagging or
 word-category disambiguation), syntactic dependencies, lemmatization, word
-embedding (i.e. multi-dimensional meaning representation of a word), and if the
-word is one of the most common words of the German language (i.e. if the word is
-part of a stop list).
+embedding (i.e. a multi-dimensional meaning representation of a word), and if
+the word is one of the most common words of the German language (i.e. if the
+word is part of a stop list).
 
@@
 \subsubsection*{Simple part-of-speech tag (\texttt{pos})} A simple
-part-of-speech tagging (grammatical tagging; word-category disambiguation) of a
-word.
+part-of-speech tagging (grammatical tagging; word-category disambiguation) of
+words.
 % annotation scheme
-The simple part-of-speech tagging tags follow the Universal Dependencies v2 POS
-tag set (\href{https://universaldependencies.org}{universaldependencies.org}).
+The tag labels of this simple part-of-speech tagging follow the Universal
+Dependencies v2 POS tag set
+(\href{https://universaldependencies.org}{universaldependencies.org}).
 % reference to table
 See Table \ref{tab:pos} for a description of the labels and the respective
-counts of all 15 labels. Nouns that spaCy mistook for proper nouns or vice
-versa were corrected via script.
+counts of all 15 labels. Nouns that spaCy mistook for proper nouns or vice versa
+were corrected via script.
 % s. list at the beginning of script code/add_part-of-speech-tagging2textgrid.py
@@
 % \href{https://www.ims.uni-stuttgart.de/forschung/ressourcen/lexika/germantagsets}{Stuttgart-Tübingen-Tagset}
-A detailed part-of-speech tagging of a word following the TIGER Treebank
+A detailed part-of-speech tagging of words following the TIGER Treebank
 annotation scheme \citep{brants2004tiger} which is based on the
@@
 See Table \ref{tab:tag} for a descripion  of the labels and the respective
-counts of the 15 most often occuring labels. Nouns that spaCy mistook for proper
-nouns or vice versa were corrected via script.
+counts of the 15 most often occuring labels (overall 43 labels). Nouns that
+spaCy mistook for proper nouns or vice versa were corrected via script.
 % s. list at the beginning of script code/add_part-of-speech-tagging2textgrid.py
@@
 type of syntactic relation that connects a "child" (the single word) to its
-"head".
+``head''.
 
@@
 % \href{https://en.wikipedia.org/wiki/Word2vec}{word vector}
-A 300-dimensional word vector providing a multi-dimensional meaning representation of a word.
-Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes were set to \texttt{\#} to save space.
+A 300-dimensional word vector providing a multi-dimensional meaning
+representation of a word.
+% handling of words unknown to the model
+Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes
+were set to \texttt{\#} to save space.
 
 \subsection*{Dataset content}
-% \href{https://bids.neuroimaging.io/}{bids.neuroimaging.io}
-The released annotation comes in two different versions.
-First, as a text-based TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be conveniently edited with the software Praat \citep{boersma2019praat}.
-Second, as a text-based, tab-separated-value (TSV) formatted table  (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS} \citep{gorgolewski2016bids}).
-The source code for all descriptive statistics included in this paper is available in \texttt{code/descriptive-statistics.py} (Python script).
+% \href{https://bids.neuroimaging.io/}{bids.neuroimaging.io} TextGrid format
+The annotation comes in two different versions. First, as a text-based TextGrid
+file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be
+conveniently edited with the software Praat \citep{boersma2019praat}.
+% TSV format
+Second, as a text-based, tab-separated-value (TSV) formatted table
+(\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with
+the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}
+\citep{gorgolewski2016bids}).
+% source code for descriptive statistics
+The source code for all descriptive statistics included in this paper is
+available in \texttt{code/descriptive-statistics.py} (Python script).
 
@@
 % sources of variability. ~170 words => das wird beim folgenden Schreiben
-% definitiv nichts werden intro
+% definitiv nichts werden
+% intro
 In order to assess data quality, we investigated if contrasting speech-related
@@
 \begin{table*}[t]
-    \caption{Overview of the events that were used to create the 26 regressors of the GLM analysis.
+    \caption{Overview of events that were used to create the 26 regressors of the GLM analysis.
 The respective counts are given for the whole stimulus and the eight segments
@@
 from onset to offset of each word \todo{This has errors that I do not know how
-to fix; sorry, unclear what you mean by that}.
+to fix; COH: sorry, unclear what you mean by that}.
 % path-of-speech labels: remaining labels
@@
 % phonemes
-The top 80 phonemes (\texttt{n} with N=6053 to \texttt{IY1} with N=32) were
-pooled to \texttt{phonemes} (N=\rPhonesAll) and each event modeled as boxcar
-function from onset to offset of the corresponding phoneme.\todo{Does that mean
-    they share events with "other"; CH: dunno what you mean, but text should be
-clearer now}.
+The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
+with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and each event
+modeled as boxcar function from onset to offset of the corresponding
+phoneme.\todo{Does that mean they share events with "other"; CH: dunno what you
+mean, but text should be clearer now}.
 % sentence (endings)
@@
 % length of no-speech events
-A length of \unit[70]{ms} was chosen for no-speech events matching the average
-length of phonemes.
+A length of \unit[70]{ms} was chosen for no-speech events matching the
+average length of phonemes.
 % low-level nuisance regressors
-Lastly, we used events\todo{They are not really events, but a continuous
-nuisance regressor; CH: okay, how do you phrase that correctly?} reflecting
-low-level auditory features (left-right difference in volume and root mean
-squared volume) averaged across the length of every movie frame (\unit[40]{ms}).
-All events were convolved with FSL's ``Double-Gamma HRF'' as a model of the
-hemodynamic response function to create the actual regressors.
+Lastly, we used continuous information about auditory features (left-right
+difference in volume and root mean squared volume) that was averaged across the
+length of every movie frame (\unit[40]{ms}) to capture variance correlating with
+low-level perceptual processes.
+% convolving
+Time series of events were convolved with FSL's ``Double-Gamma HRF'' as a model
+of the hemodynamic response function to create the actual regressors.
 % reference to figure ``correlation of regressors''
@@
 % temporal derivatives
-Temporal derivatives were also included in the design matrix and the design was
-subjected to the same temporal filtering as the BOLD time series.
-% motion parameters
-Finally, six motion parameters were used as additional nuisance regressors.
+Temporal derivatives were also included in the design matrix to compensate for
+regional differences between modeled and actual HRF.
+% motion parameters & temporal filtering of design
+% motion parameter are filtered, too. See FSL manual:
+% ``All (confound) EVs will be filtered to match the processing applied to the
+% input data''
+Finally, six motion parameters were used as additional nuisance regressors and
+the design was subjected to the same temporal filtering as the BOLD time
+series.
 
@@
 The third level analysis which averaged contrast estimates across subjects was
-carried out using FLAME stage 1 with automatic outlier de-weighting
+carried out using FLAME stage 1 with automatic outlier deweighting
 \citep{woolrich2004multilevel, woolrich2008robust}.
@@
 % COPE 1:
-The contrast words (all 21 \texttt{tag-related} regressors) > no-speech yielded
-four significant clusters (see Table \ref{tab:cope1}):
+The contrast words > no-speech yielded four significant clusters (see Table
+\ref{tab:cope1}):
 % cluster 1
@@
 % COPE 3
-The contrast proper nouns > coordinate conjunctions yielded 9 significant
+The contrast proper nouns > coordinate conjunctions yielded nine significant
 clusters (see Table \ref{tab:cope3}):
@@
 % COPE 5
-The contrast nouns > coordinate conjunctions yielded 4 significant clusters (see Table \ref{tab:cope5}):
+The contrast nouns > coordinate conjunctions yielded four significant clusters (see Table \ref{tab:cope5}):
 % cluster 1 & 2
 two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction.
+% variation in cluster 1 & 2 in comparison to COPE 1
 In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hemisphere into the anterior part of superior temporal cortex.
@@
 dem auch sei: Hier wird noch Inhalt nach dem Lesen der Reviews hinzukommen}
-% words > no-speech
-In the contrast words > no-speech, we find increased hemodynamic activity in a
+
+% Discussion words > no-speech
+For the contrast words > no-speech, we find increased hemodynamic activity in a
 bilateral cortical network including temporal, parietal and frontal regions
@@
 % dissimilarities
-Contrary to previous studies, we do not find increased medial activation in the
-precuneus or medial frontal cortex. This could be attributed to the fact that
-our contrast does not \todo{Which contrast captures ANY social aspects? CH: the
-COPEs in the references} capture social aspects of the narrative
-\citep{ferstl2008extended, mar2011neural}\todo{check it}.
+\todo{Which contrast captures ANY social aspects? CH: the COPEs in the
+references} Contrary to previous studies \citep{ferstl2008extended,
+mar2011neural}, we do not find increased medial activation in the precuneus or
+medial frontal cortex. This could be attributed to the fact that the contrast
+here was not designed to capture social aspects of the narrative.\todo{check the
+previous studies}.
 % (proper) nouns > con
 The two contrasts contrasting nouns and proper nouns respectively to coordinate
-junctions lead to unexpected results\todo{That seems like an unfortunate
-statement. We make this analysis to show expected results to conclude that the
-annotation is good. But we get unexpected results and conclude; CH: the contrast
-turned out to yield the result; cf. following explanation; I don't feel
-comfortable of HARKing}.
-% cluster location
-Increased activation is partially located in early sensory regions (Heschl's
-Gyrus; \citep{saenz2014tonotopic}) and most prominently adjacent regions
-bilaterally (planum temporale; superior temporal gyrus;
-\citep{arsenault2015distributed, mesgarani2014phonetic}).
+junctions yielded increased activation that is partially located in early
+sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
+prominently adjacent regions bilaterally (planum temporale; superior temporal
+gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
 % interpretation 1a: large amount of semantically different nouns > narrow
 % concept (conjunctions)
-This could be attributed to the fact that a high count of heterogeneous nouns
-(N=\rNnAll) and proper nouns (N=\rNeAll) were averaged across all 300 semantic
-dimensions (cf. \citep{mitchell2008predicting, huth2016natural}), and contrasted
-to coordinate conjunctions that offered a comparably small amount of events
-(N=\rKonAll).
+This could be attributed to the exploratory nature of our analysis. A high count
+of heterogeneous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) that were
+averaged across all 300 semantic dimensions (cf. \citep{mitchell2008predicting,
+huth2016natural}), and contrasted to coordinate conjunctions that offered a
+comparably small amount of events (N=\rKonAll).
 % interpretation 1b: not just narrow concept but also dominated by just two
 % different words
-Moreover, the coordinate junctions (\texttt{kon}) mostly comprises event of the
-words ``and'' (N=392) and ``but'' (N=49) and thus offered only a small amount of
-variance.
+Coordinate junctions were chosen because they were assumed to be temporally
+uncorrelated with nouns but mostly consist of the words ``and'' (N=392) and
+``but'' (N=49), and thus offered only a small amount of variance.
 % interpretation 2
 A second explanation might be that our phoneme regressors that assumed linear
-summation of approximately 70 ms lasting events in quick succession did not
-capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask: If
-you knew all these issues, why did you do it then? hindsight bias/HARKing after
-exploratory analyses?!}.
+summation of approximately \unit[70]{ms} lasting events in quick succession did
+not capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask:
+    If you knew all these issues, why did you do it then? hindsight bias/HARKing
+after exploratory analyses?!}.
 % but...
-Nevertheless and more importantly to access the validity of the dataset is the
-fact that two similar linguistic concepts (nouns and proper nouns) embedded in a
-naturalistic stimulus that was not designed for linguistic research lead to
-similar activation patterns\todo{That statement is only true, if both contrasts
-are not (solely) driven by the conjunctions. There is no evidence in the paper
-that this is not the case.}
+Nevertheless and more importantly to exploratorily access the validity of the
+dataset is the fact that two similar linguistic concepts (nouns and proper
+nouns) embedded in a naturalistic stimulus that was not designed for linguistic
+research lead to similar activation patterns\todo{That statement is only true,
+if both contrasts are not (solely) driven by the conjunctions. There is no
+evidence in the paper that this is not the case.}
 % Within the language processing systems, early sensory regions are specialized

### 2020-06-08 paper/main.tex
More TODO
delete to dos that are essentially comments

@@
 
-\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht; Werte würde ich eher runden }
+\todo{Wort zur Validierungsstudie; awesomeness (s. Aliko (2020); Es sind erst
+110 von max 300 Worten verbraucht; Werte runden statt newcommand benutzen}
 \thispagestyle{fancy}
@@
 
-\todo[inline]{revised: data-driven vs./in combination (with) model-driven}
 % data-driven methods
@@
 
-\todo[inline]{revised: why this anno is better than any previous anno and worth
-being published as a paper}
 % we:
@@
 % why even bother?
+\todo[inline]{importance/bottleneck of (missing) annotations -> Aliko (2020)}
 This publication enables researchers to model hemodynamic brain responses that
@@
 
-\subsection*{Data Legend} \todo[inline]{Minimale Info hier, dass es zwei
-Versionen gibt und sich der folgende Abschnitt auf TSV file bezieht}
+\subsection*{Data Legend}
 % TextGrid vs. TSV
@@
 N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
-from onset to offset of each word \todo{This has errors that I do not know how
-to fix; COH: sorry, unclear what you mean by that}.
+from onset to offset of each word.
 % path-of-speech labels: remaining labels
@@
 (\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
-function from onset to offset of the corresponding word\todo{I do not know what
-this mean; CH: hope it got clearer now}.
+function from onset to offset of the corresponding word.
 % phonemes
@@
 modeled as boxcar function from onset to offset of the corresponding
-phoneme.\todo{Does that mean they share events with "other"; CH: dunno what you
-mean, but text should be clearer now}.
+phoneme.
 % sentence (endings)
@@
 (N=\rSentenceAll) to capture variance correlating with sentence comprehension.
-\todo{Why? Above it says 'we tested if similar linguistic concepts providing
-    high semantic information (proper nouns and nouns)'. What does this need
-sentences for? CH: it is kinda nuisance regressor}
 % no-speech intro
@@
 longer lasting intervals between onsets and offsets of words and thus within
-intervals without audible speech \todo{Why assumed? Isn't the point of the
-annotation to "know"? CH: words where chosen to carefully; intervals don't
-contain any audible speech with >98 perc. certainty}
+intervals without audible speech.
 % minimum distance to words
@@
 
-\todo[inline]{Lass uns bzgl. der Discussion am besten unterhalten; im Grunde
-geht es darum, wie weit ich ins Detail gehen soll (kann nämlich viel zu sehr ins
-Detail gehen); im Grunde geht es imo nicht darum, alle Cluster inkl. Areale
-durchzudiskutieren, sondern zu kommunizieren, dass die Anno brauchbar ist; wie
-dem auch sei: Hier wird noch Inhalt nach dem Lesen der Reviews hinzukommen}
-
-% Discussion words > no-speech
+% Discussion
+% words > no-speech
 For the contrast words > no-speech, we find increased hemodynamic activity in a
@@
 to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
-lerner2011topographic, silbert2014coupled}.
+lerner2011topographic, silbert2014coupled, wilson2007beyond}.
 % dissimilarities
@@
 medial frontal cortex. This could be attributed to the fact that the contrast
-here was not designed to capture social aspects of the narrative.\todo{check the
-previous studies}.
+here was not designed to capture social aspects of the
+narrative.\todo{wilson2007beyond: ISC medial ja, aber decreased activation
+    compared to rest; current study in reverse contrast: posterior cingulate and
+anterior cingulate (and insula bilaterally)}.
 % (proper) nouns > con

### 2020-06-18 code/plot-zmaps.py
plot-zmaps produces now slicescolorbars.svg

@@ -66,13 +66,18 @@ def process_group_averages(outfpath, imageList=
     topImg = imageList[2]
     print('creating plot for 3rd lvl group analysis')
 
-    fig, ((ax1, ax2), (ax3, ax4)) = plt.subplots(nrows=2,
-                                                 ncols=2,
-                                                 figsize=(15, 15))
+    fsize = (15, 15)
+    fig = plt.figure(figsize=fsize, constrained_layout=False)
+
+    # adjust space between subplots
     plt.subplots_adjust(wspace=0, hspace=0)
 
+    # add the grid
+    grid = fig.add_gridspec(28, 6)
+
+
     # plot axial / horizontal plane
-    axis = ax1
+    axis = fig.add_subplot(grid[0:12, 0:3])
     mode = 'z'  # axial/horizontal slice
     coord = [9]
     plot_grp_slice(mode, coord,
@@ -80,7 +85,7 @@ def process_group_averages(outfpath, imageList=
                    title='Z>3.4, p<0.05', axis=axis)
 
     # plot coronal plane
-    axis = ax2
+    axis = fig.add_subplot(grid[0:12, 3:])
     mode = 'y'
     coord = [-18]
     plot_grp_slice(mode, coord,
@@ -88,7 +93,7 @@ def process_group_averages(outfpath, imageList=
                    axis=axis)
 
     # plot left sagittal plane
-    axis = ax3
+    axis = fig.add_subplot(grid[12:24, 0:3])
     mode = 'x'
     coord = [-55]
     plot_grp_slice(mode, coord,
@@ -98,12 +103,25 @@ def process_group_averages(outfpath, imageList=
     plt.gca().invert_xaxis()
 
     # plot right sagittal plane
-    axis = ax4
+    axis = fig.add_subplot(grid[12:24, 3:])
     mode = 'x'
     coord = [55]
     plot_grp_slice(mode, coord,
                    bottomImg, middleImg, topImg,
                    axis=axis)
+
+    # text for z threshold and significance level
+    plt.text(-330, 285,
+             'Z>3.4, p<0.05',  # title=subject
+             size=16,
+             color='white',
+             backgroundcolor='black',
+             # set boxcolor and its edge to white and make transparent
+             bbox=dict(facecolor=(1, 1, 1, 0), edgecolor=(1, 1, 1, 0)))
+
+    # add the legend
+    # plotting of the legend
+    legendAxis = fig.add_subplot(grid[24:, :3])
 
     # manually, add a legend in bottom, right plot (right sagittal plane
[…]

### 2020-06-25 paper/main.tex
some smoothing of conclusions

@@
 embeddings representing each word in a 300-dimensional semantic space.
-This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
+This annotation facilitates further studies on the cognitive neuroscience of language under conditions of real-life complexity using the \textit{studyforrest} dataset.
 \end{abstract}
@@
 correlate with a variety of aspects of spoken language ranging from a speaker's
-identity, to phonology, grammar, and semantics.
+identity, to phonology, grammar, syntacs, and semantics.
 % extending previous non-speech annotations
@@
 \texttt{fg\_ad\_lrdiff} (left-right volume difference) and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
+\todo{where from, or how created?}
 Events were convolved with FSL's ``Double-Gamma HRF'' to create the regressors.
@@
 
-\section*{Conclusions} % what the paper is about
+\section*{Conclusions}
+% what the paper is about
 As an extension of the studyforrest dataset, we present an annotation of spoken
@@
 % what for
-An additional tagging of each word's linguistic features and the public nature
-of the dataset enable independent working groups to create sophisticated models
-of hemodynamic activity correlating with speech-related events in a naturalistic
-stimulus.
+An additional tagging of each word's linguistic features enable independent
+working groups to create sophisticated models of hemodynamic activity
+correlating with linguistics aspects like phonology, grammar, syntax, and
+semantics occurring in two naturalistic stimuli.
 % results

### 2020-06-25 paper/main.tex
add Aliko (2020) and Eickhoff (2020) to Introduction

@@
 % maximal 8
-annnotation, language, speech, lateralization, narrative, natural stimulation, fMRI, studyforrest
+annotation, language, speech, lateralization, narrative, natural stimulation, fMRI, studyforrest
 
@@
 
-\section*{Introduction}
-Cognitive neuroimaging research is moving towards studying brain behavior
-under conditions of real-life-like complexity.
-Motion pictures \citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not, lerner2011topographic} are increasingly utilized as so called ``naturalistic stimuli''.
+\section*{Introduction} Cognitive and psychiatric neuroimaging are moving
+towards studying brain functions under conditions of real-life-like complexity
+\citep{sonkusare2019naturalistic, eickhoff2020towards}. Motion pictures
+\citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not,
+lerner2011topographic} are increasingly utilized as so called ``naturalistic
+stimuli''.
 
 % data-driven methods
-Because naturalistic stimuli are multi-dimensional and their temporal structure
-is usually unknown, data-driven methods like intersubject correlation
-(ISC)\citep{hasson2004intersubject} or independent component analysis
-(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
-corresponding fMRI data. However, data-driven methods alone fall usually short
-of pinpointing their results to specific, time-locked stimulus features \citep{kauttonen2015optimizing}.
+Naturalistic stimuli are usually not designed for research purposes but to
+entertain their audience. Hence, their temporal is structure usually unknown due
+to an ``annotation bottleneck'' \citep{aliko2020naturalistic}. Data-driven
+methods like intersubject correlation (ISC)\citep{hasson2004intersubject} or
+independent component analysis (ICA)\citep{bartels2004chronoarchitecture} are
+often used to analyze corresponding fMRI data circumventing this bottleneck.
+However, data-driven methods alone fall usually short of pinpointing their
+results to specific stimulus events \citep{kauttonen2015optimizing}.
 % model-driven methods
-Model-driven methods, like a general linear model (GLM), can be useful to
-investigate how hemodynamic brain responses in isolated regions correlate with
-stimulus features. They can explain not just ``how'' the brain is responding to
-a stimulus but also ``why'' \citep{hamilton2018revolution}.
+Model-driven methods, like a general linear model (GLM), can be useful to test
+hypotheses on specific brain functions under more ecologically valid conditions,
+to statistically control confounding stimulus features, and to explain not just
+``how'' the brain is responding to a stimulus but also ``why''
+\citep{hamilton2018revolution}.
 % GLM: example studies
@@
 % why even bother?
-\todo[inline]{importance/bottleneck of (missing) annotations -> Aliko (2020)}
 This publication enables researchers to model hemodynamic brain responses that
 correlate with a variety of aspects of spoken language ranging from a speaker's
-identity, to phonology, grammar, syntacs, and semantics.
+identity, to phonology, grammar, syntax, and semantics.
 % extending previous non-speech annotations
@@
 focusing on aspects of real-life cognition by serving as additional confound
-measures describing key properties of major building blocks of the stimulus.
+measures describing key properties of major building blocks of the stimuli.
 

### 2020-06-25 paper/main.tex
Fix manuscript to build again
fix reference.bib

@@
 \texttt{fg\_ad\_lrdiff} (left-right volume difference) and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
-\todo{where from, or how created?}
+\todo[inline]{where from, or how created?}
 Events were convolved with FSL's ``Double-Gamma HRF'' to create the regressors.
@@
 to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
-lerner2011topographic, silbert2014coupled, wilson2007beyond}.
+lerner2011topographic, silbert2014coupled, wilson2008beyond}.
 % dissimilarities

### 2020-06-26 paper/main.tex
manually adjust fig of regressor correlations

@@
 Clusters sorted by voxel size.
-The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
+The first brain structure given contains the voxel with the maximum Z-Value,
+followed by brain structures from posterior to anterior, and partially covered
+areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
 \label{tab:cope1}
@@
 Clusters sorted by voxel size.
-The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
+The first brain structure given contains the voxel with the maximum Z-Value,
+followed by brain structures from posterior to anterior, and partially covered
+areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
 \label{tab:cope3}
@@
 Clusters sorted by voxel size.
-The first brain structure given contains the voxel with the maximum Z-Value, followed by brain structures from posterior to anterior, and partially covered areas.}
+The first brain structure given contains the voxel with the maximum Z-Value,
+followed by brain structures from posterior to anterior, and partially covered
+areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
 \label{tab:cope5}

### 2020-06-26 paper/main.tex
revise discussion

@@
 
-\todo{manually edit/merge slices.svg and colorbars.svg for final slicescolorbars}
-
 \begin{figure*} \centering
@@
 
-% Discussion
-% words > no-speech
-For the contrast words > no-speech, we find increased hemodynamic activity in a
-bilateral cortical network including temporal, parietal and frontal regions
+% Discussion words > no-speech
+For the contrast words > no-speech, results show increased hemodynamic activity
+in a bilateral cortical network including temporal, parietal and frontal regions
 related to processing spoken language \citep{friederici2011brain,
@@
 % similarities to previous naturalistic speech paradigms
-Our results are similar to results of studies that implemented an ISC approach
-to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
-lerner2011topographic, silbert2014coupled, wilson2008beyond}.
-% dissimilarities
-\todo{Which contrast captures ANY social aspects? CH: the COPEs in the
-references} Contrary to previous studies \citep{ferstl2008extended,
-mar2011neural}, we do not find increased medial activation in the precuneus or
-medial frontal cortex. This could be attributed to the fact that the contrast
-here was not designed to capture social aspects of the
-narrative.\todo{wilson2007beyond: ISC medial ja, aber decreased activation
-    compared to rest; current study in reverse contrast: posterior cingulate and
-anterior cingulate (and insula bilaterally)}.
+These clusters resemble results of previous studies that implemented an ISC
+approach to analyze fMRI data of naturalistic auditory stimuli
+\citep{honey2012not, lerner2011topographic, silbert2014coupled}.
+% differences
+We don't find significantly increased activations in midline areas (like the
+posterior cingulate cortex and precuneus or anterior cingulate cortex and medial
+frontal cortex) which showed correlated activity across subjects in previous
+studies.
+% Wilson (2008): ISC + GLM
+In this regard, our results are similar to \citep{wilson2008beyond} who
+implemented both an ISC and a GLM analysis. The findings by
+\citep{wilson2008beyond} were that an ISC analysis yielded correlated activity
+in midline areas. But the GLM analysis contrasting blocks of listening to
+narratives to blocks of a resting condition yielded decreased activity in
+midline areas.
+\todo{fun fact regarding reverse contrast (no-speech > words):
+    clusters in posterior \& anterior cingulate (and subcallosal c. \& insulae
+bilaterally); could be mentioned, must be mentioned? How shortly? No figure,
+pls!}
+
 % (proper) nouns > con
 The two contrasts contrasting nouns and proper nouns respectively to coordinate
-junctions yielded increased activation that is partially located in early
-sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
-prominently adjacent regions bilaterally (planum temporale; superior temporal
-gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
+junctions yielded increased activation partially located in early sensory
+regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most prominently
+adjacent regions bilaterally (planum temporale; superior temporal gyrus;
+\citep{arsenault2015distributed, mesgarani2014phonetic}).
+% why these contrasts nous & proper nouns
+We chose nouns and proper nouns for these two contrasts because they represent
+linguistically similar concepts but are uncorrelated in the German language and
+stimulus (cf. \ref{fig:reg-corr})
+% coordinate conjunctions
+We contrasted nouns and proper nouns respectively to coordinate conjunctions
+because (proper) nouns and coordinate conjunctions are both linguistically
+different and uncorrelated.
+% “interpretation”
+\todo{well what's combing up next is adventurous} Despite the fact that nouns
+and proper nouns are uncorrelated, contrasts lead to spatially similar clusters
+``which were not driven by a negative correlation of coordinate conjunctions
+with the modeled time series (s. totally private data)''.
+% why it's cool
+Results suggest that our current annotation of naturalistic stimuli can be used
+to create model-based analyses to test neuroscientific hypotheses.
+
+\todo[inline]{following stuff is still here but can probably be deleted}
 % interpretation 1a: large amount of semantically different nouns > narrow
@@
 summation of approximately \unit[70]{ms} lasting events in quick succession did
-not capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask:
-    If you knew all these issues, why did you do it then? hindsight bias/HARKing
-after exploratory analyses?!}.
-% but...
-Nevertheless and more importantly to exploratorily access the validity of the
-dataset is the fact that two similar linguistic concepts (nouns and proper
-nouns) embedded in a naturalistic stimulus that was not designed for linguistic
-research lead to similar activation patterns\todo{That statement is only true,
-if both contrasts are not (solely) driven by the conjunctions. There is no
-evidence in the paper that this is not the case.}
-% Within the language processing systems, early sensory regions are specialized
-% for representing the immediate physical properties of the environment (form),
-% while higher order regions extract increasingly abstract content (Davis and
-% Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).
+not capture a sufficiently amount of nuisance variance
 

### 2020-06-26 paper/main.tex
sentence regarding continuous regressors

@@
 with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and each event
-modeled as boxcar function from onset to offset of the corresponding
-phoneme.
+modeled as boxcar function from onset to offset of the corresponding phoneme.
 % sentence (endings)
@@
 % length of no-speech events
-A length of \unit[70]{ms} was chosen for no-speech events matching the
-average length of phonemes.
+A length of \unit[70]{ms} was chosen for no-speech events matching the average
+length of phonemes.
 % low-level nuisance regressors
-Lastly, we used continuous information about auditory features (left-right
-difference in volume and root mean squared volume) that was averaged across the
-length of every movie frame (\unit[40]{ms}) to capture variance correlating with
-low-level perceptual processes.
+Lastly, we used continuous bins of information about auditory features
+(left-right difference in volume and root mean square energy) that was averaged
+across the length of every movie frame (\unit[40]{ms}) to capture variance
+correlating with low-level perceptual processes.
 % convolving
@@
 regional differences between modeled and actual HRF.
-% motion parameters & temporal filtering of design
-% motion parameter are filtered, too. See FSL manual:
-% ``All (confound) EVs will be filtered to match the processing applied to the
-% input data''
+% motion parameters & temporal filtering of design motion parameter are
+% filtered, too. See FSL manual: ``All (confound) EVs will be filtered to match
+% the processing applied to the input data''
 Finally, six motion parameters were used as additional nuisance regressors and
-the design was subjected to the same temporal filtering as the BOLD time
-series.
+the design was subjected to the same temporal filtering as the BOLD time series.
 

### 2020-06-26 paper/main.tex
approximate counts in abstract

@@
 
-\todo{Wort zur Validierungsstudie; awesomeness (s. Aliko (2020); Es sind erst
-110 von max 300 Worten verbraucht; Werte runden statt newcommand benutzen}
-\thispagestyle{fancy}
-\begin{abstract}
+\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht}
+\thispagestyle{fancy} \begin{abstract}
 % up to 300 words
-Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and its audio-description (i.e.
-the audio-only variant) as an addition to a large public functional brain imaging dataset (\href{www.studyforrest.org}{studyforrest.org}).
-The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
-Additionally for every word, we provide lemmatization, a simple
-part-of-speech-tagging putting words into 15 grammatical categories, a detailed
-part-of-speech tagging putting words into 43 grammatical categories, syntactic
-dependencies within each sentence, and a semantic analysis based on word
-embeddings representing each word in a 300-dimensional semantic space.
-This annotation facilitates further studies on the cognitive neuroscience of language under conditions of real-life complexity using the \textit{studyforrest} dataset.
+Here we present an annotation of speech in the audio-visual movie ``Forrest
+Gump'' and its audio-description (i.e. the audio-only variant) as an addition to
+a large public functional brain imaging dataset
+(\href{www.studyforrest.org}{studyforrest.org}). The annotation provides
+information about the exact timing of each of the more than 2.500 spoken
+sentences, 16.000 words (including 202 non-speech vocalizations), 66.000
+phonemes and their corresponding speaker. Additionally for every word, we
+provide lemmatization, a simple part-of-speech-tagging putting words into 15
+grammatical categories, a detailed part-of-speech tagging putting words into 43
+grammatical categories, syntactic dependencies within each sentence, and a
+semantic analysis based on word embeddings representing each word in a
+300-dimensional semantic space. This annotation facilitates creating models of
+brain activity related to processing spoken language under conditions of
+real-life complexity.
 \end{abstract}

### 2020-06-26 paper/main.tex
revise intro regarding anno bottleneck

@@
 \todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht}
-\thispagestyle{fancy} \begin{abstract}
+\thispagestyle{fancy}
+\begin{abstract}
 % up to 300 words
@@
 
-\section*{Introduction} Cognitive and psychiatric neuroimaging are moving
-towards studying brain functions under conditions of real-life-like complexity
+\section*{Introduction}
+% intro to intro
+Cognitive and psychiatric neuroimaging are moving towards studying brain
+functions under conditions of real-life-like complexity
 \citep{sonkusare2019naturalistic, eickhoff2020towards}. Motion pictures
@@
 
+% annotation bottleneck
+Naturalistic stimuli are usually designed for commercial purposes and to
+entertain their audience. Thus, the temporal structure of their feature space is
+usually not explicitly known leading to an ``annotation bottleneck'' when used
+for research purposes \citep{aliko2020naturalistic}.
 % data-driven methods
-Naturalistic stimuli are usually not designed for research purposes but to
-entertain their audience. Hence, their temporal is structure usually unknown due
-to an ``annotation bottleneck'' \citep{aliko2020naturalistic}. Data-driven
-methods like intersubject correlation (ISC)\citep{hasson2004intersubject} or
-independent component analysis (ICA)\citep{bartels2004chronoarchitecture} are
-often used to analyze corresponding fMRI data circumventing this bottleneck.
-However, data-driven methods alone fall usually short of pinpointing their
-results to specific stimulus events \citep{kauttonen2015optimizing}.
+Data-driven methods like intersubject correlation
+(ISC)\citep{hasson2004intersubject} or independent component analysis
+(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
+corresponding fMRI data circumventing this bottleneck. However, data-driven
+methods alone fall usually short of pinpointing their results to specific
+stimulus events \citep{kauttonen2015optimizing}.
 % model-driven methods

### 2020-06-28 paper/main.tex
little changes in abstract

@@
 
-\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht}
-\thispagestyle{fancy}
-\begin{abstract}
+\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten
+verbraucht} \thispagestyle{fancy} \begin{abstract}
 % up to 300 words
 Here we present an annotation of speech in the audio-visual movie ``Forrest
-Gump'' and its audio-description (i.e. the audio-only variant) as an addition to
-a large public functional brain imaging dataset
+Gump'' and its audio-description (i.e. the audio-only variant of the movie) as
+an addition to a large public functional brain imaging dataset
 (\href{www.studyforrest.org}{studyforrest.org}). The annotation provides
-information about the exact timing of each of the more than 2.500 spoken
-sentences, 16.000 words (including 202 non-speech vocalizations), 66.000
-phonemes and their corresponding speaker. Additionally for every word, we
-provide lemmatization, a simple part-of-speech-tagging putting words into 15
-grammatical categories, a detailed part-of-speech tagging putting words into 43
-grammatical categories, syntactic dependencies within each sentence, and a
-semantic analysis based on word embeddings representing each word in a
-300-dimensional semantic space. This annotation facilitates creating models of
-brain activity related to processing spoken language under conditions of
-real-life complexity.
-\end{abstract}
+information about the exact timing of each of the more than 2500 spoken
+sentences, 16000 words (including 202 non-speech vocalizations), 66000 phonemes,
+and their corresponding speaker. Additionally for every word, we provide
+lemmatization, a simple part-of-speech-tagging (15 grammatical categories), a
+detailed part-of-speech tagging (43 grammatical categories), syntactic
+dependencies, and a semantic analysis based on word embeddings which represents
+each word in a 300-dimensional semantic space. This annotation enables
+researchers to create sophisticated models of brain activity related to
+phonetics, grammar, syntax, and semantics under conditions of real-life
+complexity.  \end{abstract}
 

### 2020-06-28 paper/main.tex
little changes in intro

@@
 % maximal 8
-annotation, language, speech, lateralization, narrative, natural stimulation, fMRI, studyforrest
+annotation, language, speech, narrative, natural stimulation, fMRI, studyforrest
 
@@
 Cognitive and psychiatric neuroimaging are moving towards studying brain
-functions under conditions of real-life-like complexity
+functions under conditions of lifelike complexity
 \citep{sonkusare2019naturalistic, eickhoff2020towards}. Motion pictures
@@
 in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
-audio-description (i.e. the audio-only variant of the
-movie)\citep{ForrestGumpGermanAD}.
+audio-description \citep{ForrestGumpGermanAD}.
 % the studyforrest dataset
@@
 % why even bother?
-This publication enables researchers to model hemodynamic brain responses that
-correlate with a variety of aspects of spoken language ranging from a speaker's
-identity, to phonology, grammar, syntax, and semantics.
+The current publication enables researchers to model hemodynamic brain responses
+that correlate with a variety of aspects of spoken language ranging from a
+speaker's identity, to phonetics, grammar, syntax, and semantics.
 % extending previous non-speech annotations
@@
 focusing on aspects of real-life cognition by serving as additional confound
-measures describing key properties of major building blocks of the stimuli.
+measures describing the the temporal structure and feature space of the stimuli.
 

### 2020-06-28 paper/main.tex
little changes on annotation procedure

@@
 Preliminary, manual orthographic transcriptions of dialogs, non-speech
-vocalizations (e.g. laughter or groaning) and script for the audio-description's
-narrator were merged and converted to Praat's \citep{boersma2019praat} TextGrid
-format.
+vocalizations (e.g. laughter or groaning) and the script for the
+audio-description's narrator were merged and converted to Praat's
+\citep{boersma2019praat} TextGrid format.
 % preparing annotation in Praat before forced alignment
@@
 couple of sentences was edited in Praat for manual validation against the
-original audio.
+actual content of the audio material.
 % steps conducted
@@
 too.
+
 % intro for forced aligner
@@
 (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).
-
 % performing the forced alignment audio input to the aligner
@@
 % inputs
-This WAV file, the transcription of sentences, and the updated dictionary were
+This WAV file, the merged transcription, and the updated dictionary were
 submitted to the aligner that first trained an acoustic model on the data and
 then performed the alignment.
+
 % output
 The resulting .TextGrid file that contains onsets and offsets of words and
-phonemes was corrected manually and iteratively in several passes:
+phonemes was corrected manually and iteratively in several passes using Praat:
 % onset/offset checking & correction
 In a first step, onsets and offsets on which the automatic alignment performed
-moderately were corrected in Praat.
+moderately were corrected.
 % handling poor performance
-Some low volume sentences that are spoken in continuously noisy settings
-(pursuit, battle, hurricane, rally, disco) were removed due to poor overall
-alignment performance.
+Some low volume sentences that are spoken in continuously noisy settings (e.g.
+during battle or hurricane) were removed due to poor overall alignment
+performance.
 % adding whole sentences
@@
 
-% natural language processing (NLP) spaCy
-To automatically analyze linguistic features of each word in their corresponding
-sentence, we employed the Python package spaCy \citep{spacy2} and its
-accompanying German language model (\texttt{de\_core\_news\_md} that was trained
-on the TIGER Treebank corpus \citep{brants2004tiger}.
-% Tiger Treebank Corpus:
-% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.  dropping of
-% non-speech vocalizations because they often delude the algo
+% natural language processing (NLP); Tiger Treebank Corpus:
+% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
+We employed the Python package spaCy \citep{spacy2} and its accompanying German
+language model (\texttt{de\_core\_news\_md}; trained on the TIGER
+Treebank corpus \citep{brants2004tiger}) to automatically analyze linguistic
+features of each word in their corresponding sentence.
+% dropping of non-speech vocalizations because they often delude the algo
 Non-speech vocalizations were dropped from the sentences before analysis to

### 2020-06-28 paper/main.tex
little changes on data legend

@@
 The annotation is available in two different versions, both providing the same
-information: a) as a (text-based) Praat TextGrid file and b) as a text-based,
+information: a) as a text-based Praat TextGrid file and b) as a text-based,
 tab-separated value (TSV) formatted table.
@@
 The following descriptions refer to the ten columns of the TSV file, namely
-\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text} (of sentence,
-word or phoneme), \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma},
+\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text}, \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma},
 \texttt{stop}, \texttt{vector}.
@@
 
-\subsubsection*{Duration (\texttt{duration})} The duration of the sentences,
+\subsubsection*{Duration (\texttt{duration})} The duration of the sentence,
 word or phoneme provided the format seconds.milliseconds.
@@
 Additionally in cells of this column, sentences are tagged as \texttt{SENTENCE},
-and phonemes are tagged as \texttt{PHONEME} to facilitate sorting, and filtering
-in potential further processing steps.
+and phonemes are tagged as \texttt{PHONEME} to facilitate filtering in potential
+further processing steps.
 
@@
 child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the
-type of syntactic relation that connects a "child" (the single word) to its
+type of syntactic relation that connects a "child" (the word) to its
 ``head''.
@@
 file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be
-conveniently edited with the software Praat \citep{boersma2019praat}.
+conveniently edited using the software Praat \citep{boersma2019praat}.
 % TSV format
@@
 (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with
-the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}
-\citep{gorgolewski2016bids}).
+the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS})
+\citep{gorgolewski2016bids}.
 % source code for descriptive statistics

### 2020-06-28 paper/main.tex
little changes on dataset validation

@@
 field-of-view) \citep{hanke2014audiomovie}.
+
 % motion correction
@@
 The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
-N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
+N=\rNnAll\space to \texttt{prf} with N=\rPrfAll) were modeled as boxcar function
 from onset to offset of each word.
@@
 The remaining other part-of-speech labels were pooled to a single new label
-(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
-function from onset to offset of the corresponding word.
+(\texttt{tag\_other}; N=\rTagotherAll) and modeled as a boxcar
+function from a word's onset to offset.
 % phonemes
 The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
-with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and each event
-modeled as boxcar function from onset to offset of the corresponding phoneme.
+with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and events were as
+boxcar function from a phoneme's onset to offset.
 % sentence (endings)
@@
 length of phonemes.
+
 % low-level nuisance regressors
@@
 (left-right difference in volume and root mean square energy) that was averaged
-across the length of every movie frame (\unit[40]{ms}) to capture variance
-correlating with low-level perceptual processes.
+across the length of every movie frame (\unit[40]{ms}) via Python script to
+capture variance correlating with low-level perceptual processes.
 % convolving
@@
 % Results
-Figure \ref{fig:results} depicts the results of the three contrasts (Z threshold
-Z>3.4; p<.05 cluster-corrected).
+Figure \ref{fig:results} depicts the results of the three contrasts (Z threshold >3.4; p<.05 cluster-corrected).
 % COPE 1:
@@
 posterior cingulate cortex and precuneus or anterior cingulate cortex and medial
-frontal cortex) which showed correlated activity across subjects in previous
+frontal cortex) which showed synchronized activity across subjects in previous
 studies.
@@
 implemented both an ISC and a GLM analysis. The findings by
-\citep{wilson2008beyond} were that an ISC analysis yielded correlated activity
+\citep{wilson2008beyond} were that an ISC analysis yielded synchronized activity
 in midline areas. But the GLM analysis contrasting blocks of listening to
@@
 linguistically similar concepts but are uncorrelated in the German language and
-stimulus (cf. \ref{fig:reg-corr})
+stimulus (cf. Figure \ref{fig:reg-corr})
 % coordinate conjunctions
@@
 because (proper) nouns and coordinate conjunctions are both linguistically
-different and uncorrelated.
+different and uncorrelated to coordinate conjunctions.
 % “interpretation”
@@
 % why it's cool
-Results suggest that our current annotation of naturalistic stimuli can be used
-to create model-based analyses to test neuroscientific hypotheses.
+Results suggest that our current annotation of naturalistic stimuli is of
+``sufficient quality'' and can be used to create model-based analyses to test
+neuroscientific hypotheses.
 

### 2020-06-28 paper/main.tex
little changes on conclusions

@@
 % what for
-An additional tagging of each word's linguistic features enable independent
+An additional tagging of each word's linguistic features enables independent
 working groups to create sophisticated models of hemodynamic activity
-correlating with linguistics aspects like phonology, grammar, syntax, and
+correlating with linguistics aspects like phonetics, grammar, syntax, and
 semantics occurring in two naturalistic stimuli.

### 2020-06-29 paper/main.tex
correct typos & tables

@@
 focusing on aspects of real-life cognition by serving as additional confound
-measures describing the the temporal structure and feature space of the stimuli.
+measures describing the  tempora structure and feature space of the stimuli.
 
@@
 % preliminary annotations
-Preliminary, manual orthographic transcriptions of dialogs, non-speech
+Preliminary, manual orthographic transcriptions of dialogues, non-speech
 vocalizations (e.g. laughter or groaning) and the script for the
@@
 
-\begin{table*}[tbp]
-    \caption{Overview of the annotation's content for the audio-only stimulus
-that comprises the additional narrator. Counts are given for the whole stimulus
-(\texttt{all}) and its individual segments used during fMRI scanning.
-The category \texttt{sentences} comprises complete grammatical sentences which
-are additionally marked in the annotation with a full stop at the end (``my feet hurt.'').
-It also comprises questions (``do you want a chocolate?''), exclamations (``run
-away!''), or non-speech vocalizations in quick succession (``ha, ha, ha''), or
-in isolation (e.g. ``Forrest?'', ``Forrest!'', ``ha'') at time points when
-speakers switch rapidly. The category \texttt{words} comprises each word or
-non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
-\label{tab:overview}
-\begin{tabular}{llllllllll}
-\toprule
-\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
-\midrule
-sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
-words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
-phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
-\bottomrule
-\end{tabular}
-\end{table*}
+\begin{table*}[tbp] \caption{Overview of the annotation's content for the
+        audio-description of ``Forrest Gump'' (i.e. the audio-only variant of
+        the movie) that comprises the additional narrator. Counts are given for
+        the whole stimulus (\texttt{all}) and its individual segments used
+        during fMRI scanning.  The category \texttt{sentences} comprises
+        complete grammatical sentences which are additionally marked in the
+        annotation with a full stop at the end (``my feet hurt.'').  It also
+        comprises questions (``do you want a chocolate?''), exclamations (``run
+        away!''), or non-speech vocalizations in quick succession (``ha, ha,
+        ha''), or in isolation (e.g. ``Forrest?'', ``Forrest!'', ``ha'') at time
+        points when speakers switch rapidly. The category \texttt{words}
+        comprises each word or non-speech vocalization (N=\aPosNonspeechAll) in
+    isolation.} \label{tab:overview} \begin{tabular}{llllllllll} \toprule
+        \textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3}
+        & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
+        \midrule sentences  & \aSentencesAll & \aSentencesI & \aSentencesII &
+        \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI &
+        \aSentencesVII & \aSentencesVIII \tabularnewline words  & \aWordsAll &
+        \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI &
+        \aWordsVII & \aWordsVIII \tabularnewline phonemes  & \aPhonesAll &
+        \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV &
+        \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline \bottomrule
+    \end{tabular} \end{table*}
 
 \begin{table*}[btp]
-\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurs in the audio-description of the movie.
+\caption{Sentences spoken by the ten most often occurring speakers sorted alphabetically. The narrator only occurs in the audio-description.
 Overall 97 persons were identified.
@@
 \caption{Simple part-of-speech tagging (\texttt{pos}) performed by the Python package spaCy \citep{spacy2}.
-All 15 labels sorted alpapetically.
+All 15 labels sorted alphabetically.
 Descriptions were taken from spaCy.explain().
@@
 \caption{Syntactic dependencies (\texttt{dep}) performed by the Python package spaCy \citep{spacy2}.
-The 15 most often occuring labels (overall 37 labels) sorted alphabetically.
+The 15 most often occurring labels (overall 37 labels) sorted alphabetically.
 Descriptions were taken from spaCy.explain().
@@
 The label \texttt{no-sp} represents moments when no speech was audible.
-\texttt{fg\_ad\_lrdiff} (left-right volume difference) and \texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
-\todo[inline]{where from, or how created?}
+\texttt{fg\_ad\_lrdiff} (left-right volume difference) and \texttt{fg\_ad\_rms}
+(root mean square energy) were compute for and averaged across every movie frame
+(\unit[40]{ms}) via Python script.
 Events were convolved with FSL's ``Double-Gamma HRF'' to create the regressors.
 The correlation of these regressors over the time course of the whole stimulus
-can be seen in Figure \ref{fig:reg-corr}.}
+can be seen in Figure \ref{fig:reg-corr}}.
 \label{tab:regressors}
@@
 phones & 80 most often occurring phonemes & \rPhonesAll & \rPhonesI & \rPhonesII & \rPhonesIII & \rPhonesIV & \rPhonesV & \rPhonesVI & \rPhonesVII & \rPhonesVIII \tabularnewline
-no-sp & no-speech (``soundscape'') & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
+no-sp & no-speech & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII \tabularnewline
 %\hline
@@
     hemodynamic response function and concatenated across runs before
-    performing the correlation.}
+    computing the correlation.}
 \label{fig:reg-corr} \end{figure*}
@@
     \caption{Mixed-effects group-level (N=14) GLM contrasts for the
-        audio-description of the movie Forrest Gump. Significant clusters
+        audio-description of the movie ``Forrest Gump''. Significant clusters
         (Z>3.4, p<0.05 cluster-corrected) are overlaid on the custom T2* EPI
@@
 14990 & <.001 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 &
-left Heschl's g.;
-lateral superior occipital c., angular g., superior and middle temporal g. (posterior to anterior);
-parts of supramarginal g. \&, planum temporale \\
+l. Heschl's g.;
+lateral superior occipital c., angular g., superior \& middle temporal g. (posterior to anterior);
+parts of supramarginal g. \& planum temporale \\
 14469 & <.001 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 &
-right superior temporal g.;
+r. superior temporal g.;
 angular g., superior (and middle) temporal g. (posterior to anterior), Heschl's g.;
 parts of supramarginal g., planum temporale, pars opercularis (BA44) \& pars triangularis (BA45) \\
-1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & left frontal orbital c.;
+1971 & <.001 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & l. frontal orbital c.;
 pars opercularis (BA44), pars triangularis (BA45);
 parts of precentral g. \\
-217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & left Thalamus \\
+217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & l. Thalamus \\
 \bottomrule
@@
 7691 & <.001 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 &
-left lPanum temporale; posterior inferior supramarginal g., superior temporal g., planum polare,
+l. planum temporale; posterior inferior supramarginal g., superior temporal g., planum polare,
 parts of posterior angular g.,  Heschl's g., middle temporal gyrus \\
 5928 & <.001 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 &
-right planum temporale;
+r. planum temporale;
 Heschl's g., superior temporal g., planum polare, temporal pole;
 parts of angular g. \& posterior inferior supramarginal gyrus \\
-479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & left posterior cingulate g. \\
-420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & left precuneus \\
-407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & right posterior cingulate c. \\
-294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & right precuneus \\
-121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & right occipital pole \\
-117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & right Heschl's g. \\
-115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & left superior lateral occipital c.\\
+479 & <.001 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & l. posterior cingulate g. \\
+420 & <.001 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & l. precuneus \\
+407 & <.001 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & r. posterior cingulate c. \\
+294 & <.001 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & r. precuneus \\
+121 & .024 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & r. occipital pole \\
+117 & .027 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & r. Heschl's g. \\
+115 & .029 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & l. superior lateral occipital c.\\
 \bottomrule
@@
 3166 & <.001 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 &
-left anterior superior (and middle) temporal g.;
+l. anterior superior (and middle) temporal g.;
 planum temporale, planum polare, anterior superior temporal g.;
 part of posterior supramarginal g., Heschl's g. \\
-1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & right planum temporale, anterior superior temporal g., planum polare;
+1753 & <.001 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & r. planum temporale, anterior superior temporal g., planum polare;
 part of\& part of Heschl's G. \\
 166 & .004 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 &
-right posterior cingulate g. \\
+r. posterior cingulate g. \\
 149 & .008 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 &
-right precuneus \\
+r. precuneus \\
 \bottomrule

### 2020-07-01 paper/main.tex
revision of regressor correlation fig caption

@@
 % t-contrasts
-The following three t-contrasts were defined:
+The following three $t$-contrasts were defined:
 1) words (all 21 \texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
@@
 \begin{figure*} \centering
-\includegraphics[width=\linewidth]{figures/regressor-corr}
-\caption{Pearson correlation coefficients of the 26 regressors used in the
-    analysis to validate the annotation.
-    Regressors were convolved with FSL's ``Double-Gamma HRF'' as a model of the
-    hemodynamic response function and concatenated across runs before
-    computing the correlation.}
-\label{fig:reg-corr} \end{figure*}
+    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
+        correlation coefficients of the 26 regressors used in the analysis to
+        validate the annotation. Regressors were created by convolving the
+        events with FSL's ``Double-Gamma HRF'' as a model of the hemodynamic
+        response function, temporally filtered with the same high-pass filter
+        (cut-off \unit[150]{s}) as the BOLD time series, and concatenated across
+    runs before computing the correlation.}
+    \label{fig:reg-corr}
+\end{figure*}
 

### 2020-07-02 code/plot-zmaps.py
plot-zmaps color changes and FoV

@@ -16,7 +16,7 @@ import os
 anatImg = '/usr/share/data/fsl-mni152-templates/MNI152_T1_0.5mm.nii.gz'
 
 # T2* EPI group template
-audioMask = 'code/grbold7Tad_brain_inMNI_12dof.nii.gz'
+audioMask = 'code/fov_tmpl_0.5.nii.gz'
 
 # list of primary contrasts
 # words > no-speech (bottom), Ne > kon (middle), Nn > kon (top image)
@@ -212,7 +212,8 @@ def plot_grp_slice(mode, coord,
     '''
     '''
     # underlying MNI152 T1 0.5mm image
-    colorMap = plt.cm.get_cmap('copper')
+    colorMap = plt.cm.get_cmap('Greys')
+    colorMap = colorMap.reversed()
     display = plotting.plot_anat(anat_img=anatImg,
                                  axes=axis,
                                  # title=title,
@@ -224,13 +225,9 @@ def plot_grp_slice(mode, coord,
     display.annotate(size=16)
 
     # brain mask 'grbold7Tad' in MNI space aligned with 12dof
-    colorMap = plt.cm.get_cmap('Greys')
-    colorMap = colorMap.reversed()
     display.add_overlay(audioMask,
                         cmap=colorMap,
-                        vmin=0,
-                        vmax=7000,  # adjust luminance to match MNI template
-                        alpha=.95)
+                        alpha=.9)
 
     # bottom z-map
     colorMap = plt.cm.get_cmap('Blues')

### 2020-07-02 paper/main.tex
plot-zmaps color changes and FoV
changes to caption of figure brain slices

@@
 
-\section*{Materials and methods} \subsection*{Stimulus}
+\section*{Materials and methods}
+
+\subsection*{Stimulus}
 % stimulus != DVD but ``research cut''
@@
     \includegraphics[width=\linewidth]{figures/slicescolorbars}
-    \caption{Mixed-effects group-level (N=14) GLM contrasts for the
-        audio-description of the movie ``Forrest Gump''. Significant clusters
-        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the custom T2* EPI
-        group template (gray; taken from \citep{hanke2014audiomovie}) which is
-    aligned to and overlaid on the MNI152 T1-weighted head template (copper).}
-    \label{fig:results} \end{figure*}
+    \caption{Results of the mixed-effects group-level (N=14) GLM $t$-contrasts
+        for the audio-description of the movie ``Forrest Gump''.
+        Significant clusters (Z>3.4, p<0.05 cluster-corrected) are overlaid on
+        the MNI152 T1-weighted head template (grey).
+        Light grey: The audio-description's field-of-view
+        (cf. \citep{hanke2014audiomovie}).}
+    \label{fig:results}
+\end{figure*} \todo{manual finalization of the figures spatial layout }
 

### 2020-07-20 paper/main.tex
correction of some typos

@@
 % Results
-Figure \ref{fig:results} depicts the results of the three contrasts (Z threshold >3.4; p<.05 cluster-corrected).
+Figure \ref{fig:results} depicts the results of the three contrasts (z-threshold
+Z>3.4; p<.05 cluster-corrected).
 % COPE 1:
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast words (all 21 \texttt{tag}-related regressors) > no-speech.
+\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected) for the contrast words (all 21 \texttt{tag}-related regressors) > no-speech.
 Clusters sorted by voxel size.
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}).
+\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected) for the contrast proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}).
 Clusters sorted by voxel size.
@@
 \begin{table*}[t]
-\caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (\texttt{nn}) > coordinate conjunctions (\texttt{kon}).
+\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected) for the contrast nouns (\texttt{nn}) > coordinate conjunctions (\texttt{kon}).
 Clusters sorted by voxel size.

### 2020-09-15 paper/main.tex
repair references.bib
clean intro

@@
 \citep{sonkusare2019naturalistic, eickhoff2020towards}. Motion pictures
-\citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not,
-lerner2011topographic} are increasingly utilized as so called ``naturalistic
+\citep{hasson2008neurocinematics} and continuous narratives
+\citep{wilson2008beyond, lerner2011topographic} are increasingly utilized as so called ``naturalistic
 stimuli''.
+% not designed for research
+Naturalistic stimuli are usually designed for commercial purposes and to
+entertain their audiences.
+% thus annotation bottleneck
+Thus, the temporal structure of their feature space is usually not explicitly
+known leading to an ``annotation bottleneck'' \citep{aliko2020naturalistic} when
+used for neuroscientific research.
 
-% annotation bottleneck
-Naturalistic stimuli are usually designed for commercial purposes and to
-entertain their audience. Thus, the temporal structure of their feature space is
-usually not explicitly known leading to an ``annotation bottleneck'' when used
-for research purposes \citep{aliko2020naturalistic}.
-% data-driven methods
+% data-driven methods..
 Data-driven methods like intersubject correlation
@@
 (ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
-corresponding fMRI data circumventing this bottleneck. However, data-driven
-methods alone fall usually short of pinpointing their results to specific
-stimulus events \citep{kauttonen2015optimizing}.
+corresponding fMRI data circumventing this bottleneck.
+% ..are nice but:
+However, data-driven methods alone fall usually short of pinpointing their
+results to specific stimulus events \citep{kauttonen2015optimizing}.
 % model-driven methods
-Model-driven methods, like a general linear model (GLM), can be useful to test
-hypotheses on specific brain functions under more ecologically valid conditions,
-to statistically control confounding stimulus features, and to explain not just
-``how'' the brain is responding to a stimulus but also ``why''
-\citep{hamilton2018revolution}.
+Model-driven methods, like a general linear model (GLM), that are based on
+stimulus annotations can be useful to test hypotheses on specific brain
+functions under more ecologically valid conditions, to statistically control
+confounding stimulus features, and to explain not just ``how'' the brain is
+responding to a stimulus but also ``why'' \citep{hamilton2018revolution}.
 % GLM: example studies
-For example, studies using GLMs based on annotations of a stimulus' temporal
-structure have elucidated how the brain responds to visual features of a movie
+Studies using GLMs based on annotations of a stimulus' temporal structure have
+elucidated for example how the brain responds to visual features of a movie
 \citep{bartels2004mapping} or speech-related features of a narrative
-\citep{rocca2019language}.
+\citep{rocca2020language}.
 % combination of data-driven and model-driven approaches
-Additionally, stimulus annotations can inform data-driven methods about a
+Furthermore, stimulus annotations can inform data-driven methods about a
 stimulus' temporal dynamics, or model-driven and data-driven methods can be
@@
 
-% we:
+% This publication
+% there was stuff that needed to be honed
 For this publication, we revised previous, preliminary annotations done by our
-lab and now provide one single annotation with exact onset and offset of each
+lab.
+% now the honed stuff for AV and AO
+We now provide one single annotation with exact onset and offset of each
 sentence, word and phoneme (see Table \ref{tab:overview} for an overview) spoken
 in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
-audio-description \citep{ForrestGumpGermanAD}.
+audio-description (i.e. the movie's audio-only variant with an additional
+narrator)\citep{ForrestGumpGermanAD}.
 % the studyforrest dataset
@@
 % extending previous non-speech annotations
-The current annotation of speech extends already available annotations of
-portrayed emotions \citep{labs2015portrayed}, perceived emotions
-\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the
-movie \citep{haeusler2016annotation}. All annotations can be used in any study
-focusing on aspects of real-life cognition by serving as additional confound
-measures describing the  tempora structure and feature space of the stimuli.
+This publication extends already available annotations of portrayed emotions
+\citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy},
+as well as cuts and locations depicted in the movie
+\citep{haeusler2016annotation}.
+% just use it all
+All annotations can be used in any study focusing on aspects of real-life
+cognition by serving as additional confound measures describing the  temporal
+structure and feature space of the stimuli.
 

### 2020-09-15 paper/main.tex
clean methods until data legend

@@
 % stimulus != DVD but ``research cut''
-We annotated speech in the slightly shortened ``research cut'' of the movie
-\citep{hanke2016simultaneous} and its temporally aligned audio-description
-\citep{hanke2014audiomovie}.
-% movie source
-For the movie stimulus, we used the audio track of the German DVD release
-\citep{ForrestGumpDVD}.
-% audio source
-For the audio-only stimulus, we used the movie's audio-description that was
-broadcast as an additional audio track for visually impaired listeners on Swiss
-public television \citep{ForrestGumpGermanAD}.
-% diff in audio AV vs. AO
+We annotated speech in the slightly shortened ``research cut'' \citep{hanke2014audiomovie, hanke2016simultaneous} of the movie and its
+temporally aligned audio-description that was broadcast as an additional audio
+track for visually impaired listeners on Swiss public television
+\citep{ForrestGumpGermanAD}.
+%  what the AO contains
 The plot of the movie is already carried by an off-screen voice of the main
@@
 % \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
-The merged transcription containing a rough onset and offset for usually a
-couple of sentences was edited in Praat for manual validation against the
-actual content of the audio material.
+This merged transcription that contained a rough onset and offset for usually a
+couple of sentences was edited in Praat for manual validation against the actual
+content of the audio material.
 % steps conducted
@@
 When two or more persons were speaking simultaneously the less dominant voice
-was dropped. Low volume background speech (especially occurring during music or
-continuous environmental noise) or low volume non-speech vocalizations which
-were subjectively assessed to be incomprehensible for the audience were dropped,
-too.
+was dropped. Low volume non-speech vocalizations or low volume background speech
+(especially during music or continuous environmental noise) which were
+subjectively assessed to be incomprehensible for the audience were dropped, too.
 
@@
 % performing the forced alignment audio input to the aligner
-The audio track was converted from FLAC to WAV via FFmpeg \citep{ffmpeg} to meet
-the aligner's requirements.
+The audio track of the audio-description was converted from FLAC to WAV via
+FFmpeg \citep{ffmpeg} to meet the aligner's input requirements.
 % inputs

### 2020-09-15 paper/main.tex
clean validation analysis and its discussion

@@
 The annotation is available in two different versions, both providing the same
-information: a) as a text-based Praat TextGrid file and b) as a text-based,
+information: a) as a text-based Praat TextGrid file, and b) as a text-based,
 tab-separated value (TSV) formatted table.
@@
 \midrule
-ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII \tabularnewline
+ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV
+& \aPosAdjV & \aPosAdjVI & \aPosAdjVII & \aPosAdjVIII \tabularnewline
 ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
@@
 child2, ...'', where the ``arc label'' (see Table \ref{tab:dep}) describes the
-type of syntactic relation that connects a "child" (the word) to its
+type of syntactic relation that connects a "child" (the current word) to its
 ``head''.
@@
 % sources of variability. ~170 words => das wird beim folgenden Schreiben
-% definitiv nichts werden
-% intro
-In order to assess data quality, we investigated if contrasting speech-related
-events to events without speech lead to increased activation in areas known to
-be involved in semantic processing \citep{hickok2007cortical}.
+% definitiv nichts werden intro
+In order to assess the annotation's quality, we investigated if contrasting
+speech-related events to events without speech lead to increased activation in
+areas known to be involved in language processing \citep{hickok2007cortical}.
 % nouns and proper nouns resp. > coordinate junctions
@@
 congruent brain areas.
-% data source
-% data aligned by applying an affine transformation only are available in
-% bold_dico_dico7Tad2grpbold7Tad.nii.gz.
-% data aligned by non-linear warping are available in
-% bold_dico_dico7Tad2grpbold7Tad_nl.nii.gz.
+% data source data aligned by applying an affine transformation only are
+% available in bold_dico_dico7Tad2grpbold7Tad.nii.gz.  data aligned by
+% non-linear warping are available in bold_dico_dico7Tad2grpbold7Tad_nl.nii.gz.
 We used a dataset providing blood oxygenation level-dependent (BOLD) functional
@@
 The correlation of these regressors over the time course of the whole stimulus
-can be seen in Figure \ref{fig:reg-corr}}.
+can be seen in Figure \ref{fig:reg-corr}.}
 \label{tab:regressors}
@@
 At the first level analyzing each segment for each subject individually, we
-created 26 regressors based on events drawn from the annotation (see Table
-\ref{tab:regressors}).
+created 26 regressors (see Table \ref{tab:regressors}) based on events drawn
+from the annotation.
 % part-of-speech labels: labels to events, top 20
@@
 The remaining other part-of-speech labels were pooled to a single new label
-(\texttt{tag\_other}; N=\rTagotherAll) and modeled as a boxcar
-function from a word's onset to offset.
+(\texttt{tag\_other}; N=\rTagotherAll) and modeled as a boxcar function from a
+word's onset to offset.
 % phonemes
 The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
-with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and events were as
+with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and modeled as
 boxcar function from a phoneme's onset to offset.
@@
 condition were created by the following rationale: events were fitted into
-longer lasting intervals between onsets and offsets of words and thus within
-intervals without audible speech.
+intervals without audible speech that lasted at least \unit[3.6]{s}.
 % minimum distance to words
@@
 length of phonemes.
-
 % low-level nuisance regressors
@@
 the design was subjected to the same temporal filtering as the BOLD time series.
-
 % t-contrasts
@@
 % 2nd lvl
-The second-level analysis which averaged contrast estimates across the eight
+The second-level analysis that averaged contrast estimates across the eight
 stimulus segments per subject was carried out using a fixed effects model by
@@
 % cluster 1
-one left lateralized cluster spanning from the angular gyrus and inferior
+one left-lateralized cluster spanning from the angular gyrus and inferior
 posterior supramarginal gyrus across the superior and middle temporal gyrus,
@@
 % cluster 1
-one left lateralized cluster spanning from the angular gyrus across planum
+one left-lateralized cluster spanning from the angular gyrus across planum
 temporale and superior temporal gyrus, partially covering the Heschl's gyrus,
@@
 % COPE 5
-The contrast nouns > coordinate conjunctions yielded four significant clusters (see Table \ref{tab:cope5}):
+The contrast nouns > coordinate conjunctions yielded four significant clusters
+(see Table \ref{tab:cope5}):
 % cluster 1 & 2
-two clusters that are slightly smaller than lateral temporal clusters of contrast nouns > coordinate conjunction.
+two clusters that are slightly smaller than lateral temporal clusters of
+contrast nouns > coordinate conjunction.
 % variation in cluster 1 & 2 in comparison to COPE 1
-In this case, spanning from angular gyrus in the left hemisphere and from planum temporale in the right hemisphere into the anterior part of superior temporal cortex.
+In this case, spanning from angular gyrus in the left hemisphere and from planum
+temporale in the right hemisphere into the anterior part of superior temporal
+cortex.
 % cluster 3 & 4
-Finally, two small right lateralized clusters in the right posterior cingulate
+Finally, two small right-lateralized clusters in the right posterior cingulate
 gyrus and right precuneus.
@@
     \label{fig:results}
-\end{figure*} \todo{manual finalization of the figures spatial layout }
+\end{figure*}
 
@@
 In this regard, our results are similar to \citep{wilson2008beyond} who
-implemented both an ISC and a GLM analysis. The findings by
-\citep{wilson2008beyond} were that an ISC analysis yielded synchronized activity
-in midline areas. But the GLM analysis contrasting blocks of listening to
-narratives to blocks of a resting condition yielded decreased activity in
-midline areas.
-\todo{fun fact regarding reverse contrast (no-speech > words):
-    clusters in posterior \& anterior cingulate (and subcallosal c. \& insulae
-bilaterally); could be mentioned, must be mentioned? How shortly? No figure,
-pls!}
+implemented both an ISC and a GLM analysis. In this study, the ISC analysis
+showed synchronized activity in midline areas but the GLM analysis contrasting
+blocks of listening to narratives to blocks of a resting condition showed
+significantly decreased activity in these areas.
+\todo[inline]{our reverse contrast (no-speech > words): clusters in posterior \&
+anterior cingulate (and subcallosal c. \& insulae bilaterally); I think opening
+the pandora's box of the reverse contrasts is not worth it here}
 
 % (proper) nouns > con
-The two contrasts contrasting nouns and proper nouns respectively to coordinate
-junctions yielded increased activation partially located in early sensory
-regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most prominently
-adjacent regions bilaterally (planum temporale; superior temporal gyrus;
-\citep{arsenault2015distributed, mesgarani2014phonetic}).
+The two contrasts that contrasted nouns and proper nouns respectively to
+coordinate junctions yielded increased activation partially located in early
+sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
+prominently adjacent regions bilaterally (planum temporale; superior temporal
+gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
 % why these contrasts nous & proper nouns
@@
 We contrasted nouns and proper nouns respectively to coordinate conjunctions
-because (proper) nouns and coordinate conjunctions are both linguistically
-different and uncorrelated to coordinate conjunctions.
+because (proper) nouns are linguistically different to coordinate conjunctions
+as well as uncorrelated.
 % “interpretation”
-\todo{well what's combing up next is adventurous} Despite the fact that nouns
-and proper nouns are uncorrelated, contrasts lead to spatially similar clusters
-``which were not driven by a negative correlation of coordinate conjunctions
-with the modeled time series (s. totally private data)''.
+\todo[inline]{well what's coming up next is adventurous} Both contrasts lead to
+largely spatially congruent clusters despite the fact that nouns and proper
+nouns are uncorrelated.
+% not driven by coordinate conjunction regressors
+We confirmed the validity of these interpretation by testing if the spatial
+congruency could be attributed to a negative correlation of coordinate
+conjunctions with the modeled time series which turned out to be not the case.
 % why it's cool
-Results suggest that our current annotation of naturalistic stimuli is of
-``sufficient quality'' and can be used to create model-based analyses to test
-neuroscientific hypotheses.
-
-\todo[inline]{following stuff is still here but can probably be deleted}
-% interpretation 1a: large amount of semantically different nouns > narrow
-% concept (conjunctions)
-This could be attributed to the exploratory nature of our analysis. A high count
-of heterogeneous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) that were
-averaged across all 300 semantic dimensions (cf. \citep{mitchell2008predicting,
-huth2016natural}), and contrasted to coordinate conjunctions that offered a
-comparably small amount of events (N=\rKonAll).
-% interpretation 1b: not just narrow concept but also dominated by just two
-% different words
-Coordinate junctions were chosen because they were assumed to be temporally
-uncorrelated with nouns but mostly consist of the words ``and'' (N=392) and
-``but'' (N=49), and thus offered only a small amount of variance.
-% interpretation 2
-A second explanation might be that our phoneme regressors that assumed linear
-summation of approximately \unit[70]{ms} lasting events in quick succession did
-not capture a sufficiently amount of nuisance variance
+In summary, the results of our exploratory analyses suggests that the
+annotation of speech meets the quality requirements to be used as the basis for
+model-based analyses that investigate language perception under more
+ecologically valid conditions.\todo{might be a little humble}
 
 \section*{Data availability}
-% aus der Schnitt-Annotation übernommen
+\todo{cf. other F1000 papers but probably a gift for the master}
 \texttt{This section will be auto-generated.}

### 2020-09-16 paper/main.tex
clean validation analysis and its discussion v2

@@
 
+\todo[inline]{``Dataset content'' vs. ``Data and software availability''}
+
 \section*{Introduction}
@@
 % data-driven methods..
-Data-driven methods like intersubject correlation
+Data-driven methods like inter-subject correlation
 (ISC)\citep{hasson2004intersubject} or independent component analysis
@@
 % stimulus != DVD but ``research cut''
-We annotated speech in the slightly shortened ``research cut'' \citep{hanke2014audiomovie, hanke2016simultaneous} of the movie and its
-temporally aligned audio-description that was broadcast as an additional audio
+We annotated speech in the slightly shortened ``research cut''
+\citep{hanke2014audiomovie} of the movie and its
+temporally aligned audio-description \citep{hanke2016simultaneous} that was broadcast as an additional audio
 track for visually impaired listeners on Swiss public television
@@
 We then used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
-algorithmically identify the exact onset of offset of each sentence, and the
-onset and offset of each word and phoneme.
+algorithmically identify the exact onset of offset of each word and phoneme.
 % preparing other inputs before forced alignment pronunciation dictionary
@@
 We employed the Python package spaCy \citep{spacy2} and its accompanying German
-language model (\texttt{de\_core\_news\_md}; trained on the TIGER
+language model (\texttt{de\_core\_news\_md}) that was trained on the TIGER
 Treebank corpus \citep{brants2004tiger}) to automatically analyze linguistic
@@
 \subsubsection*{Duration (\texttt{duration})} The duration of the sentence,
-word or phoneme provided the format seconds.milliseconds.
+word or phoneme provided in the format seconds.milliseconds.
 
@@
 % nouns and proper nouns resp. > coordinate junctions
-Moreover, we tested if similar linguistic concepts providing high semantic
-information (proper nouns and nouns) contrasted to a concept providing low
+Moreover, we tested if two similar linguistic concepts (proper nouns and nouns)
+providing high semantic information contrasted with a concept providing low
 semantic information (coordinate conjunctions) lead to increased activation in
 congruent brain areas.
+
 % data source data aligned by applying an affine transformation only are
@@
 field-of-view) \citep{hanke2014audiomovie}.
-
 % motion correction
@@
 to a study-specific T2*-weighted echo planar imaging (EPI) group template (cf.
-\citep{hanke2014audiomovie} for details on how the group template was created).
+\citep{hanke2014audiomovie} for exact details).
+
 % steps done by C.H.
-All further analysis steps were carried out using Feat v6.00 (FMRI Expert
-Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB's
-Software Library)\citep{smith2004fsl}.
+All further steps for the current analysis were carried out using Feat v6.00
+(FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9
+(FMRIB's Software Library)\citep{smith2004fsl}.
 % dropping of subject 10
@@
 % low-level nuisance regressors
-Lastly, we used continuous bins of information about auditory features
+Lastly, we used continuous bins of information about low-level auditory features
 (left-right difference in volume and root mean square energy) that was averaged
-across the length of every movie frame (\unit[40]{ms}) via Python script to
-capture variance correlating with low-level perceptual processes.
+across the length of every movie frame (\unit[40]{ms}) to capture variance
+correlating with low-level perceptual processes.
 % convolving
@@
 % t-contrasts
-The following three $t$-contrasts were defined:
-1) words (all 21 \texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
+The following three $t$-contrasts were defined: 1) words (all 21
+\texttt{tag}-related regressors) > no-speech (\texttt{no-sp}),
 % 1b) no-speech > words
-2) proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}; N=\rKonAll), and
+2) proper nouns (\texttt{ne}) > coordinate conjunctions (\texttt{kon}), and
 % 2b) coordinate conjunctions > proper nouns
@@
 % cluster 1 & 2
-two clusters that are slightly smaller than lateral temporal clusters of
+two clusters that are slightly smaller than the lateral temporal clusters of
 contrast nouns > coordinate conjunction.
@@
 parts of precentral g. \\
-217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & l. Thalamus \\
+217 & .002 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & l. thalamus \\
 \bottomrule
@@
 We chose nouns and proper nouns for these two contrasts because they represent
-linguistically similar concepts but are uncorrelated in the German language and
-stimulus (cf. Figure \ref{fig:reg-corr})
+linguistically similar concepts but are yet uncorrelated in the German language
+and stimulus (cf. Figure \ref{fig:reg-corr}).
 % coordinate conjunctions
 We contrasted nouns and proper nouns respectively to coordinate conjunctions
-because (proper) nouns are linguistically different to coordinate conjunctions
-as well as uncorrelated.
+because nouns and proper nouns are linguistically different to coordinate
+conjunctions as well as uncorrelated.
 % “interpretation”
-\todo[inline]{well what's coming up next is adventurous} Both contrasts lead to
-largely spatially congruent clusters despite the fact that nouns and proper
-nouns are uncorrelated.
+\todo[inline]{well what's coming up next is adventurous} Despite the fact that
+nouns and proper nouns are uncorrelated, both contrasts lead to largely
+spatially congruent clusters. Results suggest that models based on our
+annotation of similar linguistic concepts correlate with hemodynamic activity in
+spatially similar areas.
 % not driven by coordinate conjunction regressors
@@
 congruency could be attributed to a negative correlation of coordinate
-conjunctions with the modeled time series which turned out to be not the case.
+conjunctions with the modeled time series which turned out not to be the case.
 % why it's cool
-In summary, the results of our exploratory analyses suggests that the
-annotation of speech meets the quality requirements to be used as the basis for
-model-based analyses that investigate language perception under more
-ecologically valid conditions.\todo{might be a little humble}
+In summary, results of our exploratory analyses suggest that the annotation of
+speech meets the quality requirements to be used as the basis for model-based
+analyses that investigate language perception under more ecologically valid
+conditions.\todo{might be a little humble}
 
@@
 % results
-Results of our dataset validating analysis that we run as a proof of concept
-show that the annotation's content can indeed / in principle be used to
-isolate/track speech-related networks in the human brain under life-like
-conditions.
+Results of our analysis that we ran to assess the dataset's quality shows that the annotation's content can indeed be used to isolate speech-related networks in the human brain under life-like conditions.
 

### 2020-09-17 paper/main.tex
mention validation analysis in abstract

@@
 
-\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten
-verbraucht} \thispagestyle{fancy} \begin{abstract}
-% up to 300 words
-Here we present an annotation of speech in the audio-visual movie ``Forrest
-Gump'' and its audio-description (i.e. the audio-only variant of the movie) as
-an addition to a large public functional brain imaging dataset
-(\href{www.studyforrest.org}{studyforrest.org}). The annotation provides
-information about the exact timing of each of the more than 2500 spoken
-sentences, 16000 words (including 202 non-speech vocalizations), 66000 phonemes,
-and their corresponding speaker. Additionally for every word, we provide
-lemmatization, a simple part-of-speech-tagging (15 grammatical categories), a
-detailed part-of-speech tagging (43 grammatical categories), syntactic
-dependencies, and a semantic analysis based on word embeddings which represents
-each word in a 300-dimensional semantic space. This annotation enables
-researchers to create sophisticated models of brain activity related to
-phonetics, grammar, syntax, and semantics under conditions of real-life
-complexity.  \end{abstract}
+\thispagestyle{fancy}
+
+\begin{abstract}
+% up to 300 words intro
+Here we present an annotation of speech spoken in the audio-visual movie
+``Forrest Gump'' and its audio-description (i.e. the audio-only variant of the
+movie) as an addition to a large public functional brain imaging dataset
+(\href{www.studyforrest.org}{studyforrest.org}).
+% anno content 1
+The annotation provides information about the exact timing of each of the more
+than 2500 spoken sentences, 16000 words (including 202 non-speech
+vocalizations), 66000 phonemes, and their corresponding speaker.
+% anno content 2
+Additionally for every word, we provide lemmatization, a simple
+part-of-speech-tagging (15 grammatical categories), a detailed part-of-speech
+tagging (43 grammatical categories), syntactic dependencies, and a semantic
+analysis based on word embedding which represents each word in a
+300-dimensional semantic space.
+% validation
+To validate the dataset's quality, we build a model of hemodynamic brain
+activity based on information drawn from the annotation.
+% why bother
+Results suggest that the annotation's content and quality enable independent
+researchers to create sophisticated models of brain activity correlating with a
+variety of linguistic aspects under conditions of real-life complexity.
+\end{abstract} \todo{validation is now (carefully) mentioned; 150 of 300 words
+used for abstract}
 
@@
 % maximal 8
-annotation, language, speech, narrative, natural stimulation, fMRI, studyforrest
+annotation, language, speech, narrative, naturalistic stimulus, fMRI, studyforrest
 
@@
 \clearpage
-
-\todo[inline]{``Dataset content'' vs. ``Data and software availability''}
 
@@
 stimulus' temporal dynamics, or model-driven and data-driven methods can be
-combined to improve interpretability of results \citep{lahnakoski2012stimulus}.
+combined to improve the interpretability of results \citep{lahnakoski2012stimulus}.
 
@@
 \section*{Dataset validation}
-% Information about any validation carried out and/or any limitations of the
-% datasets, including any allowances made for controlling bias or unwanted
-% sources of variability. ~170 words => das wird beim folgenden Schreiben
-% definitiv nichts werden intro
+\todo[inline]{``Information about any validation carried out and/or any
+    limitations of the datasets, including any allowances made for controlling
+bias or unwanted sources of variability. ~170 words'' 170 words? lol}
+% intro
 In order to assess the annotation's quality, we investigated if contrasting
@@
 % differences
-We don't find significantly increased activations in midline areas (like the
+We do not find significantly increased activations in midline areas (like the
 posterior cingulate cortex and precuneus or anterior cingulate cortex and medial
@@
 
-\section*{Data availability}
-\todo{cf. other F1000 papers but probably a gift for the master}
-\texttt{This section will be auto-generated.}
+\section*{Data availability} \todo[inline]{``This section will be
+auto-generated.'' What do we have to do here? I cleaned input datasets
+(speechanno and speechanno as subdataset in validation analysis) of this paper
+repo from the descriptive nouns}
 
@@
 
-\todo[inline]{the paper needs to serve a purpose:
-    a) documentation for the annotation.
-    b) attract people to use this work for their own studies.
-    I would even argue that this is the \textit{main} purpose, given that the
-    annotation in itself represents to scientific progress. The need to give an
-    accurate assessment what this can be used for and what is problematic or
-    impossible.  ATM this is the only statement in this regard: 'facilitates
-    modeling of hemodynamic brain responses correlating with speech-related
-events' and the only indication of purpose is 'additional confound measures'. I
-thin this is incongruent with the amount of work and the level of detail of
-this annotation; CH: let's discuss that personally}
-
 \section*{Conclusions}
+\todo[inline]{give an accurate assessment what this can be used for and what is
+    problematic or impossible.  ATM this is the only statement in this regard:
+    'facilitates modeling of hemodynamic brain responses correlating with
+    speech-related events' and the only indication of purpose is 'additional
+confound measures'. I thin this is incongruent with the amount of work and the
+level of detail of this annotation; CH: let's discuss that personally}
 % what the paper is about
@@
 % results
-Results of our analysis that we ran to assess the dataset's quality shows that the annotation's content can indeed be used to isolate speech-related networks in the human brain under life-like conditions.
+Results of our analysis that we ran to assess the dataset's quality shows that
+the annotation's content can indeed be used to isolate speech-related networks
+in the human brain under life-like conditions.
 

### 2020-10-07 paper/main.tex
Cleanup

@@
 
-\author[1, 2]{Christian~O.~Häusler \\ email \href{mailto:c.haeusler@fz-juelich.de}{c.haeusler@fz-juelich.de} }
-\author[1, 2]{Michael~Hanke \\ email \href{mailto:m.hanke@fz-juelich.de}{m.hanke@fz-juelich.de} }
+\author[1, 2]{Christian~O.~Häusler}
+\author[1, 2]{Michael~Hanke}
 
@@
 \maketitle
-
-\todo[inline]{wie email und ORCID (du: https://orcid.org/0000-0001-6398-6370; ich: https://orcid.org/0000-0002-0936-317X) unterbringen?}
 
@@
 Results suggest that the annotation's content and quality enable independent
-researchers to create sophisticated models of brain activity correlating with a
+researchers to create models of brain activity correlating with a
 variety of linguistic aspects under conditions of real-life complexity.
-\end{abstract} \todo{validation is now (carefully) mentioned; 150 of 300 words
-used for abstract}
+\end{abstract}
+
+\section*{Contacts}
+\begin{description}
+  \item{Christian~O.~Häusler} \\
+    email: \href{mailto:c.haeusler@fz-juelich.de}{c.haeusler@fz-juelich.de} \\
+    orcid: https://orcid.org/0000-0002-0936-317X
+  \item{Michael~Hanke}\\
+    email: \href{mailto:michael.hanke@gmail.com}{michael.hanke@gmail.com} \\
+    orcid: https://orcid.org/0000-0001-6398-6370 \\
+\end{description}
 
@@
 The annotation comes in two different versions. First, as a text-based TextGrid
-file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be
+file (\texttt{annotation/ fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be
 conveniently edited using the software Praat \citep{boersma2019praat}.
@@
 Second, as a text-based, tab-separated-value (TSV) formatted table
-(\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with
+(\texttt{annotation/fg\_rscut\_ ad\_ger\_speech\_tagged.tsv}) in accordance with
 the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS})
@@
 \section*{Dataset validation}
-\todo[inline]{``Information about any validation carried out and/or any
-    limitations of the datasets, including any allowances made for controlling
-bias or unwanted sources of variability. ~170 words'' 170 words? lol}
 % intro
@@
 significantly decreased activity in these areas.
-\todo[inline]{our reverse contrast (no-speech > words): clusters in posterior \&
-anterior cingulate (and subcallosal c. \& insulae bilaterally); I think opening
-the pandora's box of the reverse contrasts is not worth it here}
 
@@
 % “interpretation”
-\todo[inline]{well what's coming up next is adventurous} Despite the fact that
+Despite the fact that
 nouns and proper nouns are uncorrelated, both contrasts lead to largely
@@
 analyses that investigate language perception under more ecologically valid
-conditions.\todo{might be a little humble}
+conditions.
 
@@
 \section*{Conclusions}
-\todo[inline]{give an accurate assessment what this can be used for and what is
-    problematic or impossible.  ATM this is the only statement in this regard:
-    'facilitates modeling of hemodynamic brain responses correlating with
-    speech-related events' and the only indication of purpose is 'additional
-confound measures'. I thin this is incongruent with the amount of work and the
-level of detail of this annotation; CH: let's discuss that personally}
 % what the paper is about
@@
 An additional tagging of each word's linguistic features enables independent
-working groups to create sophisticated models of hemodynamic activity
+working groups to create models of hemodynamic activity
 correlating with linguistics aspects like phonetics, grammar, syntax, and

### 2020-10-22 paper/main.tex
add text for section data availability

@@
 
-\section*{Data availability} \todo[inline]{``This section will be
-auto-generated.'' What do we have to do here? I cleaned input datasets
-(speechanno and speechanno as subdataset in validation analysis) of this paper
-repo from the descriptive nouns}
+\section*{Data availability}
 
-In addition, released data, code, and manuscript sources are also available on
-Github (\url{https://github.com/psychoinformatics-de/studyforrest-paper-speechannotation}).
+osf.io: The annotation as both a TSV and TextGrid file as well as scripts and
+data of the analysis, doi:
+\href{dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}
 

### 2020-10-29 paper/main.tex
some cleaning
Minor language tuning

@@
 % up to 300 words intro
-Here we present an annotation of speech spoken in the audio-visual movie
-``Forrest Gump'' and its audio-description (i.e. the audio-only variant of the
-movie) as an addition to a large public functional brain imaging dataset
+Here we present an annotation of speech in the audio-visual movie
+``Forrest Gump'' and its audio-description for a visually impaired audience,
+as an addition to a large public functional brain imaging dataset
 (\href{www.studyforrest.org}{studyforrest.org}).
@@
 % anno content 2
-Additionally for every word, we provide lemmatization, a simple
+Additionally, for every word, we provide lemmatization, a simple
 part-of-speech-tagging (15 grammatical categories), a detailed part-of-speech
@@
 researchers to create models of brain activity correlating with a
-variety of linguistic aspects under conditions of real-life complexity.
+variety of linguistic aspects under conditions of near-real-life complexity.
 \end{abstract}
@@
 
-\listoftodos
-
 \clearpage
@@
 Thus, the temporal structure of their feature space is usually not explicitly
-known leading to an ``annotation bottleneck'' \citep{aliko2020naturalistic} when
+known, leading to an ``annotation bottleneck'' \citep{aliko2020naturalistic} when
 used for neuroscientific research.
@@
 (ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
-corresponding fMRI data circumventing this bottleneck.
+such fMRI data in order to circumvent this bottleneck.
 % ..are nice but:
-However, data-driven methods alone fall usually short of pinpointing their
-results to specific stimulus events \citep{kauttonen2015optimizing}.
+However, use of data-driven methods alone falls short of associating results with
+particular stimulus events \citep{kauttonen2015optimizing}.
 % model-driven methods
-Model-driven methods, like a general linear model (GLM), that are based on
+Model-driven methods, like the general linear model (GLM), that are based on
 stimulus annotations can be useful to test hypotheses on specific brain
@@
 Studies using GLMs based on annotations of a stimulus' temporal structure have
-elucidated for example how the brain responds to visual features of a movie
+elucidated, for example, how the brain responds to visual features of a movie
 \citep{bartels2004mapping} or speech-related features of a narrative
@@
 
-osf.io: The annotation as both a TSV and TextGrid file as well as scripts and
-data of the analysis, doi:
+osf.io: The annotation as both a tab-separated values (TSV) formatted table and
+TextGrid file as well as scripts and data of the analysis, doi:
 \href{dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}

### 2020-10-29 paper/main.tex
We do not need to mention prior drafts without a publication

@@
 % there was stuff that needed to be honed
-For this publication, we revised previous, preliminary annotations done by our
-lab.
+%For this publication, we revised previous, preliminary annotations done by our
+%lab.
 % now the honed stuff for AV and AO
-We now provide one single annotation with exact onset and offset of each
+Here we provide an annotation with exact onset and offset of each
 sentence, word and phoneme (see Table \ref{tab:overview} for an overview) spoken
 in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its
-audio-description (i.e. the movie's audio-only variant with an additional
+audio-description (i.e. the movie's soundtrack with an additional
 narrator)\citep{ForrestGumpGermanAD}.

### 2020-10-29 paper/main.tex
Language tuning Methods

@@
 We annotated speech in the slightly shortened ``research cut''
-\citep{hanke2014audiomovie} of the movie and its
-temporally aligned audio-description \citep{hanke2016simultaneous} that was broadcast as an additional audio
-track for visually impaired listeners on Swiss public television
-\citep{ForrestGumpGermanAD}.
+\citep{hanke2014audiomovie} of the movie ``Forrest Gump'' and its temporally
+aligned audio-description \citep{hanke2016simultaneous} that was broadcast as
+an additional audio track for visually impaired listeners on Swiss public
+television \citep{ForrestGumpGermanAD}.
 %  what the AO contains
-The plot of the movie is already carried by an off-screen voice of the main
-character Forrest Gump. In the largely identical audio-description, a male
-narrator additionally describes essential aspects of the visual scenery when
+The plot of the original movie is already carried by an off-screen voice of the
+main character Forrest Gump. In the audio-description, an additional male
+narrator describes essential aspects of the visual scenery when
 there is no off-screen voice, dialog, or other relevant auditory content.
@@
 % preliminary annotations
-Preliminary, manual orthographic transcriptions of dialogues, non-speech
+Preliminary, manual orthographic transcripts of dialogues, non-speech
 vocalizations (e.g. laughter or groaning) and the script for the
@@
 % \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
-This merged transcription that contained a rough onset and offset for usually a
-couple of sentences was edited in Praat for manual validation against the actual
-content of the audio material.
+This merged transcript contained a rough onset and offset timings for small
+groups of sentences, and was further edited in Praat for manual validation
+against the actual content of the audio material.
 % steps conducted
-The following steps were done in several passes to iteratively improve the
-quality of the data: approximate temporal onsets and offsets were corrected, and
+The following steps were performed by a single person, already familiar with
+the stimulus, in several passes to iteratively improve the
+quality of the data: approximate temporal onsets and offsets were corrected;
 intervals containing several sentences were split into intervals containing only
-one sentence.
+one sentence;
 % dropping of sentences hard to understand
-When two or more persons were speaking simultaneously the less dominant voice
-was dropped. Low volume non-speech vocalizations or low volume background speech
+when two or more persons were speaking simultaneously the less dominant voice
+was dropped; low volume non-speech vocalizations or low volume background speech
 (especially during music or continuous environmental noise) which were
@@
 We then used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
-algorithmically identify the exact onset of offset of each word and phoneme.
+algorithmically identify the exact onset and offset of each word and phoneme.
 % preparing other inputs before forced alignment pronunciation dictionary
@@
 % output
-The resulting .TextGrid file that contains onsets and offsets of words and
-phonemes was corrected manually and iteratively in several passes using Praat:
+The resulting timings of words and
+phonemes were corrected manually and iteratively in several passes using Praat:
 % onset/offset checking & correction
@@
 % constant on-the-fly checking of previous
-During every step results from previous steps were constantly checked again for
+During every step previous results were repeatedly checked for
 errors and further improvements.
@@
 \subsubsection*{Start (\texttt{start})} The onset of the sentence, word or
-phoneme. Time stamps are provided in the format seconds.milliseconds of stimulus
+phoneme. Time stamps are provided in the format seconds.milliseconds from stimulus
 onset.

### 2020-10-29 paper/main.tex
Some Q

@@
 condition were created by the following rationale: events were fitted into
-intervals without audible speech that lasted at least \unit[3.6]{s}.
+intervals without audible speech that lasted at least \unit[3.6]{s} \todo{why 3.6?}.
 % minimum distance to words
 Each event of the no-speech condition had to have a minimum distance of
-\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
+\unit[1.8]{s}\todo{why 1.8} to an onsets or offsets of a word, and to each onset to another
 event of the no-speech condition.
@@
 across the length of every movie frame (\unit[40]{ms}) to capture variance
-correlating with low-level perceptual processes.
+correlating with assumed low-level perceptual processes.
 % convolving

### 2020-10-29 paper/main.tex
Double-check label, copied from above.
Make more obvious that 3rd-level was mixed-effects

@@
 % 2b) coordinate conjunctions > proper nouns
-3) nouns (\texttt{nn}) > coordinate conjunctions.
+3) nouns (\texttt{nn}) > coordinate conjunctions (\texttt{kon}).
 % 3b) coordinate conjunctions > nouns
@@
 The third level analysis which averaged contrast estimates across subjects was
-carried out using FLAME stage 1 with automatic outlier deweighting
+carried out using a mixed-effects model (FLAME stage 1) with automatic outlier deweighting
 \citep{woolrich2004multilevel, woolrich2008robust}.

### 2020-10-29 paper/main.tex
Wording

@@
 % identification of brain regions
-Brain regions associated with observed clusters were determined with the Jülich
+Brain regions associated with observed clusters were labeled using the Jülich
 Histological Atlas \citep{eickhoff2005toolbox,eickhoff2007assignment} and the

### 2020-10-29 paper/main.tex
Fix URL plus minor stuff

@@
         the MNI152 T1-weighted head template (grey).
-        Light grey: The audio-description's field-of-view
+        Light grey: The audio-description dataset's field-of-view
         (cf. \citep{hanke2014audiomovie}).}
@@
 We chose nouns and proper nouns for these two contrasts because they represent
-linguistically similar concepts but are yet uncorrelated in the German language
+linguistically similar concepts but are uncorrelated in the German language
 and stimulus (cf. Figure \ref{fig:reg-corr}).
@@
 In summary, results of our exploratory analyses suggest that the annotation of
-speech meets the quality requirements to be used as the basis for model-based
+speech meets basic quality requirements to be a basis for model-based
 analyses that investigate language perception under more ecologically valid
@@
 TextGrid file as well as scripts and data of the analysis, doi:
-\href{dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}
+\href{http://dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}
 

### 2020-10-29 paper/main.tex
Reword availability info

@@
 
-osf.io: The annotation as both a tab-separated values (TSV) formatted table and
-TextGrid file as well as scripts and data of the analysis, doi:
-\href{http://dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}
+The annotation (tab-separated values (TSV) formatted table and TextGrid file),
+as well as scripts and data of the validation analysis are available from
+OpenScienceFramework project
+\href{http://dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}, and
+accessible as DataLad (RRID:SCR\_003931) datasets.
 

### 2020-10-29 paper/main.tex
Reword conclusions

@@
 As an extension of the studyforrest dataset, we present an annotation of spoken
-language in the two hours lasting ``research cut'' of the audio-visual movie
+language in the two-hours audio-visual movie
 ``Forrest Gump'' and its temporally aligned audio-description.
@@
 % what for
-An additional tagging of each word's linguistic features enables independent
-working groups to create models of hemodynamic activity
+An additional tagging of each word's linguistic features enables creating models
+of hemodynamic activity
 correlating with linguistics aspects like phonetics, grammar, syntax, and
@@
 % results
-Results of our analysis that we ran to assess the dataset's quality shows that
-the annotation's content can indeed be used to isolate speech-related networks
+Results of our analysis indicate that
+the annotation's content can be used to locate speech-related networks
 in the human brain under life-like conditions.

### 2020-10-29 paper/main.tex
explain pause between no-speech events

@@
 ``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
-condition were created by the following rationale: events were fitted into
-intervals without audible speech that lasted at least \unit[3.6]{s} \todo{why 3.6?}.
+condition were created by the following rationale to allow both a sufficient
+amount of events of the no-speech condition and a sufficient pause to events of
+the other categories: events were fitted into
+intervals without audible speech that lasted at least \unit[3.6]{s}.
 % minimum distance to words
 Each event of the no-speech condition had to have a minimum distance of
-\unit[1.8]{s}\todo{why 1.8} to an onsets or offsets of a word, and to each onset to another
+\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
 event of the no-speech condition.

### 2020-10-29 paper/main.tex
Reword no-speech event description

--- 2020-10-29 paper/main.tex
@@
 ``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
-condition were created by the following rationale: events were fitted into
-intervals without audible speech that lasted at least \unit[3.6]{s} \todo{why 3.6?}.
+condition were created such that a sufficient
+number of events and a minimum separation of
+speech and non-speech events were achieved. Events were randomly positioned
+in intervals without audible speech that lasted at least \unit[3.6]{s}.
 % minimum distance to words
 Each event of the no-speech condition had to have a minimum distance of
-\unit[1.8]{s}\todo{why 1.8} to an onsets or offsets of a word, and to each onset to another
-event of the no-speech condition.
+\unit[1.8]{s} to any onset or offset of a word, and to any onset of another
+no-speech event.
 % length of no-speech events

### 2020-10-29 paper/main.tex
Drop conclusions

@@
 
-\section*{Conclusions}
-% what the paper is about
-As an extension of the studyforrest dataset, we present an annotation of spoken
-language in the two-hours audio-visual movie
-``Forrest Gump'' and its temporally aligned audio-description.
-% what we did
-We annotated the onset and offset of sentences, words and phonemes, and the
-corresponding speaker's identity.
-% what for
-An additional tagging of each word's linguistic features enables creating models
-of hemodynamic activity
-correlating with linguistics aspects like phonetics, grammar, syntax, and
-semantics occurring in two naturalistic stimuli.
-% results
-Results of our analysis indicate that
-the annotation's content can be used to locate speech-related networks
-in the human brain under life-like conditions.
-
 \subsection*{Author contributions}

### 2020-10-29 paper/main.tex
Use correct funding statement

@@
 \subsection*{Grant information}
+
 COH was supported by a graduate stipend from the German federal state of
-Saxony-Anhalt and MH was supported by funds from the German federal state of
-Saxony-Anhalt and the European Regional Development Fund (ERDF), Project:
-Center for Behavioral Brain Sciences (CBBS). Work on the adapting data
-management technology for this study was in part supported by the European
-Union's Horizon 2020 Research and Innovation Programme under Grant Agreement
-no. 785907 (HBP SGA2).
+Saxony-Anhalt and MH was, in-part, supported by funds from the German federal
+state of Saxony-Anhalt and the European Regional Development Fund (ERDF),
+Project: Center for Behavioral Brain Sciences (CBBS). Development of the data
+management technology used to publish these data on the OpenScienceFramework
+was co-funded by the US National Science Foundation (NSF 1912266), and the
+German Federal Ministry of Education and Research (BMBF 01GQ1905).
 

### 2020-11-25 paper/main.tex
Noted a few issues with your manuscript

@@
 The annotation provides information about the exact timing of each of the more
-than 2500 spoken sentences, 16000 words (including 202 non-speech
-vocalizations), 66000 phonemes, and their corresponding speaker.
+than 2500 spoken sentences, 16,000 words (including 202 non-speech
+vocalizations), 66,000 phonemes, and their corresponding speaker.
 % anno content 2
@@
 % model-driven methods
-Model-driven methods, like the general linear model (GLM), that are based on
+Model-driven methods, like the general linear model (GLM), which are based on
 stimulus annotations can be useful to test hypotheses on specific brain
@@
 (especially during music or continuous environmental noise) which were
-subjectively assessed to be incomprehensible for the audience were dropped, too.
+subjectively assessed to be incomprehensible for the audience were also dropped.
 
 % intro for forced aligner
-We then used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
+We then used the \href{https://github.com/MontrealCorpusTools/Montreal-Forced-Aligner}{Montreal Forced Aligner} \citep{mcauliffe2017montreal} to
 algorithmically identify the exact onset and offset of each word and phoneme.
@@
 German audio track was taken from an English pronunciation dictionary (following
-the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab
-(\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).
+the ARPAbet PhoneSet) provided by the \href{http://mlmlab.org/mfa/dictionaries/english.dict}{Montreal Language Modeling lab}.
 % performing the forced alignment audio input to the aligner
 The audio track of the audio-description was converted from FLAC to WAV via
-FFmpeg \citep{ffmpeg} to meet the aligner's input requirements.
+\href{https://ffmpeg.org/}{FFmpeg} \citep{ffmpeg} to meet the aligner's input requirements. %Please state version of FFmpeg used
 % inputs
@@
 The resulting timings of words and
-phonemes were corrected manually and iteratively in several passes using Praat:
+phonemes were corrected manually and iteratively in several passes using \href{https://www.fon.hum.uva.nl/praat/}{Praat}:%Please state version
 % onset/offset checking & correction
@@
     isolation.} \label{tab:overview} \begin{tabular}{llllllllll} \toprule
-        \textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3}
+        \textbf{Category} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3}
         & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
-        \midrule sentences  & \aSentencesAll & \aSentencesI & \aSentencesII &
+        \midrule Sentences  & \aSentencesAll & \aSentencesI & \aSentencesII &
         \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI &
-        \aSentencesVII & \aSentencesVIII \tabularnewline words  & \aWordsAll &
+        \aSentencesVII & \aSentencesVIII \tabularnewline Words  & \aWordsAll &
         \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI &
-        \aWordsVII & \aWordsVIII \tabularnewline phonemes  & \aPhonesAll &
+        \aWordsVII & \aWordsVIII \tabularnewline Phonemes  & \aPhonesAll &
         \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV &
@@
 \toprule
-\textbf{name} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
+\textbf{Name} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
 \midrule
@@
 % \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
-We employed the Python package spaCy \citep{spacy2} and its accompanying German
+We employed the Python package \href{https://spacy.io/}{spaCy} \citep{spacy2} %Please state version
+and its accompanying German
 language model (\texttt{de\_core\_news\_md}) that was trained on the TIGER
@@
 
-\subsection*{Data Legend}
+\subsection*{Data legend}
 % TextGrid vs. TSV
@@
 \toprule
-\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\textbf{Label} & \textbf{Description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
@@
 \toprule
-\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\textbf{Label} & \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
@@
 magnetic resonance imaging (fMRI) data of 20 subjects (age 21–38 years, mean age
-26.6 years, 12 male) listening to the 2h audio-description (\unit[7]{Tesla},
+26.6 years, 12 male) listening to the 2 h audio-description (\unit[7]{Tesla},
 \unit[2]{s} repetition time, 3599 volumes, 36 axial slices, thickness
@@
 % steps done by C.H.
-All further steps for the current analysis were carried out using Feat v6.00
+All further steps for the current analysis were carried out using \href{https://fsl.fmrib.ox.ac.uk/fsl/fslwiki/FEAT}{FEAT} v6.00
 (FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9
@@
 \toprule
-\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
+\textbf{Label} &  \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
 \midrule
@@
 \toprule
-& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
+& & & \multicolumn{3}{r}{Max location (MNI)} & \multicolumn{3}{r}{Center of gravity (MNI)} &
 \\ \cmidrule{4-6} \cmidrule{7-9}
-voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
+Voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & Structure \\
 \midrule
@@
 \section*{Data availability}
+\subsection*{Underlying data}
+Open Science Framework: studyforrest-paper-speechannotation. \href{https://doi.org/10.17605/OSF.IO/GFRME}{https://doi.org/10.17605/OSF.IO/GFRME}. %Please see email
+\newline
+This project contains the following underlying data: 
+%Please use this section to describe all data files included within your dataset. Where there are too many files to describe individually, please describe groups of files together.
+\begin{itemize}
+\item 
+\end{itemize}
+
+Data are available under the terms of the \href{https://creativecommons.org/licenses/by/4.0/legalcode}{Creative Commons Attribution 4.0 International license} (CC-BY 4.0).
 
@@
 OpenScienceFramework project
-\href{http://dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}, and
-accessible as DataLad (RRID:SCR\_003931) datasets.
+, and
+accessible as DataLad (RRID:SCR\_003931) datasets.%Please confirm - I cannot find this RRID number
 
@@
 \subsection*{Grant information}
-
+%Please ensure all available grant numbers are provided
 COH was supported by a graduate stipend from the German federal state of
@@
 COH is grateful to Valeri Kippes who took care of the author's mental sanity by providing excellent training at his gym in Jülich during the mentally draining period of manual corrections of the annotation.
+%Please see email
 
